### 2025-04-11 age_structure_forecasts.qmd
Added report

---
title: "The future age structure of scientific disciplines"
author:
- name: Rob J Hyndman
  affiliations:
    - name: Monash University
      department: Department of Econometrics & Business Statistics
      city: Clayton
      country: Australia
      postal-code: 3800
  email: Rob.Hyndman@monash.edu
  corresponding: true
- name: Kelly Vanh Nguyen
  affiliations:
    - name: Monash University
      department: Department of Econometrics & Business Statistics
      city: Clayton VIC
      country: Australia
      postal-code: 3800
abstract: |
  A brief summary of our ideas
keywords: [blah, blah]
bibliography: refs.bib
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: true
linestretch: 1.5
format:
  wp-pdf:
    keep-tex: true
filters:
  - blindable-div
execute:
  eval: false
---

```{r setup, include=FALSE}
library(ggplot2)
library(patchwork)
library(vital)
library(fable)
library(dplyr)
library(tidyr)
library(stringr)
library(forcats)
library(knitr)
library(purrr)
library(kableExtra)
library(gganimate)
library(ggokabeito)

# Set default colors
options(
  ggplot2.discrete.colour = c("#D55E00", "#0072B2", "#009E73", "#CC79A7", "#E69F00", "#56B4E9", "#F0E442"),
  ggplot2.discrete.fill = c("#D55E00", "#0072B2", "#009E73", "#CC79A7", "#E69F00", "#56B4E9", "#F0E442")
)
```

# Introduction

The @AAS is dedicated to advancing Australia’s scientific knowledge by providing evidence-informed advice and advocacy to support decision-making in government. As part of this mission, it has launched _Australian Science, Australia’s Future: Science 2035_, an initiative assessing the capability of the national science system and its role in achieving Australia’s ambitions [@AAS2035]. This report supports this initiative by forecasting future science workforce age structures, providing data-driven insights on how Australia’s science workforce will change over the next decade.

This analysis primarily focuses on Natural and Physical Sciences as defined in the Australian Standard Classification of Education (ASCED) by the @ABSASCED (ABS). For consistency, the report refers to ASCED’s Narrow Fields as "disciplines".

The report forecasts the number of individuals in each one-year age group who are active in the workforce and hold a bachelor’s degree or higher in the following scientific disciplines: Physics and Astronomy, Mathematical Sciences, Chemical Sciences, Earth Sciences, Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences not further defined (n.f.d.).

Projections extend over a 20-year period to 2041, with particular focus on workforce composition in 2035. These estimates account for key demographic factors, including mortality, retirement, graduation, and migration.

The report begins by outlining the [Methodology](#methodology), [Data Sources](#data-sources), and statistical techniques used to generate the forecasts. A [Worked Example](#physics-and-astronomy) using Physics and Astronomy illustrates the application of these methods in detail, providing a foundation for understanding the approach. The [Findings](#findings) section then extends this analysis to all other disciplines, focusing on comparison and contrast rather than procedural details. Finally, the report explores [Broader Applications](#broader-applications) beyond science, considering how these forecasting methods could be applied to other fields. The results aim to inform future workforce planning and policy decisions to support the growth of Australia’s scientific community.

\newpage

# Methodology {#methodology}

Let $P_{i,x,t}$ denote the number of equivalent full-time workers in scientific discipline $i$ who are aged $x$ at the start of year $t$, where $i=1,\dots,I$ and $x=15,16,\dots$. The starting age of 15 is the minimum age at which individuals are counted as part of the labour force in the Australian Census [@ABSLFSP]. Forecasts are generated for $P_{i,x,T+h}$ across all ages and disciplines, for some forecast horizon $h>0$.

Let $D_{i,x,t}$ denote the number of deaths, and $R_{i,x,t}$ the number of retirements, of people aged $x$ in scientific discipline $i$ in year $t$. This is the number of equivalent full-time workers leaving the workforce during year $t$ who were aged $x$ *at the start* of year $t$.

Two migration processes are required: one representing new Australian workers in the discipline graduating from university courses ($N_{i,x,t}$), and the other representing the net migration process resulting from scientists leaving or arriving in Australia ($G_{i,x,t}$). New workers are treated as a migration process because they can be of any age (unlike births).

The population can be forecasted using a model similar to the stochastic population model of @HB08, excluding the birth process. The demographic growth-balance equation can be written as: $$
P_{i,x+1,t+1} = P_{i,x,t} - D_{i,x,t} - R_{i,x,t} + N_{i,x,t} + G_{i,x,t}, \quad x = 15,16,\dots
$$ {#eq-dgb} That is, the population each year is equal to the population from the previous year having aged 1 year, minus the deaths or retirements that occurred during the previous year, plus the new graduates, plus the net migrants (which may be negative). The assumption is that $D_{i,x,t} + R_{i,x,t} \le P_{i,x,t}$ and $N_{i,x,t} = G_{i,x,t} = 0$ above some age threshold (say $x=100$). Once $P_{i,x,t} = 0$ when $x$ is above that threshold, all future populations $P_{i,x+k,t+k} = 0$, $k=1,2,\dots$. That is, when the cohort aged $x$ in year $t$ has all retired or died, they will not be replaced through new graduates or migrants of the same age.

As a first approximation, the components $D$, $R$, $N$ and $G$ can be assumed to behave independently. In reality, there may be a negative correlation between $G$ and $N$ as insufficient graduates would probably lead to employers finding people from overseas, while too many graduates would lead to scientists seeking work elsewhere.

Data on $D$, $N$, and $R$ is required, and the remaining component $G$ will be estimated using @eq-dgb.

To obtain forecasts of $P$, forecasts of $D$, $R$, $N$, and $G$ must then be computed. Each of these can be estimated using a functional data model [@HU07].

\newpage

# Data {#data-sources}

## Data Sources

This analysis utilises Australian data sources to generate accurate forecasts. These include the ABS, the Human Mortality Database (HMD), and the Department of Education.

Specifically, the *Census of Population and Housing* (2006, 2011, 2016, and 2021) [@ABSCensus] provides data on the population of individuals with bachelor's degrees or higher who are active in the labour market. This dataset encompasses labour force participation status, age group, educational qualification level (QALLP), discipline (QALFP), and the industries in which individuals work. Labour force participation data is available only for 2016 and 2021 [@ABSLFFP]. QALLP captures the highest level of completed non-school qualification, while QALFP identifies the corresponding field of study [@ABSQALFP].

Australian age-specific death counts and population exposures from 1971 to 2021 were sourced from the @HMD. This dataset includes death counts and population exposures categorised by age.

Retirement data is sourced from the *Retirement and Retirement Intentions* dataset (Catalogue 6238) for the 2022–2023 financial year [@ABS6238]. It provides insights into expected retirement ages for workers in age groups ranging from 45 to 70 across various industries.

Graduate completion statistics from 2006 to 2023, categorised by age group and including individuals with a bachelor’s degree or higher, are derived from the *Award Course Completions* dataset [@DeptEdu]. Additionally, the Department of Education provides data on the number of graduates with a bachelor’s degree or higher, categorised by discipline and year, for the same period [@DeptEdu_Private]. These datasets include both domestic and international students.

Data limitations include the availability of labour force participation data only for 2016 and 2021, the absence of full-time worker data outside census years, and the aggregated nature of retirement intentions data. These gaps are addressed using specific handling of labour force participation data, cohort interpolation methods, and smoothed disaggregation, as detailed in Sections [3.2](#labour), [3.3](#cohort), and [3.4](#smooth).

Another limitation is that retirement intentions data is unavailable by educational discipline, with industry-level data serving as the closest proxy. Since scientists work across multiple industries, this does not capture discipline-specific retirement patterns but is used in this context through methods outlined in Section [3.5](#retirement).

## Labour Force Participation {#labour}

Labour force participation data is available for 2016 and 2021. To estimate worker numbers for 2006 and 2011, the average participation rates from these later years are applied, assuming overall patterns remain consistent. While participation rates were generally stable between 2016 and 2021, smaller groups experienced more volatility.

Younger and older age groups within some disciplines were particularly affected by this volatility, especially when sample sizes were small. For example, in a group of five 15–19-year-olds, a single individual's employment status change could significantly shift the participation rate. Similarly, fluctuations in smaller cohorts of older scientists impacted participation rates. Averaging the rates from 2016 and 2021 helps mitigate this volatility and provides a more stable estimate for 2006 and 2011. Any discrepancies in participation rates are minimal due to the small cohort sizes, making this a more reliable approach than relying on a single year.

@fig-labour-force displays the labour force participation rates for the broader category of Natural and Physical Sciences for 2016, 2021, and their average, which serves as a proxy for 2006 and 2011. While estimation is conducted separately at both the discipline and category levels, the figure below illustrates this approach using the broader category as an example.

```{r}
#| label: fig-labour-force
#| fig-cap: Labour force participation rates by one-year age groups for 2016 and 2021, along with the average of these two years, which is used as a proxy for 2006 and 2011.

census_science <- census |>
  filter(category == "Natural and Physical Sciences")

cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF", "#000000")
names(cols) <- c(unique(census_science$Year), "Average")

census_science <- census_science |>
  mutate(
    age_group = fct_relevel(age_group, "100+", after = Inf),
    Year = factor(Year, levels = c(2006, 2011, 2016, 2021))
  )

census_participation <- census_science |>
  mutate(
    Year = case_when(
      Year == 2011 ~ "Average",
      TRUE ~ as.character(Year)
    ),
    age_group = fct_relevel(age_group, "100+", after = Inf),
    Year = factor(Year, levels = c(2006, "Average", 2016, 2021))
  )

ggplot(census_participation |> filter(Year %in% c("Average", 2016, 2021)), 
       aes(x = as.numeric(gsub("\\+", "", age_group)), y = participation, 
           shape = as.factor(Year), color = as.factor(Year))) +
  geom_point(size = 1.5) +
  labs(
    title = "Labour Force Participation",
    subtitle = "Natural and Physical Sciences",
    x = "One-year age groups",
    y = "Participation rate",
    shape = "Census Year",
    color = "Census Year"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10), labels = c(seq(20, 90, by = 10), "100+")) +
  scale_shape_manual(values = c(1, 2, 0)) +
  scale_color_manual(values = cols) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## Cohort Interpolation {#cohort}

The Census data on scientists active in the labour market, provided by the ABS in one-year age groups, is shown in @fig-census as a line graph to highlight differences across Census years.

As data is only available in Census years (2006, 2011, 2016, 2021), cohort interpolation will be used to estimate intercensal values for the intervening years. These are the years between Census points (e.g., 2007, 2008, 2009, etc.), for which direct population data are unavailable.

Cohort interpolation methods, as described by @STUPP88, approximate these missing values by leveraging available Census data. For this analysis, linear interpolation is applied to estimate the population distribution for the years between Census points, as it provides reasonable approximations given the available data. In this context, linear interpolation produces gradual transitions that reflect realistic population growth and decline.

The completed historical dataset forms the basis for forecasting future workforce trends. The results of this interpolation are shown in @fig-cohort-interpolation.

```{r}
#| label: fig-census
#| fig-cap: Distribution of scientists active in the labour market by age across Census years (2006, 2011, 2016, 2021).
years <- seq(2006, 2021, by = 5)
cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF")
names(cols) <- years
natural_and_physical_sciences |>
  as_tibble() |>
  filter(Year %in% years) |>
  mutate(Year = factor(Year, levels = rev(years))) |>
  ggplot() +
  aes(x = Age, y = Working, color = Year, group = Year) +
  geom_line() +
  labs(y = "Number of active scientists") +
  scale_color_manual(values = cols, name = "Census Year") +
  labs(
    title = "Working Population",
    subtitle = "Natural and Physical Sciences"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

```{r}
#| label: fig-cohort-interpolation
#| fig-cap: Interpolated number of scientists in Australia, 2006–2021, using linear cohort interpolation.

natural_and_physical_sciences  |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Natural and Physical Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

## Smoothed Disaggregation {#smooth}

Retirement intentions data is categorised by the industry of an individual's main job and is provided in broad age groups, as shown in @fig-beforedisaggregation. While the ABS dataset covers 19 industries, only the key industries relevant to this study are displayed in the figure.

To estimate single-year age distributions, a monotonic cubic spline [@SHW04] is applied directly to the cumulative values of these age groups, ensuring a smooth transition between them. This method preserves the overall distribution while generating continuous single-year estimates, as shown in @fig-afterdisaggregation.

```{r}
#| label: fig-beforedisaggregation
#| fig-cap: Retirement intentions for key industries before smoothed disaggregation.

industry_retirement <- bind_rows(
  retirement_data |> mutate(industry = "Professional, scientific and technical services"),
  industry_retirement  
)

ggplot(industry_retirement, aes(x = age_group, y = pc)) +
  geom_col(alpha=0.6) +
  facet_wrap(~industry, ncol=2) +
  labs(
    title = "Retirement Intentions Across Key Industries",
    subtitle = "2022–23 Financial Year",
    x = "Age group",
    y = "Percentage of retirement intentions"
  ) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )
```

```{r}
#| label: fig-afterdisaggregation
#| fig-cap: Retirement intentions across key industries after smoothed disaggregation.

all_retirement |> 
  ggplot(aes(x = Age, y = pc, group = industry)) +
  geom_line() +
  facet_wrap(~industry, ncol=2) +
  labs(
    y = "Percentage of retirement intentions",
    title = "Retirement Intentions Across Key Industries",
    subtitle = "2022–23 Financial Year"
  ) +
  scale_x_continuous(breaks = seq(40, 100, by = 10)) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

## Retirement Distribution by Age {#retirement}

After smoothing the retirement intentions data, the appropriate industry-level retirement distribution or combination of distributions must be selected. Since scientists work across multiple industries, industry-level data must be adapted to reflect discipline-specific trends. While distributions may vary, retirement trends generally follow similar patterns across sectors. By focusing on the top industries, which account for the majority of workers in each discipline, a stable foundation for analysis is ensured, minimising unnecessary variability arising from changing worker proportions in different industries over time.

For the Natural and Physical Sciences, the three primary industries in which the workforce is employed are Education and Training, Professional, Scientific and Technical Services, and Health Care and Social Assistance, representing 15.81%, 15.48%, and 14.65%, respectively. The proportions in other industries decrease significantly beyond this point. To estimate retirement intentions, a weighted average was calculated using these top three industries, with proportions rescaled to sum to 1.

The data show that a significant portion of workers plan to retire between the ages of 60 and 70. This distribution of retirement ages exhibits positive kurtosis, with the highest peak at age 67, where 13.16% of workers indicate their intention to retire, as shown in @fig-retirements and summarised in @tbl-retirements.

```{r}
#| label: fig-retirements
#| fig-cap: Age distribution of retirement intentions for the 2022--2023 Australian financial year.
ggplot(retirement_science) +
  aes(x = Age, y = pc) +
  geom_line() +
  labs(y = "Percentage of retirement intentions",
       title = "Retirement Intentions",
       subtitle = "Natural and Physical Sciences\n2022–23 Financial Year") +
  scale_x_continuous(breaks = seq(40, 100, by = 10)) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

```{r}
#| label: tbl-retirements
#| tbl-cap: Percentage distribution of retirement intentions for ages 64-69 for the Australian financial year 2022--2023.

retirement_science |>
  filter(Age >= 64 & Age <= 69) |>
  mutate(pc = paste0(round(pc, 2), "%")) |>
  select(Age, pc) |>
  kable(col.names = c("Age", "Percentage of Retirement Intentions"), align = "c") |>
  add_header_above(c("Percentage of Retirement Intentions Ages 64–69" = 2), bold = TRUE) |>
  kable_styling(latex_options = c("striped"))
```

From this distribution, the empirical probability of retirement at each age can be calculated using standard life table methods [@MRC18]. These probabilities are shown in @fig-retirements2. These probabilities, which exhibit a significant increase after age 59, are used to estimate $R_{i,x,t}$ from $P_{i,x,t}$​, and are treated as fixed for the simulation, assuming that retirement patterns will remain stable over time.

```{r}
#| label: fig-retirements2
#| fig-cap: Age-specific probability of retirement based on the 2022--2023 Australian financial year.
retirement_science |>
  filter(Age < 100) |>
  ggplot() +
  aes(x = Age, y = retire_prob) +
  geom_line() +
  labs(y = "Probability of retirement",
    title = "Probability of Retirement",
    subtitle = "Natural and Physical Sciences\n2022–23 Financial Year"
  ) +
  scale_x_continuous(breaks = seq(40, 100, by = 10)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

\newpage

In this approach, retirement is treated as a final state, meaning that once a scientist retires, they are not reintroduced into the workforce. This assumption considers workforce exit to be final. Mortality data, discussed in the next section, is incorporated into the calculation of the total probability of leaving the workforce, adjusting for the possibility of death before retirement. This ensures that the combined probability of exiting the workforce (through retirement or death) does not exceed 100%.

## Death Probabilities by Age

Age-specific mortality rates from 1971 to 2021 are obtained from the @HMD. Using standard life table methods, these rates are converted into age-specific probabilities of death, as shown in @fig-death-probs. Over time, mortality probabilities have generally declined across all age groups, reflecting improvements in Australian life expectancy. Consequently, fewer scientists are expected to exit the workforce due to death, illness, or related factors. Similar to retirement, death is treated as a final state; once a scientist dies, they are no longer part of the workforce.

```{r}
#| label: fig-death-probs
#| fig-cap: Age-specific probabilities of death (on a logarithmic scale) for each year from 1971 to 2021.
aus_death_prob |>
  autoplot(death_prob) +
  scale_y_log10(labels = scales::label_number()) +
  labs(y = "Log-scaled probability of death") +
  labs(
    title = "Australian Mortality-Based Death Probabilities",
    subtitle = "1971 - 2021"
  ) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

Although the final workforce forecasts focus on individuals aged 15 and older, mortality probability estimates are derived from data covering ages 0 to 100. These probabilities serve as inputs for estimating $D_{i,x,t}$, the number of deaths among full-time equivalent workers in scientific discipline $i$ at age $x$ in year $t$, based on $P_{i,x,t}$, the corresponding population of such workers. Death estimates are calculated by applying the forecasted mortality probabilities to the workforce population.

## Graduate Completions by Age

Data on graduate completions by age and year is not available for individual disciplines. However, it is available in aggregate across all disciplines, allowing for an analysis of how the age distribution of graduates has changed over time.

@fig-completions1 shows the percentage distribution of graduate completions by age for each year from 2006 to 2023. Some missing values result in gaps in certain lines, but the overall pattern remains highly consistent across years. Given this consistency, the data is averaged across all available years to construct a representative age distribution of graduates at the bachelor's level and higher.

```{r}
#| label: fig-completions1
#| fig-cap: Percentage distribution of graduate completions by age for each year from 2006 to 2023.

completions_step |>
  ggplot() +
  aes(x = Age, y = pc, colour = Year, group = Year) +
  geom_line() +
  scale_color_gradientn(colours = rainbow(10)[1:8]) +
  labs(
    y = "Percentage of graduates",
    title = "Graduate Completions by Year and Age",
    subtitle = "2006 - 2023"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  scale_y_continuous(
    labels = scales::percent_format(scale = 1)
  ) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

The resulting averaged distribution, shown in @fig-completions2, smooths out year-to-year fluctuations and provides a stable estimate of graduate completions by age. This transformation assumes that the overall age distribution of graduates remains relatively stable over time, allowing for a more reliable estimate when applied to specific disciplines.

```{r}
#| label: fig-completions2
#| fig-cap: Percentage distribution of graduate completions by age, aggregated over the years 2006 to 2023.
ave_completions |>
  ggplot() +
  aes(x = Age, pc) +
  geom_line() +
  labs(y = "Percentage of graduates") +
  labs(
    title = "Graduate Completions by Age",
    subtitle = "2006 - 2023"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

@tbl-completions highlights the percentage distribution of graduates aged 20 to 25, demonstrating a pronounced peak in this range, with the highest percentage observed at age 21. This reflects the typical age at which students complete their tertiary education.

\newpage

```{r}
#| label: tbl-completions
#| tbl-cap: Percentage distribution of graduate completions for ages 20-25 for the years 2006 to 2023.

ave_completions |>
  filter(Age >= 20 & Age <= 25) |>
  mutate(pc = paste0(round(pc, 2), "%")) |>
  select(Age, pc) |>
  kable(col.names = c("Age", "Percentage of Graduates"), align = "c") |>
  add_header_above(c("Percentage of Graduates Ages 20-25" = 2), bold = TRUE) |>
  kable_styling(latex_options = c("striped"))
```

## Net Migration

The demographic growth-balance equation (@eq-dgb), when rearranged, provides an estimate of net migration: $$
G_{i,x,t} = P_{i,x+1,t+1} - P_{i,x,t} + D_{i,x,t} + R_{i,x,t} - N_{i,x,t}, \quad x = 15,16,\dots
$$ {#eq-netmigration}

In this equation, $G$ represents the difference required to balance population changes over time after accounting for deaths ($D$), retirements ($R$), new graduates ($N$), and the population at time $t$. It serves as the residual value, reflecting the components influencing the workforce's age structure.

\newpage

# Worked Example: Physics and Astronomy {#physics-and-astronomy}

This section provides a detailed demonstration of the forecasting process using Physics and Astronomy as a case study.

The analysis begins by interpolating the working population from available data, followed by the estimation of graduate completions and calculation of net migration. These data points are then used to simulate multiple future scenarios, applying demographic processes of death and retirement. The final step is to compile these components into a projection of the age structure of scientists in Physics and Astronomy for the next 20 years.

This case study establishes the approach, which is later applied across all disciplines for comparison in the [Findings](#findings) section.

## Working Population

To estimate the future working population accurately, historical data is required. The Australian Census provides such data, but it is only available every five years. @fig-physicists shows the population of physicists and astronomers active in the labour market as recorded in the Census for the years 2006, 2011, 2016, and 2021.

Visually, the distribution for each year is positively skewed, with a long right tail. Over time, the distribution has shifted upward, indicating an increase in the total number of working physicists and astronomers. The right tail has gradually grown heavier, reflecting an increasing proportion of older scientists, while the distribution has also become wider, indicating a broader age range in the workforce.

As shown in @tbl-stats-physics, physicists and astronomers have a median age of approximately 44 years, which suggests a concentration of workers in mid-career stages. The 10th and 90th percentiles, representing the typical adult working age range, indicate that the 10th percentile is in the late 20s and the 90th percentile is in the early 60s. This age range has progressively widened from the first to the last Census.

After estimating the intervening years using linear cohort interpolation [@STUPP88], the resulting population estimates are shown in @fig-physicists2. These interpolated values form the basis for forecasting the future working population, representing the values of $P_{i,x,t}$ for physicists and astronomers. The projected changes in age distribution are visible.

```{r}
#| label: fig-physicists
#| fig-cap: The number of scientists in Physics and Astronomy active in the Australian labour market, shown by age, as recorded in the Australian Census for the years 2006, 2011, 2016, and 2021.
years <- seq(2006, 2021, by = 5)
cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF")
names(cols) <- years
physics_and_astronomy |>
  as_tibble() |>
  filter(Year %in% years) |>
  mutate(Year = factor(Year, levels = rev(years))) |>
  ggplot() +
  aes(x = Age, y = Working, color = Year, group = Year) +
  geom_line() +
  labs(y = "Number of active scientists") +
  scale_color_manual(values = cols, name = "Census Year") +
  labs(
    title = "Working Population",
    subtitle = "Physics and Astronomy"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

```{r}
#| label: fig-physicists2
#| fig-cap: Interpolated number of scientists in Physics and Astronomy active in the Australian labour market, 2006–2021, using linear cohort interpolation.
physics_and_astronomy |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Physics and Astronomy\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

\newpage

```{r}
#| label: tbl-stats-physics
#| tbl-cap: Summary statistics of physicists and astronomers active in the Australian labour market as recorded in the Australian Census for the years 2006, 2011, 2016, and 2021.

weighted_percentile <- function(x, w, prob) {
  o <- order(x)
  x <- x[o]
  w <- w[o]
  cumsum_w <- cumsum(w) / sum(w)
  x[min(which(cumsum_w >= prob))]
}

statistics <- physics_and_astronomy |>
  as_tibble() |>
  filter(Year %in% years) |>
  mutate(Age = as.numeric(as.character(Age))) |>
  group_by(Year) |>
  summarise(
    `10th Percentile Age` = weighted_percentile(Age, Working, prob = 0.1),
    `90th Percentile Age` = weighted_percentile(Age, Working, prob = 0.9),
    `Weighted Average Age` = round(sum(Age * Working, na.rm = TRUE) / sum(Working, na.rm = TRUE), 1),
    `Weighted Median Age` = weighted_percentile(Age, Working, prob = 0.5)
  )

kable(statistics, align = "c") |>
  add_header_above(c("Summary Statistics of Physics and Astronomy" = ncol(statistics)), bold = TRUE) |>
  kable_styling(latex_options = c("striped"))
```

## Graduate Completions

To estimate the number of new graduates entering the workforce, trends in graduate numbers from 2006 to 2023 are examined. As shown in @fig-physics-leavers, the number of graduates majoring in Physics and Astronomy fluctuated around 375 to 500 annually, with no consistent trend, seasonality, or cyclical pattern. These figures represent total graduate completions ($\sum_x N_{i,x,t}$) in Physics and Astronomy.

To forecast future graduate numbers, a global ARIMA model was employed, following the principles outlined by @HM21. ARIMA is a time series forecasting method that identifies underlying trends in past data, assuming these trends will continue. The global model captures overall trends across disciplines by scaling graduate data within each discipline, ensuring proportional contributions from all disciplines before fitting the global ARIMA model. This improves robustness by incorporating information across disciplines. The model is then used to generate discipline-specific forecasts, with simulations run 500 times to account for variability and generate 90% prediction intervals. The results, along with these intervals, are shown in @fig-future-grads-physics for Physics and Astronomy.

```{r}
#| label: fig-physics-leavers
#| fig-cap: Annual number of graduates in Physics and Astronomy, 2006–2023.
ggplot(course_leavers_lvl4 |> filter(discipline == "Physics and Astronomy"), aes(x = Year, y = Graduates)) +
  geom_line() +
  scale_x_continuous(breaks = seq(2006, 2023, by = 2)) +
  labs(
    title = "Graduates",
    subtitle = "Physics and Astronomy\n2006–2023",
    y = "Number of graduates"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

```{r}
#| label: fig-future-grads-physics
#| fig-cap: Projected number of Physics and Astronomy graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
physics_grads <- future_course_leavers_science |>
  filter(discipline == "Physics and Astronomy") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(physics_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Physics and Astronomy"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
       title = "Forecast of Graduates",
    subtitle = "Physics and Astronomy\nForecasted Years: 2024–2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

Since workforce projections require not only total graduate numbers but also their age distribution, the forecasted totals (depicted in @fig-future-grads-physics) are disaggregated using the percentage distribution of graduate completions by age across all disciplines (as shown in @fig-completions2). This enables an estimation of how many graduates will enter each age group in future years, ensuring consistency with observed patterns in the broader graduate population.

## Net Migration

Net migration ($G_{i,x,t}$) is estimated using the demographic growth-balance equation, which is rearranged to calculate the net number of migrants each year (@eq-netmigration). @fig-net-migrants shows the age distribution of net migration among scientists in Physics and Astronomy between 2006 and 2020.

Significant emigration is observed between the ages of 20 and 27, primarily driven by international students leaving Australia after completing their studies, with some domestic graduates also seeking employment overseas. As the graduate data includes both domestic and international students, this emigration is largely influenced by international students returning home.

Beyond this age range, net migration fluctuates between small levels of immigration and emigration. However, these variations are relatively minor, with annual net migration reaching no more than approximately 15 individuals per age group. Given the small magnitudes, these fluctuations may not reflect meaningful migration patterns but rather noise or systematic cohort effects due to input data limitations.

As outlined in the methodology, these estimates rely on forecasting the other components ($D$, $N$, and $R$). Therefore, only estimated historical values up to 2020 are shown here. While historical data on the working population extends to 2021, net migration values for 2021 can only be obtained by incorporating forecasted components due to the structure of the equation.

```{r}
#| label: fig-net-migrants
#| fig-cap: Net migration of scientists in Physics and Astronomy by age, 2006–2020.
physics_and_astronomy |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Physics and Astronomy\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

## Simulating Future Populations

To forecast the future age structure of the scientific workforce in Australia, a simulation-based approach is employed. This approach uses a stochastic population model, adapted from the demographic growth-balance model described in @HB08 and excluding birth processes, to project future populations. This model incorporates uncertainties in demographic processes, generating a range of potential future scenarios for the scientific workforce. The following steps outline the process for projecting the future working population:

1.  **Death Probabilities:** Fit a functional data model [@HU07] to the death probabilities shown in @fig-death-probs, with ARIMA models for the coefficients. This model is used to simulate values of age-specific death probabilities in future years.
2.  **Net Migration:** Fit a separate functional data model to the age-specific migrant numbers shown in @fig-net-migrants, with ARIMA models for the coefficients. This model simulates values of age-specific net migrant numbers in future years.
3.  **Graduate Numbers:** Fit an ARIMA model [@fpp3] to simulate total numbers of graduates in each future year from the numbers shown in @fig-physics-leavers. These graduate numbers will then be disaggregated by age using the age distribution shown in @fig-completions2 to estimate age-specific graduate numbers in each year.
4.  **Retirements:** Estimate retirements in each year by multiplying the number of people of working age in each age bracket (@fig-physicists2) by the retirement probabilities shown in @fig-retirements2. Fixed age-specific retirement probabilities are used.
5.  **Deaths:** Estimate deaths in each year by multiplying the number of people of working age in each age bracket by the forecast death probabilities. 
6.  **Demographic Growth-Balance:** Use the demographic growth-balance equation [@eq-dgb] to obtain the next year's age-specific population values. This step incorporates the graduate numbers, net migration, retirements, and deaths, to produce the forecasted population for the next year.

A total of 500 simulations are run to obtain a distribution of possible future population scenarios, allowing for quantification of forecast uncertainty. @fig-future-physics shows two example simulations. Historical data (2006--2021) are shown in gray, with simulated future populations (2022--2041) in colour. While both simulations exhibit similar trends, differences arise due to inherent uncertainties in model inputs, including variations in graduate numbers, migration patterns, and workforce exits through death and retirement. These sources of uncertainty are incorporated into the model, contributing to the range of possible future trajectories.

```{r}
#| label: fig-future-physics
#| fig-height: 3
#| fig-cap: Two example simulations from a set of 500, using historical data from 2006-2021 to forecast age-specific population distributions for 2022-2041.
p <- physics_and_astronomy |>
  ggplot() +
  aes(x = Age, y = Working, group = Year) +
  geom_line(colour = "gray")
p1 <- p +
  geom_line(data = future_physics_and_astronomy |> filter(.rep == "1"), aes(colour = Year)) +
  labs(y = "Number of working scientists") +
  scale_color_gradientn(colors = rainbow(10)[1:8]) +
  labs(
    title = "Simulation 1",
    subtitle = "Forecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "none"  # Remove legend
  )

p2 <- p +
  geom_line(data = future_physics_and_astronomy |> filter(.rep == "2"), aes(colour = Year)) +
  labs(y = NULL) +  # Remove y-axis label
  scale_color_gradientn(colors = rainbow(10)[1:8]) +
  labs(
    title = "Simulation 2",
    subtitle = "Forecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )

p1 + p2
```

## Forecast Results

The average of the 500 simulations provides the mean age-specific forecast, while quantiles estimate forecast uncertainty. @fig-future-physics-2035 presents the mean and 90% prediction intervals for 2025 and 2035.

In 2035, forecast variability is highest at younger ages, starting from 15 and widening before gradually narrowing as the workforce ages. The prediction interval becomes especially narrow during the retirement phase, where the workforce dynamics become more predictable, indicating greater certainty in this portion of the forecast.

Prediction intervals are also shown for 2025, as it represents a forecast rather than observed workforce data. This comparison helps illustrate how the age distribution is expected to evolve over the next decade.

Between 2025 and 2035, the forecasts indicate an aging workforce, with increases in the number of scientists in their late 30s, and from ages 45 to 80. This trend is particularly evident in the wider gap at ages 45-60 between the forecasted distributions over the ten-year period.

Additionally, patterns in the age distribution persist over time. A dip or trough observed at a given age in 2025 reappears 10 years later as the same cohort progresses through the workforce. While these shifts may be harder to distinguish due to the structure of single-year age cohort data, they reveal how workforce cohorts evolve and how observed patterns carry through in future projections.

Summing over age groups allows for estimating the total number of working scientists in each future year, as shown in @fig-total-future-physics. This highlights whether the workforce is growing, stabilising, or declining. On average, projections indicate continued growth, but at a gradually slower pace. The lower bound remains nearly flat, suggesting workforce stagnation in a conservative scenario. Even in an optimistic scenario, growth only slightly exceeds the current pace.

```{r}
#| label: fig-future-physics-2035
#| fig-cap: Forecasted age distribution of the working population for Physics and Astronomy in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.

# 2025 and 2035
eg_forecast <- future_physics_and_astronomy |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.75) +
    labs(
      y = "Number of working scientists",
      title = "Forecast of Working Population",
      subtitle = "Physics and Astronomy",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      legend.position = "top"
    )
```

```{r}
#| label: fig-total-future-physics
#| fig-cap: Forecasted total number of working scientists for Physics and Astronomy (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.

sum_physics_and_astronomy <- physics_and_astronomy |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_physics_and_astronomy <- future_physics_and_astronomy |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_physics_and_astronomy) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_physics_and_astronomy, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Physics and Astronomy\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  )
```

\newpage

# Findings: Natural and Physical Sciences {#findings}

The forecasting process applied to Physics and Astronomy is now extended to all scientific disciplines. Rather than reiterating the methodological details, this section presents key findings, highlighting differences and comparisons across disciplines. The analysis follows the same structure, covering the working population, graduate completions, net migration, and forecast results based on future population simulations.

@tbl-disciplines lists the scientific disciplines (ASCED Narrow Fields) included in this analysis, along with their corresponding Detailed Fields. This table provides essential context for understanding the specific areas classified under each discipline. "n.f.d." stands for "Not Further Defined," and "n.e.c." stands for "Not Elsewhere Classified."

```{r}
#| label: tbl-disciplines
#| tbl-cap: Classification of scientific disciplines, based on the ASCED Narrow Fields of Education within the Broad Field of Natural and Physical Sciences. The table lists their corresponding Detailed Fields.

discipline_table <- tibble(
  Narrow_Discipline = c(
    "Physics and Astronomy", "Mathematical Sciences", "Chemical Sciences",
    "Earth Sciences", "Biological Sciences", "Other Natural and Physical Sciences",
    "Natural and Physical Sciences n.f.d."
  ),
  Detailed_Field = c(
    "Physics, Astronomy.",
    "Mathematics, Statistics, Mathematical Sciences, n.e.c.",
    "Organic Chemistry, Inorganic Chemistry, Chemical Sciences, n.e.c.",
    "Atmospheric Sciences, Geology, Geophysics, Geochemistry, Soil Science, Hydrology, Oceanography, Earth Sciences, n.e.c.",
    "Biochemistry and Cell Biology, Botany, Ecology and Evolution, Marine Science, Genetics, Microbiology, Human Biology, Zoology, Biological Sciences, n.e.c.",
    "Medical Science, Forensic Science, Food Science and Biotechnology, Pharmacology, Laboratory Technology, Natural and Physical Sciences, n.e.c.",
    " "
  )
)

discipline_table |>
  kable(col.names = c("Narrow Fields", "Detailed Fields")) |>
  add_header_above(c("Broad Field: Natural and Physical Sciences" = 2), bold = TRUE) |>
  kable_styling(latex_options = c("striped"), full_width = FALSE) |>
  column_spec(2, width = "20em")
```

## Working Population

The age distribution of the working population across different scientific disciplines is shown in @fig-working-population. Similar to Physics and Astronomy, the age distributions in these disciplines are positively skewed, with a growing proportion of older workers and a widening age range. Moreover, the number of working scientists has increased over time, especially in Mathematical Sciences in the latest 2021 Census, as well as in Biological Sciences and Other Natural and Physical Sciences. While the Y-axis scales vary across disciplines to reflect differences in population sizes, the data nonetheless indicate a substantial shift in working populations over time within these disciplines.

```{r}
#| label: fig-working-population
#| fig-cap: "Age distribution of the working population across scientific disciplines based on Census data from 2006, 2011, 2016, and 2021. Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age for each Census year."
#| fig-height: 5.5
disciplines_combined <- bind_rows(
  as_tibble(physics_and_astronomy) |> mutate(Discipline = "Physics and Astronomy"),
  as_tibble(mathematical_sciences) |> mutate(Discipline = "Mathematical Sciences"),
  as_tibble(chemical_sciences) |> mutate(Discipline = "Chemical Sciences"),
  as_tibble(earth_sciences) |> mutate(Discipline = "Earth Sciences"),
  as_tibble(biological_sciences) |> mutate(Discipline = "Biological Sciences"),
  as_tibble(other_natural_and_physical_sciences) |> mutate(Discipline = "Other Natural and Physical Sciences"),
  as_tibble(natural_and_physical_sciences__nfd) |> mutate(Discipline = "Natural and Physical Sciences (n.f.d.)")
)

disciplines_combined$Discipline <- factor(
  disciplines_combined$Discipline,
  levels = c("Physics and Astronomy", "Mathematical Sciences", "Chemical Sciences", "Earth Sciences", "Biological Sciences", "Other Natural and Physical Sciences", "Natural and Physical Sciences (n.f.d.)")
)

disciplines_combined |>
  filter(Year %in% years) |>
  mutate(Year = factor(Year, levels = rev(years))) |>
  ggplot() +
  aes(x = Age, y = Working, color = Year, group = Year) +
  geom_line() +
  scale_color_manual(values = cols, name = "Census Year") +
  labs(
    y = "Number of active scientists",
    title = "Working Population by Discipline",
    subtitle = "Natural and Physical Sciences"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  facet_wrap(~Discipline, scales = "free_y") +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top"
  )
```

In terms of age structure, most disciplines have median ages in the mid-forties. However, a few disciplines show lower median ages, including Biological Sciences with an approximate median age of 40, Other Natural and Physical Sciences at 34, and Natural and Physical Sciences (n.f.d.) at 39. A table summarising the statistics for each discipline is provided in @tbl-disciplines-stats in the appendix for further reference.

Additionally, the graph with interpolated data, shown in @fig-interpolated-working-population, provides a smoother representation of trends and highlights changes within each discipline.

```{r}
#| label: fig-interpolated-working-population
#| fig-cap: "Age distribution of the working population across scientific disciplines, interpolated from Census data between 2006 and 2021. Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age and year."
#| fig-height: 6
ggplot(disciplines_combined) +
  aes(x = Age, y = Working, group = Year, color = Year) +
  geom_line() +
  facet_wrap(~Discipline, scales = "free_y") +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  scale_color_gradientn(
    colours = rainbow(10)
  ) +
  labs(
    y = "Number of active scientists",
    title = "Interpolated Working Population by Discipline",
    subtitle = "Natural and Physical Sciences\n2006 - 2021"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top"
  )
```

## Graduate Completions

@fig-graduates-disciplines shows the number of graduates across disciplines from 2006 to 2023. A significant positive trend is observed in three disciplines: Mathematical Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences (n.f.d.). Note that the Y-axis scales vary across disciplines to reflect differences in the number of completions.

```{r}
#| label: fig-graduates-disciplines
#| fig-cap: "Number of graduates across scientific disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."

course_leavers_arranged <- course_leavers_lvl4_science
course_leavers_arranged$discipline <- course_leavers_lvl4_science$discipline |>
  fct_recode(
    "Natural and Physical Sciences (n.f.d.)" = "Natural and Physical Sciences, nfd"
  ) |>
  fct_relevel(
    "Physics and Astronomy",
    "Mathematical Sciences",
    "Chemical Sciences",
    "Earth Sciences",
    "Biological Sciences",
    "Other Natural and Physical Sciences",
    "Natural and Physical Sciences (n.f.d.)"
  )

ggplot(course_leavers_arranged) +
  aes(x = Year, y = Graduates) +
  geom_line() +
  facet_wrap(~discipline, scales = "free_y") +
  labs(
    y = "Number of graduates",
    title = "Graduates by Discipline",
    subtitle = "Natural and Physical Sciences\n2006 - 2023"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "none"
  )
```

The increase in the working population observed in the 2021 Census for Mathematical Sciences, as mentioned earlier, can be partly attributed to the sharp rise in graduate numbers between 2016 and 2021. This surge in graduates during that period provides insight into the corresponding growth in the working population.

Similarly, disciplines such as Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences (n.f.d.) were characterised by lower median ages in their working populations. The higher graduate numbers in these fields may contribute to this trend, as younger graduates naturally lower the median age of the workforce.

As with the example in Physics and Astronomy, future graduate numbers have been forecasted for each discipline. The corresponding graphs for these forecasts are included in the appendix (see @fig-future-grads-math, @fig-future-grads-chem, @fig-future-grads-earth, @fig-future-grads-bio, @fig-future-grads-other, and @fig-future-grads-nfd).

## Net Migration

@fig-net-migration-disciplines shows the age distribution of net migration across disciplines. Emigration during the early career stage is largely driven by international students graduating and returning home. This negative net migration in the early career stage is a significant factor across all disciplines.

Other Natural and Physical Sciences and Natural and Physical Sciences (n.f.d.) show little to no immigration beyond this stage. Given their larger workforce sizes (as seen on the y-axis), these disciplines exhibit more stable net migration patterns.

In contrast, core scientific disciplines, which have smaller populations, show more fluctuation in migration levels after the early career stage. This variability is likely due to workforce mobility, the sensitivity of estimates for smaller populations, and cohort effects, rather than reflecting actual migration dynamics.

```{r}
#| label: fig-net-migration-disciplines
#| fig-cap: Estimated net migration by age across scientific disciplines (2006–2020). Each panel represents a different discipline, showing net migration trends across age groups.
#| fig-height: 6
ggplot(disciplines_combined) +
  aes(x = Age, y = Migrants, group = Year, color = Year) +
  geom_line() +
  facet_wrap(~Discipline, scales = "free_y") +
  scale_x_continuous(breaks = seq(10, 100, by = 10)) +
  scale_color_gradientn(
    colours = rainbow(10)
  ) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration by Discipline",
    subtitle = "Natural and Physical Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top"
  )
```

## Forecast Results

After 500 simulations of the future population for each discipline, the projections ten years apart (2025 and 2035) shown in @fig-forecast-working-population provide a basis for comparing estimates of the current and future workforce.

The projections indicate wider prediction intervals for younger age groups due to uncertainty in future graduate numbers, while mid-to-late career estimates primarily reflect the aging of existing cohorts. Across disciplines, the typical working population spans from the mid-to-late 20s (10th percentile) to the mid-50s and early 60s (90th percentile), as shown in @tbl-disciplines-stats in the appendix. Since retirements increase after the late 50s, workforce participation beyond 60 serves as a benchmark for identifying trends in delayed retirement and extended career duration.

\newpage

```{r}
#| label: fig-forecast-working-population
#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across scientific disciplines. The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
#| fig-height: 5.5
future_disciplines_combined <- bind_rows(
  as_tibble(future_physics_and_astronomy) |> mutate(Discipline = "Physics and Astronomy"),
  as_tibble(future_mathematical_sciences) |> mutate(Discipline = "Mathematical Sciences"),
  as_tibble(future_chemical_sciences) |> mutate(Discipline = "Chemical Sciences"),
  as_tibble(future_earth_sciences) |> mutate(Discipline = "Earth Sciences"),
  as_tibble(future_biological_sciences) |> mutate(Discipline = "Biological Sciences"),
  as_tibble(future_other_natural_and_physical_sciences) |> mutate(Discipline = "Other Natural and Physical Sciences"),
  as_tibble(future_natural_and_physical_sciences__nfd) |> mutate(Discipline = "Natural and Physical Sciences (n.f.d.)")
)

future_disciplines_combined$Discipline <- factor(
  future_disciplines_combined$Discipline,
  levels = c("Physics and Astronomy", "Mathematical Sciences", "Chemical Sciences", "Earth Sciences", "Biological Sciences", "Other Natural and Physical Sciences", "Natural and Physical Sciences (n.f.d.)")
)

# 2025 and 2035
eg_forecast <- future_disciplines_combined |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Discipline, Age, Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.75) +
    labs(
      y = "Number of working scientists",
      title = "Forecast of Working Population by Discipline", 
      subtitle = "Natural and Physical Sciences",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      legend.position = "top"
    ) +
    facet_wrap(~Discipline, scales = "free_y")
```

The key findings from @fig-forecast-working-population are summarised below:

-   **Physics and Astronomy** *(Aging Workforce):* The 35–45 age group shows a higher average than the previous 2025 cohort. There is a growing number of scientists aged 45 to 60, and more individuals aged 60+ are remaining in the workforce longer. These patterns indicate a gradual transition toward an older age structure, reflecting an aging workforce.
-   **Mathematical Sciences** *(Expansive Workforce):* Workforce growth is evident across a broad range of ages, particularly among individuals aged 25 to 70. The most significant increase occurs before 60, though there is also a clear rise in older workers (60+) remaining in the workforce rather than retiring. Overall, workforce growth is strong and evident across age groups.
-   **Chemical Sciences** *(Stationary Workforce):* The average workforce size remains stable, with a relatively narrow prediction interval, indicating a predictable pattern of stability over time. While there is a minor increase in the number of workers aged 70, this change is not substantial enough to suggest a broader shift in workforce dynamics.
\newpage
-   **Earth Sciences** *(Aging Workforce):* Early-career workforce projections are more uncertain relative to its size. A decline in the working population is observed in the mid-thirties, followed by an increase throughout the forties, though both remain modest. While the overall workforce remains relatively stable, these patterns indicate a slow shift toward an older age distribution.
-   **Biological Sciences** *(Aging Workforce):* The number of workers aged 50 to 65 is increasing, indicating growth in later-career participation.
-   **Other Natural and Physical Sciences** *(Expansive Workforce):* Workforce growth is strong across ages 30 to 70, characteristic of an expanding workforce.
-   **Natural and Physical Sciences (n.f.d.)** *(Aging Workforce):* Growth is primarily concentrated in the 55–70 age range, indicating delayed retirement and an aging workforce.

These trends are further validated by the total workforce projections shown in @fig-forecast-total-working-scientists. This figure presents the total number of working scientists by discipline at each point in time, illustrating changes in workforce size over the forecast period. While all disciplines exhibit widening prediction intervals resembling an open funnel, this primarily reflects increasing uncertainty over time as forecasts extend further into the future. The extent of this uncertainty varies by discipline, with some exhibiting more stable trends while others show greater variability in potential workforce outcomes.

```{r}
#| label: fig-forecast-total-working-scientists
#| fig-cap: "Projected total number of working scientists across scientific disciplines from 2022 to 2041. The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."

sum_disciplines_combined  <- disciplines_combined |>
  group_by(Discipline, Year) |>
  summarise(Working = sum(Working), .groups = "drop")

sum_future_disciplines_combined <- future_disciplines_combined |>
  group_by(Discipline, Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Discipline, Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

ggplot(sum_future_disciplines_combined) +
  aes(x = Year) +
  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
  geom_line(aes(y = mean), color = "#c14b14") +
  geom_line(data = sum_disciplines_combined, aes(y = Working)) +
  labs(
    y = "Total number of working scientists (thousands)",
    title = "Forecast of Total Working Population by Discipline",
    subtitle = "Natural and Physical Sciences\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 10)) +
  scale_y_continuous(labels = scales::label_number(scale = 1e-3)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  facet_wrap(~Discipline, scales = "free_y")
```

\newpage

From the plot, Mathematical Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences (n.f.d.) are projected to grow at an accelerating pace. Chemical Sciences, on the other hand, is more likely to decline, while the remaining disciplines are expected to experience more stable growth. However, it is important to consider the prediction intervals when interpreting these trends. These patterns are largely consistent with workforce structure classifications, with expansive disciplines experiencing faster growth, aging disciplines maintaining more stable trends, and constrictive disciplines showing signs of decline.

\newpage

# Broader Applications: Beyond Natural and Physical Sciences {#broader-applications}

The forecasting process can be applied to any ASCED educational field. This section demonstrates its broader applicability by extending the analysis to three additional Broad Fields: Information Technology, Engineering and Related Technologies, and Agriculture, Environmental, and Related Studies. As each field presents different industry characteristics, the retirement intentions data is adjusted accordingly. Forecasts for all disciplines within each Broad Field offer a comprehensive view of workforce trends across these areas.

## Information Technology

```{r eval=FALSE }
#| label: fig-working-population-infotech
#| fig-cap: "Age distribution of the working population across Information Technology disciplines based on Census data from 2006, 2011, 2016, and 2021. Each panel represents a different discipline, with lines indicating the number of active IT professionals in the Australian labour market by age for each Census year."

disciplines_combined <- bind_rows(
  as_tibble(computer_science) |> mutate(Discipline = "Computer Science"),
  as_tibble(information_systems) |> mutate(Discipline = "Information Systems"),
  as_tibble(other_information_technology) |> mutate(Discipline = "Other"),
  as_tibble(information_technology__nfd) |> mutate(Discipline = "Not Further Defined")
)

disciplines_combined$Discipline <- factor(
  disciplines_combined$Discipline,
  levels = c("Computer Science", "Information Systems", "Other", "Not Further Defined")
)

disciplines_combined |>
  filter(Year %in% years) |>
  mutate(Year = factor(Year, levels = rev(years))) |>
  ggplot() +
  aes(x = Age, y = Working, color = Year, group = Year) +
  geom_line() +
  scale_color_manual(values = cols) +
  labs(
    y = "Number of active IT professionals",
    title = "Working Population by Discipline",
    subtitle = "Census Years: 2006, 2011, 2016, 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  facet_wrap(~Discipline, scales = "free_y") +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top"
  )
```

```{r eval=FALSE  }
#| label: fig-graduates-disciplines-infotech
#| fig-cap: "Number of graduates across information technology disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."

course_leavers_arranged <- course_leavers_lvl4_infotech

ggplot(course_leavers_arranged) +
  aes(x = Year, y = Graduates) +
  geom_line() +
  facet_wrap(~discipline, scales = "free_y") +
  labs(
    y = "Number of graduates",
    title = "Graduates Across Disciplines",
    subtitle = "Years: 2006 - 2023"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "none"
  )
```

In the 2022-2023 financial year, the majority of Information Technology workers were employed in the Professional, Scientific, and Technical Services industry, accounting for 28.89% of the workforce. For forecasting retirement trends, the retirement intentions data from this industry serves as the basis.

In @fig-forecast-working-population-infotech, the forecasts for the Information Technology disciplines show the following workforce trends from 2025 to 2035:

-   **Computer Science** *(Expansive Workforce):* Workforce growth is observed, particularly in the 30–40 age range and significantly in the 50–70 range. The higher average forecast reflects both expansion and delayed retirements.
-   **Information Systems** *(Uncertain Workforce):* Extremely large prediction intervals are present at workforce entry due to low current workforce numbers but high graduate inflows. The projected workforce remains relatively small on average, with estimates indicating fewer individuals aged 45 in the workforce by 2035.
-   **Other Information Technology** *(Uncertain Workforce):* Workforce projections show extreme uncertainty. Despite large graduate inflows, the projected workforce remains small, and the absence of prediction intervals indicates a lack of certainty in future participation.
-   **Information Technology (n.f.d.)** *(Expansive Workforce):* Workforce growth is expected in the 35–45 age range, with a significant increase in the 50–70 age group, reflecting sustained participation among older workers.

```{r}
#| label: fig-forecast-working-population-infotech
#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across IT disciplines. The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
#| fig-height: 4.5

future_disciplines_combined <- bind_rows(
  as_tibble(future_computer_science) |> mutate(Discipline = "Computer Science"),
  as_tibble(future_information_systems) |> mutate(Discipline = "Information Systems"),
  as_tibble(future_other_information_technology) |> mutate(Discipline = "Other"),
  as_tibble(future_information_technology__nfd) |> mutate(Discipline = "Not Further Defined")
)

future_disciplines_combined$Discipline <- factor(
  future_disciplines_combined$Discipline,
  levels = c("Computer Science", "Information Systems", "Other", "Not Further Defined"
))

# 2025 and 2035
eg_forecast <- future_disciplines_combined |>
  filter(Year %in% c(2025, 2035), Working >= 0) |>
  group_by(Discipline, Age, Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.75) +
    labs(
      y = "Number of working IT professionals",
      title = "Forecast of Working Population by Discipline",
      subtitle = "Information Technology",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      legend.position = "top"
    ) +
    facet_wrap(~Discipline, scales = "free_y", ncol = 3)
```

The Information Technology workforce consists of both expansive and uncertain disciplines. Computer Science and Information Technology (n.f.d.) exhibit workforce growth across multiple age groups, including delayed retirements beyond 60. In contrast, Information Systems and Other Information Technology show significant uncertainty, where high graduate inflows contrast with low workforce numbers, leading to substantial forecast variability.

\newpage

Unlike other Information Technology disciplines that cover multiple fields, Other Information Technology consists solely of Security Science, a single, specialised field. Historically, its workforce was minimal in 2006 and 2011, with some growth in 2016 and 2021. Despite thousands of graduates, the projected workforce remains relatively small. This mismatch between graduate numbers and workforce participation introduces substantial uncertainty. Since the model relies on graduate inflows, this occurs when historical workforce participation is low, and graduates do not transition into the workforce as expected. This reflects the characteristics of the available data rather than a limitation of the model.

The absence of a prediction interval despite the presence of an average further highlights this uncertainty. The data range is so large that both the lower and upper bounds collapse to zero, even though the true range is much wider. While this may make the forecast appear incomplete, it actually reflects extreme variability in workforce participation. Understanding the underlying cause would require external data, such as why Security Science sees consistently high graduate numbers despite low workforce participation, how ASCED classifies this discipline, or whether industry demand, employment pathways, or policy incentives influence trends.

\newpage

In @fig-forecast-total-working-it, Computer Science and Information Technology (n.f.d.) are experiencing workforce growth. Information Systems indicates a potential decline on average, though the large prediction intervals in later years suggest possible expansion. Other Information Technology remains highly unpredictable, with no clear alignment between the average and the prediction interval.

```{r}
#| label: fig-forecast-total-working-it
#| fig-cap: "Projected total number of working IT professionals across IT disciplines from 2022 to 2041. The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."
#| fig-height: 4

disciplines_combined <- bind_rows(
  as_tibble(computer_science) |> mutate(Discipline = "Computer Science"),
  as_tibble(information_systems) |> mutate(Discipline = "Information Systems"),
  as_tibble(other_information_technology) |> mutate(Discipline = "Other"),
  as_tibble(information_technology__nfd) |> mutate(Discipline = "Not Further Defined")
)

disciplines_combined$Discipline <- factor(
  disciplines_combined$Discipline,
  levels = c("Computer Science", "Information Systems", "Other", "Not Further Defined")
)

sum_disciplines_combined  <- disciplines_combined |>
  group_by(Discipline, Year) |>
  summarise(Working = sum(Working), .groups = "drop")

sum_future_disciplines_combined <- future_disciplines_combined |>
  group_by(Discipline, Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Discipline, Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

ggplot(sum_future_disciplines_combined) +
  aes(x = Year) +
  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
  geom_line(aes(y = mean), color = "#c14b14") +
  geom_line(data = sum_disciplines_combined, aes(y = Working)) +
  labs(
    y = "Total number of working IT Professionals (thousands)",
    title = "Forecast of Total Working Population by Discipline",
    subtitle = "Information Technology\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 10)) +
  scale_y_continuous(labels = scales::label_number(scale = 1e-3)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  facet_wrap(~Discipline, scales = "free_y", ncol = 3)
```

## Engineering and Related Technologies

```{r eval=FALSE }
#| label: fig-working-population-engineering
#| fig-cap: "Age distribution of the working population across Engineering disciplines based on Census data from 2006, 2011, 2016, and 2021. Each panel represents a different discipline, with lines indicating the number of active engineers in the Australian labour market by age for each Census year."
#| fig-height: 5.5

disciplines_combined <- bind_rows(
  as_tibble(manufacturing_engineering_and_technology) |> mutate(Discipline = "Manufacturing"),
  as_tibble(process_and_resources_engineering) |> mutate(Discipline = "Process and Resources"),
  as_tibble(automotive_engineering_and_technology) |> mutate(Discipline = "Automotive"),
  as_tibble(mechanical_and_industrial_engineering_and_technology) |> mutate(Discipline = "Mechanical and Industrial"),
  as_tibble(civil_engineering) |> mutate(Discipline = "Civil"),
  as_tibble(geomatic_engineering) |> mutate(Discipline = "Geomatic"),
  as_tibble(electrical_and_electronic_engineering_and_technology) |> mutate(Discipline = "Electrical and Electronic"),
  as_tibble(aerospace_engineering_and_technology) |> mutate(Discipline = "Aerospace"),
  as_tibble(maritime_engineering_and_technology) |> mutate(Discipline = "Maritime"),
  as_tibble(other_engineering_and_related_technologies) |> mutate(Discipline = "Other"),
  as_tibble(engineering_and_related_technologies__nfd) |> mutate(Discipline = "Not Further Defined")
)

disciplines_combined$Discipline <- factor(
  disciplines_combined$Discipline,
  levels = c("Manufacturing", "Process and Resources", "Automotive", "Mechanical and Industrial", 
             "Civil", "Geomatic", "Electrical and Electronic", "Aerospace", "Maritime", 
             "Other", "Not Further Defined")
)

disciplines_combined |>
  filter(Year %in% years) |>
  mutate(Year = factor(Year, levels = rev(years))) |>
  ggplot() +
  aes(x = Age, y = Working, color = Year, group = Year) +
  geom_line() +
  scale_color_manual(values = cols) +
  labs(
    y = "Number of active engineers",
    title = "Working Population by Discipline",
    subtitle = "Census Years: 2006, 2011, 2016, 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  facet_wrap(~Discipline, scales = "free_y") +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "top"
  )
```

```{r eval=FALSE }
#| label: fig-graduates-disciplines-engineering
#| fig-cap: "Number of graduates across engineering disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."

course_leavers_arranged <- course_leavers_lvl4_engineering %>%
  mutate(discipline = case_when(
    discipline == "Manufacturing Engineering and Technology" ~ "Manufacturing",
    discipline == "Process and Resources Engineering" ~ "Process and Resources",
    discipline == "Automotive Engineering and Technology" ~ "Automotive",
    discipline == "Mechanical and Industrial Engineering and Technology" ~ "Mechanical and Industrial",
    discipline == "Civil Engineering" ~ "Civil",
    discipline == "Geomatic Engineering" ~ "Geomatic",
    discipline == "Electrical and Electronic Engineering and Technology" ~ "Electrical and Electronic",
    discipline == "Aerospace Engineering and Technology" ~ "Aerospace",
    discipline == "Maritime Engineering and Technology" ~ "Maritime",
    discipline == "Other Engineering and Related Technologies" ~ "Other",
    discipline == "Engineering and Related Technologies, nfd" ~ "Not Further Defined",
    TRUE ~ discipline
  ))

ggplot(course_leavers_arranged) +
  aes(x = Year, y = Graduates) +
  geom_line() +
  facet_wrap(~discipline, scales = "free_y") +
  labs(
    y = "Number of graduates",
    title = "Graduates Across Disciplines",
    subtitle = "Years: 2006 - 2023"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "none"
  )
```

In the 2022-2023 financial year, the majority of Engineering and Related Technologies workers were employed in the Professional, Scientific, and Technical Services industry, accounting for 23.54% of the workforce. As this is the largest share across industries, the retirement intentions data from this sector serves as the basis for forecasting trends.

In @fig-forecast-working-population-engineering, the forecasts for the Engineering disciplines show the following workforce trends from 2025 to 2035:

-   **Manufacturing and Engineering Technology** *(Aging Workforce):* Wide prediction intervals at workforce entry suggest uncertainty in younger age groups, while workforce growth is concentrated in the 40-70 age range, indicating an aging trend.
-   **Process and Resources Engineering** *(Declining Workforce):* Workforce numbers are projected to decline up to age 40, while growth in the 40–65 range indicates an aging trend. Large prediction intervals at workforce entry suggest uncertainty, but the overall pattern points to a shrinking workforce rather than sustainable aging.
\newpage
-   **Automotive Engineering and Technology** *(Aging Workforce):* Large prediction intervals at workforce entry indicate uncertainty in younger age groups, while workforce growth is concentrated in the 50-70 age range, suggesting an aging trend.
-   **Mechanical and Industrial Engineering and Technology** *(Aging Workforce):* Wide prediction intervals before age 40 indicate uncertainty in workforce entry. Workforce growth is concentrated in the 40-70 age range, suggesting an older workforce with potential delayed retirements beyond age 60.
-   **Civil Engineering** *(Aging Workforce):* Workforce growth is concentrated in the 40-70 age range, indicating an aging workforce.
-   **Geomatic Engineering** *(Aging Workforce):* Workforce growth is observed primarily in the 50-70 age range, though the increase is modest.
-   **Electrical and Electronic Engineering and Technology** *(Aging Workforce):* Significant workforce growth in the 45-70 age range suggests an older workforce with delayed retirements.
-   **Aerospace Engineering and Technology** *(Expansive Workforce):* Workforce numbers are projected to be higher than in 2025, with growth mainly in the 40–70 age range. Despite an aging trend, the higher average number of younger entrants suggests overall expansion. However, large prediction intervals before age 35 indicate some uncertainty in workforce entry patterns.
-   **Maritime Engineering and Technology** *(Aging Workforce):* Workforce growth is concentrated in the 40-65 age range, indicating an older workforce.
-   **Other Engineering and Related Technologies** *(Declining Workforce):* Workforce numbers in the 30-40 age group are projected to decline. The prediction intervals remain wide throughout, but on average, the workforce is shrinking over time.
-   **Engineering and Related Technologies (n.f.d.)** *(Expansive Workforce):* Workforce growth is projected across all age groups, from 20 to 70.

```{r}
#| label: fig-forecast-working-population-engineering
#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across Engineering disciplines. The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
#| fig-height: 6.5

future_disciplines_combined <- bind_rows(
  as_tibble(future_manufacturing_engineering_and_technology) |> mutate(Discipline = "Manufacturing"),
  as_tibble(future_process_and_resources_engineering) |> mutate(Discipline = "Process and Resources"),
  as_tibble(future_automotive_engineering_and_technology) |> mutate(Discipline = "Automotive"),
  as_tibble(future_mechanical_and_industrial_engineering_and_technology) |> mutate(Discipline = "Mechanical and Industrial"),
  as_tibble(future_civil_engineering) |> mutate(Discipline = "Civil"),
  as_tibble(future_geomatic_engineering) |> mutate(Discipline = "Geomatic"),
  as_tibble(future_electrical_and_electronic_engineering_and_technology) |> mutate(Discipline = "Electrical and Electronic"),
  as_tibble(future_aerospace_engineering_and_technology) |> mutate(Discipline = "Aerospace"),
  as_tibble(future_maritime_engineering_and_technology) |> mutate(Discipline = "Maritime"),
  as_tibble(future_other_engineering_and_related_technologies) |> mutate(Discipline = "Other"),
  as_tibble(future_engineering_and_related_technologies__nfd) |> mutate(Discipline = "Not Further Defined")
)

future_disciplines_combined$Discipline <- factor(
  future_disciplines_combined$Discipline,
  levels = c("Manufacturing", "Process and Resources", "Automotive", "Mechanical and Industrial", "Civil", "Geomatic", "Electrical and Electronic", "Aerospace", "Maritime", "Other", "Not Further Defined"
))

eg_forecast <- future_disciplines_combined |>
  filter(Year %in% c(2025, 2035)) |> 
  group_by(Discipline, Age, Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), linewidth = 0.75) +
    labs(
      y = "Number of working engineers",
      title = "Forecast of Working Population by Discipline",
      subtitle = "Engineering and Related Technologies",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      legend.position = "top"
    ) +
    facet_wrap(~Discipline, scales = "free_y", ncol=3)
```

In @fig-forecast-total-working-engineering, Civil Engineering, Geomatic Engineering, Aerospace Engineering and Technology, and Engineering and Related Technologies (n.f.d.) have more predictable workforce trends. Other Engineering and Related Technologies is the only discipline with a clear decline in workforce numbers.

Overall, most Engineering disciplines are projected to have an aging workforce, with workforce growth primarily occurring in older age groups.

```{r}
#| label: fig-forecast-total-working-engineering
#| fig-cap: "Projected total number of working engineers across Engineering disciplines from 2022 to 2041. The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."
#| fig-height: 6.5

disciplines_combined <- bind_rows(
  as_tibble(manufacturing_engineering_and_technology) |> mutate(Discipline = "Manufacturing"),
  as_tibble(process_and_resources_engineering) |> mutate(Discipline = "Process and Resources"),
  as_tibble(automotive_engineering_and_technology) |> mutate(Discipline = "Automotive"),
  as_tibble(mechanical_and_industrial_engineering_and_technology) |> mutate(Discipline = "Mechanical and Industrial"),
  as_tibble(civil_engineering) |> mutate(Discipline = "Civil"),
  as_tibble(geomatic_engineering) |> mutate(Discipline = "Geomatic"),
  as_tibble(electrical_and_electronic_engineering_and_technology) |> mutate(Discipline = "Electrical and Electronic"),
  as_tibble(aerospace_engineering_and_technology) |> mutate(Discipline = "Aerospace"),
  as_tibble(maritime_engineering_and_technology) |> mutate(Discipline = "Maritime"),
  as_tibble(other_engineering_and_related_technologies) |> mutate(Discipline = "Other"),
  as_tibble(engineering_and_related_technologies__nfd) |> mutate(Discipline = "Not Further Defined")
)

disciplines_combined$Discipline <- factor(
  disciplines_combined$Discipline,
  levels = c("Manufacturing", "Process and Resources", "Automotive", "Mechanical and Industrial", 
             "Civil", "Geomatic", "Electrical and Electronic", "Aerospace", "Maritime", 
             "Other", "Not Further Defined")
)

sum_disciplines_combined  <- disciplines_combined |>
  group_by(Discipline, Year) |>
  summarise(Working = sum(Working), .groups = "drop")

sum_future_disciplines_combined <- future_disciplines_combined |>
  group_by(Discipline, Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Discipline, Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

ggplot(sum_future_disciplines_combined) +
  aes(x = Year) +
  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
  geom_line(aes(y = mean), color = "#c14b14") +
  geom_line(data = sum_disciplines_combined, aes(y = Working)) +
  labs(
    y = "Total number of working engineers (thousands)",
    title = "Forecast of Total Working Population by Discipline",
    subtitle = "Engineering and Related Technologies\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 10)) +
  scale_y_continuous(labels = scales::label_number(scale = 1e-3)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  facet_wrap(~Discipline, scales = "free_y", ncol=3)
```

## Agriculture, Environmental and Related Studies

```{r eval=FALSE }
#| label: fig-graduates-disciplines-agriculture
#| fig-cap: "Number of graduates across agriculture disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."

course_leavers_arranged <- course_leavers_lvl4_agriculture

ggplot(course_leavers_arranged) +
  aes(x = Year, y = Graduates) +
  geom_line() +
  facet_wrap(~discipline, scales = "free_y") +
  labs(
    y = "Number of graduates",
    title = "Graduates Across Disciplines",
    subtitle = "Years: 2006 - 2023"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5),
    legend.position = "none"
  )
```

In the 2022-2023 financial year, the majority of Agriculture, Environmental, and Related Studies workers were employed in the Public Administration and Safety (17.87%), Agriculture, Forestry and Fishing (14.83%), and Professional, Scientific and Technical Services (13.69%) industries. As these sectors account for the largest shares of the workforce, the retirement intentions data from these industries serves as the basis for forecasting trends.

In @fig-forecast-working-population-agriculture, the forecasts for Agriculture disciplines from 2025 to 2035 indicate the following workforce trends:

-   **Agriculture** *(Expansive Workforce):* The number of workers across all age groups is projected to increase on average compared to 2025, with most growth occurring in the 40–60 age range.
-   **Horticulture and Viticulture** *(Declining Workforce):* Workforce numbers are decreasing, particularly in the 40–55 range, while increasing from 60 to 80. The lack of younger replacements indicates workforce decline rather than just aging.
-   **Forestry Studies** *(Declining Workforce):* Workforce numbers are expected to decline across all age groups, particularly in the 40–60 and 70+ ranges.
-   **Fisheries Studies** *(Declining Workforce):* Workforce numbers are projected to decline significantly in the 20–50 range, while growth is expected in the 60–70 group, reflecting an aging but ultimately shrinking workforce.
-   **Environmental Studies** *(Aging Workforce):* A wide prediction interval in the early years reflects uncertainty in younger age group participation. By 2035, growth is concentrated in workers aged 50–70.
-   **Other Agriculture, Environmental and Related Studies** *(Expansive Workforce):* Growth is expected in the 30–40 range, with the overall workforce projected to be larger than in 2025. However, large prediction intervals in the 20–40 group create uncertainty about sustained growth.
-   **Agriculture, Environmental and Related Studies (n.f.d.)** *(Declining Workforce):* Workforce numbers are decreasing across all age groups, with the most pronounced decline in the 20–40 range. The total number of workers in any given age group remains low, with a maximum of about 10 at a time.

@fig-forecast-total-working-agriculture shows a decline in the workforce for Horticulture and Viticulture, Forestry Studies, Fisheries Studies, and Agriculture, Environmental and Related Studies (n.f.d.), which are smaller disciplines. In contrast, Agriculture and Other Agriculture, Environmental and Related Studies are projected to grow. Environmental Studies is also expected to grow, though at a slower pace than before.

```{r }
#| label: fig-forecast-working-population-agriculture
#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across Agricultural and Environmental disciplines. The shaded regions represent the 95% prediction intervals, and the solid lines indicate the mean estimates for each year."
#| fig-height: 5.5

future_disciplines_combined <- bind_rows(
  as_tibble(future_agriculture) |> mutate(Discipline = "Agriculture"),
  as_tibble(future_horticulture_and_viticulture) |> mutate(Discipline = "Horticulture and Viticulture"),
  as_tibble(future_forestry_studies) |> mutate(Discipline = "Forestry Studies"),
  as_tibble(future_fisheries_studies) |> mutate(Discipline = "Fisheries Studies"),
  as_tibble(future_environmental_studies) |> mutate(Discipline = "Environmental Studies"),
  as_tibble(future_other_agriculture__environmental_and_related_studies) |> mutate(Discipline = "Other"),
  as_tibble(future_agriculture__environmental_and_related_studies__nfd) |> mutate(Discipline = "Not Further Defined"),
)

future_disciplines_combined$Discipline <- factor(
  future_disciplines_combined$Discipline,
  levels = c("Agriculture", "Horticulture and Viticulture", "Forestry Studies", "Fisheries Studies", "Environmental Studies", "Other", "Not Further Defined"
))

# 2025 and 2035
eg_forecast <- future_disciplines_combined |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Discipline, Age, Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.75) +
    labs(
      y = "Number of working agriculturists",
      title = "Forecast of Working Population by Discipline",
      subtitle = "Agriculture, Environmental and Related Studies",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      legend.position = "top"
    ) +
    facet_wrap(~Discipline, scales = "free_y")
```

```{r}
#| label: fig-forecast-total-working-agriculture
#| fig-cap: "Projected total number of working agriculturists across Agriculture and Environmental disciplines from 2022 to 2041. The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."

disciplines_combined <- bind_rows(
  as_tibble(agriculture) |> mutate(Discipline = "Agriculture"),
  as_tibble(horticulture_and_viticulture) |> mutate(Discipline = "Horticulture and Viticulture"),
  as_tibble(forestry_studies) |> mutate(Discipline = "Forestry Studies"),
  as_tibble(fisheries_studies) |> mutate(Discipline = "Fisheries Studies"),
  as_tibble(environmental_studies) |> mutate(Discipline = "Environmental Studies"),
  as_tibble(other_agriculture__environmental_and_related_studies) |> mutate(Discipline = "Other"),
  as_tibble(agriculture__environmental_and_related_studies__nfd) |> mutate(Discipline = "Not Further Defined"),
)

disciplines_combined$Discipline <- factor(
  disciplines_combined$Discipline,
  levels =  c("Agriculture", "Horticulture and Viticulture", "Forestry Studies", "Fisheries Studies", "Environmental Studies", "Other", "Not Further Defined"
))

sum_disciplines_combined  <- disciplines_combined |>
  group_by(Discipline, Year) |>
  summarise(Working = sum(Working), .groups = "drop")

sum_future_disciplines_combined <- future_disciplines_combined |>
  group_by(Discipline, Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Discipline, Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

ggplot(sum_future_disciplines_combined) +
  aes(x = Year) +
  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
  geom_line(aes(y = mean), color = "#c14b14") +
  geom_line(data = sum_disciplines_combined, aes(y = Working)) +
  labs(
    y = "Total number of working agriculturists (thousands)",
    title = "Forecast of Total Working Population by Discipline",
    subtitle = "Agriculture, Environmental and Related Studies\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 10)) +
  scale_y_continuous(labels = scales::label_number(scale = 1e-3)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5)
  ) +
  facet_wrap(~Discipline, scales = "free_y", ncol=3)
```

# Conclusion

This report provides data-driven forecasts of Australia's science workforce age structures, outlining expected changes across disciplines by 2035. The Natural and Physical Sciences, along with Engineering, are projected to experience workforce aging, with growth concentrated in older age groups. Information Technology is expected to expand, though some disciplines remain uncertain due to high graduate numbers not translating into workforce participation. Smaller disciplines within Agriculture and Environmental Studies are projected to decline.

When interpreting these projections, policymakers should consider data limitations, particularly in discipline classification and reporting. Variations in self-reporting and ASCED categorisation may not fully capture industry or education changes, impacting accuracy, especially in smaller or evolving disciplines.

Additionally, while these projections provide a solid foundation for workforce planning, it is important to note that they are entirely driven by historical trends and do not account for possible new developments, such as the impact of AI and other emerging technologies on the labour market in different scientific disciplines. Other factors, such as policy changes or global economic shifts, may also influence workforce trends and should be taken into account.

While alternative demographic methodologies, such as the Lee-Carter model, could be considered for estimating demographic components, the methods employed in this report, including the functional data model, ARIMA model, and demographic growth-balance equation, are better suited to the specific characteristics of the data and the goals of this analysis.

Other quantitative studies, such as job market forecasting, may offer complementary insights into broader trends in the scientific workforce. Qualitative studies can also uncover latent factors that go beyond historical data. While this report focuses on forecasting based on past trends, these alternative approaches can provide additional perspectives on the scientific workforce in Australia.

Future work could enhance the accessibility of these projections through interactive visualisations, improve accuracy with new Census data, and broaden the analysis to additional ASCED fields. Refining estimation methods would further strengthen projection reliability and robustness.

This analysis contributes to the Australian Academy of Science’s initiative _Australian Science, Australia’s Future: Science 2035_ by identifying shifts in the workforce, helping anticipate future demand for science capabilities, and highlighting potential workforce gaps as aging and retirement reshape workforce dynamics.

\newpage

# Appendix

```{r}
#| label: tbl-disciplines-stats
#| tbl-cap: Summary statistics for the scientific disciplines, including the 10th and 90th percentile ages, weighted average age, and weighted median age, calculated from the Australian Census data for the years 2006, 2011, 2016, and 2021.

calculate_statistics <- function(discipline_data, discipline_name, years) {
  stats <- discipline_data |>
    as_tibble() |>
    filter(Year %in% years) |>
    mutate(Age = as.numeric(as.character(Age))) |>
    group_by(Year) |>
    summarise(
      `10th Percentile` = weighted_percentile(Age, Working, prob = 0.1),
      `90th Percentile` = weighted_percentile(Age, Working, prob = 0.9),
      `Weighted Average` = round(sum(Age * Working, na.rm = TRUE) / sum(Working, na.rm = TRUE), 1),
      `Weighted Median` = weighted_percentile(Age, Working, prob = 0.5)
    )

  stats <- stats |> mutate(Discipline = discipline_name)

  return(stats)
}

statistics_math <- calculate_statistics(mathematical_sciences, "Mathematical Sciences", years)
statistics_chem <- calculate_statistics(chemical_sciences, "Chemical Sciences", years)
statistics_earth <- calculate_statistics(earth_sciences, "Earth Sciences", years)
statistics_bio <- calculate_statistics(biological_sciences, "Biological Sciences", years)
statistics_other <- calculate_statistics(other_natural_and_physical_sciences, "Other Natural and Physical Sciences", years)
statistics_nfd <- calculate_statistics(natural_and_physical_sciences__nfd, "Natural and Physical Sciences (n.f.d.)", years)

all_statistics <- bind_rows(statistics_math, statistics_chem, statistics_earth, statistics_bio, statistics_other, statistics_nfd)

kable(all_statistics[, c("Year", "10th Percentile", "90th Percentile", "Weighted Average", "Weighted Median")]) |>
  add_header_above(c("Summary Statistics of Scientific Disciplines" = ncol(all_statistics)), bold = TRUE) |>
  kable_styling(full_width = FALSE) |>
  column_spec(1, width = "10em") |>
  column_spec(2, width = "5em") |>
  column_spec(3, width = "5em") |>
  column_spec(4, width = "5em") |>
  column_spec(5, width = "5em") |>
  column_spec(6, width = "5em") |>
  group_rows("Mathematical Sciences", 1, 4) |>
  group_rows("Chemical Sciences", 5, 8) |>
  group_rows("Earth Sciences", 9, 12) |>
  group_rows("Biological Sciences", 13, 16) |>
  group_rows("Other Natural and Physical Sciences", 17, 20) |>
  group_rows("Natural and Physical Sciences (n.f.d.)", 21, 24)
```

## Mathematical Sciences

```{r}
#| label: fig-mathematicians
#| fig-cap: Interpolated number of scientists in Mathematical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5
mathematical_sciences |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Mathematical Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-math
#| fig-cap: Projected number of Mathematical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
#| fig-height: 3.5
#| fig-width: 5.5
math_grads <- future_course_leavers_science |>
  filter(discipline == "Mathematical Sciences") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(math_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Mathematical Sciences"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Mathematical Sciences\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-maths
#| fig-cap: Net migration of scientists in Mathematical Sciences by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

mathematical_sciences |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Mathematical Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-mathematicians-2035
#| fig-cap: Forecasted age distribution of the working population for Mathematical Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5
# 2025 and 2035
eg_forecast <- future_mathematical_sciences |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.6) +
  labs(y = "Number of working scientists",
    title = "Forecast of Working Population",
    subtitle = "Mathematical Sciences",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    legend.position = "top"
  )
```

```{r}
#| label: fig-total-future-mathematicians
#| fig-cap: Forecasted total number of working scientists for Mathematical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

sum_mathematical_sciences  <- mathematical_sciences |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_mathematical_sciences <- future_mathematical_sciences |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_mathematical_sciences) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_mathematical_sciences, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Mathematical Sciences\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

## Chemical Sciences

```{r}
#| label: fig-chemists
#| fig-cap: Interpolated number of scientists in Chemical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5

chemical_sciences |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Chemical Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-chem
#| fig-cap: Projected number of Chemical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
#| fig-height: 3.5
#| fig-width: 5.5

chem_grads <- future_course_leavers_science |>
  filter(discipline == "Chemical Sciences") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(chem_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Chemical Sciences"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Chemical Sciences\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-chem
#| fig-cap: Net migration of scientists in Chemical Sciences by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

chemical_sciences |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Chemical Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-chemists-2035
#| fig-cap: Forecasted age distribution of the working population for Chemical Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

# 2025 and 2035
eg_forecast <- future_chemical_sciences |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.6) +
  labs(y = "Number of working scientists",
    title = "Forecast of Working Population",
    subtitle = "Chemical Sciences",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    legend.position = "top"
  )
```

```{r}
#| label: fig-total-future-chemists
#| fig-cap: Forecasted total number of working scientists for Chemical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

sum_chemical_sciences  <- chemical_sciences |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_chemical_sciences <- future_chemical_sciences |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_chemical_sciences) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_chemical_sciences, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Chemical Sciences\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

## Earth Sciences

```{r}
#| label: fig-earthscientists
#| fig-cap: Interpolated number of scientists in Earth Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5

earth_sciences |>
  autoplot(Working) +
  labs(
    y = "Number of active scientists",
    title = "Interpolated Working Population",
    subtitle = "Earth Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-earth
#| fig-cap: Projected number of Earth Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
#| fig-height: 3.5
#| fig-width: 5.5

earth_grads <- future_course_leavers_science |>
  filter(discipline == "Earth Sciences") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(earth_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Earth Sciences"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Earth Sciences\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-earth
#| fig-cap: Net migration of scientists in Earth Sciences by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

earth_sciences |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Earth Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-earthscientists-2035
#| fig-cap: Forecasted age distribution of the working population for Earth Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

# 2025 and 2035
eg_forecast <- future_earth_sciences |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.6) +
  labs(y = "Number of working scientists",
    title = "Forecast of Working Population",
    subtitle = "Earth Sciences",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    legend.position = "top"
  )
```

```{r}
#| label: fig-total-future-earthscientists
#| fig-cap: Forecasted total number of working scientists for Earth Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

sum_earth_sciences  <- earth_sciences |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_earth_sciences <- future_earth_sciences |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_earth_sciences) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_earth_sciences, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Earth Sciences\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

## Biological Sciences

```{r}
#| label: fig-biologists
#| fig-cap: Interpolated number of scientists in Biological Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5

biological_sciences |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Biological Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-bio
#| fig-cap: Projected number of Biological Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023. intervals.
#| fig-height: 3.5
#| fig-width: 5.5

bio_grads <- future_course_leavers_science |>
  filter(discipline == "Biological Sciences") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(bio_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Biological Sciences"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Biological Sciences\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-biology
#| fig-cap: Net migration of scientists in Biological Sciences by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

biological_sciences |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Biological Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-biologists-2035
#| fig-cap: Forecasted age distribution of the working population for Biological Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

# 2025 and 2035
eg_forecast <- future_biological_sciences |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.6) +
  labs(y = "Number of working scientists",
    title = "Forecast of Working Population",
    subtitle = "Biological Sciences",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    legend.position = "top"
  )
```

```{r}
#| label: fig-total-future-biologists
#| fig-cap: Forecasted total number of working scientists for Biological Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

sum_biological_sciences  <- biological_sciences |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_biological_sciences <- future_biological_sciences |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_biological_sciences) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_biological_sciences, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Biological Sciences\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

## Other Natural and Physical Sciences

```{r}
#| label: fig-otherscientists
#| fig-cap: Interpolated number of scientists in Other Natural and Physical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5

other_natural_and_physical_sciences |>
  autoplot(Working) +
  labs(y = "Number of active scientists") +
  labs(
    title = "Interpolated Working Population",
    subtitle = "Other Natural and Physical Sciences\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-other
#| fig-cap: Projected number of Other Natural and Physical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
#| fig-height: 3.5
#| fig-width: 5.5

other_grads <- future_course_leavers_science |>
  filter(discipline == "Other Natural and Physical Sciences") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(other_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Other Natural and Physical Sciences"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Other Natural and Physical Sciences\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-other
#| fig-cap: Net migration of scientists in Other Natural and Physical Sciences by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

other_natural_and_physical_sciences |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Other Natural and Physical Sciences\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-otherscientists-2035
#| fig-cap: Forecasted age distribution of the working population for Other Natural and Physical Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

# 2025 and 2035
eg_forecast <- future_other_natural_and_physical_sciences |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.6) +
  labs(y = "Number of working scientists",
    title = "Forecast of Working Population",
    subtitle = "Other Natural and Physical Sciences",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    legend.position = "top"
  )
```

```{r}
#| label: fig-total-future-otherscientists
#| fig-cap: Forecasted total number of working scientists for Other Natural and Physical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

sum_other_natural_and_physical_sciences  <- other_natural_and_physical_sciences |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_other_natural_and_physical_sciences <- future_other_natural_and_physical_sciences |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_other_natural_and_physical_sciences) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_other_natural_and_physical_sciences, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Other Natural and Physical Sciences\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

## Natural and Physical Sciences (Not Further Defined)

```{r}
#| label: fig-nfd
#| fig-cap: Interpolated number of scientists in Natural and Physical Sciences (n.f.d.) active in the Australian labour market, 2006–2021, using linear cohort interpolation
#| fig-height: 3.5
#| fig-width: 5.5

natural_and_physical_sciences__nfd |>
  autoplot(Working) +
  labs(
    y = "Number of active scientists",
    title = "Interpolated Working Population",
    subtitle = "Natural and Physical Sciences (n.f.d.)\n2006 - 2021"
  ) +
  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-grads-nfd
#| fig-cap: Projected number of Natural and Physical Sciences (n.f.d.) graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
#| fig-height: 3.5
#| fig-width: 5.5

nfd_grads <- future_course_leavers_science |>
  filter(discipline == "Natural and Physical Sciences, nfd") |>
  summarise(
    mean = mean(Graduates),
    lo = quantile(Graduates, prob = 0.05),
    hi = quantile(Graduates, prob = 0.95)
  )
ggplot(nfd_grads) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Natural and Physical Sciences, nfd"), aes(y = Graduates)) +
  labs(y = "Number of graduates",
    title = "Forecast of Graduates",
    subtitle = "Natural and Physical Sciences (n.f.d.)\nForecasted Years: 2024 - 2041"
  ) +
 scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-net-migrants-nfd
#| fig-cap: Net migration of scientists in Natural and Physical Sciences (n.f.d.) by age, 2006–2020.
#| fig-height: 3.5
#| fig-width: 5.5

natural_and_physical_sciences__nfd |>
  autoplot(Migrants) +
  scale_x_continuous(breaks = seq(10,100,by=10)) +
  labs(
    y = "Number of net migrants",
    title = "Estimated Net Migration",
    subtitle = "Natural and Physical Sciences (n.f.d.)\n2006 - 2020"
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

```{r}
#| label: fig-future-nfd-2035
#| fig-cap: Forecasted age distribution of the working population for Natural and Physical Sciences (n.f.d.) in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

# 2025 and 2035
eg_forecast <- future_natural_and_physical_sciences__nfd |>
  filter(Year %in% c(2025, 2035)) |>
  group_by(Age) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )

# Overlay
ggplot(eg_forecast) +
    aes(x = Age, color = factor(Year)) +
    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
    geom_line(aes(y = mean), size = 0.6) +
  labs(y = "Number of working scientists",
    title = "Forecast of Working Population",
    subtitle = "Natural and Physical Sciences (n.f.d.)",
      color = "Forecast Year",
      fill = "Forecast Year"
    ) +
    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
    theme_classic() +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    legend.position = "top"
  )
```

```{r}
#| label: fig-total-future-nfd
#| fig-cap: Forecasted total number of working scientists for Natural and Physical Sciences (n.f.d.) (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
#| fig-height: 3.5
#| fig-width: 5.5

sum_natural_and_physical_sciences_nfd  <- natural_and_physical_sciences__nfd |>
  as_tibble() |>
  group_by(Year) |>
  summarise(Working = sum(Working), .groups = "drop")
sum_future_natural_and_physical_sciences_nfd <- future_natural_and_physical_sciences__nfd |>
  as_tibble() |>
  group_by(Year, .rep) |>
  summarise(Working = sum(Working), .groups = "drop")  |>
  group_by(Year) |>
  summarise(
    mean = mean(Working),
    lo = quantile(Working, prob = 0.05),
    hi = quantile(Working, prob = 0.95),
    .groups = "drop"
  )
ggplot(sum_future_natural_and_physical_sciences_nfd) +
    aes(x = Year) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
    geom_line(aes(y = mean), color = "#c14b14") +
    geom_line(data = sum_natural_and_physical_sciences_nfd, aes(y = Working)) +
 labs(y = "Total number of working scientists") +
  labs(
    title = "Forecast of Total Working Population",
    subtitle = "Natural and Physical Sciences (n.f.d.)\nForecasted Years: 2022 - 2041"
  ) +
  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme_classic()  +
  theme(
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(size = 9, hjust = 0.5),
    axis.title = element_text(size = 9),
    axis.text = element_text(size = 7),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7)
  )
```

### 2025-04-12 age_structure_forecasts.qmd
Started on quarto doc

@@
 ```{r setup, include=FALSE}
+#| eval: true
 library(ggplot2)
 library(patchwork)
-library(vital)
-library(fable)
-library(dplyr)
-library(tidyr)
-library(stringr)
-library(forcats)
 library(knitr)
-library(purrr)
 library(kableExtra)
-library(gganimate)
-library(ggokabeito)
 
@@
 #| fig-cap: Labour force participation rates by one-year age groups for 2016 and 2021, along with the average of these two years, which is used as a proxy for 2006 and 2011.
-
-census_science <- census |>
-  filter(category == "Natural and Physical Sciences")
-
-cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF", "#000000")
-names(cols) <- c(unique(census_science$Year), "Average")
-
-census_science <- census_science |>
-  mutate(
-    age_group = fct_relevel(age_group, "100+", after = Inf),
-    Year = factor(Year, levels = c(2006, 2011, 2016, 2021))
-  )
-
-census_participation <- census_science |>
-  mutate(
-    Year = case_when(
-      Year == 2011 ~ "Average",
-      TRUE ~ as.character(Year)
-    ),
-    age_group = fct_relevel(age_group, "100+", after = Inf),
-    Year = factor(Year, levels = c(2006, "Average", 2016, 2021))
-  )
-
-ggplot(census_participation |> filter(Year %in% c("Average", 2016, 2021)), 
-       aes(x = as.numeric(gsub("\\+", "", age_group)), y = participation, 
-           shape = as.factor(Year), color = as.factor(Year))) +
-  geom_point(size = 1.5) +
-  labs(
-    title = "Labour Force Participation",
-    subtitle = "Natural and Physical Sciences",
-    x = "One-year age groups",
-    y = "Participation rate",
-    shape = "Census Year",
-    color = "Census Year"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10), labels = c(seq(20, 90, by = 10), "100+")) +
-  scale_shape_manual(values = c(1, 2, 0)) +
-  scale_color_manual(values = cols) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  )
+tar_read(fig1)
 ```
@@
 #| fig-cap: Distribution of scientists active in the labour market by age across  Census years (2006, 2011, 2016, 2021).
-years <- seq(2006, 2021, by = 5)
-cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF")
-names(cols) <- years
-natural_and_physical_sciences |>
-  as_tibble() |>
-  filter(Year %in% years) |>
-  mutate(Year = factor(Year, levels = rev(years))) |>
-  ggplot() +
-  aes(x = Age, y = Working, color = Year, group = Year) +
-  geom_line() +
-  labs(y = "Number of active scientists") +
-  scale_color_manual(values = cols, name = "Census Year") +
-  labs(
-    title = "Working Population",
-    subtitle = "Natural and Physical Sciences"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
+tar_read(fig2)
 ```
@@
 #| fig-cap: Interpolated number of scientists in Australia, 2006–2021, using linear cohort interpolation.
-
-natural_and_physical_sciences  |>
-  autoplot(Working) +
-  labs(y = "Number of active scientists") +
-  labs(
-    title = "Interpolated Working Population",
-    subtitle = "Natural and Physical Sciences\n2006 - 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
+tar_read(fig3)
 ```
@@
 #| fig-cap: Retirement intentions for key industries before smoothed disaggregation.
-
-industry_retirement <- bind_rows(
-  retirement_data |> mutate(industry = "Professional, scientific and technical services"),
-  industry_retirement  
-)
-
-ggplot(industry_retirement, aes(x = age_group, y = pc)) +
-  geom_col(alpha=0.6) +
-  facet_wrap(~industry, ncol=2) +
-  labs(
-    title = "Retirement Intentions Across Key Industries",
-    subtitle = "2022–23 Financial Year",
-    x = "Age group",
-    y = "Percentage of retirement intentions"
-  ) +
-  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    axis.text.x = element_text(angle = 45, hjust = 1),
-    legend.position = "none"
-  )
+tar_read(fig4)
 ```
@@
 #| fig-cap: Retirement intentions across key industries after smoothed disaggregation.
-
-all_retirement |> 
-  ggplot(aes(x = Age, y = pc, group = industry)) +
-  geom_line() +
-  facet_wrap(~industry, ncol=2) +
-  labs(
-    y = "Percentage of retirement intentions",
-    title = "Retirement Intentions Across Key Industries",
-    subtitle = "2022–23 Financial Year"
-  ) +
-  scale_x_continuous(breaks = seq(40, 100, by = 10)) +
-  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
+tar_read(fig5)
 ```

### 2025-04-12 _targets.R

@@ -1,4 +1,5 @@
 library(targets)
+library(tarchetypes)
 
 tar_option_set(
   packages = c(
@@ -83,5 +84,15 @@ list(
       nsim = nsim
     )
   ),
+
+  # Figures
+  tar_target(fig1, make_fig1(census)),
+  tar_target(fig2, make_fig2(census1)),
+  tar_target(fig3, make_fig3(census1)),
+  tar_target(fig4, make_fig4(retirement_data)),
+  tar_target(fig5, make_fig4(retirements)),
+  
+  # Document
+  #tar_render(report, "age_structure_forecasts.qmd"),
   NULL
 )

### 2025-04-14 age_structure_forecasts.qmd
Working on converting quarto doc figures

@@
 #| eval: true
-library(ggplot2)
-library(patchwork)
-library(knitr)
-library(kableExtra)
+library(targets)
 
@@
 
-\newpage
-
 # Data {#data-sources}
@@
 #| label: fig-labour-force
+#| eval: true
 #| fig-cap: Labour force participation rates by one-year age groups for 2016 and 2021, along with the average of these two years, which is used as a proxy for 2006 and 2011.
@@
 #| label: fig-census
+#| eval: true
 #| fig-cap: Distribution of scientists active in the labour market by age across  Census years (2006, 2011, 2016, 2021).
@@
 #| label: fig-cohort-interpolation
+#| eval: true
 #| fig-cap: Interpolated number of scientists in Australia, 2006–2021, using linear cohort interpolation.
@@
 #| label: fig-beforedisaggregation
+#| eval: true
 #| fig-cap: Retirement intentions for key industries before smoothed disaggregation.
@@
 #| label: fig-afterdisaggregation
+#| eval: true
 #| fig-cap: Retirement intentions across key industries after smoothed disaggregation.
@@
 The data show that a significant portion of workers plan to retire between the ages of 60 and 70.
-This distribution of retirement ages exhibits positive kurtosis, with the highest peak at age 67, where 13.16% of workers indicate their intention to retire, as shown in @fig-retirements and summarised in @tbl-retirements.
+This distribution of retirement ages exhibits positive kurtosis, with the highest peak at age 67, where 13.16% of workers indicate their intention to retire, as shown in @fig-retirements.
 
@@
 #| label: fig-retirements
+#| eval: true
 #| fig-cap: Age distribution of retirement intentions for the 2022--2023 Australian financial year.
-ggplot(retirement_science) +
-  aes(x = Age, y = pc) +
-  geom_line() +
-  labs(y = "Percentage of retirement intentions",
-       title = "Retirement Intentions",
-       subtitle = "Natural and Physical Sciences\n2022–23 Financial Year") +
-  scale_x_continuous(breaks = seq(40, 100, by = 10)) +
-  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
-```
-
-```{r}
-#| label: tbl-retirements
-#| tbl-cap: Percentage distribution of retirement intentions for ages 64-69 for the Australian financial year 2022--2023.
-
-retirement_science |>
-  filter(Age >= 64 & Age <= 69) |>
-  mutate(pc = paste0(round(pc, 2), "%")) |>
-  select(Age, pc) |>
-  kable(col.names = c("Age", "Percentage of Retirement Intentions"), align = "c") |>
-  add_header_above(c("Percentage of Retirement Intentions Ages 64–69" = 2), bold = TRUE) |>
-  kable_styling(latex_options = c("striped"))
+tar_read(fig6)
 ```
@@
 #| label: fig-retirements2
+#| eval: true
 #| fig-cap: Age-specific probability of retirement based on the 2022--2023 Australian financial year.
-retirement_science |>
-  filter(Age < 100) |>
-  ggplot() +
-  aes(x = Age, y = retire_prob) +
-  geom_line() +
-  labs(y = "Probability of retirement",
-    title = "Probability of Retirement",
-    subtitle = "Natural and Physical Sciences\n2022–23 Financial Year"
-  ) +
-  scale_x_continuous(breaks = seq(40, 100, by = 10)) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
-```
-
-\newpage
+tar_read(fig7)
+```
 
@@
 #| label: fig-death-probs
+#| eval: true
 #| fig-cap: Age-specific probabilities of death (on a logarithmic scale) for each year from 1971 to 2021.
-aus_death_prob |>
-  autoplot(death_prob) +
-  scale_y_log10(labels = scales::label_number()) +
-  labs(y = "Log-scaled probability of death") +
-  labs(
-    title = "Australian Mortality-Based Death Probabilities",
-    subtitle = "1971 - 2021"
-  ) +
-  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
+tar_read(fig8)
 ```
@@
 #| label: fig-completions1
+#| eval: true
 #| fig-cap: Percentage distribution of graduate completions by age for each year from 2006 to 2023.
-
-completions_step |>
-  ggplot() +
-  aes(x = Age, y = pc, colour = Year, group = Year) +
-  geom_line() +
-  scale_color_gradientn(colours = rainbow(10)[1:8]) +
-  labs(
-    y = "Percentage of graduates",
-    title = "Graduate Completions by Year and Age",
-    subtitle = "2006 - 2023"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  scale_y_continuous(
-    labels = scales::percent_format(scale = 1)
-  ) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
+tar_read(fig9)
 ```
@@
 #| label: fig-completions2
+#| eval: true
 #| fig-cap: Percentage distribution of graduate completions by age, aggregated over the years 2006 to 2023.
-ave_completions |>
-  ggplot() +
-  aes(x = Age, pc) +
-  geom_line() +
-  labs(y = "Percentage of graduates") +
-  labs(
-    title = "Graduate Completions by Age",
-    subtitle = "2006 - 2023"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
+tar_read(fig10)
 ```
@@
 
-\newpage
-
 ```{r}
 #| label: tbl-completions
+#| eval: true
 #| tbl-cap: Percentage distribution of graduate completions for ages 20-25 for the years 2006 to 2023.
-
-ave_completions |>
-  filter(Age >= 20 & Age <= 25) |>
-  mutate(pc = paste0(round(pc, 2), "%")) |>
-  select(Age, pc) |>
-  kable(col.names = c("Age", "Percentage of Graduates"), align = "c") |>
-  add_header_above(c("Percentage of Graduates Ages 20-25" = 2), bold = TRUE) |>
-  kable_styling(latex_options = c("striped"))
+tar_read(tab2)
 ```
@@
 
-\newpage
-
 # Worked Example: Physics and Astronomy {#physics-and-astronomy}
@@
 #| fig-cap: The number of scientists in Physics and Astronomy active in the Australian labour market, shown by age, as recorded in the Australian Census for the years 2006, 2011, 2016, and 2021.
-years <- seq(2006, 2021, by = 5)
-cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF")
-names(cols) <- years
-physics_and_astronomy |>
-  as_tibble() |>
-  filter(Year %in% years) |>
-  mutate(Year = factor(Year, levels = rev(years))) |>
-  ggplot() +
-  aes(x = Age, y = Working, color = Year, group = Year) +
-  geom_line() +
-  labs(y = "Number of active scientists") +
-  scale_color_manual(values = cols, name = "Census Year") +
-  labs(
-    title = "Working Population",
-    subtitle = "Physics and Astronomy"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
+#| eval: true
+tar_read(fig11)
 ```
@@
 #| label: fig-physicists2
+#| eval: true
 #| fig-cap: Interpolated number of scientists in Physics and Astronomy active in the Australian labour market, 2006–2021, using linear cohort interpolation.
-physics_and_astronomy |>
-  autoplot(Working) +
-  labs(y = "Number of active scientists") +
-  labs(
-    title = "Interpolated Working Population",
-    subtitle = "Physics and Astronomy\n2006 - 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
-```
-
-\newpage
-
-```{r}
-#| label: tbl-stats-physics
-#| tbl-cap: Summary statistics of physicists and astronomers active in the Australian labour market as recorded in the Australian Census for the years 2006, 2011, 2016, and 2021.
-
-weighted_percentile <- function(x, w, prob) {
-  o <- order(x)
-  x <- x[o]
-  w <- w[o]
-  cumsum_w <- cumsum(w) / sum(w)
-  x[min(which(cumsum_w >= prob))]
-}
-
-statistics <- physics_and_astronomy |>
-  as_tibble() |>
-  filter(Year %in% years) |>
-  mutate(Age = as.numeric(as.character(Age))) |>
-  group_by(Year) |>
-  summarise(
-    `10th Percentile Age` = weighted_percentile(Age, Working, prob = 0.1),
-    `90th Percentile Age` = weighted_percentile(Age, Working, prob = 0.9),
-    `Weighted Average Age` = round(sum(Age * Working, na.rm = TRUE) / sum(Working, na.rm = TRUE), 1),
-    `Weighted Median Age` = weighted_percentile(Age, Working, prob = 0.5)
-  )
-
-kable(statistics, align = "c") |>
-  add_header_above(c("Summary Statistics of Physics and Astronomy" = ncol(statistics)), bold = TRUE) |>
-  kable_styling(latex_options = c("striped"))
+tar_read(fig12)
 ```
@@
 #| label: fig-physics-leavers
+#| eval: true
 #| fig-cap: Annual number of graduates in Physics and Astronomy, 2006–2023.
-ggplot(course_leavers_lvl4 |> filter(discipline == "Physics and Astronomy"), aes(x = Year, y = Graduates)) +
-  geom_line() +
-  scale_x_continuous(breaks = seq(2006, 2023, by = 2)) +
-  labs(
-    title = "Graduates",
-    subtitle = "Physics and Astronomy\n2006–2023",
-    y = "Number of graduates"
-  ) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
+tar_read(fig13)
 ```
@@
 #| fig-cap: Projected number of Physics and Astronomy graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
-physics_grads <- future_course_leavers_science |>
-  filter(discipline == "Physics and Astronomy") |>
-  summarise(
-    mean = mean(Graduates),
-    lo = quantile(Graduates, prob = 0.05),
-    hi = quantile(Graduates, prob = 0.95)
-  )
-ggplot(physics_grads) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Physics and Astronomy"), aes(y = Graduates)) +
-  labs(y = "Number of graduates",
-       title = "Forecast of Graduates",
-    subtitle = "Physics and Astronomy\nForecasted Years: 2024–2041"
-  ) +
- scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
+#| eval: true
+tar_read(fig14)
 ```
@@
 #| label: fig-net-migrants
+#| eval: true
 #| fig-cap: Net migration of scientists in Physics and Astronomy by age, 2006–2020.
-physics_and_astronomy |>
-  autoplot(Migrants) +
-  scale_x_continuous(breaks = seq(10,100,by=10)) +
-  labs(
-    y = "Number of net migrants",
-    title = "Estimated Net Migration",
-    subtitle = "Physics and Astronomy\n2006 - 2020"
-  ) +
-  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
+tar_read(fig15)
 ```
@@
 #| label: fig-future-physics
+#| eval: false
 #| fig-height: 3
@@
 #| label: fig-future-physics-2035
+#| eval: false
 #| fig-cap: Forecasted age distribution of the working population for Physics and Astronomy in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-total-future-physics
+#| eval: false
 #| fig-cap: Forecasted total number of working scientists for Physics and Astronomy (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-working-population
+#| eval: false
 #| fig-cap: "Age distribution of the working population across scientific disciplines based on Census data from 2006, 2011, 2016, and 2021.
@@
 #| fig-height: 6
+#| eval: false
 ggplot(disciplines_combined) +
@@
 #| label: fig-graduates-disciplines
+#| eval: false
 #| fig-cap: "Number of graduates across scientific disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."
@@
 #| label: fig-net-migration-disciplines
+#| eval: false
 #| fig-cap: Estimated net migration by age across scientific disciplines (2006–2020). Each panel represents a different discipline, showing net migration trends across age groups.
@@
 #| label: fig-forecast-working-population
+#| eval: false
 #| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across scientific disciplines.
@@
 #| label: fig-forecast-total-working-scientists
+#| eval: false
 #| fig-cap: "Projected total number of working scientists across scientific disciplines from 2022 to 2041.
@@
 
-\newpage
-
-# Broader Applications: Beyond Natural and Physical Sciences {#broader-applications}
-
-The forecasting process can be applied to any ASCED educational field.
-This section demonstrates its broader applicability by extending the analysis to three additional Broad Fields: Information Technology, Engineering and Related Technologies, and Agriculture, Environmental, and Related Studies.
-As each field presents different industry characteristics, the retirement intentions data is adjusted accordingly.
-Forecasts for all disciplines within each Broad Field offer a comprehensive view of workforce trends across these areas.
-
-## Information Technology
-
-```{r eval=FALSE }
-#| label: fig-working-population-infotech
-#| fig-cap: "Age distribution of the working population across Information Technology disciplines based on Census data from 2006, 2011, 2016, and 2021.
-Each panel represents a different discipline, with lines indicating the number of active IT professionals in the Australian labour market by age for each Census year."
-
-disciplines_combined <- bind_rows(
-  as_tibble(computer_science) |> mutate(Discipline = "Computer Science"),
-  as_tibble(information_systems) |> mutate(Discipline = "Information Systems"),
-  as_tibble(other_information_technology) |> mutate(Discipline = "Other"),
-  as_tibble(information_technology__nfd) |> mutate(Discipline = "Not Further Defined")
-)
-
-disciplines_combined$Discipline <- factor(
-  disciplines_combined$Discipline,
-  levels = c("Computer Science", "Information Systems", "Other", "Not Further Defined")
-)
-
-disciplines_combined |>
-  filter(Year %in% years) |>
-  mutate(Year = factor(Year, levels = rev(years))) |>
-  ggplot() +
-  aes(x = Age, y = Working, color = Year, group = Year) +
-  geom_line() +
-  scale_color_manual(values = cols) +
-  labs(
-    y = "Number of active IT professionals",
-    title = "Working Population by Discipline",
-    subtitle = "Census Years: 2006, 2011, 2016, 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  facet_wrap(~Discipline, scales = "free_y") +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    legend.position = "top"
-  )
-```
-
-```{r eval=FALSE  }
-#| label: fig-graduates-disciplines-infotech
-#| fig-cap: "Number of graduates across information technology disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."
-
-course_leavers_arranged <- course_leavers_lvl4_infotech
-
-ggplot(course_leavers_arranged) +
-  aes(x = Year, y = Graduates) +
-  geom_line() +
-  facet_wrap(~discipline, scales = "free_y") +
-  labs(
-    y = "Number of graduates",
-    title = "Graduates Across Disciplines",
-    subtitle = "Years: 2006 - 2023"
-  ) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    legend.position = "none"
-  )
-```
-
-In the 2022-2023 financial year, the majority of Information Technology workers were employed in the Professional, Scientific, and Technical Services industry, accounting for 28.89% of the workforce.
-For forecasting retirement trends, the retirement intentions data from this industry serves as the basis.
-
-In @fig-forecast-working-population-infotech, the forecasts for the Information Technology disciplines show the following workforce trends from 2025 to 2035:
-
--   **Computer Science** *(Expansive Workforce):* Workforce growth is observed, particularly in the 30–40 age range and significantly in the 50–70 range.
-The higher average forecast reflects both expansion and delayed retirements.
--   **Information Systems** *(Uncertain Workforce):* Extremely large prediction intervals are present at workforce entry due to low current workforce numbers but high graduate inflows.
-The projected workforce remains relatively small on average, with estimates indicating fewer individuals aged 45 in the workforce by 2035.
--   **Other Information Technology** *(Uncertain Workforce):* Workforce projections show extreme uncertainty.
-Despite large graduate inflows, the projected workforce remains small, and the absence of prediction intervals indicates a lack of certainty in future participation.
--   **Information Technology (n.f.d.)** *(Expansive Workforce):* Workforce growth is expected in the 35–45 age range, with a significant increase in the 50–70 age group, reflecting sustained participation among older workers.
-
-```{r}
-#| label: fig-forecast-working-population-infotech
-#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across IT disciplines.
-The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
-#| fig-height: 4.5
-
-future_disciplines_combined <- bind_rows(
-  as_tibble(future_computer_science) |> mutate(Discipline = "Computer Science"),
-  as_tibble(future_information_systems) |> mutate(Discipline = "Information Systems"),
-  as_tibble(future_other_information_technology) |> mutate(Discipline = "Other"),
-  as_tibble(future_information_technology__nfd) |> mutate(Discipline = "Not Further Defined")
-)
-
-future_disciplines_combined$Discipline <- factor(
-  future_disciplines_combined$Discipline,
-  levels = c("Computer Science", "Information Systems", "Other", "Not Further Defined"
-))
-
-# 2025 and 2035
-eg_forecast <- future_disciplines_combined |>
-  filter(Year %in% c(2025, 2035), Working >= 0) |>
-  group_by(Discipline, Age, Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), size = 0.75) +
-    labs(
-      y = "Number of working IT professionals",
-      title = "Forecast of Working Population by Discipline",
-      subtitle = "Information Technology",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme_classic() +
-    theme(
-      plot.title = element_text(hjust = 0.5, face = "bold"),
-      plot.subtitle = element_text(hjust = 0.5),
-      legend.position = "top"
-    ) +
-    facet_wrap(~Discipline, scales = "free_y", ncol = 3)
-```
-
-The Information Technology workforce consists of both expansive and uncertain disciplines.
-Computer Science and Information Technology (n.f.d.) exhibit workforce growth across multiple age groups, including delayed retirements beyond 60.
-In contrast, Information Systems and Other Information Technology show significant uncertainty, where high graduate inflows contrast with low workforce numbers, leading to substantial forecast variability.
-
-\newpage
-
-Unlike other Information Technology disciplines that cover multiple fields, Other Information Technology consists solely of Security Science, a single, specialised field.
-Historically, its workforce was minimal in 2006 and 2011, with some growth in 2016 and 2021.
-Despite thousands of graduates, the projected workforce remains relatively small.
-This mismatch between graduate numbers and workforce participation introduces substantial uncertainty.
-Since the model relies on graduate inflows, this occurs when historical workforce participation is low, and graduates do not transition into the workforce as expected.
-This reflects the characteristics of the available data rather than a limitation of the model.
-
-The absence of a prediction interval despite the presence of an average further highlights this uncertainty.
-The data range is so large that both the lower and upper bounds collapse to zero, even though the true range is much wider.
-While this may make the forecast appear incomplete, it actually reflects extreme variability in workforce participation.
-Understanding the underlying cause would require external data, such as why Security Science sees consistently high graduate numbers despite low workforce participation, how ASCED classifies this discipline, or whether industry demand, employment pathways, or policy incentives influence trends.
-
-\newpage
-
-In @fig-forecast-total-working-it, Computer Science and Information Technology (n.f.d.) are experiencing workforce growth.
-Information Systems indicates a potential decline on average, though the large prediction intervals in later years suggest possible expansion.
-Other Information Technology remains highly unpredictable, with no clear alignment between the average and the prediction interval.
-
-```{r}
-#| label: fig-forecast-total-working-it
-#| fig-cap: "Projected total number of working IT professionals across IT disciplines from 2022 to 2041.
-The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."
-#| fig-height: 4
-
-disciplines_combined <- bind_rows(
-  as_tibble(computer_science) |> mutate(Discipline = "Computer Science"),
-  as_tibble(information_systems) |> mutate(Discipline = "Information Systems"),
-  as_tibble(other_information_technology) |> mutate(Discipline = "Other"),
-  as_tibble(information_technology__nfd) |> mutate(Discipline = "Not Further Defined")
-)
-
-disciplines_combined$Discipline <- factor(
-  disciplines_combined$Discipline,
-  levels = c("Computer Science", "Information Systems", "Other", "Not Further Defined")
-)
-
-sum_disciplines_combined  <- disciplines_combined |>
-  group_by(Discipline, Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-
-sum_future_disciplines_combined <- future_disciplines_combined |>
-  group_by(Discipline, Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Discipline, Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-ggplot(sum_future_disciplines_combined) +
-  aes(x = Year) +
-  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-  geom_line(aes(y = mean), color = "#c14b14") +
-  geom_line(data = sum_disciplines_combined, aes(y = Working)) +
-  labs(
-    y = "Total number of working IT Professionals (thousands)",
-    title = "Forecast of Total Working Population by Discipline",
-    subtitle = "Information Technology\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 10)) +
-  scale_y_continuous(labels = scales::label_number(scale = 1e-3)) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  ) +
-  facet_wrap(~Discipline, scales = "free_y", ncol = 3)
-```
-
-## Engineering and Related Technologies
-
-```{r eval=FALSE }
-#| label: fig-working-population-engineering
-#| fig-cap: "Age distribution of the working population across Engineering disciplines based on Census data from 2006, 2011, 2016, and 2021.
-Each panel represents a different discipline, with lines indicating the number of active engineers in the Australian labour market by age for each Census year."
-#| fig-height: 5.5
-
-disciplines_combined <- bind_rows(
-  as_tibble(manufacturing_engineering_and_technology) |> mutate(Discipline = "Manufacturing"),
-  as_tibble(process_and_resources_engineering) |> mutate(Discipline = "Process and Resources"),
-  as_tibble(automotive_engineering_and_technology) |> mutate(Discipline = "Automotive"),
-  as_tibble(mechanical_and_industrial_engineering_and_technology) |> mutate(Discipline = "Mechanical and Industrial"),
-  as_tibble(civil_engineering) |> mutate(Discipline = "Civil"),
-  as_tibble(geomatic_engineering) |> mutate(Discipline = "Geomatic"),
-  as_tibble(electrical_and_electronic_engineering_and_technology) |> mutate(Discipline = "Electrical and Electronic"),
-  as_tibble(aerospace_engineering_and_technology) |> mutate(Discipline = "Aerospace"),
-  as_tibble(maritime_engineering_and_technology) |> mutate(Discipline = "Maritime"),
-  as_tibble(other_engineering_and_related_technologies) |> mutate(Discipline = "Other"),
-  as_tibble(engineering_and_related_technologies__nfd) |> mutate(Discipline = "Not Further Defined")
-)
-
-disciplines_combined$Discipline <- factor(
-  disciplines_combined$Discipline,
-  levels = c("Manufacturing", "Process and Resources", "Automotive", "Mechanical and Industrial", 
-             "Civil", "Geomatic", "Electrical and Electronic", "Aerospace", "Maritime", 
-             "Other", "Not Further Defined")
-)
-
-disciplines_combined |>
-  filter(Year %in% years) |>
-  mutate(Year = factor(Year, levels = rev(years))) |>
-  ggplot() +
-  aes(x = Age, y = Working, color = Year, group = Year) +
-  geom_line() +
-  scale_color_manual(values = cols) +
-  labs(
-    y = "Number of active engineers",
-    title = "Working Population by Discipline",
-    subtitle = "Census Years: 2006, 2011, 2016, 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  facet_wrap(~Discipline, scales = "free_y") +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    legend.position = "top"
-  )
-```
-
-```{r eval=FALSE }
-#| label: fig-graduates-disciplines-engineering
-#| fig-cap: "Number of graduates across engineering disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."
-
-course_leavers_arranged <- course_leavers_lvl4_engineering %>%
-  mutate(discipline = case_when(
-    discipline == "Manufacturing Engineering and Technology" ~ "Manufacturing",
-    discipline == "Process and Resources Engineering" ~ "Process and Resources",
-    discipline == "Automotive Engineering and Technology" ~ "Automotive",
-    discipline == "Mechanical and Industrial Engineering and Technology" ~ "Mechanical and Industrial",
-    discipline == "Civil Engineering" ~ "Civil",
-    discipline == "Geomatic Engineering" ~ "Geomatic",
-    discipline == "Electrical and Electronic Engineering and Technology" ~ "Electrical and Electronic",
-    discipline == "Aerospace Engineering and Technology" ~ "Aerospace",
-    discipline == "Maritime Engineering and Technology" ~ "Maritime",
-    discipline == "Other Engineering and Related Technologies" ~ "Other",
-    discipline == "Engineering and Related Technologies, nfd" ~ "Not Further Defined",
-    TRUE ~ discipline
-  ))
-
-ggplot(course_leavers_arranged) +
-  aes(x = Year, y = Graduates) +
-  geom_line() +
-  facet_wrap(~discipline, scales = "free_y") +
-  labs(
-    y = "Number of graduates",
-    title = "Graduates Across Disciplines",
-    subtitle = "Years: 2006 - 2023"
-  ) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    legend.position = "none"
-  )
-```
-
-In the 2022-2023 financial year, the majority of Engineering and Related Technologies workers were employed in the Professional, Scientific, and Technical Services industry, accounting for 23.54% of the workforce.
-As this is the largest share across industries, the retirement intentions data from this sector serves as the basis for forecasting trends.
-
-In @fig-forecast-working-population-engineering, the forecasts for the Engineering disciplines show the following workforce trends from 2025 to 2035:
-
--   **Manufacturing and Engineering Technology** *(Aging Workforce):* Wide prediction intervals at workforce entry suggest uncertainty in younger age groups, while workforce growth is concentrated in the 40-70 age range, indicating an aging trend.
--   **Process and Resources Engineering** *(Declining Workforce):* Workforce numbers are projected to decline up to age 40, while growth in the 40–65 range indicates an aging trend.
-Large prediction intervals at workforce entry suggest uncertainty, but the overall pattern points to a shrinking workforce rather than sustainable aging.
-\newpage
--   **Automotive Engineering and Technology** *(Aging Workforce):* Large prediction intervals at workforce entry indicate uncertainty in younger age groups, while workforce growth is concentrated in the 50-70 age range, suggesting an aging trend.
--   **Mechanical and Industrial Engineering and Technology** *(Aging Workforce):* Wide prediction intervals before age 40 indicate uncertainty in workforce entry.
-Workforce growth is concentrated in the 40-70 age range, suggesting an older workforce with potential delayed retirements beyond age 60.
--   **Civil Engineering** *(Aging Workforce):* Workforce growth is concentrated in the 40-70 age range, indicating an aging workforce.
--   **Geomatic Engineering** *(Aging Workforce):* Workforce growth is observed primarily in the 50-70 age range, though the increase is modest.
--   **Electrical and Electronic Engineering and Technology** *(Aging Workforce):* Significant workforce growth in the 45-70 age range suggests an older workforce with delayed retirements.
--   **Aerospace Engineering and Technology** *(Expansive Workforce):* Workforce numbers are projected to be higher than in 2025, with growth mainly in the 40–70 age range.
-Despite an aging trend, the higher average number of younger entrants suggests overall expansion.
-However, large prediction intervals before age 35 indicate some uncertainty in workforce entry patterns.
--   **Maritime Engineering and Technology** *(Aging Workforce):* Workforce growth is concentrated in the 40-65 age range, indicating an older workforce.
--   **Other Engineering and Related Technologies** *(Declining Workforce):* Workforce numbers in the 30-40 age group are projected to decline.
-The prediction intervals remain wide throughout, but on average, the workforce is shrinking over time.
--   **Engineering and Related Technologies (n.f.d.)** *(Expansive Workforce):* Workforce growth is projected across all age groups, from 20 to 70.
-
-```{r}
-#| label: fig-forecast-working-population-engineering
-#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across Engineering disciplines.
-The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
-#| fig-height: 6.5
-
-future_disciplines_combined <- bind_rows(
-  as_tibble(future_manufacturing_engineering_and_technology) |> mutate(Discipline = "Manufacturing"),
-  as_tibble(future_process_and_resources_engineering) |> mutate(Discipline = "Process and Resources"),
-  as_tibble(future_automotive_engineering_and_technology) |> mutate(Discipline = "Automotive"),
-  as_tibble(future_mechanical_and_industrial_engineering_and_technology) |> mutate(Discipline = "Mechanical and Industrial"),
-  as_tibble(future_civil_engineering) |> mutate(Discipline = "Civil"),
-  as_tibble(future_geomatic_engineering) |> mutate(Discipline = "Geomatic"),
-  as_tibble(future_electrical_and_electronic_engineering_and_technology) |> mutate(Discipline = "Electrical and Electronic"),
-  as_tibble(future_aerospace_engineering_and_technology) |> mutate(Discipline = "Aerospace"),
-  as_tibble(future_maritime_engineering_and_technology) |> mutate(Discipline = "Maritime"),
-  as_tibble(future_other_engineering_and_related_technologies) |> mutate(Discipline = "Other"),
-  as_tibble(future_engineering_and_related_technologies__nfd) |> mutate(Discipline = "Not Further Defined")
-)
-
-future_disciplines_combined$Discipline <- factor(
-  future_disciplines_combined$Discipline,
-  levels = c("Manufacturing", "Process and Resources", "Automotive", "Mechanical and Industrial", "Civil", "Geomatic", "Electrical and Electronic", "Aerospace", "Maritime", "Other", "Not Further Defined"
-))
-
-eg_forecast <- future_disciplines_combined |>
-  filter(Year %in% c(2025, 2035)) |> 
-  group_by(Discipline, Age, Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), linewidth = 0.75) +
-    labs(
-      y = "Number of working engineers",
-      title = "Forecast of Working Population by Discipline",
-      subtitle = "Engineering and Related Technologies",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme_classic() +
-    theme(
-      plot.title = element_text(hjust = 0.5, face = "bold"),
-      plot.subtitle = element_text(hjust = 0.5),
-      legend.position = "top"
-    ) +
-    facet_wrap(~Discipline, scales = "free_y", ncol=3)
-```
-
-In @fig-forecast-total-working-engineering, Civil Engineering, Geomatic Engineering, Aerospace Engineering and Technology, and Engineering and Related Technologies (n.f.d.) have more predictable workforce trends.
-Other Engineering and Related Technologies is the only discipline with a clear decline in workforce numbers.
-
-Overall, most Engineering disciplines are projected to have an aging workforce, with workforce growth primarily occurring in older age groups.
-
-```{r}
-#| label: fig-forecast-total-working-engineering
-#| fig-cap: "Projected total number of working engineers across Engineering disciplines from 2022 to 2041.
-The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."
-#| fig-height: 6.5
-
-disciplines_combined <- bind_rows(
-  as_tibble(manufacturing_engineering_and_technology) |> mutate(Discipline = "Manufacturing"),
-  as_tibble(process_and_resources_engineering) |> mutate(Discipline = "Process and Resources"),
-  as_tibble(automotive_engineering_and_technology) |> mutate(Discipline = "Automotive"),
-  as_tibble(mechanical_and_industrial_engineering_and_technology) |> mutate(Discipline = "Mechanical and Industrial"),
-  as_tibble(civil_engineering) |> mutate(Discipline = "Civil"),
-  as_tibble(geomatic_engineering) |> mutate(Discipline = "Geomatic"),
-  as_tibble(electrical_and_electronic_engineering_and_technology) |> mutate(Discipline = "Electrical and Electronic"),
-  as_tibble(aerospace_engineering_and_technology) |> mutate(Discipline = "Aerospace"),
-  as_tibble(maritime_engineering_and_technology) |> mutate(Discipline = "Maritime"),
-  as_tibble(other_engineering_and_related_technologies) |> mutate(Discipline = "Other"),
-  as_tibble(engineering_and_related_technologies__nfd) |> mutate(Discipline = "Not Further Defined")
-)
-
-disciplines_combined$Discipline <- factor(
-  disciplines_combined$Discipline,
-  levels = c("Manufacturing", "Process and Resources", "Automotive", "Mechanical and Industrial", 
-             "Civil", "Geomatic", "Electrical and Electronic", "Aerospace", "Maritime", 
-             "Other", "Not Further Defined")
-)
-
-sum_disciplines_combined  <- disciplines_combined |>
-  group_by(Discipline, Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-
-sum_future_disciplines_combined <- future_disciplines_combined |>
-  group_by(Discipline, Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Discipline, Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-ggplot(sum_future_disciplines_combined) +
-  aes(x = Year) +
-  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-  geom_line(aes(y = mean), color = "#c14b14") +
-  geom_line(data = sum_disciplines_combined, aes(y = Working)) +
-  labs(
-    y = "Total number of working engineers (thousands)",
-    title = "Forecast of Total Working Population by Discipline",
-    subtitle = "Engineering and Related Technologies\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 10)) +
-  scale_y_continuous(labels = scales::label_number(scale = 1e-3)) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  ) +
-  facet_wrap(~Discipline, scales = "free_y", ncol=3)
-```
-
-## Agriculture, Environmental and Related Studies
-
-```{r eval=FALSE }
-#| label: fig-graduates-disciplines-agriculture
-#| fig-cap: "Number of graduates across agriculture disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."
-
-course_leavers_arranged <- course_leavers_lvl4_agriculture
-
-ggplot(course_leavers_arranged) +
-  aes(x = Year, y = Graduates) +
-  geom_line() +
-  facet_wrap(~discipline, scales = "free_y") +
-  labs(
-    y = "Number of graduates",
-    title = "Graduates Across Disciplines",
-    subtitle = "Years: 2006 - 2023"
-  ) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    legend.position = "none"
-  )
-```
-
-In the 2022-2023 financial year, the majority of Agriculture, Environmental, and Related Studies workers were employed in the Public Administration and Safety (17.87%), Agriculture, Forestry and Fishing (14.83%), and Professional, Scientific and Technical Services (13.69%) industries.
-As these sectors account for the largest shares of the workforce, the retirement intentions data from these industries serves as the basis for forecasting trends.
-
-In @fig-forecast-working-population-agriculture, the forecasts for Agriculture disciplines from 2025 to 2035 indicate the following workforce trends:
-
--   **Agriculture** *(Expansive Workforce):* The number of workers across all age groups is projected to increase on average compared to 2025, with most growth occurring in the 40–60 age range.
--   **Horticulture and Viticulture** *(Declining Workforce):* Workforce numbers are decreasing, particularly in the 40–55 range, while increasing from 60 to 80.
-The lack of younger replacements indicates workforce decline rather than just aging.
--   **Forestry Studies** *(Declining Workforce):* Workforce numbers are expected to decline across all age groups, particularly in the 40–60 and 70+ ranges.
--   **Fisheries Studies** *(Declining Workforce):* Workforce numbers are projected to decline significantly in the 20–50 range, while growth is expected in the 60–70 group, reflecting an aging but ultimately shrinking workforce.
--   **Environmental Studies** *(Aging Workforce):* A wide prediction interval in the early years reflects uncertainty in younger age group participation.
-By 2035, growth is concentrated in workers aged 50–70.
--   **Other Agriculture, Environmental and Related Studies** *(Expansive Workforce):* Growth is expected in the 30–40 range, with the overall workforce projected to be larger than in 2025.
-However, large prediction intervals in the 20–40 group create uncertainty about sustained growth.
--   **Agriculture, Environmental and Related Studies (n.f.d.)** *(Declining Workforce):* Workforce numbers are decreasing across all age groups, with the most pronounced decline in the 20–40 range.
-The total number of workers in any given age group remains low, with a maximum of about 10 at a time.
-
-@fig-forecast-total-working-agriculture shows a decline in the workforce for Horticulture and Viticulture, Forestry Studies, Fisheries Studies, and Agriculture, Environmental and Related Studies (n.f.d.), which are smaller disciplines.
-In contrast, Agriculture and Other Agriculture, Environmental and Related Studies are projected to grow.
-Environmental Studies is also expected to grow, though at a slower pace than before.
-
-```{r }
-#| label: fig-forecast-working-population-agriculture
-#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across Agricultural and Environmental disciplines.
-The shaded regions represent the 95% prediction intervals, and the solid lines indicate the mean estimates for each year."
-#| fig-height: 5.5
-
-future_disciplines_combined <- bind_rows(
-  as_tibble(future_agriculture) |> mutate(Discipline = "Agriculture"),
-  as_tibble(future_horticulture_and_viticulture) |> mutate(Discipline = "Horticulture and Viticulture"),
-  as_tibble(future_forestry_studies) |> mutate(Discipline = "Forestry Studies"),
-  as_tibble(future_fisheries_studies) |> mutate(Discipline = "Fisheries Studies"),
-  as_tibble(future_environmental_studies) |> mutate(Discipline = "Environmental Studies"),
-  as_tibble(future_other_agriculture__environmental_and_related_studies) |> mutate(Discipline = "Other"),
-  as_tibble(future_agriculture__environmental_and_related_studies__nfd) |> mutate(Discipline = "Not Further Defined"),
-)
-
-future_disciplines_combined$Discipline <- factor(
-  future_disciplines_combined$Discipline,
-  levels = c("Agriculture", "Horticulture and Viticulture", "Forestry Studies", "Fisheries Studies", "Environmental Studies", "Other", "Not Further Defined"
-))
-
-# 2025 and 2035
-eg_forecast <- future_disciplines_combined |>
-  filter(Year %in% c(2025, 2035)) |>
-  group_by(Discipline, Age, Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), size = 0.75) +
-    labs(
-      y = "Number of working agriculturists",
-      title = "Forecast of Working Population by Discipline",
-      subtitle = "Agriculture, Environmental and Related Studies",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme_classic() +
-    theme(
-      plot.title = element_text(hjust = 0.5, face = "bold"),
-      plot.subtitle = element_text(hjust = 0.5),
-      legend.position = "top"
-    ) +
-    facet_wrap(~Discipline, scales = "free_y")
-```
-
-```{r}
-#| label: fig-forecast-total-working-agriculture
-#| fig-cap: "Projected total number of working agriculturists across Agriculture and Environmental disciplines from 2022 to 2041.
-The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."
-
-disciplines_combined <- bind_rows(
-  as_tibble(agriculture) |> mutate(Discipline = "Agriculture"),
-  as_tibble(horticulture_and_viticulture) |> mutate(Discipline = "Horticulture and Viticulture"),
-  as_tibble(forestry_studies) |> mutate(Discipline = "Forestry Studies"),
-  as_tibble(fisheries_studies) |> mutate(Discipline = "Fisheries Studies"),
-  as_tibble(environmental_studies) |> mutate(Discipline = "Environmental Studies"),
-  as_tibble(other_agriculture__environmental_and_related_studies) |> mutate(Discipline = "Other"),
-  as_tibble(agriculture__environmental_and_related_studies__nfd) |> mutate(Discipline = "Not Further Defined"),
-)
-
-disciplines_combined$Discipline <- factor(
-  disciplines_combined$Discipline,
-  levels =  c("Agriculture", "Horticulture and Viticulture", "Forestry Studies", "Fisheries Studies", "Environmental Studies", "Other", "Not Further Defined"
-))
-
-sum_disciplines_combined  <- disciplines_combined |>
-  group_by(Discipline, Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-
-sum_future_disciplines_combined <- future_disciplines_combined |>
-  group_by(Discipline, Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Discipline, Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-ggplot(sum_future_disciplines_combined) +
-  aes(x = Year) +
-  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-  geom_line(aes(y = mean), color = "#c14b14") +
-  geom_line(data = sum_disciplines_combined, aes(y = Working)) +
-  labs(
-    y = "Total number of working agriculturists (thousands)",
-    title = "Forecast of Total Working Population by Discipline",
-    subtitle = "Agriculture, Environmental and Related Studies\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 10)) +
-  scale_y_continuous(labels = scales::label_number(scale = 1e-3)) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  ) +
-  facet_wrap(~Discipline, scales = "free_y", ncol=3)
-```
-
 # Conclusion
@@
 #| label: tbl-disciplines-stats
+#| eval: false
 #| tbl-cap: Summary statistics for the scientific disciplines, including the 10th and 90th percentile ages, weighted average age, and weighted median age, calculated from the Australian Census data for the years 2006, 2011, 2016, and 2021.
@@
 #| label: fig-mathematicians
+#| eval: false
 #| fig-cap: Interpolated number of scientists in Mathematical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
@@
 #| label: fig-future-grads-math
+#| eval: false
 #| fig-cap: Projected number of Mathematical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
@@
 #| label: fig-net-migrants-maths
+#| eval: false
 #| fig-cap: Net migration of scientists in Mathematical Sciences by age, 2006–2020.
@@
 #| label: fig-future-mathematicians-2035
+#| eval: false
 #| fig-cap: Forecasted age distribution of the working population for Mathematical Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-total-future-mathematicians
+#| eval: false
 #| fig-cap: Forecasted total number of working scientists for Mathematical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-chemists
+#| eval: false
 #| fig-cap: Interpolated number of scientists in Chemical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
@@
 #| label: fig-future-grads-chem
+#| eval: false
 #| fig-cap: Projected number of Chemical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
@@
 #| label: fig-net-migrants-chem
+#| eval: false
 #| fig-cap: Net migration of scientists in Chemical Sciences by age, 2006–2020.
@@
 #| label: fig-future-chemists-2035
+#| eval: false
 #| fig-cap: Forecasted age distribution of the working population for Chemical Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-total-future-chemists
+#| eval: false
 #| fig-cap: Forecasted total number of working scientists for Chemical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-earthscientists
+#| eval: false
 #| fig-cap: Interpolated number of scientists in Earth Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
@@
 #| label: fig-future-grads-earth
+#| eval: false
 #| fig-cap: Projected number of Earth Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
@@
 #| label: fig-net-migrants-earth
+#| eval: false
 #| fig-cap: Net migration of scientists in Earth Sciences by age, 2006–2020.
@@
 #| label: fig-future-earthscientists-2035
+#| eval: false
 #| fig-cap: Forecasted age distribution of the working population for Earth Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-total-future-earthscientists
+#| eval: false
 #| fig-cap: Forecasted total number of working scientists for Earth Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-biologists
+#| eval: false
 #| fig-cap: Interpolated number of scientists in Biological Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
@@
 #| label: fig-future-grads-bio
+#| eval: false
 #| fig-cap: Projected number of Biological Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023. intervals.
@@
 #| label: fig-net-migrants-biology
+#| eval: false
 #| fig-cap: Net migration of scientists in Biological Sciences by age, 2006–2020.
@@
 #| label: fig-future-biologists-2035
+#| eval: false
 #| fig-cap: Forecasted age distribution of the working population for Biological Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-total-future-biologists
+#| eval: false
 #| fig-cap: Forecasted total number of working scientists for Biological Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-otherscientists
+#| eval: false
 #| fig-cap: Interpolated number of scientists in Other Natural and Physical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
@@
 #| label: fig-future-grads-other
+#| eval: false
 #| fig-cap: Projected number of Other Natural and Physical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
@@
 #| label: fig-net-migrants-other
+#| eval: false
 #| fig-cap: Net migration of scientists in Other Natural and Physical Sciences by age, 2006–2020.
@@
 #| label: fig-future-otherscientists-2035
+#| eval: false
 #| fig-cap: Forecasted age distribution of the working population for Other Natural and Physical Sciences in 2025 and 2035, comparing changes over 10 years.
@@
 #| label: fig-total-future-otherscientists
+#| eval: false
 #| fig-cap: Forecasted total number of working scientists for Other Natural and Physical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
@@
 #| label: fig-nfd
+#| eval: false
 #| fig-cap: Interpolated number of scientists in Natural and Physical Sciences (n.f.d.) active in the Australian labour market, 2006–2021, using linear cohort interpolation
@@
 #| label: fig-future-grads-nfd
+#| eval: false
 #| fig-cap: Projected number of Natural and Physical Sciences (n.f.d.) graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
@@
 #| label: fig-net-migrants-nfd
+#| eval: false
 #| fig-cap: Net migration of scientists in Natural and Physical Sciences (n.f.d.) by age, 2006–2020.
@@
 #| label: fig-future-nfd-2035
+#| eval: false
 #| fig-cap: Forecasted age distribution of the working population for Natural and Physical Sciences (n.f.d.) in 2025 and 2035, comparing changes over 10 years.
@@
 #| label: fig-total-future-nfd
+#| eval: false
 #| fig-cap: Forecasted total number of working scientists for Natural and Physical Sciences (n.f.d.) (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.

### 2025-04-14 R/census_figs.R

@@ -1,4 +1,4 @@
-make_fig2 <- function(census) {
+make_fig2 <- function(census, subtitle) {
   years <- seq(2006, 2021, by = 5)
   cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF")
   names(cols) <- years
@@ -13,7 +13,7 @@ make_fig2 <- function(census) {
     scale_color_manual(values = cols, name = "Census Year") +
     labs(
       title = "Working Population",
-      subtitle = "Natural and Physical Sciences"
+      subtitle = subtitle
     ) +
     scale_x_continuous(breaks = seq(20, 100, by = 10)) +
     theme_classic() +
@@ -21,4 +21,20 @@ make_fig2 <- function(census) {
       plot.title = element_text(hjust = 0.5, face = "bold"),
       plot.subtitle = element_text(hjust = 0.5)
     )
+}
+
+make_fig3 <- function(census, subtitle) {
+  census |>
+  autoplot(Working) +
+  labs(y = "Number of active scientists") +
+  labs(
+    title = "Interpolated Working Population",
+    subtitle = paste0(subtitle, "\n2006 - 2021")
+  ) +
+  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+  theme_classic()  +
+  theme(
+    plot.title = element_text(hjust = 0.5, face = "bold"),
+    plot.subtitle = element_text(hjust = 0.5)
+  )
 }

### 2025-04-14 R/fig3.R

@@ -1,15 +1,0 @@
-make_fig3 <- function(census) {
-  census |>
-  autoplot(Working) +
-  labs(y = "Number of active scientists") +
-  labs(
-    title = "Interpolated Working Population",
-    subtitle = "Natural and Physical Sciences\n2006 - 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
-}

### 2025-04-14 R/fig4.R

@@ -1,18 +1,0 @@
-make_fig4 <- function(retirements) {
-  ggplot(retirements, aes(x = age_group, y = pc)) +
-    geom_col(alpha = 0.6) +
-    labs(
-      title = "Retirement Intentions Across Key Industries",
-      subtitle = "2022–23 Financial Year",
-      x = "Age group",
-      y = "Percentage of retirement intentions"
-    ) +
-    scale_y_continuous(labels = scales::percent_format(scale = 1)) +
-    theme_classic() +
-    theme(
-      plot.title = element_text(hjust = 0.5, face = "bold"),
-      plot.subtitle = element_text(hjust = 0.5),
-      axis.text.x = element_text(angle = 45, hjust = 1),
-      legend.position = "none"
-    )
-}

### 2025-04-14 R/fig8.R

@@ -1,0 +1,16 @@
+make_fig8 <- function(death_prob) {
+  death_prob |>
+    autoplot(death_prob) +
+    scale_y_log10(labels = scales::label_number()) +
+    labs(y = "Log-scaled probability of death") +
+    labs(
+      title = "Australian Mortality-Based Death Probabilities",
+      subtitle = "1971 - 2021"
+    ) +
+    scale_x_continuous(breaks = seq(0, 100, by = 10)) +
+    theme_classic() +
+    theme(
+      plot.title = element_text(hjust = 0.5, face = "bold"),
+      plot.subtitle = element_text(hjust = 0.5)
+    )
+}

### 2025-04-14 R/fig9.R

@@ -1,0 +1,53 @@
+make_fig9 <- function(completions) {
+  completions |>
+    ggplot() +
+    aes(x = Age, y = pc, colour = Year, group = Year) +
+    geom_line() +
+    scale_color_gradientn(colours = rainbow(10)[1:8]) +
+    labs(
+      y = "Percentage of graduates",
+      title = "Graduate Completions by Year and Age",
+      subtitle = "2006 - 2023"
+    ) +
+    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+    scale_y_continuous(
+      labels = scales::percent_format(scale = 1)
+    ) +
+    theme_classic() +
+    theme(
+      plot.title = element_text(hjust = 0.5, face = "bold"),
+      plot.subtitle = element_text(hjust = 0.5)
+    )
+}
+
+make_fig10 <- function(ave_completions) {
+  ave_completions |>
+    ggplot() +
+    aes(x = Age, pc) +
+    geom_line() +
+    labs(y = "Percentage of graduates") +
+    labs(
+      title = "Graduate Completions by Age",
+      subtitle = "2006 - 2023"
+    ) +
+    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+    scale_y_continuous(labels = scales::percent_format(scale = 1)) +
+    theme_classic() +
+    theme(
+      plot.title = element_text(hjust = 0.5, face = "bold"),
+      plot.subtitle = element_text(hjust = 0.5)
+    )
+}
+
+make_table2 <- function(ave_completions) {
+  ave_completions |>
+    filter(Age >= 20 & Age <= 25) |>
+    mutate(pc = paste0(round(pc, 2), "%")) |>
+    select(Age, pc) |>
+    kable(col.names = c("Age", "Percentage of Graduates"), align = "c") |>
+    add_header_above(
+      c("Percentage of Graduates Ages 20-25" = 2),
+      bold = TRUE
+    ) |>
+    kable_styling(latex_options = c("striped"))
+}

### 2025-04-14 R/graduates.R

@@ -96,9 +96,15 @@ read_completions <- function(file) {
     ) |>
     select(Year, age_group, pc)
 
-  completions_step <- completions |>
-    make_single_age(pc, smooth = FALSE)
+  return(completions)
+}
 
+make_completions_step <- function(completions) {
+  completions |>
+    make_single_age(pc, smooth = FALSE)
+}
+
+make_completions_ave <- function(completions) {
   # Average over years
   ave_completions <- completions |>
     group_by(age_group) |>

### 2025-04-14 R/lvl2.R

@@ -1,37 +1,33 @@
-# Course leavers
-
-# Numbers of people at census
-read_census <- function(file) {
+read_census2 <- function(file) {
+  # Numbers of people at census
   y2006 <- readxl::read_excel(file, sheet = "2006", skip = 10) |>
     janitor::clean_names() |>
-    head(3535) |>
+    head(3030) |>
     transmute(
-      discipline = non_school_qualification_field_of_study_qalfp_2_digit,
+      category = non_school_qualification_field_of_study_qalfp_1_digit,
       qualification = non_school_qualification_level_of_education_qallp_1_digit,
       age_group = age_in_single_years_agep,
       persons = persons
     ) |>
     mutate(age_group = as.character(age_group))
-
   y2011 <- readxl::read_excel(file, sheet = "2011", skip = 10) |>
     janitor::clean_names() |>
-    head(3010) |>
+    head(2580) |>
     transmute(
-      discipline = qalfp_4_digit_level,
+      category = qalfp_2_digit_level,
       qualification = qallp_1_digit_level,
       age_group = age_in_single_years_agep,
       persons = persons
     )
-
   y2016 <- readxl::read_excel(
     file,
     sheet = "2016 - Labour force flag",
     skip = 10
   ) |>
     janitor::clean_names() |>
-    head(7070) |>
+    head(6060) |>
     transmute(
-      discipline = qalfp_4_digit_level,
+      category = qalfp_2_digit_level,
       participation = lffp_labour_force_participation_flag,
       qualification = qallp_1_digit_level,
       age_group = agep_age,
@@ -44,9 +40,9 @@ read_census <- function(file) {
     skip = 10
   ) |>
     janitor::clean_names() |>
-    head(7070) |>
+    head(6060) |>
     transmute(
-      discipline = x4_digit_level_qalfp_non_school_qualification_field_of_study,
+      category = x2_digit_level_qalfp_non_school_qualification_field_of_study,
       participation = lffp_labour_force_participation_flag,
       qualification = x1_digit_level_qallp_non_school_qualification_level_of_education,
       age_group = agep_age,
@@ -61,6 +57,15 @@ read_census <- function(file) {
   ) |>
     filter(qualification != "Certificate Level") |>
     filter(qualification != "Advanced Diploma and Diploma Level") |>
+    filter(
+      category %in%
+        c(
+          "Natural and Physical Sciences",
+          "Information Technology",
+          "Agriculture, Environmental and Related Studies",
[…]

### 2025-04-14 R/physics_figs.R

@@ -1,0 +1,58 @@
+make_fig13 <- function(physics, subtitle) {
+  physics |>
+    ggplot(aes(x = Year, y = Graduates)) +
+    geom_line() +
+    scale_x_continuous(breaks = seq(2006, 2023, by = 2)) +
+    labs(
+      title = "Graduates",
+      subtitle = paste0(subtitle, "\n2006–2023"),
+      y = "Number of graduates"
+    ) +
+    theme_classic() +
+    theme(
+      plot.title = element_text(hjust = 0.5, face = "bold"),
+      plot.subtitle = element_text(hjust = 0.5)
+    )
+}
+
+make_fig14 <- function(future_physics_grads, physics_grads) {
+  future_physics_grads <- future_physics_grads |>
+    summarise(
+      mean = mean(Graduates),
+      lo = quantile(Graduates, prob = 0.05),
+      hi = quantile(Graduates, prob = 0.95)
+    )
+  ggplot(future_physics_grads) +
+    aes(x = Year) +
+    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
+    geom_line(aes(y = mean), color = "#c14b14") +
+    geom_line(data = physics_grads, aes(y = Graduates)) +
+    labs(
+      y = "Number of graduates",
+      title = "Forecast of Graduates",
+      subtitle = "Physics and Astronomy\nForecasted Years: 2024–2041"
+    ) +
+    scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
+    theme_classic() +
+    theme(
+      plot.title = element_text(hjust = 0.5, face = "bold"),
+      plot.subtitle = element_text(hjust = 0.5)
+    )
+}
+
+make_fig15 <- function(physics) {
+physics |>
+  autoplot(Migrants) +
+  scale_x_continuous(breaks = seq(10,100,by=10)) +
+  labs(
+    y = "Number of net migrants",
+    title = "Estimated Net Migration",
+    subtitle = "Physics and Astronomy\n2006 - 2020"
+  ) +
+  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
+  theme_classic()  +
+  theme(
+    plot.title = element_text(hjust = 0.5, face = "bold"),
+    plot.subtitle = element_text(hjust = 0.5)
+  )
+}

### 2025-04-14 R/retirement_figs.R

@@ -1,0 +1,37 @@
+make_fig4 <- function(retirements) {
+  ggplot(retirements, aes(x = age_group, y = pc)) +
+    geom_col(alpha = 0.6) +
+    labs(
+      title = "Retirement Intentions",
+      subtitle = "2022--23 Financial Year",
+      x = "Age group",
+      y = "Percentage of retirement intentions"
+    ) +
+    scale_y_continuous(labels = scales::percent_format(scale = 1)) +
+    theme_classic() +
+    theme(
+      plot.title = element_text(hjust = 0.5, face = "bold"),
+      plot.subtitle = element_text(hjust = 0.5),
+      axis.text.x = element_text(angle = 45, hjust = 1),
+      legend.position = "none"
+    )
+}
+
+make_fig6 <- function(retirements, var) {
+  retirements |>
+    filter(Age < 100) |>
+    ggplot() +
+    aes(x = Age, y = {{ var }}) +
+    geom_line() +
+    labs(
+      y = "Probability of retirement",
+      title = "Probability of Retirement",
+      subtitle = "Professional, scientific and technical services\n2022–23 Financial Year"
+    ) +
+    scale_x_continuous(breaks = seq(40, 100, by = 10)) +
+    theme_classic() +
+    theme(
+      plot.title = element_text(hjust = 0.5, face = "bold"),
+      plot.subtitle = element_text(hjust = 0.5)
+    )
+}

### 2025-04-14 R/retirements.R

@@ -1,13 +1,28 @@
-# Script to read in age distribution of retirement intentions
-# mortality.R needs to be run first to get Australian population data
+# Age distribution of retirement intentions
 
 read_retirements <- function(file) {
   readxl::read_excel(file, sheet = "Retirement intentions by occ", skip = 10) |>
     janitor::clean_names() |>
     head(56) |>
-    filter(x1 == "Professional, scientific and technical services") |>
+    filter(
+      x1 %in%
+        c(
+          "Professional, scientific and technical services",
+          "Education and training",
+          "Health care and social assistance"
+        )
+    ) |>
     select(contains("years")) |>
-    tidyr::pivot_longer(everything(), names_to = "age_group", values_to = "count") |>
+    mutate(across(
+      everything(),
+      function(x) as.numeric(x) * c(15.81, 15.48, 14.65) / 100
+    )) |>
+    summarise(across(everything(), sum)) |>
+    tidyr::pivot_longer(
+      everything(),
+      names_to = "age_group",
+      values_to = "count"
+    ) |>
     transmute(
       age_group = stringr::str_remove(age_group, "^x"),
       age_group = stringr::str_remove(age_group, "_years"),
@@ -29,7 +44,11 @@ single_age_retirements <- function(retirement_data, death_prob) {
   # That looks weird below 55. Let's just replace that section by a linear interpolation
 
   retirement <- retirement |>
-    mutate(pc = if_else(Age <= 59, (Age - 44) * 0.0727505, pc))
+    mutate(
+      pc = if_else(Age <= 59, (Age - 44) * 0.0727505, pc),
+      pc = pc/sum(pc)*100
+    )
+
 
   # retirement |> ggplot(aes(x=Age, y=pc)) + geom_line()
   # Looks better

### 2025-04-14 _targets.R

@@ -10,7 +10,9 @@ tar_option_set(
     "tidyr",
     "tsibble",
     "fable",
-    "feasts"
+    "feasts",
+    "knitr",
+    "kableExtra"
   )
 )
 tar_source()
@@ -41,6 +43,8 @@ list(
     )
   ),
   tar_target(completions, read_completions(grad_file)),
+  tar_target(completions_step, make_completions_step(completions)),
+  tar_target(ave_completions, make_completions_ave(completions)),
 
   # Course leavers
   tar_target(
@@ -55,14 +59,20 @@ list(
       select(-category)
   ),
 
-  # Census
-  tar_target(census, read_census(science_file4)),
+  # Census 2 digit
+  tar_target(science_file2, here::here("data/2-digit - Single year.xlsx")),
+  tar_target(census2, read_census2(science_file2)),
+  tar_target(census2_1,
+    make_census_single_year(census2, course_leavers, ave_completions, retirements, aus_death_prob)),
+
+  # Census 4 digit
+  tar_target(census4, read_census(science_file4)),
   tar_target(
-    census1,
+    census4_1,
     make_census_single_year(
-      census,
+      census4,
       course_leavers,
-      completions,
+      ave_completions,
       retirements,
       aus_death_prob
     )
@@ -74,9 +84,9 @@ list(
   tar_target(
     future_pop_science,
     forecast_pop(
-      census1,
+      census4_1,
       course_leavers,
-      completions,
+      ave_completions,
       retirements,
       aus_death_prob,
       arma_coef_science,
@@ -85,14 +95,44 @@ list(
     )
   ),
 
+  # Physics
+  tar_target(
+    physics,
+    census4_1 |>
+      filter(discipline == "Physics and Astronomy") |>
+      select(-discipline)
+  ),
+  tar_target(
+    physics_leavers,
+    course_leavers |>
+      filter(discipline == "Physics and Astronomy") |>
+      select(-discipline, -category)
+  ),
+  tar_target(
+    future_physics_leavers,
+    future_course_leavers_science |>
+      filter(discipline == "Physics and Astronomy") |>
+      select(-discipline)
+  ),
+
   # Figures
-  tar_target(fig1, make_fig1(census)),
-  tar_target(fig2, make_fig2(census1)),
-  tar_target(fig3, make_fig3(census1)),
[…]

### 2025-04-15 age_structure_forecasts.qmd
Now compiling
Added more figures and edited some existing figures

@@
 options(
-  ggplot2.discrete.colour = c("#D55E00", "#0072B2", "#009E73", "#CC79A7", "#E69F00", "#56B4E9", "#F0E442"),
-  ggplot2.discrete.fill = c("#D55E00", "#0072B2", "#009E73", "#CC79A7", "#E69F00", "#56B4E9", "#F0E442")
+  ggplot2.discrete.colour = c(
+    "#D55E00",
+    "#0072B2",
+    "#009E73",
+    "#CC79A7",
+    "#E69F00",
+    "#56B4E9",
+    "#F0E442"
+  ),
+  ggplot2.discrete.fill = c(
+    "#D55E00",
+    "#0072B2",
+    "#009E73",
+    "#CC79A7",
+    "#E69F00",
+    "#56B4E9",
+    "#F0E442"
+  )
 )
@@
 The results aim to inform future workforce planning and policy decisions to support the growth of Australia’s scientific community.
-
-\newpage
 
@@
 tar_read(fig4)
-```
-
-```{r}
-#| label: fig-afterdisaggregation
-#| eval: true
-#| fig-cap: Retirement intentions across key industries after smoothed disaggregation.
-tar_read(fig5)
 ```
@@
 #| label: fig-future-physics
-#| eval: false
+#| eval: true
 #| fig-height: 3
 #| fig-cap: Two example simulations from a set of 500, using historical data from 2006-2021 to forecast age-specific population distributions for 2022-2041.
-p <- physics_and_astronomy |>
-  ggplot() +
-  aes(x = Age, y = Working, group = Year) +
-  geom_line(colour = "gray")
-p1 <- p +
-  geom_line(data = future_physics_and_astronomy |> filter(.rep == "1"), aes(colour = Year)) +
-  labs(y = "Number of working scientists") +
-  scale_color_gradientn(colors = rainbow(10)[1:8]) +
-  labs(
-    title = "Simulation 1",
-    subtitle = "Forecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    legend.position = "none"  # Remove legend
-  )
-
-p2 <- p +
-  geom_line(data = future_physics_and_astronomy |> filter(.rep == "2"), aes(colour = Year)) +
-  labs(y = NULL) +  # Remove y-axis label
-  scale_color_gradientn(colors = rainbow(10)[1:8]) +
-  labs(
-    title = "Simulation 2",
-    subtitle = "Forecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
-
-p1 + p2
+tar_read(fig16)
 ```
@@
 #| label: fig-future-physics-2035
-#| eval: false
+#| eval: true
 #| fig-cap: Forecasted age distribution of the working population for Physics and Astronomy in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
-
-# 2025 and 2035
-eg_forecast <- future_physics_and_astronomy |>
-  filter(Year %in% c(2025, 2035)) |>
-  group_by(Age) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), size = 0.75) +
-    labs(
-      y = "Number of working scientists",
-      title = "Forecast of Working Population",
-      subtitle = "Physics and Astronomy",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme_classic() +
-    theme(
-      plot.title = element_text(hjust = 0.5, face = "bold"),
-      plot.subtitle = element_text(hjust = 0.5),
-      legend.position = "top"
-    )
+tar_read(fig17)
 ```
@@
 #| label: fig-total-future-physics
-#| eval: false
+#| eval: true
 #| fig-cap: Forecasted total number of working scientists for Physics and Astronomy (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
-
-sum_physics_and_astronomy <- physics_and_astronomy |>
-  as_tibble() |>
-  group_by(Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-sum_future_physics_and_astronomy <- future_physics_and_astronomy |>
-  as_tibble() |>
-  group_by(Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-ggplot(sum_future_physics_and_astronomy) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = sum_physics_and_astronomy, aes(y = Working)) +
- labs(y = "Total number of working scientists") +
-  labs(
-    title = "Forecast of Total Working Population",
-    subtitle = "Physics and Astronomy\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  scale_y_continuous(labels = scales::comma_format()) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  )
-```
-
-\newpage
+tar_read(fig18)
+
+```
 
@@
 #| label: tbl-disciplines
+#| eval: true
 #| tbl-cap: Classification of scientific disciplines, based on the ASCED Narrow Fields of Education within the Broad Field of Natural and Physical Sciences.
 The table lists their corresponding Detailed Fields.
-
-discipline_table <- tibble(
-  Narrow_Discipline = c(
-    "Physics and Astronomy", "Mathematical Sciences", "Chemical Sciences",
-    "Earth Sciences", "Biological Sciences", "Other Natural and Physical Sciences",
-    "Natural and Physical Sciences n.f.d."
-  ),
-  Detailed_Field = c(
-    "Physics, Astronomy.",
-    "Mathematics, Statistics, Mathematical Sciences, n.e.c.",
-    "Organic Chemistry, Inorganic Chemistry, Chemical Sciences, n.e.c.",
-    "Atmospheric Sciences, Geology, Geophysics, Geochemistry, Soil Science, Hydrology, Oceanography, Earth Sciences, n.e.c.",
-    "Biochemistry and Cell Biology, Botany, Ecology and Evolution, Marine Science, Genetics, Microbiology, Human Biology, Zoology, Biological Sciences, n.e.c.",
-    "Medical Science, Forensic Science, Food Science and Biotechnology, Pharmacology, Laboratory Technology, Natural and Physical Sciences, n.e.c.",
-    " "
-  )
-)
-
-discipline_table |>
-  kable(col.names = c("Narrow Fields", "Detailed Fields")) |>
-  add_header_above(c("Broad Field: Natural and Physical Sciences" = 2), bold = TRUE) |>
-  kable_styling(latex_options = c("striped"), full_width = FALSE) |>
-  column_spec(2, width = "20em")
+tar_read(discipline_table)
 ```
@@
 #| label: fig-working-population
-#| eval: false
+#| eval: true
 #| fig-cap: "Age distribution of the working population across scientific disciplines based on Census data from 2006, 2011, 2016, and 2021.
@@
 #| fig-height: 5.5
-disciplines_combined <- bind_rows(
-  as_tibble(physics_and_astronomy) |> mutate(Discipline = "Physics and Astronomy"),
-  as_tibble(mathematical_sciences) |> mutate(Discipline = "Mathematical Sciences"),
-  as_tibble(chemical_sciences) |> mutate(Discipline = "Chemical Sciences"),
-  as_tibble(earth_sciences) |> mutate(Discipline = "Earth Sciences"),
-  as_tibble(biological_sciences) |> mutate(Discipline = "Biological Sciences"),
-  as_tibble(other_natural_and_physical_sciences) |> mutate(Discipline = "Other Natural and Physical Sciences"),
-  as_tibble(natural_and_physical_sciences__nfd) |> mutate(Discipline = "Natural and Physical Sciences (n.f.d.)")
-)
-
-disciplines_combined$Discipline <- factor(
-  disciplines_combined$Discipline,
-  levels = c("Physics and Astronomy", "Mathematical Sciences", "Chemical Sciences", "Earth Sciences", "Biological Sciences", "Other Natural and Physical Sciences", "Natural and Physical Sciences (n.f.d.)")
-)
-
-disciplines_combined |>
-  filter(Year %in% years) |>
-  mutate(Year = factor(Year, levels = rev(years))) |>
-  ggplot() +
-  aes(x = Age, y = Working, color = Year, group = Year) +
-  geom_line() +
-  scale_color_manual(values = cols, name = "Census Year") +
-  labs(
-    y = "Number of active scientists",
-    title = "Working Population by Discipline",
-    subtitle = "Natural and Physical Sciences"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  facet_wrap(~Discipline, scales = "free_y") +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    legend.position = "top"
-  )
+tar_read(fig19)
 ```
@@
 #| label: fig-interpolated-working-population
+#| eval: true
 #| fig-cap: "Age distribution of the working population across scientific disciplines, interpolated from Census data between 2006 and 2021.
@@
 #| fig-height: 6
-#| eval: false
-ggplot(disciplines_combined) +
-  aes(x = Age, y = Working, group = Year, color = Year) +
-  geom_line() +
-  facet_wrap(~Discipline, scales = "free_y") +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  scale_color_gradientn(
-    colours = rainbow(10)
-  ) +
-  labs(
-    y = "Number of active scientists",
-    title = "Interpolated Working Population by Discipline",
-    subtitle = "Natural and Physical Sciences\n2006 - 2021"
-  ) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    legend.position = "top"
-  )
+tar_read(fig20)
 ```
@@
 #| label: fig-graduates-disciplines
-#| eval: false
+#| eval: true
 #| fig-cap: "Number of graduates across scientific disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."
-
-course_leavers_arranged <- course_leavers_lvl4_science
-course_leavers_arranged$discipline <- course_leavers_lvl4_science$discipline |>
-  fct_recode(
-    "Natural and Physical Sciences (n.f.d.)" = "Natural and Physical Sciences, nfd"
-  ) |>
-  fct_relevel(
-    "Physics and Astronomy",
-    "Mathematical Sciences",
-    "Chemical Sciences",
-    "Earth Sciences",
-    "Biological Sciences",
-    "Other Natural and Physical Sciences",
-    "Natural and Physical Sciences (n.f.d.)"
-  )
-
-ggplot(course_leavers_arranged) +
-  aes(x = Year, y = Graduates) +
-  geom_line() +
-  facet_wrap(~discipline, scales = "free_y") +
-  labs(
-    y = "Number of graduates",
-    title = "Graduates by Discipline",
-    subtitle = "Natural and Physical Sciences\n2006 - 2023"
-  ) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    legend.position = "none"
-  )
+tar_read(fig21)
+```
+
+```{r}
+#| label: fig-grad-forecasts
+#| eval: true
+#| fig-cap: "Forecast number of graduates by discipline, 2024-2041, with 90% prediction intervals, based on historical data from 2006--2023."
+tar_read(fig_grad_forecasts)
 ```
@@
 #| label: fig-net-migration-disciplines
-#| eval: false
+#| eval: true
 #| fig-cap: Estimated net migration by age across scientific disciplines (2006–2020). Each panel represents a different discipline, showing net migration trends across age groups.
 #| fig-height: 6
-ggplot(disciplines_combined) +
-  aes(x = Age, y = Migrants, group = Year, color = Year) +
-  geom_line() +
-  facet_wrap(~Discipline, scales = "free_y") +
-  scale_x_continuous(breaks = seq(10, 100, by = 10)) +
-  scale_color_gradientn(
-    colours = rainbow(10)
-  ) +
-  labs(
-    y = "Number of net migrants",
-    title = "Estimated Net Migration by Discipline",
-    subtitle = "Natural and Physical Sciences\n2006 - 2020"
-  ) +
-  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5),
-    legend.position = "top"
-  )
+tar_read(fig22)
 ```
@@
 
-\newpage
-
 ```{r}
 #| label: fig-forecast-working-population
-#| eval: false
+#| eval: true
 #| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across scientific disciplines.
@@
 #| fig-height: 5.5
-future_disciplines_combined <- bind_rows(
-  as_tibble(future_physics_and_astronomy) |> mutate(Discipline = "Physics and Astronomy"),
-  as_tibble(future_mathematical_sciences) |> mutate(Discipline = "Mathematical Sciences"),
-  as_tibble(future_chemical_sciences) |> mutate(Discipline = "Chemical Sciences"),
-  as_tibble(future_earth_sciences) |> mutate(Discipline = "Earth Sciences"),
-  as_tibble(future_biological_sciences) |> mutate(Discipline = "Biological Sciences"),
-  as_tibble(future_other_natural_and_physical_sciences) |> mutate(Discipline = "Other Natural and Physical Sciences"),
-  as_tibble(future_natural_and_physical_sciences__nfd) |> mutate(Discipline = "Natural and Physical Sciences (n.f.d.)")
-)
-
-future_disciplines_combined$Discipline <- factor(
-  future_disciplines_combined$Discipline,
-  levels = c("Physics and Astronomy", "Mathematical Sciences", "Chemical Sciences", "Earth Sciences", "Biological Sciences", "Other Natural and Physical Sciences", "Natural and Physical Sciences (n.f.d.)")
-)
-
 # 2025 and 2035
-eg_forecast <- future_disciplines_combined |>
-  filter(Year %in% c(2025, 2035)) |>
-  group_by(Discipline, Age, Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), size = 0.75) +
-    labs(
-      y = "Number of working scientists",
-      title = "Forecast of Working Population by Discipline",
-      subtitle = "Natural and Physical Sciences",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme_classic() +
-    theme(
-      plot.title = element_text(hjust = 0.5, face = "bold"),
-      plot.subtitle = element_text(hjust = 0.5),
-      legend.position = "top"
-    ) +
-    facet_wrap(~Discipline, scales = "free_y")
+tar_read(fig23)
 ```
@@
 While there is a minor increase in the number of workers aged 70, this change is not substantial enough to suggest a broader shift in workforce dynamics.
-\newpage
 -   **Earth Sciences** *(Aging Workforce):* Early-career workforce projections are more uncertain relative to its size.
@@
 #| label: fig-forecast-total-working-scientists
-#| eval: false
+#| eval: true
 #| fig-cap: "Projected total number of working scientists across scientific disciplines from 2022 to 2041.
 The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."
-
-sum_disciplines_combined  <- disciplines_combined |>
-  group_by(Discipline, Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-
-sum_future_disciplines_combined <- future_disciplines_combined |>
-  group_by(Discipline, Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Discipline, Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-ggplot(sum_future_disciplines_combined) +
-  aes(x = Year) +
-  geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-  geom_line(aes(y = mean), color = "#c14b14") +
-  geom_line(data = sum_disciplines_combined, aes(y = Working)) +
-  labs(
-    y = "Total number of working scientists (thousands)",
-    title = "Forecast of Total Working Population by Discipline",
-    subtitle = "Natural and Physical Sciences\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 10)) +
-  scale_y_continuous(labels = scales::label_number(scale = 1e-3)) +
-  theme_classic() +
-  theme(
-    plot.title = element_text(hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(hjust = 0.5)
-  ) +
-  facet_wrap(~Discipline, scales = "free_y")
-```
-
-\newpage
+tar_read(fig24)
+```
 

### 2025-04-15 R/discipline_table.R

@@ -1,0 +1,33 @@
+make_discipline_table <- function() {
+  tibble::tibble(
+    Narrow_Discipline = c(
+      "Physics and Astronomy",
+      "Mathematical Sciences",
+      "Chemical Sciences",
+      "Earth Sciences",
+      "Biological Sciences",
+      "Other Natural and Physical Sciences"
+    ),
+    Detailed_Field = c(
+      "Physics, Astronomy.",
+      "Mathematics, Statistics, Mathematical Sciences, n.e.c.",
+      "Organic Chemistry, Inorganic Chemistry, Chemical Sciences, n.e.c.",
+      "Atmospheric Sciences, Geology, Geophysics, Geochemistry, Soil Science, Hydrology, Oceanography, Earth Sciences, n.e.c.",
+      "Biochemistry and Cell Biology, Botany, Ecology and Evolution, Marine Science, Genetics, Microbiology, Human Biology, Zoology, Biological Sciences, n.e.c.",
+      "Medical Science, Forensic Science, Food Science and Biotechnology, Pharmacology, Laboratory Technology, Natural and Physical Sciences, n.e.c."
+    )
+  ) |>
+    kableExtra::kbl(
+      format = "latex",
+      col.names = c("Narrow Fields", "Detailed Fields")
+    ) |>
+    kableExtra::add_header_above(
+      c("Broad Field: Natural and Physical Sciences" = 2),
+      bold = TRUE
+    ) |>
+    kableExtra::kable_styling(
+      latex_options = c("striped"),
+      full_width = FALSE
+    ) |>
+    kableExtra::column_spec(2, width = "20em")
+}

### 2025-04-15 R/lv4_science.R

@@ -116,9 +116,20 @@ read_census <- function(file) {
     select(-avg_participation)
 
   # Combine all years
-  census |>
+  census <- census |>
     bind_rows(censusp) |>
     mutate(Working = persons * participation)
+
+  # Combine "Other Natural and Physical Sciences" and "Natural and Physical Sciences (n.f.d.)"
+  census <- census |>
+    mutate(
+      discipline = if_else(
+        discipline == "Natural and Physical Sciences (n.f.d.)",
+        "Other Natural and Physical Sciences",
+        discipline
+      )
+    )
+  return(census)
 }
 
 # Convert census data to single age groups and separate the disciplines

### 2025-04-15 R/mortality.R

@@ -12,7 +12,7 @@ read_mortality <- function(mx_path, ex_path) {
 # Then smooth the result and add in population data
 compute_death_prob <- function(mortality) {
   life_table(mortality) |>
-    smooth_mortality(qx, k = 20) |>
+    smooth_mortality(qx, k = 50) |>
     mutate(death_prob = c(.smooth)) |>
     select(Year, Age, death_prob) |>
     left_join(

### 2025-04-15 R/physics_figs.R

@@ -29,25 +29,116 @@ make_fig14 <- function(future_physics_grads, physics_grads) {
     ) +
     scale_x_continuous(breaks = seq(2010, 2040, by = 5))
 }
+
+make_fig15 <- function(physics) {
+  physics |>
+    autoplot(Migrants) +
+    scale_x_continuous(breaks = seq(10, 100, by = 10)) +
+    labs(
+      y = "Number of net migrants",
+      title = "Estimated Net Migration",
+      subtitle = "Physics and Astronomy\n2006 - 2020"
+    ) +
+    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5)
+}
+
+
+make_fig16 <- function(physics, future_physics) {
+  p <- physics |>
+    ggplot() +
+    aes(x = Age, y = Working, group = Year) +
+    geom_line(colour = "gray")
+  p1 <- p +
+    geom_line(
+      data = future_physics |> filter(.rep == "1"),
+      aes(colour = Year)
+    ) +
+    labs(y = "Number of working scientists") +
+    scale_color_gradientn(colors = rainbow(10)[1:8]) +
+    labs(
+      title = "Simulation 1",
+      subtitle = "Forecasted Years: 2022 - 2041"
+    ) +
+    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
     theme(
-      plot.title = element_text(hjust = 0.5, face = "bold"),
-      plot.subtitle = element_text(hjust = 0.5)
+      legend.position = "none" # Remove legend
+    )
+
+  p2 <- p +
+    geom_line(
+      data = future_physics |> filter(.rep == "2"),
+      aes(colour = Year)
+    ) +
+    labs(y = NULL) + # Remove y-axis label
+    scale_color_gradientn(colors = rainbow(10)[1:8]) +
+    labs(
+      title = "Simulation 2",
+      subtitle = "Forecasted Years: 2022 - 2041"
+    ) +
+    scale_x_continuous(breaks = seq(20, 100, by = 10))
+
+  p1 + p2
+}
+
+make_fig17 <- function(future_physics) {
+  # 2025 and 2035
+  eg_forecast <- future_physics |>
+    filter(Year %in% c(2025, 2035)) |>
+    group_by(Age) |>
+    summarise(
+      mean = mean(Working),
+      lo = quantile(Working, prob = 0.05),
+      hi = quantile(Working, prob = 0.95),
+      .groups = "drop"
+    )
+
+  # Overlay
[…]

### 2025-04-15 R/sec5_figures.R

@@ -1,0 +1,186 @@
+make_fig19 <- function(disciplines_combined) {
+  years <- seq(2006, 2021, by = 5)
+  cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF")
+  names(cols) <- years
+
+  disciplines_combined |>
+    as_tibble() |>
+    filter(Year %in% years) |>
+    mutate(Year = factor(Year, levels = rev(years))) |>
+    ggplot() +
+    aes(x = Age, y = Working, color = Year, group = Year) +
+    geom_line() +
+    scale_color_manual(values = cols, name = "Census Year") +
+    labs(
+      y = "Number of active scientists",
+      title = "Working Population by Discipline",
+      subtitle = "Natural and Physical Sciences"
+    ) +
+    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+    facet_wrap(~discipline, scales = "free_y") +
+    theme(
+      legend.position = "top"
+    )
+}
+
+make_fig20 <- function(disciplines_combined) {
+  ggplot(disciplines_combined) +
+    aes(x = Age, y = Working, group = Year, color = Year) +
+    geom_line() +
+    facet_wrap(~discipline, scales = "free_y") +
+    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+    scale_color_gradientn(
+      colours = rainbow(10)
+    ) +
+    labs(
+      y = "Number of active scientists",
+      title = "Interpolated Working Population by Discipline",
+      subtitle = "Natural and Physical Sciences\n2006 - 2021"
+    ) +
+    theme(
+      legend.position = "top"
+    )
+}
+
+make_fig21 <- function(course_leavers) {
+  course_leavers$discipline <- course_leavers$discipline |>
+    forcats::fct_recode(
+      "Natural and Physical Sciences (n.f.d.)" = "Natural and Physical Sciences, nfd"
+    ) |>
+    forcats::fct_relevel(
+      "Physics and Astronomy",
+      "Mathematical Sciences",
+      "Chemical Sciences",
+      "Earth Sciences",
+      "Biological Sciences",
+      "Other Natural and Physical Sciences",
+      "Natural and Physical Sciences (n.f.d.)"
+    )
+
+  ggplot(course_leavers) +
+    aes(x = Year, y = Graduates) +
+    geom_line() +
+    facet_wrap(~discipline, scales = "free_y") +
+    labs(
[…]

### 2025-04-15 _targets.R

@@ -12,7 +12,8 @@ tar_option_set(
     "fable",
     "feasts",
     "knitr",
-    "kableExtra"
+    "kableExtra",
+    "patchwork"
   )
 )
 tar_source()
@@ -23,6 +24,7 @@ list(
   tar_target(ex_file, here::here("data/Exposures_1x1.txt"), format = "file"),
   tar_target(mortality, read_mortality(mx_file, ex_file)),
   tar_target(aus_death_prob, compute_death_prob(mortality)),
+  tar_target(fig8, make_fig8(aus_death_prob)),
 
   # Retirement data
   tar_target(
@@ -34,6 +36,9 @@ list(
     retirements,
     single_age_retirements(retirement_data, aus_death_prob)
   ),
+  tar_target(fig4, make_fig4(retirement_data)),
+  tar_target(fig6, make_fig6(retirements, pc)),
+  tar_target(fig7, make_fig6(retirements, retire_prob)),
 
   # Graduates
   tar_target(
@@ -45,6 +50,9 @@ list(
   tar_target(completions, read_completions(grad_file)),
   tar_target(completions_step, make_completions_step(completions)),
   tar_target(ave_completions, make_completions_ave(completions)),
+  tar_target(fig9, make_fig9(completions_step)),
+  tar_target(fig10, make_fig10(ave_completions)),
+  tar_target(tab2, make_table2(ave_completions)),
 
   # Course leavers
   tar_target(
@@ -62,8 +70,19 @@ list(
   # Census 2 digit
   tar_target(science_file2, here::here("data/2-digit - Single year.xlsx")),
   tar_target(census2, read_census2(science_file2)),
-  tar_target(census2_1,
-    make_census_single_year(census2, course_leavers, ave_completions, retirements, aus_death_prob)),
+  tar_target(
+    census2_1,
+    make_census_single_year(
+      census2,
+      course_leavers,
+      ave_completions,
+      retirements,
+      aus_death_prob
+    )
+  ),
+  tar_target(fig1, make_fig1(census2)),
+  tar_target(fig2, make_fig2(census2_1, "Natural and Physical Sciences")),
+  tar_target(fig3, make_fig3(census2_1, "Natural and Physical Sciences")),
 
   # Census 4 digit
   tar_target(census4, read_census(science_file4)),
@@ -114,23 +133,32 @@ list(
       filter(discipline == "Physics and Astronomy") |>
       select(-discipline)
[…]

### 2025-04-15 age_structure_forecasts.qmd
Removed appendix

@@
 linestretch: 1.5
+include-in-header: preamble.tex
 format:
@@
 This analysis contributes to the Australian Academy of Science’s initiative _Australian Science, Australia’s Future: Science 2035_ by identifying shifts in the workforce, helping anticipate future demand for science capabilities, and highlighting potential workforce gaps as aging and retirement reshape workforce dynamics.
-
-\newpage
-
-# Appendix
-
-```{r}
-#| label: tbl-disciplines-stats
-#| eval: false
-#| tbl-cap: Summary statistics for the scientific disciplines, including the 10th and 90th percentile ages, weighted average age, and weighted median age, calculated from the Australian Census data for the years 2006, 2011, 2016, and 2021.
-
-calculate_statistics <- function(discipline_data, discipline_name, years) {
-  stats <- discipline_data |>
-    as_tibble() |>
-    filter(Year %in% years) |>
-    mutate(Age = as.numeric(as.character(Age))) |>
-    group_by(Year) |>
-    summarise(
-      `10th Percentile` = weighted_percentile(Age, Working, prob = 0.1),
-      `90th Percentile` = weighted_percentile(Age, Working, prob = 0.9),
-      `Weighted Average` = round(sum(Age * Working, na.rm = TRUE) / sum(Working, na.rm = TRUE), 1),
-      `Weighted Median` = weighted_percentile(Age, Working, prob = 0.5)
-    )
-
-  stats <- stats |> mutate(Discipline = discipline_name)
-
-  return(stats)
-}
-
-statistics_math <- calculate_statistics(mathematical_sciences, "Mathematical Sciences", years)
-statistics_chem <- calculate_statistics(chemical_sciences, "Chemical Sciences", years)
-statistics_earth <- calculate_statistics(earth_sciences, "Earth Sciences", years)
-statistics_bio <- calculate_statistics(biological_sciences, "Biological Sciences", years)
-statistics_other <- calculate_statistics(other_natural_and_physical_sciences, "Other Natural and Physical Sciences", years)
-statistics_nfd <- calculate_statistics(natural_and_physical_sciences__nfd, "Natural and Physical Sciences (n.f.d.)", years)
-
-all_statistics <- bind_rows(statistics_math, statistics_chem, statistics_earth, statistics_bio, statistics_other, statistics_nfd)
-
-kable(all_statistics[, c("Year", "10th Percentile", "90th Percentile", "Weighted Average", "Weighted Median")]) |>
-  add_header_above(c("Summary Statistics of Scientific Disciplines" = ncol(all_statistics)), bold = TRUE) |>
-  kable_styling(full_width = FALSE) |>
-  column_spec(1, width = "10em") |>
-  column_spec(2, width = "5em") |>
-  column_spec(3, width = "5em") |>
-  column_spec(4, width = "5em") |>
-  column_spec(5, width = "5em") |>
-  column_spec(6, width = "5em") |>
-  group_rows("Mathematical Sciences", 1, 4) |>
-  group_rows("Chemical Sciences", 5, 8) |>
-  group_rows("Earth Sciences", 9, 12) |>
-  group_rows("Biological Sciences", 13, 16) |>
-  group_rows("Other Natural and Physical Sciences", 17, 20) |>
-  group_rows("Natural and Physical Sciences (n.f.d.)", 21, 24)
-```
-
-## Mathematical Sciences
-
-```{r}
-#| label: fig-mathematicians
-#| eval: false
-#| fig-cap: Interpolated number of scientists in Mathematical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
-#| fig-height: 3.5
-#| fig-width: 5.5
-mathematical_sciences |>
-  autoplot(Working) +
-  labs(y = "Number of active scientists") +
-  labs(
-    title = "Interpolated Working Population",
-    subtitle = "Mathematical Sciences\n2006 - 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-grads-math
-#| eval: false
-#| fig-cap: Projected number of Mathematical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
-#| fig-height: 3.5
-#| fig-width: 5.5
-math_grads <- future_course_leavers_science |>
-  filter(discipline == "Mathematical Sciences") |>
-  summarise(
-    mean = mean(Graduates),
-    lo = quantile(Graduates, prob = 0.05),
-    hi = quantile(Graduates, prob = 0.95)
-  )
-ggplot(math_grads) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Mathematical Sciences"), aes(y = Graduates)) +
-  labs(y = "Number of graduates",
-    title = "Forecast of Graduates",
-    subtitle = "Mathematical Sciences\nForecasted Years: 2024 - 2041"
-  ) +
- scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-net-migrants-maths
-#| eval: false
-#| fig-cap: Net migration of scientists in Mathematical Sciences by age, 2006–2020.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-mathematical_sciences |>
-  autoplot(Migrants) +
-  scale_x_continuous(breaks = seq(10,100,by=10)) +
-  labs(
-    y = "Number of net migrants",
-    title = "Estimated Net Migration",
-    subtitle = "Mathematical Sciences\n2006 - 2020"
-  ) +
-  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-mathematicians-2035
-#| eval: false
-#| fig-cap: Forecasted age distribution of the working population for Mathematical Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-# 2025 and 2035
-eg_forecast <- future_mathematical_sciences |>
-  filter(Year %in% c(2025, 2035)) |>
-  group_by(Age) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), size = 0.6) +
-  labs(y = "Number of working scientists",
-    title = "Forecast of Working Population",
-    subtitle = "Mathematical Sciences",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme_classic() +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7),
-    legend.position = "top"
-  )
-```
-
-```{r}
-#| label: fig-total-future-mathematicians
-#| eval: false
-#| fig-cap: Forecasted total number of working scientists for Mathematical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-sum_mathematical_sciences  <- mathematical_sciences |>
-  as_tibble() |>
-  group_by(Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-sum_future_mathematical_sciences <- future_mathematical_sciences |>
-  as_tibble() |>
-  group_by(Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-ggplot(sum_future_mathematical_sciences) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = sum_mathematical_sciences, aes(y = Working)) +
- labs(y = "Total number of working scientists") +
-  labs(
-    title = "Forecast of Total Working Population",
-    subtitle = "Mathematical Sciences\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  scale_y_continuous(labels = scales::comma_format()) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-## Chemical Sciences
-
-```{r}
-#| label: fig-chemists
-#| eval: false
-#| fig-cap: Interpolated number of scientists in Chemical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-chemical_sciences |>
-  autoplot(Working) +
-  labs(y = "Number of active scientists") +
-  labs(
-    title = "Interpolated Working Population",
-    subtitle = "Chemical Sciences\n2006 - 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-grads-chem
-#| eval: false
-#| fig-cap: Projected number of Chemical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-chem_grads <- future_course_leavers_science |>
-  filter(discipline == "Chemical Sciences") |>
-  summarise(
-    mean = mean(Graduates),
-    lo = quantile(Graduates, prob = 0.05),
-    hi = quantile(Graduates, prob = 0.95)
-  )
-ggplot(chem_grads) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Chemical Sciences"), aes(y = Graduates)) +
-  labs(y = "Number of graduates",
-    title = "Forecast of Graduates",
-    subtitle = "Chemical Sciences\nForecasted Years: 2024 - 2041"
-  ) +
- scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-net-migrants-chem
-#| eval: false
-#| fig-cap: Net migration of scientists in Chemical Sciences by age, 2006–2020.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-chemical_sciences |>
-  autoplot(Migrants) +
-  scale_x_continuous(breaks = seq(10,100,by=10)) +
-  labs(
-    y = "Number of net migrants",
-    title = "Estimated Net Migration",
-    subtitle = "Chemical Sciences\n2006 - 2020"
-  ) +
-  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-chemists-2035
-#| eval: false
-#| fig-cap: Forecasted age distribution of the working population for Chemical Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-# 2025 and 2035
-eg_forecast <- future_chemical_sciences |>
-  filter(Year %in% c(2025, 2035)) |>
-  group_by(Age) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), size = 0.6) +
-  labs(y = "Number of working scientists",
-    title = "Forecast of Working Population",
-    subtitle = "Chemical Sciences",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7),
-    legend.position = "top"
-  )
-```
-
-```{r}
-#| label: fig-total-future-chemists
-#| eval: false
-#| fig-cap: Forecasted total number of working scientists for Chemical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-sum_chemical_sciences  <- chemical_sciences |>
-  as_tibble() |>
-  group_by(Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-sum_future_chemical_sciences <- future_chemical_sciences |>
-  as_tibble() |>
-  group_by(Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-ggplot(sum_future_chemical_sciences) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = sum_chemical_sciences, aes(y = Working)) +
- labs(y = "Total number of working scientists") +
-  labs(
-    title = "Forecast of Total Working Population",
-    subtitle = "Chemical Sciences\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  scale_y_continuous(labels = scales::comma_format()) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-## Earth Sciences
-
-```{r}
-#| label: fig-earthscientists
-#| eval: false
-#| fig-cap: Interpolated number of scientists in Earth Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-earth_sciences |>
-  autoplot(Working) +
-  labs(
-    y = "Number of active scientists",
-    title = "Interpolated Working Population",
-    subtitle = "Earth Sciences\n2006 - 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-grads-earth
-#| eval: false
-#| fig-cap: Projected number of Earth Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-earth_grads <- future_course_leavers_science |>
-  filter(discipline == "Earth Sciences") |>
-  summarise(
-    mean = mean(Graduates),
-    lo = quantile(Graduates, prob = 0.05),
-    hi = quantile(Graduates, prob = 0.95)
-  )
-ggplot(earth_grads) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Earth Sciences"), aes(y = Graduates)) +
-  labs(y = "Number of graduates",
-    title = "Forecast of Graduates",
-    subtitle = "Earth Sciences\nForecasted Years: 2024 - 2041"
-  ) +
- scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-net-migrants-earth
-#| eval: false
-#| fig-cap: Net migration of scientists in Earth Sciences by age, 2006–2020.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-earth_sciences |>
-  autoplot(Migrants) +
-  scale_x_continuous(breaks = seq(10,100,by=10)) +
-  labs(
-    y = "Number of net migrants",
-    title = "Estimated Net Migration",
-    subtitle = "Earth Sciences\n2006 - 2020"
-  ) +
-  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-earthscientists-2035
-#| eval: false
-#| fig-cap: Forecasted age distribution of the working population for Earth Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-# 2025 and 2035
-eg_forecast <- future_earth_sciences |>
-  filter(Year %in% c(2025, 2035)) |>
-  group_by(Age) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), size = 0.6) +
-  labs(y = "Number of working scientists",
-    title = "Forecast of Working Population",
-    subtitle = "Earth Sciences",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme_classic() +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7),
-    legend.position = "top"
-  )
-```
-
-```{r}
-#| label: fig-total-future-earthscientists
-#| eval: false
-#| fig-cap: Forecasted total number of working scientists for Earth Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-sum_earth_sciences  <- earth_sciences |>
-  as_tibble() |>
-  group_by(Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-sum_future_earth_sciences <- future_earth_sciences |>
-  as_tibble() |>
-  group_by(Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-ggplot(sum_future_earth_sciences) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = sum_earth_sciences, aes(y = Working)) +
- labs(y = "Total number of working scientists") +
-  labs(
-    title = "Forecast of Total Working Population",
-    subtitle = "Earth Sciences\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  scale_y_continuous(labels = scales::comma_format()) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-## Biological Sciences
-
-```{r}
-#| label: fig-biologists
-#| eval: false
-#| fig-cap: Interpolated number of scientists in Biological Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-biological_sciences |>
-  autoplot(Working) +
-  labs(y = "Number of active scientists") +
-  labs(
-    title = "Interpolated Working Population",
-    subtitle = "Biological Sciences\n2006 - 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-grads-bio
-#| eval: false
-#| fig-cap: Projected number of Biological Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023. intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-bio_grads <- future_course_leavers_science |>
-  filter(discipline == "Biological Sciences") |>
-  summarise(
-    mean = mean(Graduates),
-    lo = quantile(Graduates, prob = 0.05),
-    hi = quantile(Graduates, prob = 0.95)
-  )
-ggplot(bio_grads) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Biological Sciences"), aes(y = Graduates)) +
-  labs(y = "Number of graduates",
-    title = "Forecast of Graduates",
-    subtitle = "Biological Sciences\nForecasted Years: 2024 - 2041"
-  ) +
- scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-net-migrants-biology
-#| eval: false
-#| fig-cap: Net migration of scientists in Biological Sciences by age, 2006–2020.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-biological_sciences |>
-  autoplot(Migrants) +
-  scale_x_continuous(breaks = seq(10,100,by=10)) +
-  labs(
-    y = "Number of net migrants",
-    title = "Estimated Net Migration",
-    subtitle = "Biological Sciences\n2006 - 2020"
-  ) +
-  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-biologists-2035
-#| eval: false
-#| fig-cap: Forecasted age distribution of the working population for Biological Sciences in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-# 2025 and 2035
-eg_forecast <- future_biological_sciences |>
-  filter(Year %in% c(2025, 2035)) |>
-  group_by(Age) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), size = 0.6) +
-  labs(y = "Number of working scientists",
-    title = "Forecast of Working Population",
-    subtitle = "Biological Sciences",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme_classic() +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7),
-    legend.position = "top"
-  )
-```
-
-```{r}
-#| label: fig-total-future-biologists
-#| eval: false
-#| fig-cap: Forecasted total number of working scientists for Biological Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-sum_biological_sciences  <- biological_sciences |>
-  as_tibble() |>
-  group_by(Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-sum_future_biological_sciences <- future_biological_sciences |>
-  as_tibble() |>
-  group_by(Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-ggplot(sum_future_biological_sciences) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = sum_biological_sciences, aes(y = Working)) +
- labs(y = "Total number of working scientists") +
-  labs(
-    title = "Forecast of Total Working Population",
-    subtitle = "Biological Sciences\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  scale_y_continuous(labels = scales::comma_format()) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-## Other Natural and Physical Sciences
-
-```{r}
-#| label: fig-otherscientists
-#| eval: false
-#| fig-cap: Interpolated number of scientists in Other Natural and Physical Sciences active in the Australian labour market, 2006–2021, using linear cohort interpolation
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-other_natural_and_physical_sciences |>
-  autoplot(Working) +
-  labs(y = "Number of active scientists") +
-  labs(
-    title = "Interpolated Working Population",
-    subtitle = "Other Natural and Physical Sciences\n2006 - 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-grads-other
-#| eval: false
-#| fig-cap: Projected number of Other Natural and Physical Sciences graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-other_grads <- future_course_leavers_science |>
-  filter(discipline == "Other Natural and Physical Sciences") |>
-  summarise(
-    mean = mean(Graduates),
-    lo = quantile(Graduates, prob = 0.05),
-    hi = quantile(Graduates, prob = 0.95)
-  )
-ggplot(other_grads) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Other Natural and Physical Sciences"), aes(y = Graduates)) +
-  labs(y = "Number of graduates",
-    title = "Forecast of Graduates",
-    subtitle = "Other Natural and Physical Sciences\nForecasted Years: 2024 - 2041"
-  ) +
- scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-net-migrants-other
-#| eval: false
-#| fig-cap: Net migration of scientists in Other Natural and Physical Sciences by age, 2006–2020.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-other_natural_and_physical_sciences |>
-  autoplot(Migrants) +
-  scale_x_continuous(breaks = seq(10,100,by=10)) +
-  labs(
-    y = "Number of net migrants",
-    title = "Estimated Net Migration",
-    subtitle = "Other Natural and Physical Sciences\n2006 - 2020"
-  ) +
-  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-otherscientists-2035
-#| eval: false
-#| fig-cap: Forecasted age distribution of the working population for Other Natural and Physical Sciences in 2025 and 2035, comparing changes over 10 years.
-Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-# 2025 and 2035
-eg_forecast <- future_other_natural_and_physical_sciences |>
-  filter(Year %in% c(2025, 2035)) |>
-  group_by(Age) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), size = 0.6) +
-  labs(y = "Number of working scientists",
-    title = "Forecast of Working Population",
-    subtitle = "Other Natural and Physical Sciences",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme_classic() +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7),
-    legend.position = "top"
-  )
-```
-
-```{r}
-#| label: fig-total-future-otherscientists
-#| eval: false
-#| fig-cap: Forecasted total number of working scientists for Other Natural and Physical Sciences (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-sum_other_natural_and_physical_sciences  <- other_natural_and_physical_sciences |>
-  as_tibble() |>
-  group_by(Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-sum_future_other_natural_and_physical_sciences <- future_other_natural_and_physical_sciences |>
-  as_tibble() |>
-  group_by(Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-ggplot(sum_future_other_natural_and_physical_sciences) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = sum_other_natural_and_physical_sciences, aes(y = Working)) +
- labs(y = "Total number of working scientists") +
-  labs(
-    title = "Forecast of Total Working Population",
-    subtitle = "Other Natural and Physical Sciences\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  scale_y_continuous(labels = scales::comma_format()) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-## Natural and Physical Sciences (Not Further Defined)
-
-```{r}
-#| label: fig-nfd
-#| eval: false
-#| fig-cap: Interpolated number of scientists in Natural and Physical Sciences (n.f.d.) active in the Australian labour market, 2006–2021, using linear cohort interpolation
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-natural_and_physical_sciences__nfd |>
-  autoplot(Working) +
-  labs(
-    y = "Number of active scientists",
-    title = "Interpolated Working Population",
-    subtitle = "Natural and Physical Sciences (n.f.d.)\n2006 - 2021"
-  ) +
-  scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-grads-nfd
-#| eval: false
-#| fig-cap: Projected number of Natural and Physical Sciences (n.f.d.) graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-nfd_grads <- future_course_leavers_science |>
-  filter(discipline == "Natural and Physical Sciences, nfd") |>
-  summarise(
-    mean = mean(Graduates),
-    lo = quantile(Graduates, prob = 0.05),
-    hi = quantile(Graduates, prob = 0.95)
-  )
-ggplot(nfd_grads) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = course_leavers_lvl4 |> filter(discipline == "Natural and Physical Sciences, nfd"), aes(y = Graduates)) +
-  labs(y = "Number of graduates",
-    title = "Forecast of Graduates",
-    subtitle = "Natural and Physical Sciences (n.f.d.)\nForecasted Years: 2024 - 2041"
-  ) +
- scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-net-migrants-nfd
-#| eval: false
-#| fig-cap: Net migration of scientists in Natural and Physical Sciences (n.f.d.) by age, 2006–2020.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-natural_and_physical_sciences__nfd |>
-  autoplot(Migrants) +
-  scale_x_continuous(breaks = seq(10,100,by=10)) +
-  labs(
-    y = "Number of net migrants",
-    title = "Estimated Net Migration",
-    subtitle = "Natural and Physical Sciences (n.f.d.)\n2006 - 2020"
-  ) +
-  geom_hline(yintercept = 0, linetype = "dashed", alpha=0.5) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```
-
-```{r}
-#| label: fig-future-nfd-2035
-#| eval: false
-#| fig-cap: Forecasted age distribution of the working population for Natural and Physical Sciences (n.f.d.) in 2025 and 2035, comparing changes over 10 years.
-Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-# 2025 and 2035
-eg_forecast <- future_natural_and_physical_sciences__nfd |>
-  filter(Year %in% c(2025, 2035)) |>
-  group_by(Age) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-
-# Overlay
-ggplot(eg_forecast) +
-    aes(x = Age, color = factor(Year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(Year)), alpha = 0.1) +
-    geom_line(aes(y = mean), size = 0.6) +
-  labs(y = "Number of working scientists",
-    title = "Forecast of Working Population",
-    subtitle = "Natural and Physical Sciences (n.f.d.)",
-      color = "Forecast Year",
-      fill = "Forecast Year"
-    ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme_classic() +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7),
-    legend.position = "top"
-  )
-```
-
-```{r}
-#| label: fig-total-future-nfd
-#| eval: false
-#| fig-cap: Forecasted total number of working scientists for Natural and Physical Sciences (n.f.d.) (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
-#| fig-height: 3.5
-#| fig-width: 5.5
-
-sum_natural_and_physical_sciences_nfd  <- natural_and_physical_sciences__nfd |>
-  as_tibble() |>
-  group_by(Year) |>
-  summarise(Working = sum(Working), .groups = "drop")
-sum_future_natural_and_physical_sciences_nfd <- future_natural_and_physical_sciences__nfd |>
-  as_tibble() |>
-  group_by(Year, .rep) |>
-  summarise(Working = sum(Working), .groups = "drop")  |>
-  group_by(Year) |>
-  summarise(
-    mean = mean(Working),
-    lo = quantile(Working, prob = 0.05),
-    hi = quantile(Working, prob = 0.95),
-    .groups = "drop"
-  )
-ggplot(sum_future_natural_and_physical_sciences_nfd) +
-    aes(x = Year) +
-    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "#c14b1444") +
-    geom_line(aes(y = mean), color = "#c14b14") +
-    geom_line(data = sum_natural_and_physical_sciences_nfd, aes(y = Working)) +
- labs(y = "Total number of working scientists") +
-  labs(
-    title = "Forecast of Total Working Population",
-    subtitle = "Natural and Physical Sciences (n.f.d.)\nForecasted Years: 2022 - 2041"
-  ) +
-  scale_x_continuous(breaks = seq(2010, 2040, by = 5)) +
-  scale_y_continuous(labels = scales::comma_format()) +
-  theme_classic()  +
-  theme(
-    plot.title = element_text(size = 10, hjust = 0.5, face = "bold"),
-    plot.subtitle = element_text(size = 9, hjust = 0.5),
-    axis.title = element_text(size = 9),
-    axis.text = element_text(size = 7),
-    legend.title = element_text(size = 9),
-    legend.text = element_text(size = 7)
-  )
-```

### 2025-04-16 age_structure_forecasts.qmd
Restructured report to not include physics as special case

@@
 
-# Introduction
+# Introduction {#sec-intro}
 
-The @AAS is dedicated to advancing Australia’s scientific knowledge by providing evidence-informed advice and advocacy to support decision-making in government.
-As part of this mission, it has launched _Australian Science, Australia’s Future: Science 2035_, an initiative assessing the capability of the national science system and its role in achieving Australia’s ambitions [@AAS2035].
-This report supports this initiative by forecasting future science workforce age structures, providing data-driven insights on how Australia’s science workforce will change over the next decade.
+In planning for the future labour market, it is necessary to forecast the age structure of the workforce, in order to enable data-driven decision-making on policies concerning universities and immigration.
+We demonstrate a statistical modelling approach to this problem, illustrated using various scientific disciplines in Australia, forecasting future workforce age structures over the next decade.
+The forecasts described have been used by the Australian Academy of Science as part of _Australian Science, Australia’s Future: Science 2035_, an initiative assessing the capability of the national science system and its role in achieving Australia’s ambitions [@AAS2035].
 
-This analysis primarily focuses on Natural and Physical Sciences as defined in the Australian Standard Classification of Education (ASCED) by the @ABSASCED (ABS).
+This analysis focuses on the Natural and Physical Sciences as defined in the Australian Standard Classification of Education (ASCED) by the @ABSASCED.
 For consistency, the report refers to ASCED’s Narrow Fields as "disciplines".
@@
 
-The report begins by outlining the [Methodology](#methodology), [Data Sources](#data-sources), and statistical techniques used to generate the forecasts.
-A [Worked Example](#physics-and-astronomy) using Physics and Astronomy illustrates the application of these methods in detail, providing a foundation for understanding the approach.
-The [Findings](#findings) section then extends this analysis to all other disciplines, focusing on comparison and contrast rather than procedural details.
-Finally, the report explores [Broader Applications](#broader-applications) beyond science, considering how these forecasting methods could be applied to other fields.
+We describe the methodology in @sec-methodology, data sources in @sec-data, and statistical techniques used to generate the forecasts.
+The results in @sec-results illustrates the application of the ideas to scientific disciplines, focusing on comparison and contrast rather than procedural details.
+Finally, we provide some discussion and conclusions in @sec-conclusion.
 The results aim to inform future workforce planning and policy decisions to support the growth of Australia’s scientific community.
 
-# Methodology {#methodology}
+# Methodology {#sec-methodology}
 
@@
 
-The population can be forecasted using a model similar to the stochastic population model of @HB08, excluding the birth process. The demographic growth-balance equation can be written as: $$
+The population can be forecasted using a model similar to the stochastic population model of @HB08, excluding the birth process. The demographic growth-balance equation can be written as:
+$$
 P_{i,x+1,t+1} = P_{i,x,t} - D_{i,x,t} - R_{i,x,t} + N_{i,x,t} + G_{i,x,t}, \quad x = 15,16,\dots
-$$ {#eq-dgb} That is, the population each year is equal to the population from the previous year having aged 1 year, minus the deaths or retirements that occurred during the previous year, plus the new graduates, plus the net migrants (which may be negative).
+$$ {#eq-dgb}
+That is, the population each year is equal to the population from the previous year having aged 1 year, minus the deaths or retirements that occurred during the previous year, plus the new graduates, plus the net migrants (which may be negative).
 The assumption is that $D_{i,x,t} + R_{i,x,t} \le P_{i,x,t}$ and $N_{i,x,t} = G_{i,x,t} = 0$ above some age threshold (say $x=100$).
@@
 
-# Data {#data-sources}
+# Data {#sec-data}
 
@@
 Data limitations include the availability of labour force participation data only for 2016 and 2021, the absence of full-time worker data outside census years, and the aggregated nature of retirement intentions data.
-These gaps are addressed using specific handling of labour force participation data, cohort interpolation methods, and smoothed disaggregation, as detailed in Sections [3.2](#labour), [3.3](#cohort), and [3.4](#smooth).
+These gaps are addressed using specific handling of labour force participation data, cohort interpolation methods, and smoothed disaggregation, as detailed in Sections -@sec-labour, -@sec-cohort, and -@sec-smooth.
 
 Another limitation is that retirement intentions data is unavailable by educational discipline, with industry-level data serving as the closest proxy.
-Since scientists work across multiple industries, this does not capture discipline-specific retirement patterns but is used in this context through methods outlined in Section [3.5](#retirement).
+Since scientists work across multiple industries, this does not capture discipline-specific retirement patterns but is used in this context through methods outlined in @sec-retirement.
 
-## Labour Force Participation {#labour}
+## Labour Force Participation {#sec-labour}
 
@@
 
-## Cohort Interpolation {#cohort}
+## Cohort Interpolation {#sec-cohort}
 
@@
 
-## Smoothed Disaggregation {#smooth}
+## Smoothed Disaggregation {#sec-smooth}
 
@@
 To estimate single-year age distributions, a monotonic cubic spline [@SHW04] is applied directly to the cumulative values of these age groups, ensuring a smooth transition between them.
-This method preserves the overall distribution while generating continuous single-year estimates, as shown in @fig-afterdisaggregation.
+This method preserves the overall distribution while generating continuous single-year estimates, as shown in @fig-retirements.
 
@@
 
-## Retirement Distribution by Age {#retirement}
+## Retirement Distribution by Age {#sec-retirement}
 
@@
 
-The demographic growth-balance equation (@eq-dgb), when rearranged, provides an estimate of net migration: $$
+The demographic growth-balance equation (@eq-dgb), when rearranged, provides an estimate of net migration:
+$$
 G_{i,x,t} = P_{i,x+1,t+1} - P_{i,x,t} + D_{i,x,t} + R_{i,x,t} - N_{i,x,t}, \quad x = 15,16,\dots
@@
 
-# Worked Example: Physics and Astronomy {#physics-and-astronomy}
+# Results {#sec-results}
 
-This section provides a detailed demonstration of the forecasting process using Physics and Astronomy as a case study.
+@tbl-disciplines lists the scientific disciplines (as per @ABSASCED Narrow Fields) included in this analysis, along with their corresponding Detailed Fields.
+This table provides essential context for understanding the specific areas classified under each discipline.
 
-The analysis begins by interpolating the working population from available data, followed by the estimation of graduate completions and calculation of net migration.
-These data points are then used to simulate multiple future scenarios, applying demographic processes of death and retirement.
-The final step is to compile these components into a projection of the age structure of scientists in Physics and Astronomy for the next 20 years.
-
-This case study establishes the approach, which is later applied across all disciplines for comparison in the [Findings](#findings) section.
+```{r}
+#| label: tbl-disciplines
+#| eval: true
+#| tbl-cap: Classification of scientific disciplines, based on the ASCED Narrow Fields of Education within the Broad Field of Natural and Physical Sciences.
+The table lists their corresponding Detailed Fields.
+"n.e.c." stands for "Not Elsewhere Classified."
+tar_read(discipline_table)
+```
 
@@
 
-To estimate the future working population accurately, historical data is required.
-The Australian Census provides such data, but it is only available every five years.
-@fig-physicists shows the population of physicists and astronomers active in the labour market as recorded in the Census for the years 2006, 2011, 2016, and 2021.
-
-Visually, the distribution for each year is positively skewed, with a long right tail.
-Over time, the distribution has shifted upward, indicating an increase in the total number of working physicists and astronomers.
+The Australian Census provide working population data every five years.
+@fig-working-population shows the age distribution of scientists active in the labour market as recorded in the Census for the years 2006, 2011, 2016, and 2021.
+There are notable differences over time, and between disciplines.
+The number of working scientists has increased over time, especially in Mathematical Sciences in the latest 2021 Census, as well as in Biological Sciences and Other Natural and Physical Sciences.
 The right tail has gradually grown heavier, reflecting an increasing proportion of older scientists, while the distribution has also become wider, indicating a broader age range in the workforce.
 
-As shown in @tbl-stats-physics, physicists and astronomers have a median age of approximately 44 years, which suggests a concentration of workers in mid-career stages.
-The 10th and 90th percentiles, representing the typical adult working age range, indicate that the 10th percentile is in the late 20s and the 90th percentile is in the early 60s.
-This age range has progressively widened from the first to the last Census.
-
-After estimating the intervening years using linear cohort interpolation [@STUPP88], the resulting population estimates are shown in @fig-physicists2.
-These interpolated values form the basis for forecasting the future working population, representing the values of $P_{i,x,t}$ for physicists and astronomers.
-The projected changes in age distribution are visible.
+The working population for years between census are estimated using linear cohort interpolation [@STUPP88], with the resulting population estimates shown in @fig-interpolated-working-population.
+These interpolated values form the basis for forecasting the future working population, representing the values of $P_{i,x,t}$.
 
 ```{r}
-#| label: fig-physicists
-#| fig-cap: The number of scientists in Physics and Astronomy active in the Australian labour market, shown by age, as recorded in the Australian Census for the years 2006, 2011, 2016, and 2021.
+#| label: fig-working-population
 #| eval: true
-tar_read(fig11)
+#| fig-cap: "Age distribution of the working population across scientific disciplines based on Census data from 2006, 2011, 2016, and 2021.
+Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age for each Census year."
+#| fig-height: 5.5
+tar_read(fig19)
 ```
@@
 ```{r}
-#| label: fig-physicists2
+#| label: fig-interpolated-working-population
 #| eval: true
-#| fig-cap: Interpolated number of scientists in Physics and Astronomy active in the Australian labour market, 2006–2021, using linear cohort interpolation.
-tar_read(fig12)
+#| fig-cap: "Age distribution of the working population across scientific disciplines, interpolated from Census data using linear cohort interpolation.
+Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age and year."
+#| fig-height: 6
+tar_read(fig20)
 ```
@@
 
-To estimate the number of new graduates entering the workforce, trends in graduate numbers from 2006 to 2023 are examined.
-As shown in @fig-physics-leavers, the number of graduates majoring in Physics and Astronomy fluctuated around 375 to 500 annually, with no consistent trend, seasonality, or cyclical pattern.
-These figures represent total graduate completions ($\sum_x N_{i,x,t}$) in Physics and Astronomy.
+@fig-grad-forecasts shows the number of total graduate completions from 2006 to 2023 ($\sum_x N_{i,x,t}$).
+A significant positive trend is observed in three disciplines: Mathematical Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences (n.f.d.).
+Note that the Y-axis scales vary across disciplines to reflect differences in the number of completions.
+
+The increase in the working population observed in the 2021 Census for Mathematical Sciences, as mentioned earlier, can be partly attributed to the sharp rise in graduate numbers between 2016 and 2021.
+This surge in graduates during that period provides insight into the corresponding growth in the working population.
 
@@
 The model is then used to generate discipline-specific forecasts, with simulations run 500 times to account for variability and generate 90% prediction intervals.
-The results, along with these intervals, are shown in @fig-future-grads-physics for Physics and Astronomy.
+The results, along with these intervals, are shown in @fig-grad-forecasts.
 
 ```{r}
-#| label: fig-physics-leavers
+#| label: fig-grad-forecasts
 #| eval: true
-#| fig-cap: Annual number of graduates in Physics and Astronomy, 2006–2023.
-tar_read(fig13)
+#| fig-cap: "Forecast number of graduates by discipline, 2024-2041, with 90% prediction intervals, based on historical data from 2006--2023."
+tar_read(fig_grad_forecasts)
 ```
 
-```{r}
-#| label: fig-future-grads-physics
-#| fig-cap: Projected number of Physics and Astronomy graduates, 2024–2041, with 90% prediction intervals, based on historical data from 2006–2023.
-#| eval: true
-tar_read(fig14)
-```
-
-Since workforce projections require not only total graduate numbers but also their age distribution, the forecasted totals (depicted in @fig-future-grads-physics) are disaggregated using the percentage distribution of graduate completions by age across all disciplines (as shown in @fig-completions2).
+Since workforce projections require not only total graduate numbers but also their age distribution, the forecasted totals (depicted in @fig-grad-forecasts) are disaggregated by age using the percentage distribution of graduate completions by age across all disciplines (as shown in @fig-completions2).
 This enables an estimation of how many graduates will enter each age group in future years, ensuring consistency with observed patterns in the broader graduate population.
@@
 Net migration ($G_{i,x,t}$) is estimated using the demographic growth-balance equation, which is rearranged to calculate the net number of migrants each year (@eq-netmigration).
-@fig-net-migrants shows the age distribution of net migration among scientists in Physics and Astronomy between 2006 and 2020.
+@fig-net-migration-disciplines shows the age distribution of net migration among scientists between 2006 and 2020.
+Emigration during the early career stage is largely driven by international students graduating and returning home.
+This negative net migration in the early career stage is a significant factor across all disciplines.
 
@@
 
+Other Natural and Physical Sciences and Natural and Physical Sciences (n.f.d.) show little to no immigration beyond this stage.
+Given their larger workforce sizes (as seen on the y-axis), these disciplines exhibit more stable net migration patterns.
+
+In contrast, core scientific disciplines, which have smaller populations, show more fluctuation in migration levels after the early career stage.
+This variability is likely due to workforce mobility, the sensitivity of estimates for smaller populations, and cohort effects, rather than reflecting actual migration dynamics.
+
 ```{r}
-#| label: fig-net-migrants
+#| label: fig-net-migration-disciplines
 #| eval: true
-#| fig-cap: Net migration of scientists in Physics and Astronomy by age, 2006–2020.
-tar_read(fig15)
+#| fig-cap: Estimated net migration by age across scientific disciplines (2006–2020). Each panel represents a different discipline, showing net migration trends across age groups.
+#| fig-height: 6
+tar_read(fig22)
 ```
@@
 2.
-**Net Migration:** Fit a separate functional data model to the age-specific migrant numbers shown in @fig-net-migrants, with ARIMA models for the coefficients.
+**Net Migration:** Fit a separate functional data model to the age-specific migrant numbers shown in @fig-net-migration-disciplines, with ARIMA models for the coefficients.
 This model simulates values of age-specific net migrant numbers in future years.
 3.
-**Graduate Numbers:** Fit an ARIMA model [@fpp3] to simulate total numbers of graduates in each future year from the numbers shown in @fig-physics-leavers.
+**Graduate Numbers:** Fit an ARIMA model [@fpp3] to simulate total numbers of graduates in each future year from the numbers shown in @fig-grad-forecasts.
 These graduate numbers will then be disaggregated by age using the age distribution shown in @fig-completions2 to estimate age-specific graduate numbers in each year.
 4.
-**Retirements:** Estimate retirements in each year by multiplying the number of people of working age in each age bracket (@fig-physicists2) by the retirement probabilities shown in @fig-retirements2.
+**Retirements:** Estimate retirements in each year by multiplying the number of people of working age in each age bracket (@fig-interpolated-working-population) by the retirement probabilities shown in @fig-retirements2.
 Fixed age-specific retirement probabilities are used.
@@
 The average of the 500 simulations provides the mean age-specific forecast, while quantiles estimate forecast uncertainty.
-@fig-future-physics-2035 presents the mean and 90% prediction intervals for 2025 and 2035.
+@fig-forecast-working-population presents the mean and 90% prediction intervals for 2025 and 2035.
 
@@
 
-Summing over age groups allows for estimating the total number of working scientists in each future year, as shown in @fig-total-future-physics.
+Summing over age groups allows for estimating the total number of working scientists in each future year, as shown in @fig-forecast-total-working-scientists.
 This highlights whether the workforce is growing, stabilising, or declining.
@@
 
-```{r}
-#| label: fig-future-physics-2035
-#| eval: true
-#| fig-cap: Forecasted age distribution of the working population for Physics and Astronomy in 2025 and 2035, comparing changes over 10 years. Shaded areas represent 90% prediction intervals.
-tar_read(fig17)
-```
-
-```{r}
-#| label: fig-total-future-physics
-#| eval: true
-#| fig-cap: Forecasted total number of working scientists for Physics and Astronomy (2022–2041), indicating the rate of change. Shaded areas represent 90% prediction intervals.
-tar_read(fig18)
-
-```
-
-# Findings: Natural and Physical Sciences {#findings}
-
-The forecasting process applied to Physics and Astronomy is now extended to all scientific disciplines.
-Rather than reiterating the methodological details, this section presents key findings, highlighting differences and comparisons across disciplines.
-The analysis follows the same structure, covering the working population, graduate completions, net migration, and forecast results based on future population simulations.
-
-@tbl-disciplines lists the scientific disciplines (ASCED Narrow Fields) included in this analysis, along with their corresponding Detailed Fields.
-This table provides essential context for understanding the specific areas classified under each discipline.
-"n.f.d." stands for "Not Further Defined," and "n.e.c." stands for "Not Elsewhere Classified."
-
-```{r}
-#| label: tbl-disciplines
-#| eval: true
-#| tbl-cap: Classification of scientific disciplines, based on the ASCED Narrow Fields of Education within the Broad Field of Natural and Physical Sciences.
-The table lists their corresponding Detailed Fields.
-tar_read(discipline_table)
-```
-
-## Working Population
-
-The age distribution of the working population across different scientific disciplines is shown in @fig-working-population.
-Similar to Physics and Astronomy, the age distributions in these disciplines are positively skewed, with a growing proportion of older workers and a widening age range.
-Moreover, the number of working scientists has increased over time, especially in Mathematical Sciences in the latest 2021 Census, as well as in Biological Sciences and Other Natural and Physical Sciences.
-While the Y-axis scales vary across disciplines to reflect differences in population sizes, the data nonetheless indicate a substantial shift in working populations over time within these disciplines.
-
-```{r}
-#| label: fig-working-population
-#| eval: true
-#| fig-cap: "Age distribution of the working population across scientific disciplines based on Census data from 2006, 2011, 2016, and 2021.
-Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age for each Census year."
-#| fig-height: 5.5
-tar_read(fig19)
-```
-
-In terms of age structure, most disciplines have median ages in the mid-forties.
-However, a few disciplines show lower median ages, including Biological Sciences with an approximate median age of 40, Other Natural and Physical Sciences at 34, and Natural and Physical Sciences (n.f.d.) at 39.
-A table summarising the statistics for each discipline is provided in @tbl-disciplines-stats in the appendix for further reference.
-
-Additionally, the graph with interpolated data, shown in @fig-interpolated-working-population, provides a smoother representation of trends and highlights changes within each discipline.
-
-```{r}
-#| label: fig-interpolated-working-population
-#| eval: true
-#| fig-cap: "Age distribution of the working population across scientific disciplines, interpolated from Census data between 2006 and 2021.
-Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age and year."
-#| fig-height: 6
-tar_read(fig20)
-```
-
-## Graduate Completions
-
-@fig-graduates-disciplines shows the number of graduates across disciplines from 2006 to 2023.
-A significant positive trend is observed in three disciplines: Mathematical Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences (n.f.d.).
-Note that the Y-axis scales vary across disciplines to reflect differences in the number of completions.
-
-```{r}
-#| label: fig-graduates-disciplines
-#| eval: true
-#| fig-cap: "Number of graduates across scientific disciplines from 2006 to 2023. Each panel represents a different discipline, showing the trend in graduate numbers over time."
-tar_read(fig21)
-```
-
-```{r}
-#| label: fig-grad-forecasts
-#| eval: true
-#| fig-cap: "Forecast number of graduates by discipline, 2024-2041, with 90% prediction intervals, based on historical data from 2006--2023."
-tar_read(fig_grad_forecasts)
-```
-
-The increase in the working population observed in the 2021 Census for Mathematical Sciences, as mentioned earlier, can be partly attributed to the sharp rise in graduate numbers between 2016 and 2021.
-This surge in graduates during that period provides insight into the corresponding growth in the working population.
-
-Similarly, disciplines such as Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences (n.f.d.) were characterised by lower median ages in their working populations.
-The higher graduate numbers in these fields may contribute to this trend, as younger graduates naturally lower the median age of the workforce.
-
-As with the example in Physics and Astronomy, future graduate numbers have been forecasted for each discipline.
-The corresponding graphs for these forecasts are included in the appendix (see @fig-future-grads-math, @fig-future-grads-chem, @fig-future-grads-earth, @fig-future-grads-bio, @fig-future-grads-other, and @fig-future-grads-nfd).
-
-## Net Migration
-
-@fig-net-migration-disciplines shows the age distribution of net migration across disciplines.
-Emigration during the early career stage is largely driven by international students graduating and returning home.
-This negative net migration in the early career stage is a significant factor across all disciplines.
-
-Other Natural and Physical Sciences and Natural and Physical Sciences (n.f.d.) show little to no immigration beyond this stage.
-Given their larger workforce sizes (as seen on the y-axis), these disciplines exhibit more stable net migration patterns.
-
-In contrast, core scientific disciplines, which have smaller populations, show more fluctuation in migration levels after the early career stage.
-This variability is likely due to workforce mobility, the sensitivity of estimates for smaller populations, and cohort effects, rather than reflecting actual migration dynamics.
-
-```{r}
-#| label: fig-net-migration-disciplines
-#| eval: true
-#| fig-cap: Estimated net migration by age across scientific disciplines (2006–2020). Each panel represents a different discipline, showing net migration trends across age groups.
-#| fig-height: 6
-tar_read(fig22)
-```
-
-## Forecast Results
-
 After 500 simulations of the future population for each discipline, the projections ten years apart (2025 and 2035) shown in @fig-forecast-working-population provide a basis for comparing estimates of the current and future workforce.
@@
 The projections indicate wider prediction intervals for younger age groups due to uncertainty in future graduate numbers, while mid-to-late career estimates primarily reflect the aging of existing cohorts.
-Across disciplines, the typical working population spans from the mid-to-late 20s (10th percentile) to the mid-50s and early 60s (90th percentile), as shown in @tbl-disciplines-stats in the appendix.
+Across disciplines, the typical working population spans from the mid-to-late 20s (10th percentile) to the mid-50s and early 60s (90th percentile).
 Since retirements increase after the late 50s, workforce participation beyond 60 serves as a benchmark for identifying trends in delayed retirement and extended career duration.
@@
 #| eval: true
-#| fig-cap: "Projected total number of working scientists across scientific disciplines from 2022 to 2041.
+#| fig-cap: "Forecasted total number of working scientists across scientific disciplines from 2022 to 2041.
 The shaded region represents the 90% prediction interval, the coloured line indicates the mean estimate, and the black line represents historical data."
@@
 
-# Conclusion
+# Conclusion {#sec-conclusion}
 
@@
 This analysis contributes to the Australian Academy of Science’s initiative _Australian Science, Australia’s Future: Science 2035_ by identifying shifts in the workforce, helping anticipate future demand for science capabilities, and highlighting potential workforce gaps as aging and retirement reshape workforce dynamics.
+
+# Acknowledgements
+
+We thank Alexandra Lucchetti from the Australian Academy of Science for sourcing the data required for this project, and for helpful feedback on earlier versions of this report.

### 2025-04-16 _targets.R

@@ -114,7 +114,7 @@ list(
     )
   ),
 
-  # Physics
+  # # Physics
   tar_target(
     physics,
     census4_1 |>
@@ -139,14 +139,14 @@ list(
       filter(discipline == "Physics and Astronomy") |>
       select(-discipline)
   ),
-  tar_target(fig11, make_fig2(physics, "Physics and Astronomy")),
-  tar_target(fig12, make_fig3(physics, "Physics and Astronomy")),
-  tar_target(fig13, make_fig13(physics_leavers, "Physics and Astronomy")),
-  tar_target(fig14, make_fig14(future_physics_leavers, physics_leavers)),
-  tar_target(fig15, make_fig15(physics)),
+  # tar_target(fig11, make_fig2(physics, "Physics and Astronomy")),
+  # tar_target(fig12, make_fig3(physics, "Physics and Astronomy")),
+  # tar_target(fig13, make_fig13(physics_leavers, "Physics and Astronomy")),
+  # tar_target(fig14, make_fig14(future_physics_leavers, physics_leavers)),
+  # tar_target(fig15, make_fig15(physics)),
   tar_target(fig16, make_fig16(physics, future_physics)),
-  tar_target(fig17, make_fig17(future_physics)),
-  tar_target(fig18, make_fig18(physics, future_physics)),
+  # tar_target(fig17, make_fig17(future_physics)),
+  # tar_target(fig18, make_fig18(physics, future_physics)),
 
   # Disciplines combined
   tar_target(fig19, make_fig19(census4_1)),

### 2025-04-16 age_structure_forecasts.qmd
Added some background references

@@
 
-In planning for the future labour market, it is necessary to forecast the age structure of the workforce, in order to enable data-driven decision-making on policies concerning universities and immigration.
+In planning for the future labour market, it is necessary to forecast the age structure of the workforce, in order to enable informed decision-making on policies concerning universities and immigration.
 We demonstrate a statistical modelling approach to this problem, illustrated using various scientific disciplines in Australia, forecasting future workforce age structures over the next decade.
 The forecasts described have been used by the Australian Academy of Science as part of _Australian Science, Australia’s Future: Science 2035_, an initiative assessing the capability of the national science system and its role in achieving Australia’s ambitions [@AAS2035].
+
+The economic implications of workforce age structure shifts are well-documented [e.g., @Bloom2007], affecting productivity, pensions and superannuation, and skill shortages [@PC2013; @OECD2019a; @OECD2019b; @pension].
+
+Our approach builds on functional data models, introduced to demographic modelling by @HU07.
+They combined nonparametric smoothing and functional principal components for age-specific demographic rates.
+These models were then used by @HB08 for mortality, fertility, and migration rates, providing stochastic data generating processes for the components of demographic balance equations.
+These separate component models were then simulated to form future sample paths, leading to age- and sex-specific stochastic population forecasts.
+
+This framework is adaptable to workforce dynamics by redefining the demographic components, replacing fertility with workforce entry.
+The latter functions more like a migration process than a birth process because graduates can enter the workforce at any age.
 

### 2025-04-16 age_structure_forecasts.qmd
Formatting

@@
 
-Retirement data is sourced from the *Retirement and Retirement Intentions* dataset (Catalogue 6238) for the 2022–2023 financial year [@ABS6238].
+Retirement data is sourced from the *Retirement and Retirement Intentions* dataset (Catalogue 6238) for the 2022--2023 financial year [@ABS6238].
 It provides insights into expected retirement ages for workers in age groups ranging from 45 to 70 across various industries.
@@
 Younger and older age groups within some disciplines were particularly affected by this volatility, especially when sample sizes were small.
-For example, in a group of five 15–19-year-olds, a single individual's employment status change could significantly shift the participation rate.
+For example, in a group of five 15--19-year-olds, a single individual's employment status change could significantly shift the participation rate.
 Similarly, fluctuations in smaller cohorts of older scientists impacted participation rates.
@@
 #| eval: true
-#| fig-cap: Interpolated number of scientists in Australia, 2006–2021, using linear cohort interpolation.
+#| fig-cap: Interpolated number of scientists in Australia, 2006--2021, using linear cohort interpolation.
 tar_read(fig3)
@@
 #| eval: true
-#| fig-cap: Estimated net migration by age across scientific disciplines (2006–2020). Each panel represents a different discipline, showing net migration trends across age groups.
+#| fig-cap: Estimated net migration by age across scientific disciplines (2006--2020). Each panel represents a different discipline, showing net migration trends across age groups.
 #| fig-height: 6
@@
 
--   **Physics and Astronomy** *(Aging Workforce):* The 35–45 age group shows a higher average than the previous 2025 cohort.
+-   **Physics and Astronomy** *(Aging Workforce):* The 35--45 age group shows a higher average than the previous 2025 cohort.
 There is a growing number of scientists aged 45 to 60, and more individuals aged 60+ are remaining in the workforce longer.
@@
 -   **Other Natural and Physical Sciences** *(Expansive Workforce):* Workforce growth is strong across ages 30 to 70, characteristic of an expanding workforce.
--   **Natural and Physical Sciences (n.f.d.)** *(Aging Workforce):* Growth is primarily concentrated in the 55–70 age range, indicating delayed retirement and an aging workforce.
+-   **Natural and Physical Sciences (n.f.d.)** *(Aging Workforce):* Growth is primarily concentrated in the 55--70 age range, indicating delayed retirement and an aging workforce.
 

### 2025-04-18 _targets.R
Added talk

@@ -147,5 +147,11 @@ list(
     "age_structure_forecasts.qmd",
     output_file = "age_structure_forecasts.pdf",
     extra_files = c("refs.bib", "preamble.tex")
+  ),
+  tar_quarto(
+    talk,
+    "age_structure_talk.qmd",
+    output_file = "age_structure_talk.pdf",
+    extra_files = c("header.tex")
   )
 )

### 2025-04-18 age_structure_forecasts.qmd
Compiling again

@@
 ---
-title: "The future age structure of scientific disciplines"
+title: "Forecasting the age structure of the scientific workforce in Australia"
 author:
@@
 
-The report forecasts the number of individuals in each one-year age group who are active in the workforce and hold a bachelor’s degree or higher in the following scientific disciplines: Physics and Astronomy, Mathematical Sciences, Chemical Sciences, Earth Sciences, Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences not further defined (n.f.d.).
+We forecast the number of individuals in each one-year age group who are active in the workforce and hold a bachelor’s degree or higher in the following scientific disciplines: Physics and Astronomy, Mathematical Sciences, Chemical Sciences, Earth Sciences, Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences not further defined (n.f.d.).
 

### 2025-04-18 R/census_figs.R
Updated figs for talk

@@ -21,10 +21,11 @@ make_fig2 <- function(census, subtitle) {
 make_fig3 <- function(census, subtitle) {
   census |>
     autoplot(working) +
-    labs(y = "Number of active scientists") +
     labs(
+      x = "Age",
+      y = "Number of active scientists",
       title = "Interpolated Working Population",
-      subtitle = paste0(subtitle, "\n2006 - 2021")
+      subtitle = paste0(subtitle, ": 2006 - 2021")
     ) +
     scale_x_continuous(breaks = seq(20, 100, by = 10))
 }

### 2025-04-18 R/labour_force_fig.R

@@ -1,29 +1,16 @@
 make_fig1 <- function(census_science) {
   cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF", "#000000")
-  names(cols) <- c(unique(census_science$year), "Average")
-
-  census_science <- census_science |>
-    mutate(
-      age_group = forcats::fct_relevel(age_group, "100+", after = Inf),
-      year = factor(year, levels = c(2006, 2011, 2016, 2021))
-    )
 
   census_science |>
-    filter(year %in% c("2016", "2021")) |>
-    ggplot(
-      aes(
-        x = as.numeric(gsub("\\+", "", age_group)),
-        y = participation,
-        shape = as.factor(year),
-        color = as.factor(year)
-      )
-    ) +
+    filter(year %in% c(2016, 2021)) |>
+    ggplot() +
+    aes(x = age, y = participation, color = as.factor(year)) +
     geom_point(size = 1.5) +
-    geom_line(aes(y = .smooth, color = "black")) +
+    geom_line(aes(y = .smooth), color = "black") +
     labs(
       title = "Labour Force Participation",
       subtitle = "Natural and Physical Sciences",
-      x = "One-year age groups",
+      x = "Age",
       y = "Participation rate",
       shape = "Census Year",
       color = "Census Year"

### 2025-04-18 R/retirement_figs.R

@@ -20,9 +20,9 @@ make_fig6 <- function(retirements, var) {
     aes(x = age, y = {{ var }}) +
     geom_line() +
     labs(
+      x = "Age",
       y = "Probability of retirement",
-      title = "Probability of Retirement",
-      subtitle = "Professional, scientific and technical services\n2022–23 Financial Year"
+      title = "Probability of Retirement for Scientists: 2022–23"
     ) +
     scale_x_continuous(breaks = seq(40, 100, by = 10))
 }

### 2025-04-23 _targets.R
Reorganized slides

@@ -132,6 +132,7 @@ list(
   tar_target(fig19, make_fig19(census4_1)),
   tar_target(fig20, make_fig20(census4_1)),
   tar_target(fig21, make_fig21(course_leavers)),
+  tar_target(fig21b, make_fig21(course_leavers, combine = TRUE)),
   tar_target(fig22, make_fig22(census4_1)),
   tar_target(fig23, make_fig23(future_pop_science)),
   tar_target(fig24, make_fig24(census4_1, future_pop_science)),
@@ -152,6 +153,6 @@ list(
     talk,
     "age_structure_talk.qmd",
     output_file = "age_structure_talk.pdf",
-    extra_files = c("header.tex")
+    extra_files = c("header.tex", "before-title.tex")
   )
 )

### 2025-04-24 R/census_figs.R
Figures of components

@@ -1,31 +1,54 @@
-make_fig2 <- function(census, subtitle) {
-  years <- seq(2006, 2021, by = 5)
-  cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF")
-  names(cols) <- years
-  census |>
+make_pop_fig <- function(
+  census,
+  subtitle,
+  interpolation = FALSE,
+  highlight_census = FALSE
+) {
+  p <- census |>
     as_tibble() |>
-    filter(year %in% years) |>
-    mutate(Year = factor(year, levels = rev(years))) |>
     ggplot() +
-    aes(x = age, y = working, color = Year, group = Year) +
-    geom_line() +
-    labs(y = "Number of active scientists") +
-    scale_color_manual(values = cols, name = "Census Year") +
-    labs(
-      title = "Working Population",
-      subtitle = subtitle
+    aes(x = age, y = working, color = year, group = year) +
+    geom_line(
+      data = census |> filter(year %in% seq(2006, 2021, by = 5)),
+      linewidth = 0.5 + 0.5 * highlight_census
     ) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10))
-}
-
-make_fig3 <- function(census, subtitle) {
-  census |>
-    autoplot(working) +
+    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+    scale_color_gradientn(colours = rainbow(10)) +
     labs(
       x = "Age",
       y = "Number of active scientists",
-      title = "Interpolated Working Population",
-      subtitle = paste0(subtitle, ": 2006 – 2021")
-    ) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10))
+      title = paste("Working Population:", subtitle, "(2006 – 2021)")
+    )
+  if (interpolation) {
+    p <- p +
+      geom_line(
+        data = census |> filter(!year %in% seq(2006, 2021, by = 5)),
+        linewidth = 0.5
+      )
+  }
+  p
+}
+
+make_component_fig <- function(census, variable) {
+  var <- as.character(substitute(variable))
+  minyear <- min(census$year)
+  maxyear <- max(census$year)
+  census |>
+    as_tibble() |>
+    ggplot() +
+    aes(x = age, y = {{ variable }}, color = year, group = year) +
+    geom_line() +
+    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+    scale_color_gradientn(colours = rainbow(10)) +
+    labs(
[…]

### 2025-04-24 R/fig8.R

@@ -5,8 +5,7 @@ make_fig8 <- function(death_prob) {
     labs(
       y = "Probability of death",
       x = "Age",
-      title = "Australian Death Probabilities",
-      subtitle = "1971 – 2021"
+      title = "Probability of death for Australians (1971 – 2021)",
     ) +
     scale_x_continuous(breaks = seq(0, 100, by = 10))
 }

### 2025-04-24 R/fig9.R

@@ -20,10 +20,10 @@ make_fig10 <- function(ave_completions) {
     ggplot() +
     aes(x = age, pc) +
     geom_line() +
-    labs(y = "Percentage of graduates") +
     labs(
-      title = "Graduate Completions by Age",
-      subtitle = "Averaged over 2006 – 2023"
+      x = "Age",
+      y = "Percentage of graduates",
+      title = "Average graduate completions by age (2006 – 2023)"
     ) +
     scale_x_continuous(breaks = seq(20, 100, by = 10)) +
     scale_y_continuous(labels = scales::percent_format(scale = 1))

### 2025-04-24 R/labour_force_fig.R

@@ -8,8 +8,7 @@ make_fig1 <- function(census_science) {
     geom_point(size = 1.5) +
     geom_line(aes(y = .smooth), color = "black") +
     labs(
-      title = "Labour Force Participation",
-      subtitle = "Natural and Physical Sciences",
+      title = "Labour Force Participation: Natural and Physical Sciences",
       x = "Age",
       y = "Participation rate",
       shape = "Census Year",

### 2025-04-24 R/retirement_figs.R

@@ -22,7 +22,7 @@ make_fig6 <- function(retirements, var) {
     labs(
       x = "Age",
       y = "Probability of retirement",
-      title = "Probability of Retirement for Scientists: 2022 – 23"
+      title = "Probability of retirement for Australian scientists (2022 – 23)"
     ) +
     scale_x_continuous(breaks = seq(40, 100, by = 10))
 }

### 2025-04-24 _targets.R

@@ -80,8 +80,12 @@ list(
     )
   ),
   tar_target(fig1, make_fig1(census2)),
-  tar_target(fig2, make_fig2(census2_1, "Natural and Physical Sciences")),
-  tar_target(fig3, make_fig3(census2_1, "Natural and Physical Sciences")),
+  tar_target(fig3a, make_pop_fig(census2_1, "Natural and Physical Sciences", FALSE, TRUE)),
+  tar_target(fig3b, make_pop_fig(census2_1, "Natural and Physical Sciences", TRUE, TRUE)),
+  tar_target(fig_deaths, make_component_fig(census2_1, deaths)),
+  tar_target(fig_retirements, make_component_fig(census2_1, retirees)),
+  tar_target(fig_graduates, make_component_fig(census2_1, graduates)),
+  tar_target(fig_mig, make_component_fig(census2_1, migrants)),
 
   # Census 4 digit
   tar_target(census4, read_census(science_file4)),

### 2025-04-28 R/census_figs.R
Simplifying

@@ -4,6 +4,11 @@ make_pop_fig <- function(
   interpolation = FALSE,
   highlight_census = FALSE
 ) {
+  if(!interpolation) {
+    census <- census |>
+      as_tibble() |>
+      mutate(year = factor(year, levels = rev(seq(2006, 2021, by = 5))))
+  }
   p <- census |>
     as_tibble() |>
     ggplot() +
@@ -13,7 +18,6 @@ make_pop_fig <- function(
       linewidth = 0.5 + 0.5 * highlight_census
     ) +
     scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    scale_color_gradientn(colours = rainbow(10)) +
     labs(
       x = "Age",
       y = "Number of active scientists",
@@ -24,7 +28,13 @@ make_pop_fig <- function(
       geom_line(
         data = census |> filter(!year %in% seq(2006, 2021, by = 5)),
         linewidth = 0.5
-      )
+      ) +
+        scale_color_gradientn(colours = rainbow(10))
+  } else {
+    cols <- c("#ff0000", "#32ff00", "#0065ff", "#ff0099")
+    names(cols) <- seq(2006, 2021, by = 5)
+    p <- p +
+      scale_color_manual(values = cols)
   }
   p
 }

### 2025-04-28 R/fig8.R

@@ -3,7 +3,7 @@ make_fig8 <- function(death_prob) {
     autoplot(death_prob) +
     scale_y_log10(labels = scales::label_number()) +
     labs(
-      y = "Probability of death",
+      y = latex2exp::TeX("Probability of death ($m_{x,t}$)"),
       x = "Age",
       title = "Probability of death for Australians (1971 – 2021)",
     ) +

### 2025-04-28 R/retirement_figs.R

@@ -15,13 +15,12 @@ make_fig4 <- function(retirements) {
 
 make_fig6 <- function(retirements, var) {
   retirements |>
-    filter(age < 100) |>
     ggplot() +
     aes(x = age, y = {{ var }}) +
     geom_line() +
     labs(
       x = "Age",
-      y = "Probability of retirement",
+      y = latex2exp::TeX("Probability of retirement ($r_{x,t}$)"),
       title = "Probability of retirement for Australian scientists (2022 – 23)"
     ) +
     scale_x_continuous(breaks = seq(40, 100, by = 10))

### 2025-04-28 R/retirements.R

@@ -61,7 +61,7 @@ single_age_retirements <- function(retirement_data, death_prob) {
       population = 100 * population / mean(population),
       dx = (pc / 100) * population,
       mx = dx / population,
-      qx = if_else(age == max(age), 1, mx / (1 + 0.5 * mx)),
+      qx = mx / (1 + 0.5 * mx),
       #qx = make_monotonic(qx),
       #qx = if_else(death_prob + qx > 1, 1 - death_prob, qx)
     ) |>

### 2025-04-29 R/census_figs.R
Big update to align with final modelling choices

@@ -41,6 +41,11 @@ make_pop_fig <- function(
 
 make_component_fig <- function(census, variable) {
   var <- as.character(substitute(variable))
+  if(var == "remainder") {
+    ylab = "Remainder"
+  } else {
+    ylab = paste("Estimated number of", var)
+  }
   minyear <- min(census$year)
   maxyear <- max(census$year)
   census |>
@@ -52,7 +57,7 @@ make_component_fig <- function(census, variable) {
     scale_color_gradientn(colours = rainbow(10)) +
     labs(
       x = "Age",
-      y = paste("Estimated number of", var),
+      y = ylab,
       title = paste0(
         "Natural and Physical Sciences (",
         minyear,

### 2025-04-29 R/fig8.R

@@ -1,11 +1,0 @@
-make_fig8 <- function(death_prob) {
-  death_prob |>
-    autoplot(death_prob) +
-    scale_y_log10(labels = scales::label_number()) +
-    labs(
-      y = latex2exp::TeX("Probability of death ($m_{x,t}$)"),
-      x = "Age",
-      title = "Probability of death for Australians (1971 – 2021)",
-    ) +
-    scale_x_continuous(breaks = seq(0, 100, by = 10))
-}

### 2025-04-29 R/fig9.R

@@ -1,43 +1,0 @@
-make_fig9 <- function(completions) {
-  completions |>
-    ggplot() +
-    aes(x = age, y = pc, colour = year, group = year) +
-    geom_line() +
-    scale_color_gradientn(colours = rainbow(10)[1:8]) +
-    labs(
-      y = "Percentage of graduates",
-      title = "Graduate Completions by Year and Age",
-      subtitle = "2006 - 2023"
-    ) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    scale_y_continuous(
-      labels = scales::percent_format(scale = 1)
-    )
-}
-
-make_fig10 <- function(ave_completions) {
-  ave_completions |>
-    ggplot() +
-    aes(x = age, pc) +
-    geom_line() +
-    labs(
-      x = "Age",
-      y = "Percentage of graduates",
-      title = "Average graduate completions by age (2006 – 2023)"
-    ) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    scale_y_continuous(labels = scales::percent_format(scale = 1))
-}
-
-make_table2 <- function(ave_completions) {
-  ave_completions |>
-    filter(age >= 20 & age <= 25) |>
-    mutate(pc = paste0(round(pc, 2), "%")) |>
-    select(age, pc) |>
-    kable(col.names = c("Age", "Percentage of Graduates"), align = "c") |>
-    add_header_above(
-      c("Percentage of Graduates Ages 20-25" = 2),
-      bold = TRUE
-    ) |>
-    kable_styling(latex_options = c("striped"))
-}

### 2025-04-29 R/functions.R

@@ -195,6 +195,10 @@ add_migrants <- function(df, graduates, completions, retirements, mortality) {
     select(-lead_working) |>
     as_vital(index = year, key = age, .age = "age")
 
+  # Rename migrants as remainder
+  P <- P |>
+    rename(remainder = migrants)
+
   # Return complete data
   return(P)
 }

### 2025-04-29 R/graduates.R

@@ -129,3 +129,36 @@ make_completions_ave <- function(completions) {
 
   return(ave_completions)
 }
+
+make_fig_completions <- function(completions, average = FALSE) {
+  p <- ggplot(completions)
+  if(average) {
+    p <- p + aes(x = age, y = pc) +
+      labs(title = "Average graduate completions by age (2006 – 2023)")
+  } else {
+    p <- p + aes(x = age, y = pc, colour = year, group = year) +
+    scale_color_gradientn(colours = rainbow(10)[1:8]) +
+      labs(title = "Graduate completions by year and age (2006 – 2023)")
+  }
+  p +
+    geom_line()  +
+    labs(
+      x = "Age",
+      y = "Percentage of graduates",
+    ) +
+    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+    scale_y_continuous(labels = scales::percent_format(scale = 1))
+}
+
+make_table2 <- function(ave_completions) {
+  ave_completions |>
+    filter(age >= 20 & age <= 25) |>
+    mutate(pc = paste0(round(pc, 2), "%")) |>
+    select(age, pc) |>
+    kable(col.names = c("Age", "Percentage of Graduates"), align = "c") |>
+    add_header_above(
+      c("Percentage of Graduates Ages 20-25" = 2),
+      bold = TRUE
+    ) |>
+    kable_styling(latex_options = c("striped"))
+}

### 2025-04-29 R/mortality.R

@@ -2,7 +2,7 @@
 
 read_mortality <- function(mx_path, ex_path) {
   read_hmd_files(c(mx_path, ex_path)) |>
-    filter(Sex == "Total", Year > 1970) |>
+    filter(Sex == "Total", Year >= 1970) |>
     collapse_ages() |>
     suppressWarnings() |>
     select(
@@ -26,4 +26,18 @@ compute_death_prob <- function(mortality) {
       by = c("year", "age")
     ) |>
     as_vital(index = year, key = age, .age = "age", populaton = "exposures")
+}
+
+
+# Graph showing the probability of death by age over time
+make_fig_mxt <- function(death_prob) {
+  death_prob |>
+    autoplot(death_prob) +
+    scale_y_log10(labels = scales::label_number()) +
+    labs(
+      y = latex2exp::TeX("Probability of death ($m_{x,t}$)"),
+      x = "Age",
+      title = "Probability of death for Australians (1971 – 2021)",
+    ) +
+    scale_x_continuous(breaks = seq(0, 100, by = 10))
 }

### 2025-04-29 R/retirements.R

@@ -69,3 +69,31 @@ single_age_retirements <- function(retirement_data, death_prob) {
 
   return(retirement)
 }
+
+
+make_fig_r <- function(retirements) {
+  ggplot(retirements, aes(x = age_group, y = pc)) +
+    geom_col() +
+    labs(
+      title = "Retirement Intentions of Australian scientists (2022 – 23)",
+      x = "Age group",
+      y = "Percentage of retirement intentions"
+    ) +
+    scale_y_continuous(labels = scales::percent_format(scale = 1)) +
+    theme(
+      legend.position = "none"
+    )
+}
+
+make_fig_rx <- function(retirements, var) {
+  retirements |>
+    ggplot() +
+    aes(x = age, y = {{ var }}) +
+    geom_line() +
+    labs(
+      x = "Age",
+      y = latex2exp::TeX("Probability of retirement ($r_{x,t}$)"),
+      title = "Probability of retirement for Australian scientists (2022 – 23)"
+    ) +
+    scale_x_continuous(breaks = seq(40, 100, by = 10))
+}

### 2025-04-29 _targets.R

@@ -24,7 +24,7 @@ list(
   tar_target(ex_file, here::here("data/Exposures_1x1.txt"), format = "file"),
   tar_target(mortality, read_mortality(mx_file, ex_file)),
   tar_target(aus_death_prob, compute_death_prob(mortality)),
-  tar_target(fig8, make_fig8(aus_death_prob)),
+  tar_target(fig_mxt, make_fig_mxt(aus_death_prob)),
 
   # Retirement data
   tar_target(
@@ -36,25 +36,11 @@ list(
     retirements,
     single_age_retirements(retirement_data, aus_death_prob)
   ),
-  tar_target(fig4, make_fig4(retirement_data)),
-  tar_target(fig6, make_fig6(retirements, pc)),
-  tar_target(fig7, make_fig6(retirements, retire_prob)),
+  tar_target(fig_r, make_fig_r(retirement_data)),
+  tar_target(fig_rx, make_fig_rx(retirements, pc)),
+  tar_target(fig_rx2, make_fig_rx(retirements, retire_prob)),
 
   # Graduates
-  tar_target(
-    grad_file,
-    here::here(
-      "data/Award course completions for all students by age group and course level.xlsx"
-    )
-  ),
-  tar_target(completions, read_completions(grad_file)),
-  tar_target(completions_step, make_completions_step(completions)),
-  tar_target(ave_completions, make_completions_ave(completions)),
-  tar_target(fig9, make_fig9(completions_step)),
-  tar_target(fig10, make_fig10(ave_completions)),
-  tar_target(tab2, make_table2(ave_completions)),
-
-  # Course leavers
   tar_target(
     leavers_file,
     here::here("data/Course completions - 2006 to 2023 - Totals.xlsx")
@@ -65,6 +51,24 @@ list(
     future_course_leavers_science,
     simulate_future_graduates(course_leavers, arma_coef_science)
   ),
+
+  # Graduates by age
+  tar_target(
+    grad_file,
+    here::here(
+      "data/Award course completions for all students by age group and course level.xlsx"
+    )
+  ),
+  tar_target(completions, read_completions(grad_file)),
+  tar_target(completions_step, make_completions_step(completions)),
+  tar_target(ave_completions, make_completions_ave(completions)),
+  tar_target(fig_completions, make_fig_completions(completions_step)),
+  tar_target(
[…]

### 2025-04-30 R/course_leavers.R
Working on component forecast graphs

@@ -21,3 +21,12 @@ read_course_leavers <- function(file) {
     group_by(year, discipline) |>
     summarise(graduates = sum(graduates), .groups = "drop")
 }
+
+# Level 2
+
+total_sci_grads <- function(course_leavers) {
+  course_leavers |>
+    group_by(year) |>
+    summarise(graduates = sum(graduates), .groups = "drop") |>
+    as_tsibble(index = year)
+}

### 2025-04-30 R/functions.R

@@ -176,7 +176,7 @@ add_migrants <- function(df, graduates, completions, retirements, mortality) {
     mutate(
       retire_prob = if_else(is.na(retire_prob), 0, retire_prob),
       retirees = retire_prob * working,
-      deaths = mortality * working
+      deaths = qx * working
     ) |>
     select(year, age, working, graduates, retirees, deaths)
   # Compute migrants
@@ -222,18 +222,18 @@ forecast_pop_discipline <- function(
   # (since we can't compute them using following year)
   fit_migrants <- df |>
     filter(year < last_yr, !is.na(graduates)) |>
-    model(fdm = FDM(migrants))
+    model(fdm = FDM(remainder))
   last_yr_migrants <- fit_migrants |>
     forecast(h = 1) |>
     as_tibble() |>
-    select(-migrants, -.model) |>
-    rename(migrants = .mean)
+    select(-remainder, -.model) |>
+    rename(remainder = .mean)
   # Add migrants into last year
   population <- bind_rows(
     df |> filter(year < last_yr),
     df |>
       filter(year == last_yr) |>
-      select(-migrants) |>
+      select(-remainder) |>
       left_join(
         last_yr_migrants,
         by = c("age", "year")
@@ -242,7 +242,7 @@ forecast_pop_discipline <- function(
 
   # Forecast mortality rates
   future_death_prob <- mortality |>
-    model(fdm = FDM(log(mortality))) |>
+    model(fdm = FDM(log(qx))) |>
     generate(h = h, times = nsim) |>
     rename(mortality = .sim) |>
     select(-.model)
@@ -251,7 +251,7 @@ forecast_pop_discipline <- function(
   future_migrants <- fit_migrants |>
     generate(h = h + 1, times = nsim) |>
     filter(year > last_yr) |>
-    rename(migrants = .sim) |>
+    rename(remainder = .sim) |>
     select(-.model)
 
   # Simulate future graduate numbers
@@ -295,7 +295,7 @@ forecast_pop_discipline <- function(
     transmute(
       age = age + 1,
       year = year + 1,
-      working = working - deaths - retirees + graduates + migrants,
+      working = working - deaths - retirees + graduates + remainder,
     ) |>
     filter(age <= 100) |>
     bind_rows(
@@ -327,7 +327,7 @@ forecast_pop_discipline <- function(
         deaths = working * mortality,
         retirees = working * retire_prob,
[…]

### 2025-04-30 R/mortality.R

@@ -11,7 +11,7 @@ read_mortality <- function(mx_path, ex_path) {
       mortality = Mortality,
       exposures = Exposures
     ) |>
-    as_vital(index = year, key = age, .age = "age", populaton = "exposures")
+    as_vital(index = year, key = age, .age = "age", population = "exposures")
 }
 
 # Compute lifetable to convert mortality rates to probabilities
@@ -19,8 +19,8 @@ read_mortality <- function(mx_path, ex_path) {
 compute_death_prob <- function(mortality) {
   life_table(mortality) |>
     smooth_mortality(qx, k = 50) |>
-    mutate(mortality = c(.smooth)) |>
-    select(year, age, mortality) |>
+    mutate(qx = c(.smooth)) |>
+    select(year, age, qx) |>
     left_join(
       mortality |> select(year, age, population = exposures),
       by = c("year", "age")
@@ -32,12 +32,46 @@ compute_death_prob <- function(mortality) {
 # Graph showing the probability of death by age over time
 make_fig_mxt <- function(death_prob) {
   death_prob |>
-    autoplot(mortality) +
+    autoplot(qx) +
     scale_y_log10(labels = scales::label_number()) +
     labs(
-      y = latex2exp::TeX("Probability of death ($m_{x,t}$)"),
+      y = latex2exp::TeX("Probability of death"), # ($m_{x,t}$)"),
       x = "Age",
       title = "Probability of death for Australians (1971 – 2021)",
     ) +
     scale_x_continuous(breaks = seq(0, 100, by = 10))
+}
+
+# Adaptation of vital:::autoplot.FDM to add in future sample paths
+make_future_mxt_fig <- function(object, show_order = 2) {
+  obj_time <- time_components(object)
+  obj_x <- age_components(object)
+
+  meanvar <- "mean"
+  tmp <- colnames(obj_time)
+  timevar <- tmp[grepl("beta", tmp)]
+  tmp <- colnames(obj_x)
+  agevar <- tmp[grepl("phi", tmp)]
+  index <- tsibble::index_var(obj_time)
+  keys <- head(colnames(object), -1)
+
+  # Set up list of plots
+  p <- list()
+  p[[1]] <- vital:::age_plot(obj_x, meanvar, keys) + ggplot2::ylab(meanvar)
+  for (i in seq(show_order)) {
[…]

### 2025-04-30 R/retirements.R

@@ -75,7 +75,7 @@ make_fig_r <- function(retirements) {
   ggplot(retirements, aes(x = age_group, y = pc)) +
     geom_col() +
     labs(
-      title = "Retirement Intentions of Australian scientists (2022 – 23)",
+      title = "Retirement intentions of Australian scientists (2022 – 23)",
       x = "Age group",
       y = "Percentage of retirement intentions"
     ) +
@@ -92,7 +92,7 @@ make_fig_rx <- function(retirements, var) {
     geom_line() +
     labs(
       x = "Age",
-      y = latex2exp::TeX("Probability of retirement ($r_{x,t}$)"),
+      y = latex2exp::TeX("Probability of retirement"), # ($r_{x,t}$)"),
       title = "Probability of retirement for Australian scientists (2022 – 23)"
     ) +
     scale_x_continuous(breaks = seq(40, 100, by = 10))

### 2025-04-30 R/sec5_figures.R

@@ -81,7 +81,7 @@ make_fig21 <- function(course_leavers, combine = FALSE) {
 
 make_fig22 <- function(disciplines_combined) {
   ggplot(disciplines_combined) +
-    aes(x = age, y = migrants, group = year, color = year) +
+    aes(x = age, y = remainder, group = year, color = year) +
     geom_line() +
     facet_wrap(~discipline, scales = "free_y") +
     scale_x_continuous(breaks = seq(10, 100, by = 10)) +
@@ -89,9 +89,9 @@ make_fig22 <- function(disciplines_combined) {
       colours = rainbow(10)
     ) +
     labs(
-      y = "Number of net migrants",
-      title = "Estimated Net Migration by Discipline",
-      subtitle = "Natural and Physical Sciences\n2006 - 2020"
+      y = "Remainder",
+      title = "Remainder by discipline",
+      subtitle = "Natural and Physical Sciences (2006 - 2020)"
     ) +
     geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
     theme(

### 2025-04-30 _dependencies.R

@@ -1,3 +1,5 @@
 library(visNetwork)
 library(quarto)
 library(styler)
+library(ragg)
+library(Cairo)

### 2025-04-30 _targets.R

@@ -24,8 +24,34 @@ list(
   tar_target(ex_file, here::here("data/Exposures_1x1.txt"), format = "file"),
   tar_target(mortality, read_mortality(mx_file, ex_file)),
   tar_target(aus_death_prob, compute_death_prob(mortality)),
-  tar_target(fig_mxt, make_fig_mxt(mortality)),
-  tar_target(fig_smooth_mxt, make_fig_mxt(aus_death_prob)),
+  tar_target(fig_mxt, life_table(mortality) |> make_fig_mxt()),
+  tar_target(
+    fig_smooth_mxt,
+    make_fig_mxt(aus_death_prob) +
+      labs(y = "Smoothed probability of death")
+  ),
+  tar_target(
+    model_mxt,
+    aus_death_prob |>
+      model(fdm = FDM(log(qx)))
+  ),
+  tar_target(
+    future_mxt,
+    model_mxt |>
+      generate(h = h, times = nsim) |>
+      rename(qx = .sim) |>
+      select(-.model)
+  ),
+  tar_target(
+    future_mxt_2030,
+    model_mxt |>
+      forecast(h = h) |>
+      filter(year == 2030)
+  ),
+  tar_target(
+    fig_model_mxt,
+    make_future_mxt_fig(model_mxt)
+  ),
 
   # Retirement data
   tar_target(
@@ -69,7 +95,6 @@ list(
     make_fig_completions(ave_completions, average = TRUE)
   ),
   tar_target(tab2, make_table2(ave_completions)),
-
 
   # Census 2 digit
   tar_target(science_file2, here::here("data/2-digit - Single year.xlsx")),
@@ -151,6 +176,29 @@ list(
   tar_target(
     fig_grad_forecasts,
     make_fig_grad_forecasts(course_leavers, future_course_leavers_science)
+  ),
+
+  # Graduate forecasts
+  tar_target(sci_grads, total_sci_grads(course_leavers)),
+  tar_target(arima, sci_grads |> model(ARIMA(graduates))),
+  tar_target(
+    future_grads,
+    generate(arima, h = h, times = nsim) |>
+      rename(graduates = .sim) |>
+      select(-.model)
+  ),
+  tar_target(
+    fig_future_grads,
+    sci_grads |>
+      ggplot(aes(x = year, y = graduates)) +
+      geom_line() +
+      geom_line(
+        # Only show first 99 sample paths
+        data = future_grads |> filter(stringr::str_length(.rep) <= 2),
[…]

### 2025-04-30 setup.R

@@ -1,0 +1,45 @@
+options(digits = 3, width = 88)
+options(knitr.kable.NA = "")
+
+# Colours to be viridis for continuous scales and Okabe for discrete scales
+options(
+  ggplot2.continuous.colour = "viridis",
+  ggplot2.continuous.fill = "viridis",
+  ggplot2.discrete.colour = c(
+    "#D55E00",
+    "#0072B2",
+    "#009E73",
+    "#CC79A7",
+    "#E69F00",
+    "#56B4E9",
+    "#F0E442"
+  ),
+  ggplot2.discrete.fill = c(
+    "#D55E00",
+    "#0072B2",
+    "#009E73",
+    "#CC79A7",
+    "#E69F00",
+    "#56B4E9",
+    "#F0E442"
+  )
+)
+knitr::opts_chunk$set(
+  dev.args = list(bg = "transparent", pointsize = 11)
+)
+
+# Font for graphics to be Fira Sans
+ggplot2::theme_set(
+  ggplot2::theme_get() +
+    ggplot2::theme(
+      text = ggplot2::element_text(family = "Fira Sans"),
+      plot.background = ggplot2::element_rect(
+        fill = "transparent",
+        colour = "transparent"
+      )
+    )
+)
+# Also in base R plots
+#quartzFonts(
+#  sans = c("Fira Sans Regular", "Fira Sans Bold", "Fira Sans Italic", "Fira Sans Bold Italic")
+#)

### 2025-05-01 R/mortality.R
Adding future qxt and Ext plots

@@ -18,7 +18,7 @@ read_mortality <- function(mx_path, ex_path) {
 # Then smooth the result and add in population data
 compute_death_prob <- function(mortality) {
   life_table(mortality) |>
-    smooth_mortality(qx, k = 50) |>
+    smooth_mortality(qx, k = 60) |>
     mutate(qx = c(.smooth)) |>
     select(year, age, qx) |>
     left_join(
@@ -34,17 +34,40 @@ make_fig_mxt <- function(death_prob) {
   death_prob |>
     filter(age <= 100) |>
     autoplot(qx) +
-    scale_y_log10(labels = scales::label_number()) +
     labs(
-      y = latex2exp::TeX("Probability of death"), # ($m_{x,t}$)"),
       x = "Age",
+      y = latex2exp::TeX("Probability of death"), # ($m_{x,t}$)"),
       title = "Probability of death for Australians (1971 – 2021)",
     ) +
-    scale_x_continuous(breaks = seq(0, 100, by = 10))
+    scale_x_continuous(breaks = seq(0, 100, by = 10)) +
+    scale_y_log10(labels = scales::label_number(), limits = c(2e-5, 1))
 }
 
+make_future_mxt_fig <- function(object, data, h, times, yr) {
+  object |>
+    generate(h = h, times = times) |>
+    filter(year == yr, age <= 100) |>
+    ggplot() +
+    geom_line(
+      data = life_table(data) |> filter(age <= 100),
+      aes(x = age, y = qx, group = year),
+      color = "grey"
+    ) +
+    geom_line(aes(x = age, y = .sim, col = .rep, group = .rep)) +
+    guides(color = "none") +
+    labs(
+      x = "Age",
+      y = latex2exp::TeX("Probability of death"), # ($m_{x,t}$)"),
+      title = paste("Simulated future mortality for", yr)
+    ) +
+    scale_x_continuous(breaks = seq(0, 100, by = 10)) +
+    scale_y_log10(labels = scales::label_number(), limits = c(2e-5, 1))
+}
+
+
+
 # Adaptation of vital:::autoplot.FDM to add in future sample paths
-make_future_mxt_fig <- function(object, show_order = 2) {
+make_future_fdm_fig <- function(object, show_order = 1:2) {
   obj_time <- time_components(object)
   obj_x <- age_components(object)
 
[…]

### 2025-05-01 R/remainder.R

@@ -1,0 +1,19 @@
+make_future_Ext_fig <- function(object, data, h, times, yr) {
+  object |>
+    generate(h = h, times = times) |>
+    filter(year == yr, age <= 100) |>
+    ggplot() +
+    geom_line(
+      data = data |> filter(age <= 100),
+      aes(x = age, y = remainder, group = year),
+      color = "grey"
+    ) +
+    geom_line(aes(x = age, y = .sim, col = .rep, group = .rep)) +
+    guides(color = "none") +
+    labs(
+      x = "Age",
+      y = latex2exp::TeX("Remainder"), # ($m_{x,t}$)"),
+      title = paste("Simulated future remainder for", yr)
+    ) +
+    scale_x_continuous(breaks = seq(0, 100, by = 10)) 
+}

### 2025-05-01 _targets.R

@@ -36,21 +36,28 @@ list(
       model(fdm = FDM(log(qx)))
   ),
   tar_target(
-    future_mxt,
-    model_mxt |>
-      generate(h = h, times = nsim) |>
-      rename(qx = .sim) |>
-      select(-.model)
+    fig_model_fdm1,
+    make_future_fdm_fig(model_mxt, 1:2)
   ),
   tar_target(
-    future_mxt_2030,
-    model_mxt |>
-      forecast(h = h) |>
-      filter(year == 2030)
+    fig_model_fdm2,
+    make_future_fdm_fig(model_mxt, 3:4)
   ),
   tar_target(
-    fig_model_mxt,
-    make_future_mxt_fig(model_mxt)
+    fig_model_fdm3,
+    make_future_fdm_fig(model_mxt, 5:6)
+  ),
+  tar_target(
+    fig_model_mxt0,
+    make_future_mxt_fig(model_mxt, mortality, h, 10, 2050)
+  ),
+  tar_target(
+    fig_model_mxt1,
+    make_future_mxt_fig(model_mxt, mortality, h, 10, 2030)
+  ),
+  tar_target(
+    fig_model_mxt2,
+    make_future_mxt_fig(model_mxt, mortality, h, 10, 2040)
   ),
 
   # Retirement data
@@ -131,6 +138,37 @@ list(
       retirements,
       aus_death_prob
     )
+  ),
+
+  # Remainders
+  tar_target(
+    model_Ext,
+    census2_1 |>
+      model(fdm = FDM(remainder))
+  ),
+  tar_target(
+    fig_Emodel_fdm1,
+    make_future_fdm_fig(model_Ext, 1:2)
+  ),
+  tar_target(
+    fig_Emodel_fdm2,
+    make_future_fdm_fig(model_Ext, 3:4)
+  ),
+  tar_target(
+    fig_Emodel_fdm3,
+    make_future_fdm_fig(model_Ext, 5:6)
+  ),
+  tar_target(
+    fig_model_Ext0,
+    make_future_Ext_fig(model_Ext, census2_1, h, 10, 2050)
+  ),
+  tar_target(
+    fig_model_Ext1,
+    make_future_Ext_fig(model_Ext, census2_1, h, 10, 2030)
+  ),
+  tar_target(
+    fig_model_Ext2,
+    make_future_Ext_fig(model_Ext, census2_1, h, 10, 2040)
   ),
 
   # Forecasts

### 2025-05-01 R/census_figs.R
Added graphs of future working population to talk

@@ -21,7 +21,7 @@ make_pop_fig <- function(
     labs(
       x = "Age",
       y = "Number of active scientists",
-      title = paste("Working Population:", subtitle, "(2006 – 2021)")
+      title = paste("Working population:", subtitle, "(2006 – 2021)")
     )
   if (interpolation) {
     p <- p +
@@ -59,7 +59,8 @@ make_component_fig <- function(census, variable) {
       x = "Age",
       y = ylab,
       title = paste0(
-        "Natural and Physical Sciences (",
+        ylab,
+        ": Natural and Physical Sciences (",
         minyear,
         " – ",
         maxyear,
@@ -91,4 +92,30 @@ make_fig1 <- function(census_science) {
     ) +
     scale_shape_manual(values = c(1, 2, 0)) +
     scale_color_manual(values = cols)
+}
+
+
+make_pop_future_fig <- function(object, data, yr) {
+  object <- object |> filter(year == yr)
+  if (NROW(object) == 0) {
+    title <- "Working population"
+  } else {
+    title <- paste("Simulated future working population:", yr)
+  }
+  data |>
+    as_tibble() |>
+    ggplot() +
+    aes(x = age, y = working, group = year) +
+    geom_line(color = "gray") +
+    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+    labs(
+      x = "Age",
+      y = "Number of active scientists",
+      title = title
+    ) +
+    geom_line(
+      data = object,
+      aes(x = age, y = working, group = .rep, col = .rep)
+    ) +
+    guides(color = "none")
 }

### 2025-05-01 R/mortality.R

@@ -44,9 +44,15 @@ make_fig_mxt <- function(death_prob) {
 }
 
 make_future_mxt_fig <- function(object, data, h, times, yr) {
-  object |>
+  object <- object |>
     generate(h = h, times = times) |>
-    filter(year == yr, age <= 100) |>
+    filter(year == yr, age <= 100)
+  if (NROW(object) == 0) {
+    title <- "Probability of death for Australians"
+  } else {
+    title <- paste("Simulated future mortality:", yr)
+  }
+  object |>
     ggplot() +
     geom_line(
       data = life_table(data) |> filter(age <= 100),
@@ -58,7 +64,7 @@ make_future_mxt_fig <- function(object, data, h, times, yr) {
     labs(
       x = "Age",
       y = latex2exp::TeX("Probability of death"), # ($m_{x,t}$)"),
-      title = paste("Simulated future mortality for", yr)
+      title = title
     ) +
     scale_x_continuous(breaks = seq(0, 100, by = 10)) +
     scale_y_log10(labels = scales::label_number(), limits = c(2e-5, 1))

### 2025-05-01 R/remainder.R

@@ -1,7 +1,14 @@
 make_future_Ext_fig <- function(object, data, h, times, yr) {
-  object |>
+  object <- object |> 
     generate(h = h, times = times) |>
-    filter(year == yr, age <= 100) |>
+    filter(year == yr, age <= 100)
+  if(NROW(object) == 0) {
+    title <- "Remainder"
+  } else {
+    title <- paste("Simulated future remainder:", yr)
+  }
+
+  object |>
     ggplot() +
     geom_line(
       data = data |> filter(age <= 100),
@@ -12,8 +19,8 @@ make_future_Ext_fig <- function(object, data, h, times, yr) {
     guides(color = "none") +
     labs(
       x = "Age",
-      y = latex2exp::TeX("Remainder"), # ($m_{x,t}$)"),
-      title = paste("Simulated future remainder for", yr)
+      y = latex2exp::TeX("Number of people"), # ($m_{x,t}$)"),
+      title = title
     ) +
     scale_x_continuous(breaks = seq(0, 100, by = 10))
 }

### 2025-05-01 R/sec5_figures.R

@@ -13,7 +13,7 @@ make_fig19 <- function(disciplines_combined) {
     scale_color_manual(values = cols, name = "Census Year") +
     labs(
       y = "Number of active scientists",
-      title = "Working Population by Discipline",
+      title = "Working population by discipline",
       subtitle = "Natural and Physical Sciences"
     ) +
     scale_x_continuous(breaks = seq(20, 100, by = 10)) +
@@ -34,7 +34,7 @@ make_fig20 <- function(disciplines_combined) {
     ) +
     labs(
       y = "Number of active scientists",
-      title = "Interpolated Working Population by Discipline",
+      title = "Interpolated working population by discipline",
       subtitle = "Natural and Physical Sciences\n2006 – 2021"
     ) +
     theme(
@@ -118,7 +118,7 @@ make_fig23 <- function(future_disciplines_combined) {
     geom_line(aes(y = mean), linewidth = 0.75) +
     labs(
       y = "Number of working scientists",
-      title = "Forecast of Working Population by Discipline",
+      title = "Forecast of working population by discipline",
       subtitle = "Natural and Physical Sciences",
       color = "Forecast Year",
       fill = "Forecast Year"
@@ -157,8 +157,8 @@ make_fig24 <- function(disciplines_combined, future_disciplines_combined) {
     geom_line(data = sum_disciplines_combined, aes(y = working)) +
     labs(
       y = "Total number of working scientists (thousands)",
-      title = "Forecast of Total Working Population by Discipline",
-      subtitle = "Natural and Physical Sciences\nForecasted Years: 2022 - 2041"
+      title = "Forecast of total working population by discipline",
+      subtitle = "Natural and Physical Sciences\nForecasted years: 2022 - 2041"
     ) +
     scale_x_continuous(breaks = seq(2010, 2040, by = 10)) +
     scale_y_continuous(labels = scales::label_number(scale = 1e-3)) +

### 2025-05-01 _targets.R

@@ -200,6 +200,18 @@ list(
       nsim = nsim
     )
   ),
+  tar_target(
+    fig_Pxt0,
+    make_pop_future_fig(future_pop_science2, census2_1, 2050) 
+  ),
+  tar_target(
+    fig_Pxt1,
+    make_pop_future_fig(future_pop_science2, census2_1, 2030) 
+  ),
+  tar_target(
+    fig_Pxt2,
+    make_pop_future_fig(future_pop_science2, census2_1, 2040) 
+  ),
 
   # Physics
   tar_target(
@@ -244,11 +256,11 @@ list(
       ggplot(aes(x = year, y = graduates)) +
       geom_line() +
       geom_line(
-        # Only show first 99 sample paths
-        data = future_grads |> filter(stringr::str_length(.rep) <= 2),
+        # Only show first 9 sample paths
+        data = future_grads |> filter(stringr::str_length(.rep) < 2),
         aes(color = .rep)
       ) +
-      labs(x = "Year", y = "Number of graduates") +
+      labs(x = "Year", y = "Number of graduates", title = "Total Science Graduates: Australia") +
       guides(color = "none")
   ),
 
@@ -264,6 +276,6 @@ list(
     talk,
     "age_structure_talk.qmd",
     output_file = "age_structure_talk.pdf",
-    extra_files = c("header.tex", "before-title.tex")
+    extra_files = c("setup.R", "header.tex", "before-title.tex")
   )
 )

### 2025-05-01 setup.R

@@ -36,10 +36,7 @@ ggplot2::theme_set(
       plot.background = ggplot2::element_rect(
         fill = "transparent",
         colour = "transparent"
-      )
+      ),
+      axis.title.y = ggplot2::element_text(margin = ggplot2::margin(r = 10))
     )
 )
-# Also in base R plots
-#quartzFonts(
-#  sans = c("Fira Sans Regular", "Fira Sans Bold", "Fira Sans Italic", "Fira Sans Bold Italic")
-#)

### 2025-05-01 R/census_figs.R
Ribbon figures

@@ -69,7 +69,6 @@ make_component_fig <- function(census, variable) {
     )
 }
 
-
 make_fig1 <- function(census_science) {
   cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF", "#000000")
 
@@ -94,28 +93,56 @@ make_fig1 <- function(census_science) {
     scale_color_manual(values = cols)
 }
 
+make_pop_future_fig <- function(object, data, yrs, ribbon = FALSE) {
+  lapply(yrs, make_pop_future_fig_year, object = object, data = data, ribbon = ribbon)
+}
 
-make_pop_future_fig <- function(object, data, yr) {
+make_pop_future_fig_year <- function(yr, object, data, ribbon = FALSE) {
   object <- object |> filter(year == yr)
+  if (!ribbon) {
+    object <- object |>
+      filter(stringr::str_length(.rep) < 2)
+  }
   if (NROW(object) == 0) {
     title <- "Working population"
   } else {
     title <- paste("Simulated future working population:", yr)
   }
-  data |>
+  p <- data |>
     as_tibble() |>
     ggplot() +
-    aes(x = age, y = working, group = year) +
-    geom_line(color = "gray") +
+    aes(x = age, y = working) +
+    geom_line(aes(group = year), color = "gray") +
     scale_x_continuous(breaks = seq(20, 100, by = 10)) +
     labs(
       x = "Age",
       y = "Number of active scientists",
       title = title
-    ) +
-    geom_line(
-      data = object,
-      aes(x = age, y = working, group = .rep, col = .rep)
-    ) +
+    )
+  if (!ribbon) {
+    p <- p +
+      geom_line(
+        data = object,
+        aes(x = age, y = working, group = .rep, col = .rep)
+      ) 
+  } else {
+    object <- object |>
+      as_tibble() |>
+      group_by(age) |>
+      summarise(
+        .lower = quantile(working, probs = 0.1),
+        .upper = quantile(working, probs = 0.9),
+        working = mean(working),
+      )
+    p <- p +
+      geom_ribbon(
+        data = object,
+        aes(ymin = .lower, ymax = .upper),
+        alpha = 0.3,
+        fill = "#c14b14"
+      ) +
+      geom_line(data = object, color = "#c14b14", linewidth = 1)
+  }
+  p +
     guides(color = "none")
 }

### 2025-05-01 R/functions.R

@@ -458,7 +458,6 @@ ave_smooth_pr <- function(data) {
   })
 }
 
-
 make_discipline_table <- function() {
   tibble::tibble(
     Narrow_Discipline = c(

### 2025-05-01 R/graduates.R

@@ -165,7 +165,6 @@ make_table2 <- function(ave_completions) {
     kable_styling(latex_options = c("striped"))
 }
 
-
 # Level 4
 read_course_leavers <- function(file) {
   out <- readxl::read_excel(file, sheet = "4-digit") |>

### 2025-05-01 R/lv2_science.R

@@ -147,7 +147,6 @@ find_var <- function(data, possible_names) {
   }
 }
 
-
 # Forecast the working population for all of science
 
 forecast_pop2 <- function(

### 2025-05-01 R/mortality.R

@@ -28,7 +28,6 @@ compute_death_prob <- function(mortality) {
     as_vital(index = year, key = age, .age = "age", populaton = "exposures")
 }
 
-
 # Graph showing the probability of death by age over time
 make_fig_mxt <- function(death_prob) {
   death_prob |>

### 2025-05-01 R/remainder.R

@@ -1,8 +1,8 @@
 make_future_Ext_fig <- function(object, data, h, times, yr) {
-  object <- object |> 
+  object <- object |>
     generate(h = h, times = times) |>
     filter(year == yr, age <= 100)
-  if(NROW(object) == 0) {
+  if (NROW(object) == 0) {
     title <- "Remainder"
   } else {
     title <- paste("Simulated future remainder:", yr)

### 2025-05-01 R/retirements.R

@@ -70,7 +70,6 @@ single_age_retirements <- function(retirement_data, death_prob) {
   return(retirement)
 }
 
-
 make_fig_r <- function(retirements) {
   ggplot(retirements, aes(x = age_group, y = pc)) +
     geom_col() +

### 2025-05-01 _targets.R

@@ -173,7 +173,7 @@ list(
 
   # Forecasts
   tar_target(h, 20),
-  tar_target(nsim, 10),
+  tar_target(nsim, 1000),
   tar_target(
     future_pop_science2,
     forecast_pop2(
@@ -205,14 +205,9 @@ list(
     make_pop_future_fig(future_pop_science2, census2_1, 2050) 
   ),
   tar_target(
-    fig_Pxt1,
-    make_pop_future_fig(future_pop_science2, census2_1, 2030) 
+    fig_Pxt_future,
+    make_pop_future_fig(future_pop_science2, census2_1, 2025:2035, ribbon = TRUE) 
   ),
-  tar_target(
-    fig_Pxt2,
-    make_pop_future_fig(future_pop_science2, census2_1, 2040) 
-  ),
-
   # Physics
   tar_target(
     physics,

### 2025-05-01 R/census_figs.R
Fix bug in figures

@@ -125,7 +125,7 @@ make_pop_future_fig_year <- function(yr, object, data, ribbon = FALSE) {
         data = object,
         aes(x = age, y = working, group = .rep, col = .rep)
       ) 
-  } else {
+  } else if(NROW(object) > 0) {
     object <- object |>
       as_tibble() |>
       group_by(age) |>

### 2025-05-01 R/sec5_figures.R

@@ -120,10 +120,8 @@ make_fig23 <- function(future_disciplines_combined) {
       y = "Number of working scientists",
       title = "Forecast of working population by discipline",
       subtitle = "Natural and Physical Sciences",
-      color = "Forecast Year",
       fill = "Forecast Year"
     ) +
-    scale_color_manual(values = c("2025" = "#66666644", "2035" = "#c14b14")) +
     scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
     scale_x_continuous(breaks = seq(20, 100, by = 10)) +
     theme(

### 2025-05-01 _targets.R

@@ -206,7 +206,7 @@ list(
   ),
   tar_target(
     fig_Pxt_future,
-    make_pop_future_fig(future_pop_science2, census2_1, 2025:2035, ribbon = TRUE) 
+    make_pop_future_fig(future_pop_science2, census2_1, 2022:2035, ribbon = TRUE) 
   ),
   # Physics
   tar_target(

### 2025-05-05 R/census_figs.R
Working on discipline figures

@@ -124,7 +124,7 @@ make_pop_future_fig_year <- function(yr, object, data, ribbon = FALSE) {
       geom_line(
         data = object,
         aes(x = age, y = working, group = .rep, col = .rep)
-      ) 
+      )
   } else if(NROW(object) > 0) {
     object <- object |>
       as_tibble() |>

### 2025-05-05 R/forecast_by_discipline.R

@@ -1,0 +1,62 @@
+make_pop_future_fig_discipline <- function(
+    yrs,
+    object,
+    data,
+    no_other = FALSE) {
+  lapply(yrs, make_pop_future_fig_discipline_year, object = object, data = data, no_other = no_other)
+}
+
+make_pop_future_fig_discipline_year <- function(
+    yrs,
+    object,
+    data,
+    no_other = FALSE) {
+  # Remove other group
+  if (no_other) {
+    object <- object |>
+      dplyr::filter(discipline != "Other Natural and Physical Sciences")
+    data <- data |>
+      dplyr::filter(discipline != "Other Natural and Physical Sciences")
+  }
+  object <- object |>
+    as_tibble() |>
+    dplyr::filter(year %in% yrs) |>
+    group_by(age, discipline, year) |>
+    summarise(
+      .lower = quantile(working, probs = 0.1),
+      .upper = quantile(working, probs = 0.9),
+      working = mean(working),
+      .groups = "drop"
+    )
+  disciplines <- unique(data$discipline)
+  p <- lapply(disciplines, function(d) {
+    data |>
+      filter(discipline == d) |>
+      ggplot() +
+      aes(x = age, y = working, group = factor(year)) +
+      facet_wrap(~discipline, scales = "free_y") +
+      geom_line(color = "gray") +
+      geom_ribbon(
+        data = object |> filter(discipline == d),
+        aes(ymin = .lower, ymax = .upper, fill = factor(year)),
+        alpha = 0.3
+      ) +
+      geom_line(
+        data = object |> filter(discipline == d),
+        aes(color = factor(year)), linewidth = 0.75
+      ) +
+      scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+      labs(
+        x = "Age",
+        y = "Number of active scientists",
+        fill = "Forecast year"
+      ) +
+      guides(color = "none")
+  })
+  p[[length(p) + 1]] <- patchwork::guide_area()
+  patchwork::wrap_plots(p) +
+    patchwork::plot_annotation(
+      title = "Forecast of working population by discipline",
+    ) +
+    patchwork::plot_layout(guides = "collect", axis_titles = "collect")
+}

### 2025-05-05 R/sec5_figures.R

@@ -99,37 +99,6 @@ make_fig22 <- function(disciplines_combined) {
     )
 }
 
-make_fig23 <- function(future_disciplines_combined) {
-  eg_forecast <- future_disciplines_combined |>
-    as_tibble() |>
-    filter(year %in% c(2025, 2035)) |>
-    group_by(discipline, age, year) |>
-    summarise(
-      mean = mean(working),
-      lo = quantile(working, prob = 0.05),
-      hi = quantile(working, prob = 0.95),
-      .groups = "drop"
-    )
-
-  # Overlay
-  ggplot(eg_forecast) +
-    aes(x = age, color = factor(year)) +
-    geom_ribbon(aes(ymin = lo, ymax = hi, fill = factor(year)), alpha = 0.1) +
-    geom_line(aes(y = mean), linewidth = 0.75) +
-    labs(
-      y = "Number of working scientists",
-      title = "Forecast of working population by discipline",
-      subtitle = "Natural and Physical Sciences",
-      fill = "Forecast Year"
-    ) +
-    scale_fill_manual(values = c("2025" = "#66666644", "2035" = "#c14b1444")) +
-    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
-    theme(
-      legend.position = "top"
-    ) +
-    facet_wrap(~discipline, scales = "free_y")
-}
-
 make_fig24 <- function(disciplines_combined, future_disciplines_combined) {
   sum_disciplines_combined <- disciplines_combined |>
     as_tibble() |>

### 2025-05-05 _targets.R

@@ -202,11 +202,16 @@ list(
   ),
   tar_target(
     fig_Pxt0,
-    make_pop_future_fig(future_pop_science2, census2_1, 2050) 
+    make_pop_future_fig(future_pop_science2, census2_1, 2050)
   ),
   tar_target(
     fig_Pxt_future,
-    make_pop_future_fig(future_pop_science2, census2_1, 2022:2035, ribbon = TRUE) 
+    make_pop_future_fig(
+      future_pop_science2,
+      census2_1,
+      2022:2035,
+      ribbon = TRUE
+    )
   ),
   # Physics
   tar_target(
@@ -229,7 +234,15 @@ list(
   tar_target(fig21, make_fig21(course_leavers)),
   tar_target(fig21b, make_fig21(course_leavers, combine = TRUE)),
   tar_target(fig22, make_fig22(census4_1)),
-  tar_target(fig23, make_fig23(future_pop_science)),
+  tar_target(
+    fig_Pxt_future_discipline,
+    make_pop_future_fig_discipline(
+      2022:2035,
+      future_pop_science,
+      census4_1,
+      no_other = TRUE
+    )
+  ),
   tar_target(fig24, make_fig24(census4_1, future_pop_science)),
   tar_target(
     fig_grad_forecasts,
@@ -255,7 +268,11 @@ list(
         data = future_grads |> filter(stringr::str_length(.rep) < 2),
         aes(color = .rep)
       ) +
-      labs(x = "Year", y = "Number of graduates", title = "Total Science Graduates: Australia") +
+      labs(
+        x = "Year",
+        y = "Number of graduates",
+        title = "Total Science Graduates: Australia"
+      ) +
       guides(color = "none")
   ),
 

### 2025-05-06 R/census_figs.R
Final discipline figures for talk

@@ -2,13 +2,19 @@ make_pop_fig <- function(
   census,
   subtitle,
   interpolation = FALSE,
-  highlight_census = FALSE
+  highlight_census = FALSE,
+  no_other = TRUE
 ) {
   if (!interpolation) {
     census <- census |>
       as_tibble() |>
       mutate(year = factor(year, levels = rev(seq(2006, 2021, by = 5))))
   }
+  if (no_other & "discipline" %in% names(census)) {
+    census <- census |>
+      dplyr::filter(discipline != "Other Natural and Physical Sciences")
+  }
+
   p <- census |>
     as_tibble() |>
     ggplot() +
@@ -23,6 +29,9 @@ make_pop_fig <- function(
       y = "Number of active scientists",
       title = paste("Working population:", subtitle, "(2006 – 2021)")
     )
+  if ("discipline" %in% names(census)) {
+    p <- p + facet_wrap(~discipline, scales = "free_y")
+  }
   if (interpolation) {
     p <- p +
       geom_line(
@@ -94,7 +103,13 @@ make_fig1 <- function(census_science) {
 }
 
 make_pop_future_fig <- function(object, data, yrs, ribbon = FALSE) {
-  lapply(yrs, make_pop_future_fig_year, object = object, data = data, ribbon = ribbon)
+  lapply(
+    yrs,
+    make_pop_future_fig_year,
+    object = object,
+    data = data,
+    ribbon = ribbon
+  )
 }
 
 make_pop_future_fig_year <- function(yr, object, data, ribbon = FALSE) {
@@ -105,8 +120,10 @@ make_pop_future_fig_year <- function(yr, object, data, ribbon = FALSE) {
   }
   if (NROW(object) == 0) {
     title <- "Working population"
-  } else {
+  } else if (!ribbon) {
     title <- paste("Simulated future working population:", yr)
+  } else {
+    title <- paste("90% forecast interval for working population:", yr)
   }
   p <- data |>
     as_tibble() |>
@@ -125,7 +142,7 @@ make_pop_future_fig_year <- function(yr, object, data, ribbon = FALSE) {
         data = object,
         aes(x = age, y = working, group = .rep, col = .rep)
       )
-  } else if(NROW(object) > 0) {
+  } else if (NROW(object) > 0) {
     object <- object |>
       as_tibble() |>
       group_by(age) |>

### 2025-05-06 R/forecast_by_discipline.R

@@ -1,16 +1,33 @@
-make_pop_future_fig_discipline <- function(
-    yrs,
-    object,
-    data,
-    no_other = FALSE) {
-  lapply(yrs, make_pop_future_fig_discipline_year, object = object, data = data, no_other = no_other)
+get_ymax <- function(
+  yrs,
+  object,
+  no_other = FALSE
+) {
+  # Remove other group
+  if (no_other) {
+    object <- object |>
+      dplyr::filter(discipline != "Other Natural and Physical Sciences")
+  }
+  object <- object |>
+    as_tibble() |>
+    dplyr::filter(year %in% yrs) |>
+    group_by(age, discipline, year) |>
+    summarise(
+      .upper = quantile(working, probs = 0.9),
+      .groups = "drop"
+    ) |>
+    group_by(discipline) |>
+    summarise(ymax = max(.upper))
 }
 
-make_pop_future_fig_discipline_year <- function(
-    yrs,
-    object,
-    data,
-    no_other = FALSE) {
+make_pop_future_fig_discipline <- function(
+  yrs,
+  object,
+  data,
+  no_other = FALSE,
+  ymax,
+  color_data = FALSE
+) {
   # Remove other group
   if (no_other) {
     object <- object |>
@@ -28,35 +45,100 @@ make_pop_future_fig_discipline_year <- function(
       working = mean(working),
       .groups = "drop"
     )
+  lapply(
+    yrs,
+    make_pop_future_fig_discipline_year,
+    object = object,
+    data = data,
+    ymax = ymax,
+    color_data = color_data
+  )
+}
+
+make_pop_future_fig_discipline_year <- function(
+  yrs,
+  object,
+  data,
+  ymax,
+  color_data
+) {
   disciplines <- unique(data$discipline)
+  object <- object |>
+    dplyr::filter(year %in% yrs)
   p <- lapply(disciplines, function(d) {
-    data |>
+    tmp <- data |>
       filter(discipline == d) |>
       ggplot() +
       aes(x = age, y = working, group = factor(year)) +
-      facet_wrap(~discipline, scales = "free_y") +
-      geom_line(color = "gray") +
-      geom_ribbon(
-        data = object |> filter(discipline == d),
-        aes(ymin = .lower, ymax = .upper, fill = factor(year)),
-        alpha = 0.3
-      ) +
-      geom_line(
-        data = object |> filter(discipline == d),
-        aes(color = factor(year)), linewidth = 0.75
-      ) +
[…]

### 2025-05-06 R/graduates.R

@@ -139,7 +139,7 @@ make_fig_completions <- function(completions, average = FALSE) {
   } else {
     p <- p +
       aes(x = age, y = pc, colour = year, group = year) +
-      scale_color_gradientn(colours = rainbow(10)[1:8]) +
+      scale_color_gradientn(colours = rainbow(10)) +
       labs(title = "Graduate completions by year and age (2006 – 2023)")
   }
   p +

### 2025-05-06 R/physics_figs.R

@@ -9,7 +9,7 @@ make_fig16 <- function(physics, future_physics) {
       aes(colour = year)
     ) +
     labs(y = "Number of working scientists") +
-    scale_color_gradientn(colors = rainbow(10)[1:8]) +
+    scale_color_gradientn(colors = rainbow(10)) +
     labs(
       title = "Simulation 1",
       subtitle = "Forecasted Years: 2022 - 2041"
@@ -25,7 +25,7 @@ make_fig16 <- function(physics, future_physics) {
       aes(colour = year)
     ) +
     labs(y = NULL) + # Remove y-axis label
-    scale_color_gradientn(colors = rainbow(10)[1:8]) +
+    scale_color_gradientn(colors = rainbow(10)) +
     labs(
       title = "Simulation 2",
       subtitle = "Forecasted Years: 2022 - 2041"

### 2025-05-06 R/sec5_figures.R

@@ -42,7 +42,11 @@ make_fig20 <- function(disciplines_combined) {
     )
 }
 
-make_fig21 <- function(course_leavers, combine = FALSE) {
+make_fig21 <- function(course_leavers, combine = FALSE, no_other = TRUE) {
+  if(no_other) {
+    course_leavers <- course_leavers |>
+      dplyr::filter(discipline != "Other Natural and Physical Sciences")
+  }
   course_leavers$discipline <- course_leavers$discipline |>
     forcats::fct_relevel(
       "Physics and Astronomy",
@@ -52,7 +56,7 @@ make_fig21 <- function(course_leavers, combine = FALSE) {
       "Biological Sciences",
       "Other Natural and Physical Sciences"
     )
-  subtitle <- "Natural and Physical Sciences (2006 – 2023)"
+  subtitle <- "(2006 – 2023)"
   if (combine) {
     course_leavers <- course_leavers |>
       group_by(year) |>
@@ -71,7 +75,7 @@ make_fig21 <- function(course_leavers, combine = FALSE) {
   if (!combine) {
     p <- p +
       facet_wrap(~discipline, scales = "free_y") +
-      labs(title = paste("Graduates by Discipline:", subtitle))
+      labs(title = paste("Graduates by discipline:", subtitle))
   } else {
     p <- p +
       labs(title = paste("Total graduates:", subtitle))
@@ -99,7 +103,13 @@ make_fig22 <- function(disciplines_combined) {
     )
 }
 
-make_fig24 <- function(disciplines_combined, future_disciplines_combined) {
+make_fig24 <- function(disciplines_combined, future_disciplines_combined, no_other = TRUE) {
+  if(no_other) {
+    disciplines_combined <- disciplines_combined |>
+      dplyr::filter(discipline != "Other Natural and Physical Sciences")
+    future_disciplines_combined <- future_disciplines_combined |>
+      dplyr::filter(discipline != "Other Natural and Physical Sciences")
+  }
   sum_disciplines_combined <- disciplines_combined |>
     as_tibble() |>
     group_by(discipline, year) |>
@@ -132,7 +142,13 @@ make_fig24 <- function(disciplines_combined, future_disciplines_combined) {
     facet_wrap(~discipline, scales = "free_y")
 }
 
-make_fig_grad_forecasts <- function(grads, future_grads) {
+make_fig_grad_forecasts <- function(grads, future_grads, no_other = TRUE) {
+  if(no_other) {
[…]

### 2025-05-06 _targets.R

@@ -125,6 +125,19 @@ list(
     fig_Pxt,
     make_pop_fig(census2_1, "Natural and Physical Sciences", TRUE, TRUE)
   ),
+  tar_target(
+    fig_Pxt_discipline,
+    #make_pop_fig(census4_1, "Natural and Physical Sciences", TRUE, TRUE)
+    make_pop_future_fig_discipline(
+      2050,
+      future_pop_science,
+      census4_1,
+      no_other = TRUE,
+      color_data = TRUE,
+      ymax = ymax
+    )
+  ),
+
   tar_target(fig_error, make_component_fig(census2_1, remainder)),
 
   # Census 4 digit
@@ -234,13 +247,25 @@ list(
   tar_target(fig21, make_fig21(course_leavers)),
   tar_target(fig21b, make_fig21(course_leavers, combine = TRUE)),
   tar_target(fig22, make_fig22(census4_1)),
+  tar_target(ymax, get_ymax(2022:2035, future_pop_science, no_other = TRUE)),
+  tar_target(
+    fig_Pxt_discipline0,
+    make_pop_future_fig_discipline(
+      2050,
+      future_pop_science,
+      census4_1,
+      no_other = TRUE,
+      ymax
+    )
+  ),
   tar_target(
     fig_Pxt_future_discipline,
     make_pop_future_fig_discipline(
       2022:2035,
       future_pop_science,
       census4_1,
-      no_other = TRUE
+      no_other = TRUE,
+      ymax
     )
   ),
   tar_target(fig24, make_fig24(census4_1, future_pop_science)),
@@ -274,6 +299,20 @@ list(
         title = "Total Science Graduates: Australia"
       ) +
       guides(color = "none")
+  ),
+
+  # Graduate forecasts by discipline
+  tar_target(
+    future_grads_discipline,
+    course_leavers |>
+      fit_global_model(arma_coef_science) |>
+      generate(h = h, times = nsim) |>
+      rename(graduates = .sim) |>
+      select(-.model)
+  ),
+  tar_target(
+    fig_future_grads_discipline,
+    make_fig_future_grads_discipline(course_leavers, future_grads_discipline)
   ),
 
   # Document

### 2025-06-29 R/census_figs.R
Final changes to slides

@@ -38,9 +38,9 @@ make_pop_fig <- function(
         data = census |> filter(!year %in% seq(2006, 2021, by = 5)),
         linewidth = 0.5
       ) +
-      scale_color_gradientn(colours = rainbow(10))
+      scale_color_gradientn(colours = rainbow(1000)[1:800])
   } else {
-    cols <- c("#ff0000", "#32ff00", "#0065ff", "#ff0099")
+    cols <- c("#ff0000", "#67ff00", "#00ceff", "#ca00ff")
     names(cols) <- seq(2006, 2021, by = 5)
     p <- p +
       scale_color_manual(values = cols)

### 2025-06-29 R/forecast_by_discipline.R

@@ -135,6 +135,11 @@ make_fig_future_grads_discipline <- function(course_leavers, future_grads_discip
       alpha = 0.3,
       fill = "#c14b14"
     ) +
+    geom_line(
+      data = future_grads_discipline_pi,
+      aes(x = year, y = mean),
+      color = "#c14b14"
+    ) +
     labs(
       x = "Year",
       y = "Number of graduates",

### 2025-08-21 age_structure_forecasts.qmd
Figures of components
Big update to align with final modelling choices
Started on paper

@@
 
-In planning for the future labour market, it is necessary to forecast the age structure of the workforce, in order to enable informed decision-making on policies concerning universities and immigration.
-We demonstrate a statistical modelling approach to this problem, illustrated using various scientific disciplines in Australia, forecasting future workforce age structures over the next decade.
+In planning for the future labour market, it is necessary to forecast the age structure of the workforce, in order to enable informed decision-making on policies, especially concerning universities and immigration.
+We propose a statistical modelling approach to this problem, illustrated using various scientific disciplines in Australia, forecasting future workforce age structures over the next decade.
 The forecasts described have been used by the Australian Academy of Science as part of _Australian Science, Australia’s Future: Science 2035_, an initiative assessing the capability of the national science system and its role in achieving Australia’s ambitions [@AAS2035].
@@
 The economic implications of workforce age structure shifts are well-documented [e.g., @Bloom2007], affecting productivity, pensions and superannuation, and skill shortages [@PC2013; @OECD2019a; @OECD2019b; @pension].
+The social implications are also significant, with an aging workforce leading to changes in workplace dynamics, potential problems with intergenerational knowledge transfer, and the need for policies that support older workers.
+Yet this problem does not appear to have been previously addressed from a statistical modeling perspective.
 
@@
 These separate component models were then simulated to form future sample paths, leading to age- and sex-specific stochastic population forecasts.
+The modelling framework was later extended by @HBY13 to ensure coherence of forecasts between sexes or other demographic groups.
 
-This framework is adaptable to workforce dynamics by redefining the demographic components, replacing fertility with workforce entry.
-The latter functions more like a migration process than a birth process because graduates can enter the workforce at any age.
+We propose to adapt this framework to workforce dynamics by redefining the demographic components in two ways.
+First, we replace fertility with workforce entry, which functions more like a migration process than a birth process because graduates can enter the workforce at any age.
+Second, we allow workers to leave the workforce through two processes: retirement and death.
+Of course, people may also leave the workforce for other reasons, such as a career change or family commitments, but since we do not have data on these processes, we model them implicitly via a remainder term.
 
-This analysis focuses on the Natural and Physical Sciences as defined in the Australian Standard Classification of Education (ASCED) by the @ABSASCED.
-For consistency, the report refers to ASCED’s Narrow Fields as "disciplines".
-
-We forecast the number of individuals in each one-year age group who are active in the workforce and hold a bachelor’s degree or higher in the following scientific disciplines: Physics and Astronomy, Mathematical Sciences, Chemical Sciences, Earth Sciences, Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences not further defined (n.f.d.).
-
-Projections extend over a 20-year period to 2041, with particular focus on workforce composition in 2035.
-These estimates account for key demographic factors, including mortality, retirement, graduation, and migration.
-
-We describe the methodology in @sec-methodology, data sources in @sec-data, and statistical techniques used to generate the forecasts.
-The results in @sec-results illustrates the application of the ideas to scientific disciplines, focusing on comparison and contrast rather than procedural details.
+We describe the methodology in @sec-methodology.
+By way of illustration, we apply the methodology to major scientific disciplines in Australia, focusing on the Natural and Physical Sciences.
+We describe the data sources in @sec-data, with the results provided in @sec-results.
+The aim of this analysis is to inform future workforce planning and policy decisions to support the growth of Australia’s scientific community.
 Finally, we provide some discussion and conclusions in @sec-conclusion.
-The results aim to inform future workforce planning and policy decisions to support the growth of Australia’s scientific community.
 
@@
 
-Let $P_{i,x,t}$ denote the number of equivalent full-time workers in scientific discipline $i$ who are aged $x$ at the start of year $t$, where $i=1,\dots,I$ and $x=15,16,\dots$.
+Suppose our workforce is divided into $I$ groups, indexed by $i=1,\dots,I$.
+In our application, these are scientific disciplines, but in principle they could refer to any subdivision of workers.
+Let $P_{i,x,t}$ denote the number of equivalent full-time workers in area or discipline $i$ who are aged $x$ at the start of year $t$, where $i=1,\dots,I$ and $x=15,16,\dots$.
 The starting age of 15 is the minimum age at which individuals are counted as part of the labour force in the Australian Census [@ABSLFSP].
@@
 ## Data Sources
+
+This analysis focuses on the Natural and Physical Sciences as defined in the Australian Standard Classification of Education (ASCED) by the @ABSASCED.
+For consistency, the report refers to ASCED’s Narrow Fields as "disciplines".
+
+We forecast the number of individuals in each one-year age group who are active in the workforce and hold a bachelor’s degree or higher in the following scientific disciplines: Physics and Astronomy, Mathematical Sciences, Chemical Sciences, Earth Sciences, Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences not further defined (n.f.d.).
+
+Projections extend over a 20-year period to 2041, with particular focus on workforce composition in 2035.
+These estimates account for key demographic factors, including mortality, retirement, graduation, and migration.
 
@@
 #| fig-cap: Distribution of scientists active in the labour market by age across  Census years (2006, 2011, 2016, 2021).
-tar_read(fig2)
+tar_read(fig_Pxt_census)
 ```
@@
 #| fig-cap: Interpolated number of scientists in Australia, 2006--2021, using linear cohort interpolation.
-tar_read(fig3)
+tar_read(fig_Pxt)
 ```
@@
 #| fig-cap: Retirement intentions for key industries before smoothed disaggregation.
-tar_read(fig4)
+tar_read(fig_r)
 ```
@@
 #| fig-cap: Age distribution of retirement intentions for the 2022--2023 Australian financial year.
-tar_read(fig6)
+tar_read(fig_rx)
 ```
@@
 #| fig-cap: Age-specific probability of retirement based on the 2022--2023 Australian financial year.
-tar_read(fig7)
+tar_read(fig_rx2)
 ```
@@
 #| fig-cap: Age-specific probabilities of death (on a logarithmic scale) for each year from 1971 to 2021.
-tar_read(fig8)
+tar_read(fig_mxt)
 ```
@@
 #| fig-cap: Percentage distribution of graduate completions by age for each year from 2006 to 2023.
-tar_read(fig9)
+tar_read(fig_completions)
 ```
@@
 #| fig-cap: Percentage distribution of graduate completions by age, aggregated over the years 2006 to 2023.
-tar_read(fig10)
+tar_read(fig_ave_completions)
 ```
@@
 # 2025 and 2035
-tar_read(fig23)
+#tar_read(fig23)
 ```

### 2025-08-21 _targets.R

@@ -317,12 +317,12 @@ list(
 
   # Document
   tar_target(discipline_table, make_discipline_table()),
-  #tar_quarto(
-  #  report,
-  #  "age_structure_forecasts.qmd",
-  #  output_file = "age_structure_forecasts.pdf",
-  #  extra_files = c("refs.bib", "preamble.tex")
-  #),
+  tar_quarto(
+    report,
+    "age_structure_forecasts.qmd",
+    output_file = "age_structure_forecasts.pdf",
+    extra_files = c("refs.bib", "preamble.tex")
+  ),
   tar_quarto(
     talk,
     "age_structure_talk.qmd",

### 2025-08-21 age_structure_forecasts.qmd
Working on paper

@@
 In our application, these are scientific disciplines, but in principle they could refer to any subdivision of workers.
-Let $P_{i,x,t}$ denote the number of equivalent full-time workers in area or discipline $i$ who are aged $x$ at the start of year $t$, where $i=1,\dots,I$ and $x=15,16,\dots$.
-The starting age of 15 is the minimum age at which individuals are counted as part of the labour force in the Australian Census [@ABSLFSP].
-Forecasts are generated for $P_{i,x,T+h}$ across all ages and disciplines, for some forecast horizon $h>0$.
+Let $P_{i,x,t}$ denote the number of equivalent full-time workers in group $i$ who are aged $x$ at the start of year $t$, where $x=15,16,\dots$.
+The starting age of 15 is chosen because it is the minimum age at which individuals are counted as part of the labour force in the Australian Census [@ABSLFSP].
+Forecasts are required for $P_{i,x,T+h}$ across all ages and groups, for some forecast horizon $h>0$.
 
-Let $D_{i,x,t}$ denote the number of deaths, and $R_{i,x,t}$ the number of retirements, of people aged $x$ in scientific discipline $i$ in year $t$.
-This is the number of equivalent full-time workers leaving the workforce during year $t$ who were aged $x$ *at the start* of year $t$.
+People can leave the workforce of a group through death, retirement, career change, or emigration.
+They can enter the workforce through graduation, immigration, or career change.
+Unfortunately, we typically do not have data on many of these processes, so we will combine career change and migration into a remainder term, which we denote as $E_{i,x,t}$.
+We usually do have data on numbers of deaths ($D_{i,x,t}$), numbers of retirements ($R_{i,x,t}$), and numbers of graduates ($G_{i,x,t}$); the numbers in each case are for people aged $x$ at the start of year $t$.
 
-Two migration processes are required: one representing new Australian workers in the discipline graduating from university courses ($N_{i,x,t}$), and the other representing the net migration process resulting from scientists leaving or arriving in Australia ($G_{i,x,t}$).
-New workers are treated as a migration process because they can be of any age (unlike births).
-
-The population can be forecasted using a model similar to the stochastic population model of @HB08, excluding the birth process. The demographic growth-balance equation can be written as:
+The population can be forecasted using a model similar to the stochastic population model of @HB08, excluding the birth process:
 $$
-P_{i,x+1,t+1} = P_{i,x,t} - D_{i,x,t} - R_{i,x,t} + N_{i,x,t} + G_{i,x,t}, \quad x = 15,16,\dots
+P_{i,x+1,t+1} = P_{i,x,t} - D_{i,x,t} - R_{i,x,t} + G_{i,x,t} + E_{i,x,t}, \quad x = 15,16,\dots
 $$ {#eq-dgb}
-That is, the population each year is equal to the population from the previous year having aged 1 year, minus the deaths or retirements that occurred during the previous year, plus the new graduates, plus the net migrants (which may be negative).
-The assumption is that $D_{i,x,t} + R_{i,x,t} \le P_{i,x,t}$ and $N_{i,x,t} = G_{i,x,t} = 0$ above some age threshold (say $x=100$).
+That is, the population each year is equal to the population from the previous year having aged 1 year, minus the deaths or retirements that occurred during the previous year, plus the new graduates, plus any other changes due to migration or career change (which may be negative).
+We assume that $D$, $R$ and $G$ are all non-negative, $D_{i,x,t} + R_{i,x,t} \le P_{i,x,t}$, and $E_{i,x,t} = G_{i,x,t} = 0$ above some age threshold (say $x=100$).
 Once $P_{i,x,t} = 0$ when $x$ is above that threshold, all future populations $P_{i,x+k,t+k} = 0$, $k=1,2,\dots$.
@@
 
-As a first approximation, the components $D$, $R$, $N$ and $G$ can be assumed to behave independently.
-In reality, there may be a negative correlation between $G$ and $N$ as insufficient graduates would probably lead to employers finding people from overseas, while too many graduates would lead to scientists seeking work elsewhere.
+As a first approximation, the components $D$, $R$, $E$ and $G$ can be assumed to behave independently for each combination of $i$, $x$ and $t$.
+In reality, there may be a negative correlation between $G$ and $E$ as insufficient graduates would probably lead to employers finding people from overseas, while too many graduates would lead to scientists seeking work elsewhere.
 
-Data on $D$, $N$, and $R$ is required, and the remaining component $G$ will be estimated using @eq-dgb.
-
-To obtain forecasts of $P$, forecasts of $D$, $R$, $N$, and $G$ must then be computed. Each of these can be estimated using a functional data model [@HU07].
+To use @eq-dgb, data on $P$, $D$, $R$, and $G$ is required, and the remainder component $E$ will be calculated using @eq-dgb.
+It is unlikely that we have available separate death and retirement counts for each group, so we will instead use probabilities of death and retirement across all groups, giving $D_{i,x,t} = P_{i,x,t}q_{x,t}$ and $R_{i,x,t} = P_{i,x,t}r_{x,t}$ where $q_{x,t}$ is the probability of death at each $x$ in year $t$, and $r_{x,t}$ is the probability of retirement at each $x$ in year $t$.
+Similarly, graduation numbers are rarely available by discipline and age, so we will approximate $G_{i,x,t} = g_xG_t$ where $G_{i,t}$ is the total number of graduates in year $t$ and $g_x$ is the proportion of graduates by age across all disciplines.
+So our more realistic model becomes
+$$
+P_{i,x+1,t+1} = P_{i,x,t}(1 - q_{x,t} - r_{x,t}) + g_xG_{i,t} + E_{i,x,t}, \quad x = 15,16,\dots
+$$ {#eq-dgb2}
+To obtain forecasts of $P$, forecasts of $q$, $r$, $G$, and $E$ must then be computed. Each of these can be estimated using a functional data model [@HU07].
 
@@
 
-## Data Sources
+## Data sources
 
 This analysis focuses on the Natural and Physical Sciences as defined in the Australian Standard Classification of Education (ASCED) by the @ABSASCED.
-For consistency, the report refers to ASCED’s Narrow Fields as "disciplines".
+We refer to ASCED's Narrow Fields as "disciplines"; these comprise Physics and Astronomy, Mathematical Sciences, Chemical Sciences, Earth Sciences, Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences not further defined (n.f.d.).
+We define the population of workers in a discipline as those who are active in the labour market and hold a bachelor's degree or higher in that discipline.
 
-We forecast the number of individuals in each one-year age group who are active in the workforce and hold a bachelor’s degree or higher in the following scientific disciplines: Physics and Astronomy, Mathematical Sciences, Chemical Sciences, Earth Sciences, Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences not further defined (n.f.d.).
+## Labour force participation {#sec-labour}
 
-Projections extend over a 20-year period to 2041, with particular focus on workforce composition in 2035.
-These estimates account for key demographic factors, including mortality, retirement, graduation, and migration.
+Data on $P_{i,x,t}$ are sourced from the *Census of Population and Housing* (2006, 2011, 2016, and 2021) [@ABSCensus].
+This dataset encompasses labour force participation status, age group, the highest level of completed non-school qualification level (QALLP), the corresponding field of study [QALFP; @ABSQALFP], and the industries in which individuals work.
 
-This analysis utilises Australian data sources to generate accurate forecasts. These include the ABS, the Human Mortality Database (HMD), and the Department of Education.
-
-Specifically, the *Census of Population and Housing* (2006, 2011, 2016, and 2021) [@ABSCensus] provides data on the population of individuals with bachelor's degrees or higher who are active in the labour market.
-This dataset encompasses labour force participation status, age group, educational qualification level (QALLP), discipline (QALFP), and the industries in which individuals work.
-Labour force participation data is available only for 2016 and 2021 [@ABSLFFP].
-QALLP captures the highest level of completed non-school qualification, while QALFP identifies the corresponding field of study [@ABSQALFP].
-
-Australian age-specific death counts and population exposures from 1971 to 2021 were sourced from the @HMD. This dataset includes death counts and population exposures categorised by age.
-
-Retirement data is sourced from the *Retirement and Retirement Intentions* dataset (Catalogue 6238) for the 2022--2023 financial year [@ABS6238].
-It provides insights into expected retirement ages for workers in age groups ranging from 45 to 70 across various industries.
-
-Graduate completion statistics from 2006 to 2023, categorised by age group and including individuals with a bachelor’s degree or higher, are derived from the *Award Course Completions* dataset [@DeptEdu].
-Additionally, the Department of Education provides data on the number of graduates with a bachelor’s degree or higher, categorised by discipline and year, for the same period [@DeptEdu_Private].
-These datasets include both domestic and international students.
-
-Data limitations include the availability of labour force participation data only for 2016 and 2021, the absence of full-time worker data outside census years, and the aggregated nature of retirement intentions data.
-These gaps are addressed using specific handling of labour force participation data, cohort interpolation methods, and smoothed disaggregation, as detailed in Sections -@sec-labour, -@sec-cohort, and -@sec-smooth.
-
-Another limitation is that retirement intentions data is unavailable by educational discipline, with industry-level data serving as the closest proxy.
-Since scientists work across multiple industries, this does not capture discipline-specific retirement patterns but is used in this context through methods outlined in @sec-retirement.
-
-## Labour Force Participation {#sec-labour}
-
-Labour force participation data is available for 2016 and 2021.
-To estimate worker numbers for 2006 and 2011, the average participation rates from these later years are applied, assuming overall patterns remain consistent.
+However, labour force participation data is available only for 2016 and 2021 [@ABSLFFP].
+To estimate worker numbers for 2006 and 2011, the average participation rates from 2016 and 2021 were applied, assuming overall patterns remain consistent.
 While participation rates were generally stable between 2016 and 2021, smaller groups experienced more volatility.
-
 Younger and older age groups within some disciplines were particularly affected by this volatility, especially when sample sizes were small.
@@
 
-@fig-labour-force displays the labour force participation rates for the broader category of Natural and Physical Sciences for 2016, 2021, and their average, which serves as a proxy for 2006 and 2011.
-While estimation is conducted separately at both the discipline and category levels, the figure below illustrates this approach using the broader category as an example.
-
-```{r}
-#| label: fig-labour-force
-#| eval: true
-#| fig-cap: Labour force participation rates by one-year age groups for 2016 and 2021, along with the average of these two years, which is used as a proxy for 2006 and 2011.
-tar_read(fig1)
-```
-
-## Cohort Interpolation {#sec-cohort}
-
-The Census data on scientists active in the labour market, provided by the ABS in one-year age groups, is shown in @fig-census as a line graph to highlight differences across Census years.
-
-As data is only available in Census years (2006, 2011, 2016, 2021), cohort interpolation will be used to estimate intercensal values for the intervening years.
-These are the years between Census points (e.g., 2007, 2008, 2009, etc.), for which direct population data are unavailable.
-
-Cohort interpolation methods, as described by @STUPP88, approximate these missing values by leveraging available Census data.
-For this analysis, linear interpolation is applied to estimate the population distribution for the years between Census points, as it provides reasonable approximations given the available data.
-In this context, linear interpolation produces gradual transitions that reflect realistic population growth and decline.
-
-The completed historical dataset forms the basis for forecasting future workforce trends. The results of this interpolation are shown in @fig-cohort-interpolation.
-
-```{r}
-#| label: fig-census
-#| eval: true
-#| fig-cap: Distribution of scientists active in the labour market by age across  Census years (2006, 2011, 2016, 2021).
-tar_read(fig_Pxt_census)
-```
+The census data on scientists active in the labour market, provided by the ABS in one-year age groups, is shown in @fig-cohort-interpolation as the thick lines.
+As data is only available in census years (2006, 2011, 2016, 2021), cohort interpolation is used to estimate values for the intervening years.
+Cohort interpolation methods [@STUPP88] apply linear interpolation within each age cohort between census years.
 
@@
 #| eval: true
-#| fig-cap: Interpolated number of scientists in Australia, 2006--2021, using linear cohort interpolation.
+#| fig-cap: Interpolated number of scientists in Australia, 2006--2021, using linear cohort interpolation between census years. Thicker lines are used to denote census years.
 tar_read(fig_Pxt)
@@
 
-## Smoothed Disaggregation {#sec-smooth}
+## Retirement distribution {#sec-smooth}
 
@@
 ```
-
-## Retirement Distribution by Age {#sec-retirement}
 
@@
 This ensures that the combined probability of exiting the workforce (through retirement or death) does not exceed 100%.
+
+Projections extend over a 20-year period to 2041, with particular focus on workforce composition in 2035.
+These estimates account for key demographic factors, including mortality, retirement, graduation, and migration.
+
+This analysis utilises Australian data sources to generate accurate forecasts. These include the ABS, the Human Mortality Database (HMD), and the Department of Education.
+
+Australian age-specific death counts and population exposures from 1971 to 2021 were sourced from the @HMD. This dataset includes death counts and population exposures categorised by age.
+
+Retirement data is sourced from the *Retirement and Retirement Intentions* dataset (Catalogue 6238) for the 2022--2023 financial year [@ABS6238].
+It provides insights into expected retirement ages for workers in age groups ranging from 45 to 70 across various industries.
+
+Graduate completion statistics from 2006 to 2023, categorised by age group and including individuals with a bachelor’s degree or higher, are derived from the *Award Course Completions* dataset [@DeptEdu].
+Additionally, the Department of Education provides data on the number of graduates with a bachelor’s degree or higher, categorised by discipline and year, for the same period [@DeptEdu_Private].
+These datasets include both domestic and international students.
+
+Data limitations include the availability of labour force participation data only for 2016 and 2021, the absence of full-time worker data outside census years, and the aggregated nature of retirement intentions data.
+These gaps are addressed using specific handling of labour force participation data, cohort interpolation methods, and smoothed disaggregation, as detailed in Sections -@sec-labour, -@sec-cohort, and -@sec-smooth.
+
+Another limitation is that retirement intentions data is unavailable by educational discipline, with industry-level data serving as the closest proxy.
+Since scientists work across multiple industries, this does not capture discipline-specific retirement patterns but is used in this context through methods outlined in @sec-retirement.
 

### 2025-08-22 age_structure_forecasts.qmd
Working on paper

@@
 We propose a statistical modelling approach to this problem, illustrated using various scientific disciplines in Australia, forecasting future workforce age structures over the next decade.
-The forecasts described have been used by the Australian Academy of Science as part of _Australian Science, Australia’s Future: Science 2035_, an initiative assessing the capability of the national science system and its role in achieving Australia’s ambitions [@AAS2035].
+The forecasts described have been used by the Australian Academy of Science as part of _Australian Science, Australia's Future: Science 2035_, an initiative assessing the capability of the national science system and its role in achieving Australia's ambitions [@AAS2035].
 
@@
 We describe the data sources in @sec-data, with the results provided in @sec-results.
-The aim of this analysis is to inform future workforce planning and policy decisions to support the growth of Australia’s scientific community.
+The aim of this analysis is to inform future workforce planning and policy decisions to support the growth of Australia's scientific community.
 Finally, we provide some discussion and conclusions in @sec-conclusion.
@@
 The starting age of 15 is chosen because it is the minimum age at which individuals are counted as part of the labour force in the Australian Census [@ABSLFSP].
-Forecasts are required for $P_{i,x,T+h}$ across all ages and groups, for some forecast horizon $h>0$.
+We assume that data are available for years $t=1,\dots,T$, and that forecasts are required for $P_{i,x,T+h}$ across all ages and groups, for some forecast horizon $h>0$.
 
@@
 They can enter the workforce through graduation, immigration, or career change.
-Unfortunately, we typically do not have data on many of these processes, so we will combine career change and migration into a remainder term, which we denote as $E_{i,x,t}$.
-We usually do have data on numbers of deaths ($D_{i,x,t}$), numbers of retirements ($R_{i,x,t}$), and numbers of graduates ($G_{i,x,t}$); the numbers in each case are for people aged $x$ at the start of year $t$.
-
-The population can be forecasted using a model similar to the stochastic population model of @HB08, excluding the birth process:
+Unfortunately, we typically do not have data on many of these processes, so we will combine career change, emigration and immigration into a remainder term, which we denote as $E_{i,x,t}$.
+Suppose we do have data on numbers of deaths ($D_{i,x,t}$), numbers of retirements ($R_{i,x,t}$), and numbers of graduates ($G_{i,x,t}$); the numbers in each case are for people aged $x$ at the start of year $t$.
+Then population changes can be described using a model similar to the stochastic population model of @HB08, excluding the birth process:
 $$
-P_{i,x+1,t+1} = P_{i,x,t} - D_{i,x,t} - R_{i,x,t} + G_{i,x,t} + E_{i,x,t}, \quad x = 15,16,\dots
+P_{i,x+1,t+1} = P_{i,x,t} - D_{i,x,t} - R_{i,x,t} + G_{i,x,t} + E_{i,x,t}, 
 $$ {#eq-dgb}
@@
 We assume that $D$, $R$ and $G$ are all non-negative, $D_{i,x,t} + R_{i,x,t} \le P_{i,x,t}$, and $E_{i,x,t} = G_{i,x,t} = 0$ above some age threshold (say $x=100$).
-Once $P_{i,x,t} = 0$ when $x$ is above that threshold, all future populations $P_{i,x+k,t+k} = 0$, $k=1,2,\dots$.
-That is, when the cohort aged $x$ in year $t$ has all retired or died, they will not be replaced through new graduates or migrants of the same age.
+Once $P_{i,x,t} = 0$ when $x$ is above that threshold, all future populations $P_{i,x+k,t+k} = 0$, forw $k=1,2,\dots$.
+That is, when the cohort aged $x$ in year $t$ has all retired or died, they will not be replaced by new workers of the same age.
 
@@
 $$
-P_{i,x+1,t+1} = P_{i,x,t}(1 - q_{x,t} - r_{x,t}) + g_xG_{i,t} + E_{i,x,t}, \quad x = 15,16,\dots
+P_{i,x+1,t+1} = P_{i,x,t}(1 - q_{x,t} - r_{x,t}) + g_xG_{i,t} + E_{i,x,t}, 
 $$ {#eq-dgb2}
-To obtain forecasts of $P$, forecasts of $q$, $r$, $G$, and $E$ must then be computed. Each of these can be estimated using a functional data model [@HU07].
+To obtain forecasts of $P$, forecasts of $q$, $r$, $G$, and $E$ must then be computed. Each of these can be estimated using a functional time series model [@HU07].
 
@@
 Data on $P_{i,x,t}$ are sourced from the *Census of Population and Housing* (2006, 2011, 2016, and 2021) [@ABSCensus].
-This dataset encompasses labour force participation status, age group, the highest level of completed non-school qualification level (QALLP), the corresponding field of study [QALFP; @ABSQALFP], and the industries in which individuals work.
-
+This dataset encompasses labour force participation status, age group, the highest level of completed non-school qualification level (QALLP), the corresponding field of study [QALFP, @ABSQALFP], and the industries in which individuals work.
 However, labour force participation data is available only for 2016 and 2021 [@ABSLFFP].
-To estimate worker numbers for 2006 and 2011, the average participation rates from 2016 and 2021 were applied, assuming overall patterns remain consistent.
-While participation rates were generally stable between 2016 and 2021, smaller groups experienced more volatility.
-Younger and older age groups within some disciplines were particularly affected by this volatility, especially when sample sizes were small.
-For example, in a group of five 15--19-year-olds, a single individual's employment status change could significantly shift the participation rate.
-Similarly, fluctuations in smaller cohorts of older scientists impacted participation rates.
-Averaging the rates from 2016 and 2021 helps mitigate this volatility and provides a more stable estimate for 2006 and 2011.
-Any discrepancies in participation rates are minimal due to the small cohort sizes, making this a more reliable approach than relying on a single year.
+To estimate worker numbers for 2006 and 2011, the average participation rates from 2016 and 2021 were applied, assuming overall age distributions remain consistent.
 
 The census data on scientists active in the labour market, provided by the ABS in one-year age groups, is shown in @fig-cohort-interpolation as the thick lines.
-As data is only available in census years (2006, 2011, 2016, 2021), cohort interpolation is used to estimate values for the intervening years.
-Cohort interpolation methods [@STUPP88] apply linear interpolation within each age cohort between census years.
+As data is only available in census years (2006, 2011, 2016, 2021), cohort interpolation is used to estimate values for the intervening years (shown as thin lines).
+Cohort finterpolation methods [@STUPP88] apply linear interpolation within each age cohort between census years.
 
@@
 
-Retirement intentions data is categorised by the industry of an individual's main job and is provided in broad age groups, as shown in @fig-beforedisaggregation.
-While the ABS dataset covers 19 industries, only the key industries relevant to this study are displayed in the figure.
+Retirement intentions data are categorised by the industry of an individual's main job and is provided in four broad age groups (45--59, 60--64, 65--69 and 70+).
+While ABS data covers 19 industries, only the key industries relevant to science are included, namely Professional, scientific and technical services, Education and training, and Health care and social assistance.
 
-To estimate single-year age distributions, a monotonic cubic spline [@SHW04] is applied directly to the cumulative values of these age groups, ensuring a smooth transition between them.
+To estimate a single-year retirement age distribution, a monotonic cubic spline [@SHW04] is applied directly to the cumulative values of these age groups, ensuring a smooth transition between them.
 This method preserves the overall distribution while generating continuous single-year estimates, as shown in @fig-retirements.
@@
 
-Graduate completion statistics from 2006 to 2023, categorised by age group and including individuals with a bachelor’s degree or higher, are derived from the *Award Course Completions* dataset [@DeptEdu].
-Additionally, the Department of Education provides data on the number of graduates with a bachelor’s degree or higher, categorised by discipline and year, for the same period [@DeptEdu_Private].
+Graduate completion statistics from 2006 to 2023, categorised by age group and including individuals with a bachelor's degree or higher, are derived from the *Award Course Completions* dataset [@DeptEdu].
+Additionally, the Department of Education provides data on the number of graduates with a bachelor's degree or higher, categorised by discipline and year, for the same period [@DeptEdu_Private].
 These datasets include both domestic and international students.
@@
 
-This analysis contributes to the Australian Academy of Science’s initiative _Australian Science, Australia’s Future: Science 2035_ by identifying shifts in the workforce, helping anticipate future demand for science capabilities, and highlighting potential workforce gaps as aging and retirement reshape workforce dynamics.
+This analysis contributes to the Australian Academy of Science's initiative _Australian Science, Australia's Future: Science 2035_ by identifying shifts in the workforce, helping anticipate future demand for science capabilities, and highlighting potential workforce gaps as aging and retirement reshape workforce dynamics.
 

### 2025-08-25 age_structure_forecasts.qmd
End of week
Working on data section

@@
 
-## Labour force participation {#sec-labour}
+## Labour force participation
 
-Data on $P_{i,x,t}$ are sourced from the *Census of Population and Housing* (2006, 2011, 2016, and 2021) [@ABSCensus].
-This dataset encompasses labour force participation status, age group, the highest level of completed non-school qualification level (QALLP), the corresponding field of study [QALFP, @ABSQALFP], and the industries in which individuals work.
-However, labour force participation data is available only for 2016 and 2021 [@ABSLFFP].
+Data on $P_{i,x,t}$ are sourced from the *Census of Population and Housing* [@ABSCensus] for census years 2006, 2011, 2016, and 2021.
+This dataset encompasses one-year age groups, the highest level of completed non-school qualification level (QALLP), the corresponding field of study [QALFP, @ABSQALFP], and the industries in which individuals work.
+However, labour force participation status [@ABSLFFP] is available only for 2016 and 2021.
 To estimate worker numbers for 2006 and 2011, the average participation rates from 2016 and 2021 were applied, assuming overall age distributions remain consistent.
 
-The census data on scientists active in the labour market, provided by the ABS in one-year age groups, is shown in @fig-cohort-interpolation as the thick lines.
-As data is only available in census years (2006, 2011, 2016, 2021), cohort interpolation is used to estimate values for the intervening years (shown as thin lines).
-Cohort finterpolation methods [@STUPP88] apply linear interpolation within each age cohort between census years.
+The resulting data on scientists who are active in the Australian labour market is shown in @fig-cohort-interpolation as the thick lines.
+Cohort interpolation [@STUPP88], applying linear interpolation within each age cohort between census years, is used to estimate values for the intercensal years (shown as thin lines).
 
@@
 #| eval: true
-#| fig-cap: Interpolated number of scientists in Australia, 2006--2021, using linear cohort interpolation between census years. Thicker lines are used to denote census years.
-tar_read(fig_Pxt)
+#| fig-cap: "$P_{i,x,t}$: Estimated number of working scientists in Australia by discipline and age, 2006--2021. Thicker lines are used to denote census years."
+tar_read(fig20)
 ```
 
-## Retirement distribution {#sec-smooth}
+## Retirements
 
-Retirement intentions data are categorised by the industry of an individual's main job and is provided in four broad age groups (45--59, 60--64, 65--69 and 70+).
-While ABS data covers 19 industries, only the key industries relevant to science are included, namely Professional, scientific and technical services, Education and training, and Health care and social assistance.
-
-To estimate a single-year retirement age distribution, a monotonic cubic spline [@SHW04] is applied directly to the cumulative values of these age groups, ensuring a smooth transition between them.
-This method preserves the overall distribution while generating continuous single-year estimates, as shown in @fig-retirements.
-
-```{r}
-#| label: fig-beforedisaggregation
-#| eval: true
-#| fig-cap: Retirement intentions for key industries before smoothed disaggregation.
-tar_read(fig_r)
-```
-
-After smoothing the retirement intentions data, the appropriate industry-level retirement distribution or combination of distributions must be selected.
-Since scientists work across multiple industries, industry-level data must be adapted to reflect discipline-specific trends.
-While distributions may vary, retirement trends generally follow similar patterns across sectors.
-By focusing on the top industries, which account for the majority of workers in each discipline, a stable foundation for analysis is ensured, minimising unnecessary variability arising from changing worker proportions in different industries over time.
-
-For the Natural and Physical Sciences, the three primary industries in which the workforce is employed are Education and Training, Professional, Scientific and Technical Services, and Health Care and Social Assistance, representing 15.81%, 15.48%, and 14.65%, respectively.
-The proportions in other industries decrease significantly beyond this point.
-To estimate retirement intentions, a weighted average was calculated using these top three industries, with proportions rescaled to sum to 1.
-
-The data show that a significant portion of workers plan to retire between the ages of 60 and 70.
-This distribution of retirement ages exhibits positive kurtosis, with the highest peak at age 67, where 13.16% of workers indicate their intention to retire, as shown in @fig-retirements.
+Retirement data is sourced from the *Retirement and Retirement Intentions* dataset (Catalogue 6238) for the 2022--2023 financial year [@ABS6238].
+The data are categorised by the industry of an individual's main job, and are provided in four broad age groups (45--59, 60--64, 65--69 and 70+).
+There are 19 industry categories, but the majority of scientists work in Education and Training, Professional, Scientific and Technical Services, and Health Care and Social Assistance, representing 15.8%, 15.5%, and 14.6%, respectively.
+The proportions in other industries are much smaller.
+We take a weighted average of retirement intentions using these top three industries, with proportions rescaled to sum to 1.
+The data are shown in @fig-retirements as the gray line.
+To obtain a single-year-or-age retirement distribution, we disaggregate the data using a monotonic cubic spline applied to the cumulative values of these age groups [@SHW04].
+The resulting smoothed distribution is shown as the blue line in @fig-retirements.
 
@@
 #| eval: true
-#| fig-cap: Age distribution of retirement intentions for the 2022--2023 Australian financial year.
-tar_read(fig_rx)
-```
-
-From this distribution, the empirical probability of retirement at each age can be calculated using standard life table methods [@MRC18].
-These probabilities are shown in @fig-retirements2.
-These probabilities, which exhibit a significant increase after age 59, are used to estimate $R_{i,x,t}$ from $P_{i,x,t}$​, and are treated as fixed for the simulation, assuming that retirement patterns will remain stable over time.
-
-```{r}
-#| label: fig-retirements2
-#| eval: true
-#| fig-cap: Age-specific probability of retirement based on the 2022--2023 Australian financial year.
+#| fig-cap: "$r_x$: Age distribution of retirement intentions for the 2022--2023 Australian financial year. The blue line shows the smoothed distribution."
 tar_read(fig_rx2)
@@
 
-In this approach, retirement is treated as a final state, meaning that once a scientist retires, they are not reintroduced into the workforce.
-This assumption considers workforce exit to be final.
-Mortality data, discussed in the next section, is incorporated into the calculation of the total probability of leaving the workforce, adjusting for the possibility of death before retirement.
-This ensures that the combined probability of exiting the workforce (through retirement or death) does not exceed 100%.
+These probabilities are used to estimate $r_{x,t}$, and are treated as fixed for the simulation, assuming that retirement patterns will remain stable over time.
 
-Projections extend over a 20-year period to 2041, with particular focus on workforce composition in 2035.
-These estimates account for key demographic factors, including mortality, retirement, graduation, and migration.
-
-This analysis utilises Australian data sources to generate accurate forecasts. These include the ABS, the Human Mortality Database (HMD), and the Department of Education.
-
-Australian age-specific death counts and population exposures from 1971 to 2021 were sourced from the @HMD. This dataset includes death counts and population exposures categorised by age.
-
-Retirement data is sourced from the *Retirement and Retirement Intentions* dataset (Catalogue 6238) for the 2022--2023 financial year [@ABS6238].
-It provides insights into expected retirement ages for workers in age groups ranging from 45 to 70 across various industries.
-
-Graduate completion statistics from 2006 to 2023, categorised by age group and including individuals with a bachelor's degree or higher, are derived from the *Award Course Completions* dataset [@DeptEdu].
-Additionally, the Department of Education provides data on the number of graduates with a bachelor's degree or higher, categorised by discipline and year, for the same period [@DeptEdu_Private].
-These datasets include both domestic and international students.
-
-Data limitations include the availability of labour force participation data only for 2016 and 2021, the absence of full-time worker data outside census years, and the aggregated nature of retirement intentions data.
-These gaps are addressed using specific handling of labour force participation data, cohort interpolation methods, and smoothed disaggregation, as detailed in Sections -@sec-labour, -@sec-cohort, and -@sec-smooth.
-
-Another limitation is that retirement intentions data is unavailable by educational discipline, with industry-level data serving as the closest proxy.
-Since scientists work across multiple industries, this does not capture discipline-specific retirement patterns but is used in this context through methods outlined in @sec-retirement.
-
-## Death Probabilities by Age
+## Deaths
 
@@
 Over time, mortality probabilities have generally declined across all age groups, reflecting improvements in Australian life expectancy.
-Consequently, fewer scientists are expected to exit the workforce due to death, illness, or related factors.
-Similar to retirement, death is treated as a final state; once a scientist dies, they are no longer part of the workforce.
 
@@
 
-Although the final workforce forecasts focus on individuals aged 15 and older, mortality probability estimates are derived from data covering ages 0 to 100.
-These probabilities serve as inputs for estimating $D_{i,x,t}$, the number of deaths among full-time equivalent workers in scientific discipline $i$ at age $x$ in year $t$, based on $P_{i,x,t}$, the corresponding population of such workers.
-Death estimates are calculated by applying the forecasted mortality probabilities to the workforce population.
+No data are available for specific industry groups, so we assume that all scientists have the same mortality probabilities as the general population.
+These probabilities serve as estimates of $q_{x,t}$.
 
-## Graduate Completions by Age
+## Graduate Completions
 
-Data on graduate completions by age and year is not available for individual disciplines.
-However, it is available in aggregate across all disciplines, allowing for an analysis of how the age distribution of graduates has changed over time.
-
-@fig-completions1 shows the percentage distribution of graduate completions by age for each year from 2006 to 2023.
+Graduate completion statistics are obtained from the *Award Course Completions* dataset [@DeptEdu].
+@fig-completions2 shows the distribution of graduate completions with a bachelor's degree or higher, by age for each year from 2006 to 2023.
 Some missing values result in gaps in certain lines, but the overall pattern remains highly consistent across years.
-Given this consistency, the data is averaged across all available years to construct a representative age distribution of graduates at the bachelor's level and higher.
-
-```{r}
-#| label: fig-completions1
-#| eval: true
-#| fig-cap: Percentage distribution of graduate completions by age for each year from 2006 to 2023.
-tar_read(fig_completions)
-```
-
-The resulting averaged distribution, shown in @fig-completions2, smooths out year-to-year fluctuations and provides a stable estimate of graduate completions by age.
-This transformation assumes that the overall age distribution of graduates remains relatively stable over time, allowing for a more reliable estimate when applied to specific disciplines.
+Given this consistency, the data is averaged across all available years, and then smoothed by applying monotonic cubic splines to the cumulative values [@SHW04].
+The resulting averaged distribution, shown as the black line in @fig-completions2, smooths out year-to-year fluctuations and provides a stable estimate of $g_x$.
 
@@
 #| eval: true
-#| fig-cap: Percentage distribution of graduate completions by age, aggregated over the years 2006 to 2023.
+#| fig-cap: Percentage distribution of graduate completions by age over the years 2006 to 2023. The black line shows a smoothed estimate of the average distribution.
 tar_read(fig_ave_completions)
@@
 
-@tbl-completions highlights the percentage distribution of graduates aged 20 to 25, demonstrating a pronounced peak in this range, with the highest percentage observed at age 21.
-This reflects the typical age at which students complete their tertiary education.
+The Department of Education provides data on the number of graduates with a bachelor's degree or higher, categorised by discipline and year [@DeptEdu_Private].
+These datasets include both domestic and international students.
+Estimate of $G_{i,t}$, the total number of graduates in each discipline $i$ and year $t$, are shown in @fig21.
 
 ```{r}
-#| label: tbl-completions
-#| eval: true
-#| tbl-cap: Percentage distribution of graduate completions for ages 20-25 for the years 2006 to 2023.
-tar_read(tab2)
+#| label: fig21
+#| fig-cap: "Total number of graduates with a bachelor's degree or higher by discipline from 2006 to 2023."
+tar_read(fig21)
 ```

### 2025-08-25 age_structure_forecasts.qmd
past tense

@@
 
-Data on $P_{i,x,t}$ are sourced from the *Census of Population and Housing* [@ABSCensus] for census years 2006, 2011, 2016, and 2021.
+Data on $P_{i,x,t}$ were sourced from the *Census of Population and Housing* [@ABSCensus] for census years 2006, 2011, 2016, and 2021.
 This dataset encompasses one-year age groups, the highest level of completed non-school qualification level (QALLP), the corresponding field of study [QALFP, @ABSQALFP], and the industries in which individuals work.
@@
 
-Retirement data is sourced from the *Retirement and Retirement Intentions* dataset (Catalogue 6238) for the 2022--2023 financial year [@ABS6238].
+Retirement data was sourced from the *Retirement and Retirement Intentions* dataset (Catalogue 6238) for the 2022--2023 financial year [@ABS6238].
 The data are categorised by the industry of an individual's main job, and are provided in four broad age groups (45--59, 60--64, 65--69 and 70+).
-There are 19 industry categories, but the majority of scientists work in Education and Training, Professional, Scientific and Technical Services, and Health Care and Social Assistance, representing 15.8%, 15.5%, and 14.6%, respectively.
+There are 19 industry categories, with the largest numbers of scientists working in Education and Training (15.8%), Professional, Scientific and Technical Services (15.5%), and Health Care and Social Assistance (14.6%).
 The proportions in other industries are much smaller.
 We take a weighted average of retirement intentions using these top three industries, with proportions rescaled to sum to 1.
-The data are shown in @fig-retirements as the gray line.
-To obtain a single-year-or-age retirement distribution, we disaggregate the data using a monotonic cubic spline applied to the cumulative values of these age groups [@SHW04].
-The resulting smoothed distribution is shown as the blue line in @fig-retirements.
+The resulting values are shown in @fig-retirements as the gray line.
+To obtain a single-year-of-age retirement distribution, we disaggregate the data using a monotonic cubic spline applied to the cumulative values of these age groups [@SHW04].
+The resulting smoothed distribution is shown as the black line in @fig-retirements.
 
@@
 
-Age-specific mortality rates from 1971 to 2021 are obtained from the @HMD.
+Age-specific mortality rates from 1971 to 2021 were obtained from the @HMD.
 Using standard life table methods, these rates are converted into age-specific probabilities of death, as shown in @fig-death-probs.
@@
 #| eval: true
-#| fig-cap: Age-specific probabilities of death (on a logarithmic scale) for each year from 1971 to 2021.
+#| fig-cap: "$q_{x,t}$: Age-specific probabilities of death (on a logarithmic scale) for each year from 1971 to 2021."
 tar_read(fig_mxt)
@@
 
-Graduate completion statistics are obtained from the *Award Course Completions* dataset [@DeptEdu].
+Graduate completion statistics were obtained from the *Award Course Completions* dataset [@DeptEdu].
 @fig-completions2 shows the distribution of graduate completions with a bachelor's degree or higher, by age for each year from 2006 to 2023.
@@
 These datasets include both domestic and international students.
-Estimate of $G_{i,t}$, the total number of graduates in each discipline $i$ and year $t$, are shown in @fig21.
+Estimate of $G_{i,t}$, the total number of graduates in each discipline $i$ and year $t$, are shown in @fig-21.
 
 ```{r}
-#| label: fig21
+#| label: fig-21
 #| fig-cap: "Total number of graduates with a bachelor's degree or higher by discipline from 2006 to 2023."

### 2025-08-26 age_structure_forecasts.qmd
Finished Data section

@@
   - blindable-div
-execute:
-  eval: false
 ---
@@
 ```{r setup, include=FALSE}
-#| eval: true
 library(targets)
@@
 To use @eq-dgb, data on $P$, $D$, $R$, and $G$ is required, and the remainder component $E$ will be calculated using @eq-dgb.
-It is unlikely that we have available separate death and retirement counts for each group, so we will instead use probabilities of death and retirement across all groups, giving $D_{i,x,t} = P_{i,x,t}q_{x,t}$ and $R_{i,x,t} = P_{i,x,t}r_{x,t}$ where $q_{x,t}$ is the probability of death at each $x$ in year $t$, and $r_{x,t}$ is the probability of retirement at each $x$ in year $t$.
+It is unlikely that we have available separate death and retirement counts for each group, and retirement data is not available in all years.
+So we will instead use probabilities of death and retirement across all groups, and assume retirement probability does not change over time, giving $D_{i,x,t} = P_{i,x,t}q_{x,t}$ and $R_{i,x,t} = P_{i,x,t}r_{x}$ where $q_{x,t}$ is the probability of death at each age $x$ in year $t$, and $r_{x}$ is the probability of retirement at each age $x$.
 Similarly, graduation numbers are rarely available by discipline and age, so we will approximate $G_{i,x,t} = g_xG_t$ where $G_{i,t}$ is the total number of graduates in year $t$ and $g_x$ is the proportion of graduates by age across all disciplines.
@@
 $$
-P_{i,x+1,t+1} = P_{i,x,t}(1 - q_{x,t} - r_{x,t}) + g_xG_{i,t} + E_{i,x,t},
+P_{i,x+1,t+1} = P_{i,x,t}(1 - q_{x,t} - r_{x}) + g_xG_{i,t} + E_{i,x,t},
 $$ {#eq-dgb2}
@@
 
-## Data sources
-
 This analysis focuses on the Natural and Physical Sciences as defined in the Australian Standard Classification of Education (ASCED) by the @ABSASCED.
 We refer to ASCED's Narrow Fields as "disciplines"; these comprise Physics and Astronomy, Mathematical Sciences, Chemical Sciences, Earth Sciences, Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences not further defined (n.f.d.).
+@tbl-disciplines lists the detailed fields within each scientific discipline.
+
+```{r}
+#| label: tbl-disciplines
+#| tbl-cap: Classification of scientific disciplines, based on the ASCED Narrow Fields of Education within the Broad Field of Natural and Physical Sciences.
+The table lists their corresponding Detailed Fields.
+"n.e.c." stands for "Not Elsewhere Classified."
+tar_read(discipline_table)
+```
+
 We define the population of workers in a discipline as those who are active in the labour market and hold a bachelor's degree or higher in that discipline.
 
-## Labour force participation
+## Working Population
 
-Data on $P_{i,x,t}$ were sourced from the *Census of Population and Housing* [@ABSCensus] for census years 2006, 2011, 2016, and 2021.
+Data on the working population were sourced from the *Census of Population and Housing* [@ABSCensus] for census years 2006, 2011, 2016, and 2021.
 This dataset encompasses one-year age groups, the highest level of completed non-school qualification level (QALLP), the corresponding field of study [QALFP, @ABSQALFP], and the industries in which individuals work.
@@
 
-The resulting data on scientists who are active in the Australian labour market is shown in @fig-cohort-interpolation as the thick lines.
+The resulting estimates of the number of scientists who are active in the Australian labour market is shown in @fig-cohort-interpolation as the thick lines.
 Cohort interpolation [@STUPP88], applying linear interpolation within each age cohort between census years, is used to estimate values for the intercensal years (shown as thin lines).
@@
 #| label: fig-cohort-interpolation
-#| eval: true
 #| fig-cap: "$P_{i,x,t}$: Estimated number of working scientists in Australia by discipline and age, 2006--2021. Thicker lines are used to denote census years."
@@
 To obtain a single-year-of-age retirement distribution, we disaggregate the data using a monotonic cubic spline applied to the cumulative values of these age groups [@SHW04].
-The resulting smoothed distribution is shown as the black line in @fig-retirements.
+The resulting smoothed distribution ($r_x$) is shown as the black line in @fig-retirements.
 
@@
 #| label: fig-retirements
-#| eval: true
-#| fig-cap: "$r_x$: Age distribution of retirement intentions for the 2022--2023 Australian financial year. The blue line shows the smoothed distribution."
+#| fig-cap: "$r_x$: Age distribution of retirement intentions, based on data from the 2022--2023 Australian financial year. The blue line shows the smoothed probabilities."
 tar_read(fig_rx2)
 ```
-
-These probabilities are used to estimate $r_{x,t}$, and are treated as fixed for the simulation, assuming that retirement patterns will remain stable over time.
 
@@
 #| label: fig-death-probs
-#| eval: true
 #| fig-cap: "$q_{x,t}$: Age-specific probabilities of death (on a logarithmic scale) for each year from 1971 to 2021."
@@
 Graduate completion statistics were obtained from the *Award Course Completions* dataset [@DeptEdu].
-@fig-completions2 shows the distribution of graduate completions with a bachelor's degree or higher, by age for each year from 2006 to 2023.
+@fig-completions shows the distribution of graduate completions with a bachelor's degree or higher, by age for each year from 2006 to 2023.
 Some missing values result in gaps in certain lines, but the overall pattern remains highly consistent across years.
 Given this consistency, the data is averaged across all available years, and then smoothed by applying monotonic cubic splines to the cumulative values [@SHW04].
-The resulting averaged distribution, shown as the black line in @fig-completions2, smooths out year-to-year fluctuations and provides a stable estimate of $g_x$.
+The resulting averaged distribution, shown as the black line in @fig-completions, smooths out year-to-year fluctuations and provides an  estimate of $g_x$.
 
 ```{r}
-#| label: fig-completions2
-#| eval: true
-#| fig-cap: Percentage distribution of graduate completions by age over the years 2006 to 2023. The black line shows a smoothed estimate of the average distribution.
+#| label: fig-completions
+#| fig-cap: "$g_x$: Estimated distribution of graduate completions by age (black). This is estimated by averaging and smoothing the data for the years 2006 to 2023 (coloured)."
 tar_read(fig_ave_completions)
@@
 The Department of Education provides data on the number of graduates with a bachelor's degree or higher, categorised by discipline and year [@DeptEdu_Private].
-These datasets include both domestic and international students.
-Estimate of $G_{i,t}$, the total number of graduates in each discipline $i$ and year $t$, are shown in @fig-21.
+This dataset includes both domestic and international students.
+The total number of graduates in each discipline $i$ and year $t$, are shown in @fig-graduates.
 
 ```{r}
-#| label: fig-21
-#| fig-cap: "Total number of graduates with a bachelor's degree or higher by discipline from 2006 to 2023."
+#| label: fig-graduates
+#| fig-cap: "$G_{i,t}$: Total number of graduates with a bachelor's degree or higher by discipline from 2006 to 2023."
 tar_read(fig21)
@@
 
-## Net Migration
+The large increase in the working population observed in the 2021 Census for Mathematical Sciences (@fig-cohort-interpolation) can be partly attributed to the sharp rise in graduate numbers between 2016 and 2021.
 
-The demographic growth-balance equation (@eq-dgb), when rearranged, provides an estimate of net migration:
+## Remainder
+
+The demographic growth-balance equation (@eq-dgb2), when rearranged, provides an estimate of the remainder, including net migration and career changes:
 $$
-G_{i,x,t} = P_{i,x+1,t+1} - P_{i,x,t} + D_{i,x,t} + R_{i,x,t} - N_{i,x,t}, \quad x = 15,16,\dots
-$$ {#eq-netmigration}
+E_{i,x,t} = P_{i,x+1,t+1} - P_{i,x,t}(1 - q_{x,t} - r_{x}) - g_xG_{i,t},
+$$ {#eq-remainder}
+These remainders are shown in @fig-remainder.
 
-In this equation, $G$ represents the difference required to balance population changes over time after accounting for deaths ($D$), retirements ($R$), new graduates ($N$), and the population at time $t$.
-It serves as the residual value, reflecting the components influencing the workforce's age structure.
+```{r}
+#| label: fig-remainder
+#| fig-cap: Estimated remainder $E_{i,x,t}$ by discipline, age and year (2006--2020), calculated using the demographic growth-balance equation.
+tar_read(fig22)
+```
 
@@
 
-@tbl-disciplines lists the scientific disciplines (as per @ABSASCED Narrow Fields) included in this analysis, along with their corresponding Detailed Fields.
-This table provides essential context for understanding the specific areas classified under each discipline.
-
-```{r}
-#| label: tbl-disciplines
-#| eval: true
-#| tbl-cap: Classification of scientific disciplines, based on the ASCED Narrow Fields of Education within the Broad Field of Natural and Physical Sciences.
-The table lists their corresponding Detailed Fields.
-"n.e.c." stands for "Not Elsewhere Classified."
-tar_read(discipline_table)
-```
-
-## Working Population
-
-The Australian Census provide working population data every five years.
-@fig-working-population shows the age distribution of scientists active in the labour market as recorded in the Census for the years 2006, 2011, 2016, and 2021.
-There are notable differences over time, and between disciplines.
-The number of working scientists has increased over time, especially in Mathematical Sciences in the latest 2021 Census, as well as in Biological Sciences and Other Natural and Physical Sciences.
-The right tail has gradually grown heavier, reflecting an increasing proportion of older scientists, while the distribution has also become wider, indicating a broader age range in the workforce.
-
-The working population for years between census are estimated using linear cohort interpolation [@STUPP88], with the resulting population estimates shown in @fig-interpolated-working-population.
-These interpolated values form the basis for forecasting the future working population, representing the values of $P_{i,x,t}$.
-
-```{r}
-#| label: fig-working-population
-#| eval: true
-#| fig-cap: "Age distribution of the working population across scientific disciplines based on Census data from 2006, 2011, 2016, and 2021.
-Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age for each Census year."
-#| fig-height: 5.5
-tar_read(fig19)
-```
-
-```{r}
-#| label: fig-interpolated-working-population
-#| eval: true
-#| fig-cap: "Age distribution of the working population across scientific disciplines, interpolated from Census data using linear cohort interpolation.
-Each panel represents a different discipline, with lines indicating the number of active scientists in the Australian labour market by age and year."
-#| fig-height: 6
-tar_read(fig20)
-```
-
 ## Graduate Completions
-
-@fig-grad-forecasts shows the number of total graduate completions from 2006 to 2023 ($\sum_x N_{i,x,t}$).
-A significant positive trend is observed in three disciplines: Mathematical Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences (n.f.d.).
-Note that the Y-axis scales vary across disciplines to reflect differences in the number of completions.
-
-The increase in the working population observed in the 2021 Census for Mathematical Sciences, as mentioned earlier, can be partly attributed to the sharp rise in graduate numbers between 2016 and 2021.
-This surge in graduates during that period provides insight into the corresponding growth in the working population.
 
@@
 #| label: fig-grad-forecasts
-#| eval: true
 #| fig-cap: "Forecast number of graduates by discipline, 2024-2041, with 90% prediction intervals, based on historical data from 2006--2023."
@@
 
-Since workforce projections require not only total graduate numbers but also their age distribution, the forecasted totals (depicted in @fig-grad-forecasts) are disaggregated by age using the percentage distribution of graduate completions by age across all disciplines (as shown in @fig-completions2).
+Since workforce projections require not only total graduate numbers but also their age distribution, the forecasted totals (depicted in @fig-grad-forecasts) are disaggregated by age using the percentage distribution of graduate completions by age across all disciplines (as shown in @fig-completions).
 This enables an estimation of how many graduates will enter each age group in future years, ensuring consistency with observed patterns in the broader graduate population.
@@
 
-Net migration ($G_{i,x,t}$) is estimated using the demographic growth-balance equation, which is rearranged to calculate the net number of migrants each year (@eq-netmigration).
+Net migration ($G_{i,x,t}$) is estimated using the demographic growth-balance equation, which is rearranged to calculate the net number of migrants each year (@eq-remainder).
 @fig-net-migration-disciplines shows the age distribution of net migration among scientists between 2006 and 2020.
@@
 #| label: fig-net-migration-disciplines
-#| eval: true
 #| fig-cap: Estimated net migration by age across scientific disciplines (2006--2020). Each panel represents a different discipline, showing net migration trends across age groups.
@@
 **Graduate Numbers:** Fit an ARIMA model [@fpp3] to simulate total numbers of graduates in each future year from the numbers shown in @fig-grad-forecasts.
-These graduate numbers will then be disaggregated by age using the age distribution shown in @fig-completions2 to estimate age-specific graduate numbers in each year.
+These graduate numbers will then be disaggregated by age using the age distribution shown in @fig-completions to estimate age-specific graduate numbers in each year.
 4.
-**Retirements:** Estimate retirements in each year by multiplying the number of people of working age in each age bracket (@fig-interpolated-working-population) by the retirement probabilities shown in @fig-retirements2.
+**Retirements:** Estimate retirements in each year by multiplying the number of people of working age in each age bracket (@fig-interpolated-working-population) by the retirement probabilities shown in @fig-retirements.
 Fixed age-specific retirement probabilities are used.
@@
 #| label: fig-future-physics
-#| eval: true
 #| fig-height: 3
@@
 #| label: fig-forecast-working-population
-#| eval: true
 #| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across scientific disciplines.
@@
 #| label: fig-forecast-total-working-scientists
-#| eval: true
 #| fig-cap: "Forecasted total number of working scientists across scientific disciplines from 2022 to 2041.

### 2025-08-27 age_structure_forecasts.qmd
Lots of work on paper

@@
 
-People can leave the workforce of a group through death, retirement, career change, or emigration.
-They can enter the workforce through graduation, immigration, or career change.
+People can leave the workforce of a group through death, retirement, emigration, or career change; they can enter the workforce through graduation, immigration, or career change.
 Unfortunately, we typically do not have data on many of these processes, so we will combine career change, emigration and immigration into a remainder term, which we denote as $E_{i,x,t}$.
-Suppose we do have data on numbers of deaths ($D_{i,x,t}$), numbers of retirements ($R_{i,x,t}$), and numbers of graduates ($G_{i,x,t}$); the numbers in each case are for people aged $x$ at the start of year $t$.
+Let $D_{i,x,t}$ denote the number of deaths of workers in group $i$ of age $x$ in year $t$, $R_{i,x,t}$ denote the number of retirements from the same group of workers, and $G_{i,x,t}$ denote the number of new graduates of age $x$ in year $t$ who take up work in group $i$.
+The numbers in each case are for people aged $x$ at the *start* of year $t$.
 Then population changes can be described using a model similar to the stochastic population model of @HB08, excluding the birth process:
@@
 $$ {#eq-dgb}
+where
+
+* $D_{i,x,t} \sim \text{Binomial}(P_{i,x,t}, q_{i,x,t})$, with $q_{i,x,t}$ being the probability of death for group $i$ at age $x$ in year $t$;
+* $R_{i,x,t} \sim \text{Binomial}((P_{i,x,t}-D_{i,x,t}), r_{i,x,t})$, with $r_{i,x,t}$ being the probability of retirement from group $i$ at age $x$ in year $t$.
+
 That is, the population each year is equal to the population from the previous year having aged 1 year, minus the deaths or retirements that occurred during the previous year, plus the new graduates, plus any other changes due to migration or career change (which may be negative).
-We assume that $D$, $R$ and $G$ are all non-negative, $D_{i,x,t} + R_{i,x,t} \le P_{i,x,t}$, and $E_{i,x,t} = G_{i,x,t} = 0$ above some age threshold (say $x=100$).
-Once $P_{i,x,t} = 0$ when $x$ is above that threshold, all future populations $P_{i,x+k,t+k} = 0$, forw $k=1,2,\dots$.
-That is, when the cohort aged $x$ in year $t$ has all retired or died, they will not be replaced by new workers of the same age.
+We assume that $E_{i,x,t} = G_{i,x,t} = 0$ above some age threshold (say $x=100$).
+Once $P_{i,x,t} = 0$ when $x$ is above that threshold, all future populations $P_{i,x+k,t+k} = 0$, for $k=1,2,\dots$.
+That is, when the cohort aged $x$ in year $t$ has all retired or died, and $x$ is above the threshold, they will not be replaced by new workers of the same age.
 
-As a first approximation, the components $D$, $R$, $E$ and $G$ can be assumed to behave independently for each combination of $i$, $x$ and $t$.
+As a first approximation, the components $q$, $r$, $E$ and $G$ can be assumed to behave independently for each combination of $i$, $x$ and $t$.
 In reality, there may be a negative correlation between $G$ and $E$ as insufficient graduates would probably lead to employers finding people from overseas, while too many graduates would lead to scientists seeking work elsewhere.
 
-To use @eq-dgb, data on $P$, $D$, $R$, and $G$ is required, and the remainder component $E$ will be calculated using @eq-dgb.
 It is unlikely that we have available separate death and retirement counts for each group, and retirement data is not available in all years.
-So we will instead use probabilities of death and retirement across all groups, and assume retirement probability does not change over time, giving $D_{i,x,t} = P_{i,x,t}q_{x,t}$ and $R_{i,x,t} = P_{i,x,t}r_{x}$ where $q_{x,t}$ is the probability of death at each age $x$ in year $t$, and $r_{x}$ is the probability of retirement at each age $x$.
-Similarly, graduation numbers are rarely available by discipline and age, so we will approximate $G_{i,x,t} = g_xG_t$ where $G_{i,t}$ is the total number of graduates in year $t$ and $g_x$ is the proportion of graduates by age across all disciplines.
-So our more realistic model becomes
-$$
-P_{i,x+1,t+1} = P_{i,x,t}(1 - q_{x,t} - r_{x}) + g_xG_{i,t} + E_{i,x,t},
-$$ {#eq-dgb2}
-To obtain forecasts of $P$, forecasts of $q$, $r$, $G$, and $E$ must then be computed. Each of these can be estimated using a functional time series model [@HU07].
+So we will let $q_{i,x,t} = q_{x,t}$ and $r_{i,x,t} = r_{x}$, assuming that death rates and retirement rates are the same across all groups, and that retirement rates do not change over time.
+Similarly, graduation numbers are rarely available by discipline and age, so we will approximate $G_{i,x,t} = g_xG_{i,t}$ where $G_{i,t}$ is the total number of graduates in year $t$ and $g_x$ is the proportion of graduates by age across all disciplines.
+
+To obtain forecasts of $P$, we use functional time series models [@HU07] for each of $q$, $G$, and $E$, and simulate future sample paths.
 
@@
 The resulting estimates of the number of scientists who are active in the Australian labour market is shown in @fig-cohort-interpolation as the thick lines.
-Cohort interpolation [@STUPP88], applying linear interpolation within each age cohort between census years, is used to estimate values for the intercensal years (shown as thin lines).
+Cohort interpolation [@STUPP88], applying linear interpolation within each age cohort between census years, is used to estimate values for the intercensal years (shown as thin lines), giving $P_{i,x,t}$ for each discipline $i$, age $x$, and year $t$.
 
@@
 This dataset includes both domestic and international students.
-The total number of graduates in each discipline $i$ and year $t$, are shown in @fig-graduates.
+The total number of graduates, $G_{i,t}$, in each discipline $i$ and year $t$, are shown in @fig-graduates.
 
@@
 
-The demographic growth-balance equation (@eq-dgb2), when rearranged, provides an estimate of the remainder, including net migration and career changes:
+The demographic growth-balance equation (@eq-dgb), when rearranged, provides an expression for the remainder including net migration and career changes:
 $$
-E_{i,x,t} = P_{i,x+1,t+1} - P_{i,x,t}(1 - q_{x,t} - r_{x}) - g_xG_{i,t},
+E_{i,x,t} = P_{i,x+1,t+1} - P_{i,x,t} - D_{i,x,t} - R_{i,x,t} - g_xG_{i,t},
 $$ {#eq-remainder}
-These remainders are shown in @fig-remainder.
+However, we do not have data on $D_{i,x,t}$ and $R_{i,x,t}$, so we replace these by their expected values, $P_{i,x,t} q_{x,t}$ and $P_{i,x,t}(1-q_{x,t}) r_x$, respectively.
+We can only estimate remainders up to 2020 because we need data for both year $t$ and year $t+1$ in @eq-remainder, and our working population data only extends to 2021.
+The estimated remainders are shown in @fig-remainder.
 
@@
 #| label: fig-remainder
-#| fig-cap: Estimated remainder $E_{i,x,t}$ by discipline, age and year (2006--2020), calculated using the demographic growth-balance equation.
+#| fig-cap: Estimated remainder $E_{i,x,t}$ by discipline, age and year (2006--2020).
 tar_read(fig22)
@@
 
+The inclusion of international students in the graduate data leads to large positive values of the remainder for the teenage years, followed by large negative values when these students return to their home countries after graduation.
+
 # Results {#sec-results}
+
+To forecast future working population numbers, $P_{i,x,t}$, we use the demographic growth-balance equation (@eq-dgb), with forecasts of the components $G_{i,t}$, $q_{x,t}$, and $E_{i,x,t}$.
+To account for the uncertainty in each of the forecast components, we use a simulation-based approach, running 500 simulations to generate a forecast distribution of possible future outcomes.
 
@@
 
-To forecast future graduate numbers, a global ARIMA model was employed, following the principles outlined by @HM21.
-ARIMA is a time series forecasting method that identifies underlying trends in past data, assuming these trends will continue.
+To forecast future graduate numbers, $G_{i,t}$, a global ARIMA model was employed, following the principles outlined by @HM21.
 The global model captures overall trends across disciplines by scaling graduate data within each discipline, ensuring proportional contributions from all disciplines before fitting the global ARIMA model.
 This improves robustness by incorporating information across disciplines.
-The model is then used to generate discipline-specific forecasts, with simulations run 500 times to account for variability and generate 90% prediction intervals.
-The results, along with these intervals, are shown in @fig-grad-forecasts.
+The forecast distributions are shown in @fig-grad-forecasts, with the mean forecast represented by the solid line and 90% prediction intervals indicated by the shaded area.
 
@@
 #| label: fig-grad-forecasts
-#| fig-cap: "Forecast number of graduates by discipline, 2024-2041, with 90% prediction intervals, based on historical data from 2006--2023."
+#| fig-cap: "Forecast of $G_{i,t}$: the number of graduates by discipline, 2024-2035, with 90% prediction intervals, based on historical data from 2006--2023."
 tar_read(fig_grad_forecasts)
@@
 
-Since workforce projections require not only total graduate numbers but also their age distribution, the forecasted totals (depicted in @fig-grad-forecasts) are disaggregated by age using the percentage distribution of graduate completions by age across all disciplines (as shown in @fig-completions).
-This enables an estimation of how many graduates will enter each age group in future years, ensuring consistency with observed patterns in the broader graduate population.
+## Death Probabilities
 
-## Net Migration
+```{r}
+#| label: fig-death-probs-forecasts
+#| fig-cap: "Forecasts of $q_{x,t}$: age-specific probabilities of death (on a logarithmic scale) for 2035, with 90% prediction intervals, based on historical data from 1971--2021."
+tar_read(fig_model_mxt3)
+```
 
-Net migration ($G_{i,x,t}$) is estimated using the demographic growth-balance equation, which is rearranged to calculate the net number of migrants each year (@eq-remainder).
-@fig-net-migration-disciplines shows the age distribution of net migration among scientists between 2006 and 2020.
-Emigration during the early career stage is largely driven by international students graduating and returning home.
-This negative net migration in the early career stage is a significant factor across all disciplines.
+The death probabilities, $q_{x,t}$, were forecast using a functional data model [@HU07], with ARIMA models fitted to the coefficients.
+The forecasts for one year are shown in @fig-death-probs-forecasts, with the mean forecast represented by the solid line and 90% prediction intervals indicated by the shaded area.
+Note that the historical data (shown in gray) represent unsmoothed values, while the forecasts are based on the smoothed functional data model.
+The additional variation seen in the historical data is captured in the model through the Binomial death process.
 
-Significant emigration is observed between the ages of 20 and 27, primarily driven by international students leaving Australia after completing their studies, with some domestic graduates also seeking employment overseas.
-As the graduate data includes both domestic and international students, this emigration is largely influenced by international students returning home.
+## Remainder
 
-Beyond this age range, net migration fluctuates between small levels of immigration and emigration.
-However, these variations are relatively minor, with annual net migration reaching no more than approximately 15 individuals per age group.
-Given the small magnitudes, these fluctuations may not reflect meaningful migration patterns but rather noise or systematic cohort effects due to input data limitations.
-
-As outlined in the methodology, these estimates rely on forecasting the other components ($D$, $N$, and $R$).
-Therefore, only estimated historical values up to 2020 are shown here.
-While historical data on the working population extends to 2021, net migration values for 2021 can only be obtained by incorporating forecasted components due to the structure of the equation.
-
-Other Natural and Physical Sciences and Natural and Physical Sciences (n.f.d.) show little to no immigration beyond this stage.
-Given their larger workforce sizes (as seen on the y-axis), these disciplines exhibit more stable net migration patterns.
-
-In contrast, core scientific disciplines, which have smaller populations, show more fluctuation in migration levels after the early career stage.
-This variability is likely due to workforce mobility, the sensitivity of estimates for smaller populations, and cohort effects, rather than reflecting actual migration dynamics.
+The remainder, $E_{i,x,t}$, is also modelled using a functional data model [@HU07], with ARIMA models fitted to the coefficients.
+The forecasts for one year are shown in @fig-net-migration-disciplines, with the mean forecast represented by the solid line and 90% prediction intervals indicated by the shaded area.
 
@@
 #| label: fig-net-migration-disciplines
-#| fig-cap: Estimated net migration by age across scientific disciplines (2006--2020). Each panel represents a different discipline, showing net migration trends across age groups.
-#| fig-height: 6
-tar_read(fig22)
+#| fig-cap: "Forecasts of $E_{i,x,t}$: the remainder by discipline for 2035, with 90% prediction intervals, based on historical data from 2006--2020."
+tar_read(fig_model_Ext3)
 ```

### 2025-08-28 R/functions.R
Stationary remainder coefficients

@@ -222,7 +222,7 @@ forecast_pop_discipline <- function(
   # (since we can't compute them using following year)
   fit_migrants <- df |>
     filter(year < last_yr, !is.na(graduates)) |>
-    model(fdm = FDM(remainder))
+    model(fdm = FDM(remainder, coherent = TRUE))
   last_yr_migrants <- fit_migrants |>
     forecast(h = 1) |>
     as_tibble() |>

### 2025-08-28 _targets.R

@@ -165,7 +165,8 @@ list(
   tar_target(
     model_Ext,
     census2_1 |>
-      model(fdm = FDM(remainder))
+      filter(year <= 2020) |>
+      model(fdm = FDM(remainder, coherent = TRUE))
   ),
   tar_target(
     fig_Emodel_fdm1,
@@ -195,7 +196,8 @@ list(
   tar_target(
     model_Ext_discipline,
     census4_1 |>
-      model(fdm = FDM(remainder))
+      filter(year <= 2020) |>
+      model(fdm = FDM(remainder, coherent = TRUE))
   ),
   tar_target(
     fig_model_Ext3,

### 2025-08-29 age_structure_forecasts.qmd
Stationary remainder coefficients
Continuing on section 4

@@
 
-## Working Population
+## Working population
 
@@
 
-## Graduate Completions
+## Graduate completions
 
@@
 To forecast future working population numbers, $P_{i,x,t}$, we use the demographic growth-balance equation (@eq-dgb), with forecasts of the components $G_{i,t}$, $q_{x,t}$, and $E_{i,x,t}$.
-To account for the uncertainty in each of the forecast components, we use a simulation-based approach, running 500 simulations to generate a forecast distribution of possible future outcomes.
+To account for the combined uncertainty from all of the forecast components, we use a simulation-based approach, running 1000 simulations to generate a forecast distribution of possible future outcomes.
 
-## Graduate Completions
+## Graduate completions
 
@@
 
-## Death Probabilities
+## Death probabilities
 
@@
 
-The remainder, $E_{i,x,t}$, is also modelled using a functional data model [@HU07], with ARIMA models fitted to the coefficients.
+The remainder, $E_{i,x,t}$, is also modelled using a functional data model [@HU07], with stationary ARMA models fitted to the coefficients.
 The forecasts for one year are shown in @fig-net-migration-disciplines, with the mean forecast represented by the solid line and 90% prediction intervals indicated by the shaded area.
@@
 
-## Simulating Future Populations
+## Simulating future populations
 
-To forecast the future age structure of the scientific workforce in Australia, a simulation-based approach is employed.
-This approach uses a stochastic population model, adapted from the demographic growth-balance model described in @HB08 and excluding birth processes, to project future populations.
-This model incorporates uncertainties in demographic processes, generating a range of potential future scenarios for the scientific workforce.
-The following steps outline the process for projecting the future working population:
+We use the demographic growth-balance model @eq-dgb to simulate future populations, using the models described above for graduate completions, death probabilities and the remander terms.
+The following steps outline the process:
 
-1.
-**Death Probabilities:** Fit a functional data model [@HU07] to the death probabilities shown in @fig-death-probs, with ARIMA models for the coefficients.
-This model is used to simulate values of age-specific death probabilities in future years.
-2.
-**Net Migration:** Fit a separate functional data model to the age-specific migrant numbers shown in @fig-net-migration-disciplines, with ARIMA models for the coefficients.
-This model simulates values of age-specific net migrant numbers in future years.
-3.
-**Graduate Numbers:** Fit an ARIMA model [@fpp3] to simulate total numbers of graduates in each future year from the numbers shown in @fig-grad-forecasts.
-These graduate numbers will then be disaggregated by age using the age distribution shown in @fig-completions to estimate age-specific graduate numbers in each year.
-4.
-**Retirements:** Estimate retirements in each year by multiplying the number of people of working age in each age bracket (@fig-interpolated-working-population) by the retirement probabilities shown in @fig-retirements.
-Fixed age-specific retirement probabilities are used.
-5.  **Deaths:** Estimate deaths in each year by multiplying the number of people of working age in each age bracket by the forecast death probabilities.
-6.
-**Demographic Growth-Balance:** Use the demographic growth-balance equation [@eq-dgb] to obtain the next year's age-specific population values.
-This step incorporates the graduate numbers, net migration, retirements, and deaths, to produce the forecasted population for the next year.
-
-A total of 500 simulations are run to obtain a distribution of possible future population scenarios, allowing for quantification of forecast uncertainty.
-@fig-future-physics shows two example simulations.
-Historical data (2006--2021) are shown in gray, with simulated future populations (2022--2041) in colour.
-While both simulations exhibit similar trends, differences arise due to inherent uncertainties in model inputs, including variations in graduate numbers, migration patterns, and workforce exits through death and retirement.
-These sources of uncertainty are incorporated into the model, contributing to the range of possible future trajectories.
+A total of 1000 simulations are run to obtain a distribution of possible future population scenarios.
+The average of the 1000 simulations provides the mean age-specific forecast, while quantiles estimate forecast uncertainty.
+@fig-forecast-working-population presents the mean and 90% prediction intervals for 2025 and 2035.
 
 ```{r}
-#| label: fig-future-physics
-#| fig-height: 3
-#| fig-cap: Two example simulations from a set of 500, using historical data from 2006-2021 to forecast age-specific population distributions for 2022-2041.
-tar_read(fig16)
+#| label: fig-forecast-working-population
+#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across scientific disciplines.
+The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
+#| fig-height: 5.5
+# 2025 and 2035
+#tar_read(fig23)
 ```
-
-## Forecast Results
-
-The average of the 500 simulations provides the mean age-specific forecast, while quantiles estimate forecast uncertainty.
-@fig-forecast-working-population presents the mean and 90% prediction intervals for 2025 and 2035.
 
@@
 Since retirements increase after the late 50s, workforce participation beyond 60 serves as a benchmark for identifying trends in delayed retirement and extended career duration.
-
-```{r}
-#| label: fig-forecast-working-population
-#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across scientific disciplines.
-The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
-#| fig-height: 5.5
-# 2025 and 2035
-#tar_read(fig23)
-```
 

### 2025-09-09 age_structure_forecasts.qmd
Added abstract, keywords and JEL codes

@@
 abstract: |
-  A brief summary of our ideas
-keywords: [blah, blah]
+  Planning for a future workforce requires forecasts of age structure changes to inform policy decisions, particularly related to universities and immigration.
+We modify the traditional demographic growth-balance equation to account for workforce-specific dynamics, replacing births with graduate entry, modeling exits through death and retirement, and including a remainder term that captures migration and career changes.
+Functional data models are used to model age-specific components, while ARIMA models are used for time series components.
+Simulation is employed to generate forecast distributions, capturing uncertainty from all components.
+The approach is illustrated using data on Australia's scientific workforce, allowing us to forecast the age distribution of various scientific disciplines for the next ten years.
+This analysis was central to an Australian Academy of Science initiative, supporting strategic workforce planning and policy development for Australia's scientific community.
+keywords:
+  - cohort analysis
+  - demographic modelling
+  - functional data models
+  - labour market
+  - workforce planning
 bibliography: refs.bib
 wpnumber: no/yr
-jelcodes: C10,C14,C22
+jelcodes: J11, J21, C15, C22
 blind: false

### 2025-09-09 age_structure_forecasts.qmd
Minor improvements

@@
 library(targets)
+library(ggplot2)
 
@@
 The social implications are also significant, with an aging workforce leading to changes in workplace dynamics, potential problems with intergenerational knowledge transfer, and the need for policies that support older workers.
-Yet this problem does not appear to have been previously addressed from a statistical modeling perspective.
+Yet this problem does not appear to have been previously addressed from a statistical modelling perspective.
 
@@
 
-* $D_{i,x,t} \sim \text{Binomial}(P_{i,x,t}, q_{i,x,t})$, with $q_{i,x,t}$ being the probability of death for group $i$ at age $x$ in year $t$;
+* $D_{i,x,t} \sim \text{Binomial}(P_{i,x,t}, q_{i,x,t})$, with $q_{i,x,t}$ being the probability of death for group $i$ at age $x$ in year $t$; and
 * $R_{i,x,t} \sim \text{Binomial}((P_{i,x,t}-D_{i,x,t}), r_{i,x,t})$, with $r_{i,x,t}$ being the probability of retirement from group $i$ at age $x$ in year $t$.
@@
 
-To obtain forecasts of $P$, we use functional time series models [@HU07] for each of $q$, $G$, and $E$, and simulate future sample paths.
+This leads to the simpler model
+$$
+P_{i,x+1,t+1} = P_{i,x,t} - D_{i,x,t} - R_{i,x,t} + g_xG_{i,t} + E_{i,x,t},
+$$ {#eq-dgb2}
+where
+
+* $D_{i,x,t} \sim \text{Binomial}(P_{i,x,t}, q_{x,t})$; and
+* $R_{i,x,t} \sim \text{Binomial}((P_{i,x,t}-D_{i,x,t}), r_{x})$.
+
+We use functional time series models [@HU07] for $q_{x,t}$ and $E_{i,x,t}$, a global ARIMA models for $G_{i,t}$, and univariate ARIMA models for the principal component scores of the functional time series models.
+
+To forecast future working population numbers, $P_{i,x,t}$, $t>T$, we simulate future sample paths of each of the components $G_{i,t}$, $q_{x,t}$, and $E_{i,x,t}$, simulate $D_{i,x,t}$ and $R_{i,x,t}$ from their respective Binomial distributions, and then use the demographic growth-balance equation @eq-dgb2 iteratively to obtain $P_{i,x,t}$ for $t=T+1,T+2,\dots$.
+This simulation-based approach allows us to capture the uncertainty in each of the components, leading to a distribution of possible future outcomes for $P_{i,x,t}$.
 
@@
 
-This analysis focuses on the Natural and Physical Sciences as defined in the Australian Standard Classification of Education (ASCED) by the @ABSASCED.
+To illustrate the methodology, we consider the Natural and Physical Sciences as defined in the Australian Standard Classification of Education (ASCED) by the @ABSASCED.
 We refer to ASCED's Narrow Fields as "disciplines"; these comprise Physics and Astronomy, Mathematical Sciences, Chemical Sciences, Earth Sciences, Biological Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences not further defined (n.f.d.).
@@
 
-The demographic growth-balance equation (@eq-dgb), when rearranged, provides an expression for the remainder including net migration and career changes:
+The demographic growth-balance equation (@eq-dgb2), when rearranged, provides an expression for the remainder including net migration and career changes:
 $$
@@
 
-To forecast future working population numbers, $P_{i,x,t}$, we use the demographic growth-balance equation (@eq-dgb), with forecasts of the components $G_{i,t}$, $q_{x,t}$, and $E_{i,x,t}$.
-To account for the combined uncertainty from all of the forecast components, we use a simulation-based approach, running 1000 simulations to generate a forecast distribution of possible future outcomes.
-
 ## Graduate completions
@@
 #| label: fig-grad-forecasts
-#| fig-cap: "Forecast of $G_{i,t}$: the number of graduates by discipline, 2024-2035, with 90% prediction intervals, based on historical data from 2006--2023."
+#| fig-cap: "Forecast of $G_{i,t}$: the number of graduates by discipline, 2024-2035, based on historical data from 2006--2023.
+The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates."
 tar_read(fig_grad_forecasts)
@@
 #| label: fig-death-probs-forecasts
-#| fig-cap: "Forecasts of $q_{x,t}$: age-specific probabilities of death (on a logarithmic scale) for 2035, with 90% prediction intervals, based on historical data from 1971--2021."
+#| fig-cap: "Forecasts of $q_{x,t}$: age-specific probabilities of death (on a logarithmic scale) for 2035, based on historical data from 1971--2021.
+The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimate."
 tar_read(fig_model_mxt3)
@@
 #| label: fig-net-migration-disciplines
-#| fig-cap: "Forecasts of $E_{i,x,t}$: the remainder by discipline for 2035, with 90% prediction intervals, based on historical data from 2006--2020."
+#| fig-cap: "Forecasts of $E_{i,x,t}$: the remainder by discipline for 2035, based on historical data from 2006--2020.
+The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates."
 tar_read(fig_model_Ext3)
@@
 
-We use the demographic growth-balance model @eq-dgb to simulate future populations, using the models described above for graduate completions, death probabilities and the remander terms.
-The following steps outline the process:
+We use the demographic growth-balance model @eq-dgb2 to simulate future populations, using the models described above for the components. The following steps outline the process:
 
@@
 The average of the 1000 simulations provides the mean age-specific forecast, while quantiles estimate forecast uncertainty.
-@fig-forecast-working-population presents the mean and 90% prediction intervals for 2025 and 2035.
+@fig-forecast-working-population presents the mean and 90% prediction intervals for 2035.
 
@@
 #| label: fig-forecast-working-population
-#| fig-cap: "Projected age distribution of the working population in 2025 and 2035 across scientific disciplines.
-The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates for each year."
+#| fig-cap: "Forecasts of $P_{i,x,t}$: the working population by discipline for 2035. The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates."
 #| fig-height: 5.5
 # 2025 and 2035
-#tar_read(fig23)
+tar_load(fig_Pxt_future_discipline)
+i <- length(fig_Pxt_future_discipline)
+fig_Pxt_future_discipline[[i]] +
+  guides(fill = "none") +
+  labs(title = "Forecasts of working population by discipline: 2035")
 ```
@@
 Between 2025 and 2035, the forecasts indicate an aging workforce, with increases in the number of scientists in their late 30s, and from ages 45 to 80.
-This trend is particularly evident in the wider gap at ages 45-60 between the forecasted distributions over the ten-year period.
+This trend is particularly evident in the wider gap at ages 45--60 between the forecasted distributions over the ten-year period.
 

### 2025-09-09 R/forecast_by_discipline.R

@@ -104,7 +104,7 @@ make_pop_future_fig_discipline_year <- function(
   p[[length(p) + 1]] <- patchwork::guide_area()
   patchwork::wrap_plots(p) +
     patchwork::plot_annotation(
-      title = "90% forecast interval for working population by discipline",
+      title = "Forecast of working population by discipline",
     ) +
     patchwork::plot_layout(guides = "collect", axis_titles = "collect")
 }

### 2025-09-09 R/remainder.R

@@ -43,7 +43,7 @@ make_future_Ext_fig2 <- function(object, data, h, times, yr, no_other = TRUE) {
   if (NROW(object) == 0) {
     title <- "Remainder"
   } else {
-    title <- paste("Future remainder:", yr)
+    title <- paste("Forecasts of remainder by discpline:", yr)
   }
 
   data |>

### 2025-09-09 age_structure_forecasts.qmd
Added more discussion

@@
 
-In planning for the future labour market, it is necessary to forecast the age structure of the workforce, in order to enable informed decision-making on policies, especially concerning universities and immigration.
+In planning for the future labour market, it is necessary to forecast the age structure of the workforce in order to enable informed decision-making on policies, especially concerning universities and immigration.
 We propose a statistical modelling approach to this problem, illustrated using various scientific disciplines in Australia, forecasting future workforce age structures over the next decade.
@@
 As a first approximation, the components $q$, $r$, $E$ and $G$ can be assumed to behave independently for each combination of $i$, $x$ and $t$.
-In reality, there may be a negative correlation between $G$ and $E$ as insufficient graduates would probably lead to employers finding people from overseas, while too many graduates would lead to scientists seeking work elsewhere.
+In reality, there may be some negative correlation between $G$ and $E$ as insufficient graduates would probably lead to employers finding people from overseas, while too many graduates would lead to scientists seeking work elsewhere.
+
+The choice of a Binomial rather than a Poisson distribution (in contrast to @Brillinger1986) for deaths and retirements is because the Binomial distribution ensures that the number of deaths and retirements cannot exceed the population at risk.
+In a simulation context, with very small populations, this is important to avoid nonsensical results.
 
@@
 
-We use functional time series models [@HU07] for $q_{x,t}$ and $E_{i,x,t}$, a global ARIMA models for $G_{i,t}$, and univariate ARIMA models for the principal component scores of the functional time series models.
+For the age-specific time-varying components $q_{x,t}$ and $E_{i,x,t}$, we will use functional data models [@HU07]. For $q_{x,t}$, this is of the form
+$$
+\log(q_{x,t}) = \mu(x) + \sum_{k=1}^K \beta_{k,t} \phi_k(x) + \varepsilon_{x,t},
+$$ {#eq-fdm}
+where $\mu(x)$ is the mean function, $\phi_k(x)$ are functional principal components, $\beta_{k,t}$ are the principal component scores, and $\varepsilon_{x,t}$ is an error term.
+Each $\beta_{k,t}$ is then modelled using a univariate time series model, such as an ARIMA model.
+A log-link function is used to ensure that the probabilities remain positive.
+An inverse logit link function could also be used, if the probabilities are close to 1 for some ages.
+A similar model is used for $E_{i,x,t}$, with separate mean functions and principal components for each group $i$.
+The number of components $K=6$, for the reasons outlined in @HB08.
+
+Functional data models have been widely used in demography and other fields, and have been shown to work particularly well for age-specific demographic processes [@HB08;@LCcomparison].
+They enable the inherent smoothness over age to be captured, while modelling the autocorrelation over time using relatively simple univariate time series models applied to the principal component scores.
+In our application, we use univariate ARIMA models for the $q_{x,t}$ scores, and ARMA models for the $E_{i,x,t}$ scores.
+The assumption of stationarity for the $E_{i,x,t}$ scores is validated for the disciplines we consider.
+
+For the time-varying component, $G_{i,t}$, we use a global ARIMA model [@HM21] to capture the dynamics over time and across disciplines.
+The global model pools information across disciplines to improve forecast accuracy, especially for disciplines with limited historical data.
 
@@
 This simulation-based approach allows us to capture the uncertainty in each of the components, leading to a distribution of possible future outcomes for $P_{i,x,t}$.
+
+This model is somewhat pragmatic given the data available in our specific application.
+If better data were available, other variations on @eq-dgb could be used.
+For example, if death rates were available by discipline, then we would replace $q_{x,t}$ by $q_{i,x,t}$ in the Binomial deaths distribution.
+If retirement rates were available by year, or by discipline, we could similarly replace $r_x$ by a more specific retirement rate in the Binomial retirements distribution.
+If we had data on graduations by age and discipline, we could replace $g_xG_{i,t}$ by $G_{i,x,t}$.
+If we had data on migration, we could split the remainder $E_{i,x,t}$ into several components, and model them separately.
+None of this changes the overall modelling framework we are proposing.
 
@@
 We define the population of workers in a discipline as those who are active in the labour market and hold a bachelor's degree or higher in that discipline.
+For the purposes of this analysis, we will omit "Other Natural and Physical Sciences" and "Natural and Physical Sciences n.f.d.".
 
@@
 The large increase in the working population observed in the 2021 Census for Mathematical Sciences (@fig-cohort-interpolation) can be partly attributed to the sharp rise in graduate numbers between 2016 and 2021.
+This is probably due to the impact of data science, and the growing importance of statistics and machine learning in many areas of employment.
 
@@
 The global model captures overall trends across disciplines by scaling graduate data within each discipline, ensuring proportional contributions from all disciplines before fitting the global ARIMA model.
-This improves robustness by incorporating information across disciplines.
+This improves the numerical stability of the model by incorporating information across disciplines.
 The forecast distributions are shown in @fig-grad-forecasts, with the mean forecast represented by the solid line and 90% prediction intervals indicated by the shaded area.
@@
 #| label: fig-grad-forecasts
-#| fig-cap: "Forecast of $G_{i,t}$: the number of graduates by discipline, 2024-2035, based on historical data from 2006--2023.
+#| fig-cap: "Forecast of $G_{i,t}$: the number of graduates by discipline, 2024--2035, based on historical data from 2006--2023.
 The shaded regions represent the 90% prediction intervals, and the solid lines indicate the mean estimates."
@@
 
-The death probabilities, $q_{x,t}$, were forecast using a functional data model [@HU07], with ARIMA models fitted to the coefficients.
+The death probabilities shown in @fig-death-probs where first smoothed using the partially monotonic penalized spline approach of @HU07.
+Then the functional data model @eq-fdm was estimated, with ARIMA models fitted to the coefficients.
 The forecasts for one year are shown in @fig-death-probs-forecasts, with the mean forecast represented by the solid line and 90% prediction intervals indicated by the shaded area.
@@
 
-The remainder, $E_{i,x,t}$, is also modelled using a functional data model [@HU07], with stationary ARMA models fitted to the coefficients.
+The remainder, $E_{i,x,t}$, is also modelled using a functional data model [@HU07], with stationary ARMA models fitted to the principal component scores.
+The scores were found to be stationary using the KPSS test [@KPSS].
 The forecasts for one year are shown in @fig-net-migration-disciplines, with the mean forecast represented by the solid line and 90% prediction intervals indicated by the shaded area.
@@
 
-We use the demographic growth-balance model @eq-dgb2 to simulate future populations, using the models described above for the components. The following steps outline the process:
+We use the demographic growth-balance model @eq-dgb2 to iteratively simulate future populations, using the models described above for the components. The following steps outline the process.
 
-A total of 1000 simulations are run to obtain a distribution of possible future population scenarios.
+A total of 1000 simulations are run to obtain a distribution of future age-specific population scenarios.
 The average of the 1000 simulations provides the mean age-specific forecast, while quantiles estimate forecast uncertainty.
@@
 # 2025 and 2035
-tar_load(fig_Pxt_future_discipline)
-i <- length(fig_Pxt_future_discipline)
-fig_Pxt_future_discipline[[i]] +
-  guides(fill = "none") +
-  labs(title = "Forecasts of working population by discipline: 2035")
+tar_read(fig_Pxt_future_discipline) +
+  ggplot2::labs(title = "Forecasts of working population by discipline: 2035")
 ```
 
-In 2035, forecast variability is highest at younger ages, starting from 15 and widening before gradually narrowing as the workforce ages.
-The prediction interval becomes especially narrow during the retirement phase, where the workforce dynamics become more predictable, indicating greater certainty in this portion of the forecast.
-
-Prediction intervals are also shown for 2025, as it represents a forecast rather than observed workforce data.
-This comparison helps illustrate how the age distribution is expected to evolve over the next decade.
-
-Between 2025 and 2035, the forecasts indicate an aging workforce, with increases in the number of scientists in their late 30s, and from ages 45 to 80.
-This trend is particularly evident in the wider gap at ages 45--60 between the forecasted distributions over the ten-year period.
-
-Additionally, patterns in the age distribution persist over time.
-A dip or trough observed at a given age in 2025 reappears 10 years later as the same cohort progresses through the workforce.
-While these shifts may be harder to distinguish due to the structure of single-year age cohort data, they reveal how workforce cohorts evolve and how observed patterns carry through in future projections.
-
-Summing over age groups allows for estimating the total number of working scientists in each future year, as shown in @fig-forecast-total-working-scientists.
-This highlights whether the workforce is growing, stabilising, or declining.
-On average, projections indicate continued growth, but at a gradually slower pace.
-The lower bound remains nearly flat, suggesting workforce stagnation in a conservative scenario.
-Even in an optimistic scenario, growth only slightly exceeds the current pace.
-
-After 500 simulations of the future population for each discipline, the projections ten years apart (2025 and 2035) shown in @fig-forecast-working-population provide a basis for comparing estimates of the current and future workforce.
-
-The projections indicate wider prediction intervals for younger age groups due to uncertainty in future graduate numbers, while mid-to-late career estimates primarily reflect the aging of existing cohorts.
-Across disciplines, the typical working population spans from the mid-to-late 20s (10th percentile) to the mid-50s and early 60s (90th percentile).
+In 2035, forecast variability is highest in the age period 20--35 years, before gradually narrowing as the workforce ages.
+This is due to the relatively high uncertainty in the new graduates component compared to the other components.
+Mid-to-late career estimates primarily reflect the aging of existing cohorts.
+The prediction intervals becomes especially narrow during the retirement phase, where the workforce dynamics become more predictable.
 Since retirements increase after the late 50s, workforce participation beyond 60 serves as a benchmark for identifying trends in delayed retirement and extended career duration.
-
-The key findings from @fig-forecast-working-population are summarised below:
-
--   **Physics and Astronomy** *(Aging Workforce):* The 35--45 age group shows a higher average than the previous 2025 cohort.
-There is a growing number of scientists aged 45 to 60, and more individuals aged 60+ are remaining in the workforce longer.
-These patterns indicate a gradual transition toward an older age structure, reflecting an aging workforce.
--   **Mathematical Sciences** *(Expansive Workforce):* Workforce growth is evident across a broad range of ages, particularly among individuals aged 25 to 70.
-The most significant increase occurs before 60, though there is also a clear rise in older workers (60+) remaining in the workforce rather than retiring.
-Overall, workforce growth is strong and evident across age groups.
--   **Chemical Sciences** *(Stationary Workforce):* The average workforce size remains stable, with a relatively narrow prediction interval, indicating a predictable pattern of stability over time.
-While there is a minor increase in the number of workers aged 70, this change is not substantial enough to suggest a broader shift in workforce dynamics.
--   **Earth Sciences** *(Aging Workforce):* Early-career workforce projections are more uncertain relative to its size.
-A decline in the working population is observed in the mid-thirties, followed by an increase throughout the forties, though both remain modest.
-While the overall workforce remains relatively stable, these patterns indicate a slow shift toward an older age distribution.
--   **Biological Sciences** *(Aging Workforce):* The number of workers aged 50 to 65 is increasing, indicating growth in later-career participation.
--   **Other Natural and Physical Sciences** *(Expansive Workforce):* Workforce growth is strong across ages 30 to 70, characteristic of an expanding workforce.
--   **Natural and Physical Sciences (n.f.d.)** *(Aging Workforce):* Growth is primarily concentrated in the 55--70 age range, indicating delayed retirement and an aging workforce.
-
-These trends are further validated by the total workforce projections shown in @fig-forecast-total-working-scientists.
-This figure presents the total number of working scientists by discipline at each point in time, illustrating changes in workforce size over the forecast period.
-While all disciplines exhibit widening prediction intervals resembling an open funnel, this primarily reflects increasing uncertainty over time as forecasts extend further into the future.
-The extent of this uncertainty varies by discipline, with some exhibiting more stable trends while others show greater variability in potential workforce outcomes.
+Over the next ten years, we expect an aging workforce in all but the Mathematical Sciences, where a large increase in the population is forecast.
 
@@
 
-From the plot, Mathematical Sciences, Other Natural and Physical Sciences, and Natural and Physical Sciences (n.f.d.) are projected to grow at an accelerating pace.
-Chemical Sciences, on the other hand, is more likely to decline, while the remaining disciplines are expected to experience more stable growth.
-However, it is important to consider the prediction intervals when interpreting these trends.
-These patterns are largely consistent with workforce structure classifications, with expansive disciplines experiencing faster growth, aging disciplines maintaining more stable trends, and constrictive disciplines showing signs of decline.
+Also visible in @fig-forecast-working-population are cohort effects, where fluctuations in earlier ages and years propagate through to later ages and years.
+This is particularly evident in the mid-career years because there are few deaths and retirements, few graduates older than 30, and the variation due to the remainder term is relatively small after age 30.
 
-# Conclusion {#sec-conclusion}
+Summing over ages allows for estimating the forecast distribution of the total number of working scientists in each future year, as shown in @fig-forecast-total-working-scientists.
+The forecasts indicate continued growth, but at a gradually slower pace for all disciplines other than the Mathematical Sciences.
+Where the lower bound is nearly flat, workforce stagnation is possible in a conservative scenario.
+Even in the optimistic scenario (corresponding to the upper bound), growth only slightly exceeds the current pace, except for the Mathematical Sciences.
+As noted earlier, the divergent behaviour of the Mathematical Sciences is likely driven by the growing importance of data science and related fields.
 
-This report provides data-driven forecasts of Australia's science workforce age structures, outlining expected changes across disciplines by 2035.
-The Natural and Physical Sciences, along with Engineering, are projected to experience workforce aging, with growth concentrated in older age groups.
-Information Technology is expected to expand, though some disciplines remain uncertain due to high graduate numbers not translating into workforce participation.
-Smaller disciplines within Agriculture and Environmental Studies are projected to decline.
+The wide prediction intervals reflect the uncertainty in the forecasts, and show that caution is needed when interpreting the results.
+The only discipline where there is clear evidence of growth or decline is the Mathematical Sciences.
+For all other disciplines, the prediction intervals include the current level, indicating that stagnation, increase, or decline is possible.
 
-When interpreting these projections, policymakers should consider data limitations, particularly in discipline classification and reporting.
-Variations in self-reporting and ASCED categorisation may not fully capture industry or education changes, impacting accuracy, especially in smaller or evolving disciplines.
+# Discussion {#sec-conclusion}
 
-Additionally, while these projections provide a solid foundation for workforce planning, it is important to note that they are entirely driven by historical trends and do not account for possible new developments, such as the impact of AI and other emerging technologies on the labour market in different scientific disciplines.
+While these forecasts provide a foundation for workforce planning, it is important to note that they are entirely driven by historical trends and do not account for possible new developments, such as the impact of AI and other emerging technologies on the labour market in different scientific disciplines.
 Other factors, such as policy changes or global economic shifts, may also influence workforce trends and should be taken into account.
 
-While alternative demographic methodologies, such as the Lee-Carter model, could be considered for estimating demographic components, the methods employed in this report, including the functional data model, ARIMA model, and demographic growth-balance equation, are better suited to the specific characteristics of the data and the goals of this analysis.
+Things that could be improved:
 
-Other quantitative studies, such as job market forecasting, may offer complementary insights into broader trends in the scientific workforce.
-Qualitative studies can also uncover latent factors that go beyond historical data.
-While this report focuses on forecasting based on past trends, these alternative approaches can provide additional perspectives on the scientific workforce in Australia.
+- Include backtesting results by fitting the model to earlier periods and comparing forecasts to actual outcomes
+- Discuss forecast accuracy metrics and how they compare across disciplines
+- Address the challenge of validating long-term demographic forecasts with limited historical data
+- Examine how sensitive forecasts are to key assumptions (e.g., constant retirement rates across disciplines, independence of components)
+- Discuss the impact of the choice to use general population mortality rates rather than discipline-specific rates
+- Analyze how changes in the each component affect overall forecasts
+- Address potential interventions that could alter the forecasted trajectories (e.g., targeted recruitment, retention programs)
+- Discuss alternative methods.
 
-Future work could enhance the accessibility of these projections through interactive visualisations, improve accuracy with new Census data, and broaden the analysis to additional ASCED fields.
-Refining estimation methods would further strengthen projection reliability and robustness.
+- Provide more detailed discussion of the sources of uncertainty in your forecasts
 
-This analysis contributes to the Australian Academy of Science's initiative _Australian Science, Australia's Future: Science 2035_ by identifying shifts in the workforce, helping anticipate future demand for science capabilities, and highlighting potential workforce gaps as aging and retirement reshape workforce dynamics.
+- Discuss whether the methodology could be applied to other countries or workforce sectors
+- Address unique aspects of the Australian context that might limit generalizability
+
+- Expand beyond AI to discuss other technological disruptions (automation, quantum computing, biotechnology)
+- Consider demographic shifts (changing education patterns, delayed career entry, career mobility)
+- Discuss potential "black swan" events that could dramatically alter workforce dynamics
+
+- Discuss the implications of using census data with 5-year gaps
+- Address the challenge of tracking career changes and international mobility
+- Suggest improvements to data collection that would enhance future forecasting efforts
+
+# Software and reproducibility
+
+All results presented here can be reproduced using the code available at <https://github.com/robjhyndman/age_structure_forecasts>.
+The analysis was conducted using R version 4.5.1 [@R], with the following R packages: vital [@Rvital], tsibble [@Rtsibble], fable [@Rfable], targets [@targets;@targetspaper], ggplot2 [@ggplot2;@ggplotbook], and other tidyverse [@tidyverse] packages.
 

### 2025-09-09 R/forecast_by_discipline.R

@@ -26,7 +26,9 @@ make_pop_future_fig_discipline <- function(
   data,
   no_other = TRUE,
   ymax,
-  color_data = FALSE
+  color_data = FALSE,
+  guides = TRUE,
+  list = FALSE
 ) {
   # Remove other group
   if (no_other) {
@@ -45,14 +47,50 @@ make_pop_future_fig_discipline <- function(
       working = mean(working),
       .groups = "drop"
     )
-  lapply(
-    yrs,
-    make_pop_future_fig_discipline_year,
-    object = object,
-    data = data,
-    ymax = ymax,
-    color_data = color_data
-  )
+  if(list) {
+    return(make_pop_future_fig_discipline_year(
+      yrs,
+      object,
+      data,
+      ymax,
+      color_data,
+      guides
+    ))
+  }
+  p <- ggplot(data) +
+    aes(x = age, y = working, group = factor(year)) +
+    facet_wrap(~discipline, scales = "free_y")
+  if (color_data) {
+      p <- p +
+        geom_line(aes(color = year)) +
+        scale_color_gradientn(colors = rainbow(10))
+    } else {
+      p <- p + geom_line(color = "gray")
+    }
+  if (NROW(object) > 0) {
+    p <- p +
+      geom_ribbon(
+        data = object,
+        aes(ymin = .lower, ymax = .upper, fill = factor(year)),
+        alpha = 0.3
+      ) +
+      geom_line(
+        data = object,
+        aes(color = factor(year)),
+        linewidth = 0.75
+      )
+  }
+  p <- p +
+    scale_x_continuous(breaks = seq(20, 100, by = 10)) +
+    labs(
+      x = "Age",
+      y = "Number of active scientists",
+      title = "Forecast of working population by discipline"
+    )
+  if (!guides) {
+    p <- p + guides(color = "none", fill = "none")
+  }
+  p
 }
 
 make_pop_future_fig_discipline_year <- function(
@@ -60,7 +98,8 @@ make_pop_future_fig_discipline_year <- function(
   object,
   data,
   ymax,
-  color_data
+  color_data,
+  guides = TRUE
 ) {
   disciplines <- unique(data$discipline)
   object <- object |>
@@ -92,7 +131,7 @@ make_pop_future_fig_discipline_year <- function(
         ) +
         guides(color = "none")
     }
-    tmp +
+    tmp <- tmp +
[…]

### 2025-09-09 R/remainder.R

@@ -43,7 +43,7 @@ make_future_Ext_fig2 <- function(object, data, h, times, yr, no_other = TRUE) {
   if (NROW(object) == 0) {
     title <- "Remainder"
   } else {
-    title <- paste("Forecasts of remainder by discpline:", yr)
+    title <- paste("Forecasts of remainder by discipline:", yr)
   }
 
   data |>

### 2025-09-09 R/sec5_figures.R

@@ -194,6 +194,7 @@ make_fig_grad_forecasts <- function(grads, future_grads, no_other = TRUE) {
     geom_line(aes(y = mean), color = "#c14b14") +
     geom_line(data = grads, aes(y = graduates)) +
     labs(
+      x = "Year",
       y = "Number of graduates",
       title = "Forecasts of total graduates by discipline",
     ) +

### 2025-09-09 _targets.R

@@ -283,10 +283,21 @@ list(
   tar_target(
     fig_Pxt_future_discipline,
     make_pop_future_fig_discipline(
+      2035,
+      future_pop_science,
+      census4_1,
+      ymax = ymax,
+      guides = FALSE
+    )
+  ),
+  tar_target(
+    fig_Pxt_future_discipline_talk,
+    make_pop_future_fig_discipline(
       2022:2035,
       future_pop_science,
       census4_1,
-      ymax = ymax
+      ymax = ymax,
+      list = TRUE
     )
   ),
   tar_target(fig24, make_fig24(census4_1, future_pop_science)),

### 2025-09-09 extra_code/stationary.R

@@ -1,0 +1,18 @@
+# Test stationary assumption for remainder principal components
+
+library(broom)
+library(vital)
+library(tidyr)
+
+tar_load(model_Ext_discipline)
+pv <- time_components(model_Ext_discipline) |>
+  pivot_longer(cols = starts_with("beta"), names_to = "component", values_to = "value") |>
+  features(value, unitroot_kpss) |>
+  arrange(kpss_pvalue)
+
+# Given we are doing 36 tests, we use the Bonferonni correction.
+# need the p-value to be greater than 0.05/36 = 0.0014
+# to not reject the null hypothesis of stationary.
+
+pv |>
+  filter(kpss_pvalue < 0.05/36)

### 2025-09-17 age_structure_forecasts.qmd
Finished first draft

@@
   Planning for a future workforce requires forecasts of age structure changes to inform policy decisions, particularly related to universities and immigration.
-We modify the traditional demographic growth-balance equation to account for workforce-specific dynamics, replacing births with graduate entry, modeling exits through death and retirement, and including a remainder term that captures migration and career changes.
+We modify the traditional demographic growth-balance equation to account for workforce-specific dynamics, replacing births with graduate entry, modelling exits through death and retirement, and including a remainder term that captures migration and career changes.
 Functional data models are used to model age-specific components, while ARIMA models are used for time series components.
@@
 
-The death probabilities shown in @fig-death-probs where first smoothed using the partially monotonic penalized spline approach of @HU07.
+The death probabilities shown in @fig-death-probs where first smoothed using the partially monotonic penalised spline approach of @HU07.
 Then the functional data model @eq-fdm was estimated, with ARIMA models fitted to the coefficients.
@@
 Mid-to-late career estimates primarily reflect the aging of existing cohorts.
-The prediction intervals becomes especially narrow during the retirement phase, where the workforce dynamics become more predictable.
+The prediction intervals become especially narrow during the retirement phase, where the workforce dynamics become more predictable.
 Since retirements increase after the late 50s, workforce participation beyond 60 serves as a benchmark for identifying trends in delayed retirement and extended career duration.
@@
 
-Also visible in @fig-forecast-working-population are cohort effects, where fluctuations in earlier ages and years propagate through to later ages and years.
+Cohort effects are also visible in @fig-forecast-working-population, where fluctuations in earlier ages and years propagate through to later ages and years.
 This is particularly evident in the mid-career years because there are few deaths and retirements, few graduates older than 30, and the variation due to the remainder term is relatively small after age 30.
@@
 While these forecasts provide a foundation for workforce planning, it is important to note that they are entirely driven by historical trends and do not account for possible new developments, such as the impact of AI and other emerging technologies on the labour market in different scientific disciplines.
-Other factors, such as policy changes or global economic shifts, may also influence workforce trends and should be taken into account.
+Other factors, such as policy changes or global economic shifts, may also influence workforce trends.
+These exogenous factors could be accounted for by adding covariates into the time series models used, provided relevant data are available.
 
-Things that could be improved:
+Evaluating and validating these forecasts is challenging due to the relatively long forecast horizon compared to the available historical data.
+While time series cross-validation [@fpp3] could be used to assess forecast accuracy for shorter horizons, the benefit of the forecasts is primarily for longer horizons, where such validation is not possible.
+The uncertainty in the forecasts, as reflected in the wide prediction intervals, highlights the need for caution when interpreting the results.
 
-- Include backtesting results by fitting the model to earlier periods and comparing forecasts to actual outcomes
-- Discuss forecast accuracy metrics and how they compare across disciplines
-- Address the challenge of validating long-term demographic forecasts with limited historical data
-- Examine how sensitive forecasts are to key assumptions (e.g., constant retirement rates across disciplines, independence of components)
-- Discuss the impact of the choice to use general population mortality rates rather than discipline-specific rates
-- Analyze how changes in the each component affect overall forecasts
-- Address potential interventions that could alter the forecasted trajectories (e.g., targeted recruitment, retention programs)
-- Discuss alternative methods.
+If more detailed data were available, the model could be refined further by including, for example, discipline-specific death rates, retirement data by year and/or discipline, graduate data by age and discipline, and data on migration and career changes.
+It is not clear how much these refinements would improve forecast accuracy, but they would likely reduce uncertainty in the forecasts.
 
-- Provide more detailed discussion of the sources of uncertainty in your forecasts
+Forecasts are often designed not just to predict the future, but also to inform policy decisions, and so modify the future.
+In this context, these forecasts could be used to identify potential skill shortages or surpluses in specific disciplines, guiding decisions on university and immigration policy, and thus changing the future outcomes [@causality2022].
+Consequently, forecast accuracy may be less important than understanding the range of possible outcomes and their implications for policy.
 
-- Discuss whether the methodology could be applied to other countries or workforce sectors
-- Address unique aspects of the Australian context that might limit generalizability
-
-- Expand beyond AI to discuss other technological disruptions (automation, quantum computing, biotechnology)
-- Consider demographic shifts (changing education patterns, delayed career entry, career mobility)
-- Discuss potential "black swan" events that could dramatically alter workforce dynamics
-
-- Discuss the implications of using census data with 5-year gaps
-- Address the challenge of tracking career changes and international mobility
-- Suggest improvements to data collection that would enhance future forecasting efforts
+While this analysis has focused on the scientific workforce in Australia, the methodology could be applied to other countries or workforce sectors, provided similar data are available.
+The specific components of the demographic growth-balance equation may need to be adapted to reflect the available data in other applications.
 
@@
 
-# Acknowledgements
+# Acknowledgements {-}
 

### 2025-09-20 age_structure_forecasts.qmd
Fixed Kelly's name

@@
   corresponding: true
-- name: Kelly Vanh Nguyen
+- name: Khuyen Vanh Nguyen
   affiliations:

### 2025-09-20 age_structure_forecasts.qmd
Typos

@@
 #| label: fig-retirements
-#| fig-cap: "$r_x$: Age distribution of retirement intentions, based on data from the 2022--2023 Australian financial year. The blue line shows the smoothed probabilities."
+#| fig-cap: "$r_x$: Age distribution of retirement intentions, based on data from the 2022--2023 Australian financial year.
+The grey line shows the age-group probabilities; the black line shows the smoothed probabilities."
 tar_read(fig_rx2)
@@
 
-The death probabilities shown in @fig-death-probs where first smoothed using the partially monotonic penalised spline approach of @HU07.
+The death probabilities shown in @fig-death-probs were first smoothed using the partially monotonic penalised spline approach of @HU07.
 Then the functional data model @eq-fdm was estimated, with ARIMA models fitted to the coefficients.

### 2025-09-22 age_structure_forecasts.qmd
Updated statement about AAS in abstract

@@
 The approach is illustrated using data on Australia's scientific workforce, allowing us to forecast the age distribution of various scientific disciplines for the next ten years.
-This analysis was central to an Australian Academy of Science initiative, supporting strategic workforce planning and policy development for Australia's scientific community.
+This analysis was central to an Australian Academy of Science initiative examining the capability of Australia's science system and identifying workforce gaps.
 keywords:

### 2025-09-23 age_structure_forecasts.qmd
Updated yaml for new templates

@@
 title: "Forecasting the age structure of the scientific workforce in Australia"
+shorttitle: "Forecasting the workforce age structure"
 author:
 - name: Rob J Hyndman
+  affiliation:
+    - ref: ebs
+  email: Rob.Hyndman@monash.edu
+  corresponding: true
+  orcid: 0000-0002-2140-5352
+- name: Khuyen Vanh&nbsp;Nguyen
+  affiliation:
+    - ref: ebs
 affiliations:
-    - name: Monash University
+    - id: ebs
+      name: Monash University
       department: Department of Econometrics & Business Statistics
       city: Clayton
-      country: Australia
-      postal-code: 3800
-  email: Rob.Hyndman@monash.edu
-  corresponding: true
-- name: Khuyen Vanh Nguyen
-  affiliations:
-    - name: Monash University
-      department: Department of Econometrics & Business Statistics
-      city: Clayton VIC
       country: Australia
@@
   - workforce planning
+acknowledgement: |
+  We thank Alexandra Lucchetti from the Australian Academy of Science for sourcing the data required for this project, and for helpful feedback on earlier versions of this report.
+Rob Hyndman is a member of the Australian Research Council Industrial Transformation Training Centre in Optimisation Technologies, Integrated Methodologies, and Applications (OPTIMA), Project ID IC200100009.
+He also receives funding from the Australian Research Council through Discovery Project DP250100702.
 bibliography: refs.bib
@@
 format:
-  wp-pdf:
+  wp-pdf+wp: default
+  quarto-anzjs-pdf:
     keep-tex: true
+execute:
+  echo: false
+  warning: false
+  message: false
 filters:
@@
 The analysis was conducted using R version 4.5.1 [@R], with the following R packages: vital [@Rvital], tsibble [@Rtsibble], fable [@Rfable], targets [@targets;@targetspaper], ggplot2 [@ggplot2;@ggplotbook], and other tidyverse [@tidyverse] packages.
-
-# Acknowledgements {-}
-
-We thank Alexandra Lucchetti from the Australian Academy of Science for sourcing the data required for this project, and for helpful feedback on earlier versions of this report.

### 2025-09-23 age_structure_forecasts.qmd
Updated preamble to work with both templates

@@
 linestretch: 1.5
+format:
+  wp-pdf+wp:
     include-in-header: preamble.tex
-format:
-  wp-pdf+wp: default
   quarto-anzjs-pdf:
     keep-tex: true
+    include-in-header:
+      - text: |
+        \usepackage[section]{placeins}
+        \usepackage{colortbl,todonotes}
 execute:

### 2025-09-23 age_structure_forecasts.qmd
Nearly ready to submit

--- 2025-09-23 age_structure_forecasts.qmd
@@
   orcid: 0000-0002-2140-5352
-- name: Khuyen Vanh&nbsp;Nguyen
+- name:
+    given: Khuyen
+    family: Vanh Nguyen
   affiliation:
@@
 acknowledgement: |
-  We thank Alexandra Lucchetti from the Australian Academy of Science for sourcing the data required for this project, and for helpful feedback on earlier versions of this report.
+  We thank Alexandra Lucchetti from the Australian Academy of Science for sourcing the data required for this project, and for helpful feedback on earlier versions of this paper.
 Rob Hyndman is a member of the Australian Research Council Industrial Transformation Training Centre in Optimisation Technologies, Integrated Methodologies, and Applications (OPTIMA), Project ID IC200100009.
@@
 linestretch: 1.5
+format:
+  wp-pdf+wp:
     include-in-header: preamble.tex
-format:
-  wp-pdf+wp: default
+    output-file: "asf_wp.pdf"
   quarto-anzjs-pdf:
     keep-tex: true
+    fig-height: 5
+    fig-width: 8
+    output-file: "asf_anzjs.pdf"
+    include-in-header:
+      - text: |
+          \usepackage[section]{placeins}
+          \usepackage{colortbl,todonotes}
+          \usepackage{orcidlink}
 execute:

### 2025-09-23 R/sec5_figures.R

@@ -160,7 +160,7 @@ make_fig24 <- function(
     labs(
       y = "Total number of working scientists (thousands)",
       title = "Forecast of total working population by discipline",
-      subtitle = "Natural and Physical Sciences\nForecasted years: 2022 - 2041"
+      #subtitle = "Natural and Physical Sciences\nForecasted years: 2022 - 2041"
     ) +
     scale_x_continuous(breaks = seq(2010, 2040, by = 10)) +
     scale_y_continuous(labels = scales::label_number(scale = 1e-3)) +

### 2025-09-23 age_structure_forecasts.qmd
Fixed Kelly's name

@@
 - name:
-    given: Khuyen
-    family: Vanh Nguyen
+    given: Khuyen Vanh
+    family: Nguyen
   affiliation:

### 2025-09-23 age_structure_forecasts.qmd
Now saving figure files

@@
     fig-width: 8
-    output-file: "asf_anzjs.pdf"
+    knitr:
+      opts_chunk:
+        fig.path: figures/
     include-in-header:

### 2025-10-30 R/census_figs.R
Working on ASC version

@@ -36,7 +36,7 @@ make_pop_fig <- function(
     aes(x = age, y = working, color = Year, group = Year) +
     geom_line(
       data = census |> filter(Year %in% censuses),
-      linewidth = 0.4 + 0.6 * highlight_census
+      linewidth = 0.4 + 0.2 * highlight_census
     ) +
     scale_x_continuous(breaks = seq(20, 100, by = 10)) +
     labs(
@@ -48,10 +48,13 @@ make_pop_fig <- function(
     p <- p +
       facet_wrap(~discipline, scales = "free_y") +
       theme(
-        legend.direction = "horizontal",
+        legend.direction = if_else(!interpolation, "vertical", "horizontal"),
         legend.position = "inside",
         legend.position.inside = c(2 / 3, 1 / 2),
-        legend.justification = c(-0.4, 3)
+        legend.justification = c(
+          0.6 * interpolation - 1.0,
+          1.6 * interpolation + 1.4
+        )
       )
   }
   if (interpolation) {

### 2025-10-30 R/retirements.R

@@ -74,7 +74,7 @@ make_fig_r <- function(retirements) {
   ggplot(retirements, aes(x = age_group, y = pc)) +
     geom_col() +
     labs(
-      title = "Retirement intentions of Australian scientists (2022 - 23)",
+      title = "Retirement intentions of Australian scientists (2022-23)",
       x = "Age group",
       y = "Percentage of retirement intentions"
     ) +
@@ -84,7 +84,7 @@ make_fig_r <- function(retirements) {
     )
 }
 
-make_fig_rx <- function(retirements, retirement_data) {
+make_fig_rx <- function(retirements, retirement_data, add_line = TRUE) {
   retirement_data <- retirement_data |>
     mutate(
       lower = as.numeric(substr(age_group, 1, 2)),
@@ -96,15 +96,19 @@ make_fig_rx <- function(retirements, retirement_data) {
     select(-pc) |>
     left_join(retirement_data, by = join_by(age == lower)) |>
     tidyr::fill(pc, nages, .direction = "down")
-  retirements |>
+  p <- retirements |>
     ggplot() +
     aes(x = age) +
     geom_step(aes(y = pc / 100 / nages), color = "gray") +
-    geom_line(aes(y = retire_prob), color = "black") +
     labs(
       x = "Age",
       y = latex2exp::TeX("Probability of retirement"), # ($r_{x,t}$)"),
       title = "Probability of retirement for Australian scientists"
     ) +
-    scale_x_continuous(breaks = seq(40, 100, by = 10))
+    scale_x_continuous(breaks = seq(40, 100, by = 10)) +
+    ylim(0, max(retirements$retire_prob))
+  if (add_line) {
+    p <- p + geom_line(aes(y = retire_prob), color = "black")
+  }
+  return(p)
 }

### 2025-10-30 R/sec5_figures.R

@@ -1,6 +1,6 @@
 make_fig19 <- function(disciplines_combined) {
   years <- seq(2006, 2021, by = 5)
-  cols <- c("#FF6F00", "#009E73", "#009DFF", "#FF00BF")
+  cols <- c("#ff0000", "#67ff00", "#00ceff", "#ca00ff")
   names(cols) <- years
 
   disciplines_combined |>
@@ -10,16 +10,15 @@ make_fig19 <- function(disciplines_combined) {
     ggplot() +
     aes(x = age, y = working, color = Year, group = Year) +
     geom_line() +
-    scale_color_manual(values = cols, name = "Census Year") +
+    scale_color_manual(values = cols) +
     labs(
       y = "Number of active scientists",
       title = "Working population by discipline",
-      subtitle = "Natural and Physical Sciences"
     ) +
     scale_x_continuous(breaks = seq(20, 100, by = 10)) +
     facet_wrap(~discipline, scales = "free_y") +
     theme(
-      legend.position = "top"
+      legend.position = "right"
     )
 }
 
@@ -167,32 +166,27 @@ make_fig24 <- function(
     facet_wrap(~discipline, scales = "free_y")
 }
 
-make_fig_grad_forecasts <- function(grads, future_grads, no_other = TRUE) {
+make_fig_grad_forecasts <- function(
+  grads,
+  future_grads,
+  no_other = TRUE,
+  PI = TRUE
+) {
+  future_grads <- future_grads |>
+    as_tibble() |>
+    filter(year <= 2035)
+  grads <- grads |>
+    as_tibble()
   if (no_other) {
     grads <- grads |>
       dplyr::filter(discipline != "Other Natural and Physical Sciences")
     future_grads <- future_grads |>
       dplyr::filter(discipline != "Other Natural and Physical Sciences")
   }
-  future_grads <- future_grads |>
-    filter(year <= 2035) |>
-    group_by(discipline) |>
-    summarise(
-      mean = mean(graduates),
-      lo = quantile(graduates, prob = 0.05),
-      hi = quantile(graduates, prob = 0.95)
-    )
-  grads <- grads |>
-    as_tibble() |>
-    group_by(discipline, year) |>
-    summarise(graduates = sum(graduates))
-  future_grads |>
-    as_tibble() |>
+  p <- grads |>
     ggplot() +
     aes(x = year, group = discipline) +
[…]

### 2025-10-30 _targets.R

@@ -75,6 +75,7 @@ list(
     single_age_retirements(retirement_data, aus_death_prob)
   ),
   tar_target(fig_r, make_fig_r(retirement_data)),
+  tar_target(fig_rx1, make_fig_rx(retirements, retirement_data, FALSE)),
   tar_target(fig_rx2, make_fig_rx(retirements, retirement_data)),
 
   # Graduates
@@ -142,8 +143,9 @@ list(
       census4_1,
       no_other = TRUE,
       color_data = TRUE,
-      ymax = ymax
-    )
+      ymax = ymax,
+      list = TRUE
+    )[[1]]
   ),
 
   tar_target(fig_error, make_component_fig(census2_1, remainder)),
@@ -262,7 +264,10 @@ list(
   tar_target(fig16, make_fig16(physics, future_physics)),
 
   # Disciplines combined
-  tar_target(fig19, make_fig19(census4_1)),
+  tar_target(
+    fig19,
+    make_pop_fig(census4_1, "Natural and Physical Sciences", FALSE, TRUE)
+  ),
   tar_target(
     fig20,
     make_pop_fig(census4_1, "Natural and Physical Sciences", TRUE, TRUE)
@@ -277,8 +282,9 @@ list(
       2050,
       future_pop_science,
       census4_1,
-      ymax = ymax
-    )
+      ymax = ymax,
+      list = TRUE
+    )[[1]]
   ),
   tar_target(
     fig_Pxt_future_discipline,
@@ -305,10 +311,24 @@ list(
     fig_grad_forecasts,
     make_fig_grad_forecasts(course_leavers, future_course_leavers_science)
   ),
+  tar_target(
+    fig_grad_sim,
+    make_fig_grad_forecasts(
+      course_leavers,
+      future_course_leavers_science,
+      PI = FALSE
+    )
+  ),
 
   # Graduate forecasts
   tar_target(sci_grads, total_sci_grads(course_leavers)),
   tar_target(arima, sci_grads |> model(ARIMA(graduates))),
+  tar_target(
+    check_arima,
+    if (fabletools::model_sum(arima[[1]][[1]]) != "ARIMA(0,1,1) w/ drift") {
+      stop("Wrong model")
+    }
+  ),
   tar_target(
     future_grads,
     generate(arima, h = h, times = nsim) |>
@@ -349,16 +369,17 @@ list(
 
   # Document
   tar_target(discipline_table, make_discipline_table()),
[…]

### 2025-11-23 response.qmd
Added response document

---
title: "Forecasting the age structure of the scientific workforce in Australia"
author: Response to reviewers
branding: false
linestretch: 1.2
bibliography: refs.bib
format: 
  memo-typst: default # Use memo-pdf to use latex
filters:
  - reviewer.lua
pandoc-options:
---

We thank the reviewers for their helpful comments. We have included all reviewer comments [in blue]{.reviewer} below, followed by our responses in black.

# Reviewer 1

::: {.reviewer}
This manuscript presents a statistically rigorous and highly valuable approach for forecasting the age structure of specialized workforces. The proposed methodology is robust, leveraging functional data models for age-specific rates and employing a global ARIMA model to enhance graduate forecast accuracy. A simulation-based approach captures comprehensive uncertainty. The manuscript is written well, organized clearly. This manuscript is suitable for the _Australian & New Zealand Journal of Statistics_ due to its innovative extension of established functional data models and its direct application to critical national policy issues.
:::

Thanks for your positive feedback.

### Major comments

::: {.reviewer}
1. Regarding the model assumptions, the main contribution of this study lies in a practical modification of the traditional population growth balance equation. As shown in equation (2), it is assumed that the mortality rate and retirement rate are uniform across all scientific disciplines (group $i$), and that the retirement rate is constant over time ($q_{i,x,t} = q_{x,t}$ and $r_{i,x,t} = r_x$). It is suggested that the potential implications of these assumptions be more explicitly discussed. For instance, are there no significant differences in the deaths or retirements in the group 'Chemical Sciences' compared to those in the group 'Mathematical Sciences'?
:::

We assume that mortality rates change with age and time, but not with discipline; and that retirement rates change with age, but not with time and discipline. There are two reasons for these assumptions. First, there is the purely pragmatic reason that the data we have available does not allow anything else. Mortality rates by scientific discipline are not available anywhere in the world, to our knowledge, so the best we can do with the available data is to use the same mortality rates for all disciplines, while allowing for change over time and age. Fortunately, there is no reason to think scientists of different disciplines would have different mortality experiences. A century ago, the dangers of radiation did increase mortality rates amongst chemists and physicists compared to other sciences, but modern science is conducted in extremely safe environments, so it seems reasonable to assume that all science disciplines share similar mortality profiles.

Retirement data is even more difficult to come by, and we have only been able to obtain retirement data by age for a single year in broad age groups. There has been a small increase in average retirement age over the last ten years due to an increase in the age at which the old age pension can be accessed, and a steady increase in the preservation age at which superannuation can be accessed. However, there is no existing policy proposal to change either of these in the future, so it is reasonable to take the retirement age distribution in recent years as valid for the foreseeable future. Further, we know of no evidence that the socio-economic status of scientists varies with discipline, so there is no reason to think retirement intentions would change with discipline either.

The referee asks specifically about the Chemical Sciences and Mathematical Sciences groups. It is not clear to us why these have been singled out, but we know of no evidence that retirement or mortality rates would differ between these groups.

It is also worth pointing out that the remainder term $E_{i,x,t}$ will absorb any inaccuracies that result from simplifying model assumptions in the other components, and we forecast the remainder allowing for changes over time, age and discipline. In fact, we could ignore all the model components and just forecast $P_{i,x,t}$ directly using a functional time series model, but that would fail to separate out the competing dynamics at play, and lead to much wider prediction intervals. By trying to model the individual components where we have available data, even if imperfectly, we capture more of the inherent uncertainty and obtain narrower prediction intervals.

We have added new material in Section 2 incorporating some of these comments.

::: {.reviewer}
1. The authors mentioned that the age distribution of graduates entering the labor market ($g_x$) was estimated in the paper by averaging and smoothing the data across all available years (2006 to 2023). Does the assumption in this paper that $g_x$ is fixed and time-invariant ($g_{x,t} = g_x$) potentially underestimate long-term dynamic changes? It is suggested that the impact of this assumption on the variability of young population forecasts be discussed either in the Methodology or Results section.
:::

We assume the age distribution of graduates is a product of age-dependent and time-dependent variables, $g_x$ and $G_{i,t}$. Primarily, this is a pragmatic choice because we do not have more detailed data available. We can get age distributions of graduates across all disciplines in Australia, but not for each discipline; and we can get the numbers of graduates by discipline and year in Australia, but with no age breakdown.  The most likely consequence of this simplifying assumption is that the variability in graduate numbers by age and time could be underestimated. It is conceivable that older graduates are drawn to different disciplines than younger graduates, or that fashionable disciplines change over time, resulting in different age distributions of the graduates over time. But without specific data related to this issue, we can only speculate. In any case, the comment above regarding the remainder term is also relevant here.

We have added a new paragraph in Section 2 along these lines.

::: {.reviewer}
3. The authors mentioned that the remainder includes large positive and negative fluctuations caused by international students returning to their home countries after graduation, as well as complex economic behaviors involving career changes and international migration. Strictly speaking, are these macroeconomic and social trends ($E_{i,x,t}$) thought to be long-term stationary? It is recommended that the discussion take into account that the stationarity assumption will fail if major policy or global economic structural changes take place, and this is a significant factor in forecasting uncertainty.
:::

We do not assume that the remainder term is stationary. We used stationary ARMA processes for the corresponding principal component scores because they all were found to be stationary using a KPSS test. But there is no reason why they could not be modelled using non-stationary processes if the data supported it. In particular, if major policy or global economic structural changes took place, this is likely to lead to non-stationarity in the remainder term, leading to greater forecast uncertainty.

We have clarified this point in Section 3.

# Reviewer 2

::: {.reviewer}
In this paper, the authors studied the forecasting of the workforce of different scientific disciplines. The forecasting approach was built upon early studies by the authors with a reminder term to account for migration and career changes. Although the empirical study in Sections 3 and 4 may be interesting to applied scientists, the statistical contributions of the paper are unclear. More detailed comments are given below.
:::

### Other comments:

::: {.reviewer}
1. On page 2, it seems restrictive to have only two reasons, retirement and death, for people
to leave the workforce.
:::

We do not have only these two reasons for people to leave the workforce. We also mention career changes, migration, and career disruption. These are handled implicitly in the remainder term, as we do not have data available for these processes. Deaths and retirement can be handled explicitly as we have suitable data available.

We have added clarifying statements in Section 2 to address this misunderstanding.

::: {.reviewer}
2. On page 4, assuming $q_{i,x,t} = q_{x,t}$ and $r_{i,x,t} = r_{x,t}$ needs justification rather than for modeling convenience.
:::

See the response to Reviewer 1, comment 1.

::: {.reviewer}
1. The main model setup is stated on pages 6 and 7. It is not clear which parts of the model
are new in the literature.
:::

To the best of our knowledge, there has been no previous attempt to forecast the age-structure of a workforce using a stochastic model. So the model is entirely new. We apologize if we gave a different impression in discussing the connection between our proposed model and the population forecasting model of Hyndman and Booth (IJF, 2008). Both involve age-structure forecasting, but with very different processes. We are proposing a new model for workforce age structure forecasting, that is somewhat inspired by the statistical model proposed by Hyndman and Booth (IJF, 2008) for population forecasting. The latter involves different inputs (births and immigration) and fewer outputs (deaths and emigration). Labour market forecasting is more complicated with no birth process, but several more inputs (graduates, immigration, career changes, career renewal) and several more outputs (deaths, retirements, emigration, career disruption and career changes).

We have now made this clearer in Section 2, and in the abstract.

::: {.reviewer}
4. In equation (3), why don’t the authors consider a multivariate time series model for $\beta_{k,t}$, $k = 1, \dots, K$?
:::

The $\beta_{k,t}$ values are principal component scores, so they are uncorrelated by construction. While it is possible for there to be some cross-correlations between the series at lags other than zero, these are usually not large enough for a multivariate model to give more accurate forecasts [see, @HU07] except in contrived simulated examples. On the other hand, @Aue2015 did use multivariate models to capture these cross-correlations, although they did not compare them on real data.

We have added a new paragraph along these lines in Section 2.

::: {.reviewer}
5. There is no mention of the statistical inference of the unknown parameters. For example,
how were the unknown parameters in the model on pages 6 and 7 estimated?
:::

Functional principal components [@HU07] was used to compute the principal component scores. 
All univariate ARIMA models were estimated using maximum likelihood estimation.  The global ARIMA model was estimated using least squares estimation (as a full likelihood is somewhat  difficult to compute across multiple series).

This has now been noted in Section 2.

::: {.reviewer}
6. There is no simulation experiment to investigate the performance of the inference proce-
dure.
:::

Statistical inference is not the point of this paper. We estimate model parameters in order to produce forecasts. The values of the parameters themselves are of little interest. In any case, the functional time series models used for each component have been well-studied previously [@HU07;@HS09;@Horvath2012;@Aue2015;@Haghbin2023].

::: {.reviewer}
7. In Section 4, the forecasting was done using simulation methods. There is no validation
of the forecasting accuracy. It is important to demonstrate how good the forecasts are
compared with existing models.
:::

Which existing models? There are no existing statistical models for forecasting labour market age-structure as far as we know, so we can't compare against them.

However, we have added a new appendix validating the coverage of the one-step prediction intervals for the last year of census data, using data up to the previous census. Given the use of interpolation between censuses, it would be invalid to test the accuracy of our forecasts between censuses, and there is insufficient data to properly evaluate forecasts earlier than the last census.

::: {.reviewer}
In short, the contributions of the current version of the paper do not seem to be adequate for
publication in the journal. Much more work is required to illustrate the value of the proposed
changes in the workforce modeling.
:::

It is not clear what is meant by "proposed changes in the workforce modeling". We are not proposing changes, we are proposing an entirely new model --- the first statistical model of any kind to allow age structure forecasting for a labour market. Hopefully the comments above, and the new material in the paper, will have made this clearer.

### 2025-11-23 _targets.R

@@ -369,12 +369,18 @@ list(
 
   # Document
   tar_target(discipline_table, make_discipline_table()),
-  # tar_quarto(
-  #   paper,
-  #   "age_structure_forecasts.qmd",
-  #   extra_files = c("refs.bib", "preamble.tex"),
-  #   quiet = FALSE
-  # ),
+  tar_quarto(
+    paper,
+    "age_structure_forecasts.qmd",
+    extra_files = c("refs.bib", "preamble.tex"),
+    quiet = FALSE
+  ),
+  tar_quarto(
+    response,
+    "response.qmd",
+    extra_files = "refs.bib",
+    quiet = FALSE
+  ),
   tar_quarto(
     talk,
     "age_structure_talk.qmd",

### 2025-11-23 age_structure_forecasts.qmd
Updated paper

@@
   Planning for a future workforce requires forecasts of age structure changes to inform policy decisions, particularly related to universities and immigration.
-We modify the traditional demographic growth-balance equation to account for workforce-specific dynamics, replacing births with graduate entry, modelling exits through death and retirement, and including a remainder term that captures migration and career changes.
+We propose a new dynamic statistical model for forecasting the age structure of a workforce.
+Our approach is inspired by a stochastic model used in population forecasting, replacing births with graduate entry, modelling exits through death and retirement, and including a remainder term that captures migration and career changes.
 Functional data models are used to model age-specific components, while ARIMA models are used for time series components.
@@
 
-We propose to adapt this framework to workforce dynamics by redefining the demographic components in two ways.
+We propose a related approach for modelling workforce dynamics by redefining the demographic components in two ways.
 First, we replace fertility with workforce entry, which functions more like a migration process than a birth process because graduates can enter the workforce at any age.
-Second, we allow workers to leave the workforce through two processes: retirement and death.
-Of course, people may also leave the workforce for other reasons, such as a career change or family commitments, but since we do not have data on these processes, we model them implicitly via a remainder term.
+Second, we *explicitly* model workers leaving the workforce through two processes: retirement and death.
+Of course, people may also leave the workforce for other reasons, such as a career change or family commitments, but since we do not have data on these processes, we model them *implicitly* via a remainder term.
 
@@
 
-People can leave the workforce of a group through death, retirement, emigration, or career change; they can enter the workforce through graduation, immigration, or career change.
-Unfortunately, we typically do not have data on many of these processes, so we will combine career change, emigration and immigration into a remainder term, which we denote as $E_{i,x,t}$.
+People can leave the workforce of a group through death, retirement, emigration, family responsibilities, or career change; they can enter the workforce through graduation, immigration, changes in family responsibilities, or career change.
+Unfortunately, we typically do not have data on many of these processes, so we will combine changes due to family responsibilities, career changes, emigration and immigration into a remainder term, which we denote as $E_{i,x,t}$.
 Let $D_{i,x,t}$ denote the number of deaths of workers in group $i$ of age $x$ in year $t$, $R_{i,x,t}$ denote the number of retirements from the same group of workers, and $G_{i,x,t}$ denote the number of new graduates of age $x$ in year $t$ who take up work in group $i$.
 The numbers in each case are for people aged $x$ at the *start* of year $t$.
-Then population changes can be described using a model similar to the stochastic population model of @HB08, excluding the birth process:
+Then population changes can be described using the following model:
 $$
@@
 That is, when the cohort aged $x$ in year $t$ has all retired or died, and $x$ is above the threshold, they will not be replaced by new workers of the same age.
+
+While our model was inspired by the stochastic population model of @HB08, that model has different inputs (births and immigration) and fewer outputs (deaths and emigration).
+Labour market forecasting is more complicated with no birth process, several more inputs (graduates, immigration, career changes, career renewal), and several more outputs (deaths, retirements, emigration, career disruption and career changes).
 
@@
 
+Because the $\beta_{k,t}$ values are principal component scores, they are uncorrelated by construction.
+While it is possible for there to be some cross-correlations between the series at lags other than zero, these are usually not large enough for a multivariate model to give more accurate forecasts [see, @HU07] except in contrived simulated examples.
+On the other hand, @Aue2015 did use multivariate models to capture these cross-correlations, although they did not compare them on real data.
+
 Functional data models have been widely used in demography and other fields, and have been shown to work particularly well for age-specific demographic processes [@HB08;@LCcomparison].
 They enable the inherent smoothness over age to be captured, while modelling the autocorrelation over time using relatively simple univariate time series models applied to the principal component scores.
-In our application, we use univariate ARIMA models for the $q_{x,t}$ scores, and ARMA models for the $E_{i,x,t}$ scores.
-The assumption of stationarity for the $E_{i,x,t}$ scores is validated for the disciplines we consider.
+In our application, we use univariate ARIMA models for the $q_{x,t}$ scores, and ARMA models for the $E_{i,x,t}$ scores, each estimated using maximum likelihood estimation.
+The assumption of stationarity for the $E_{i,x,t}$ scores is validated for the disciplines we consider, but is not a requirement in general.
 
 For the time-varying component, $G_{i,t}$, we use a global ARIMA model [@HM21] to capture the dynamics over time and across disciplines.
+This is estimated using least squares estimation.
 The global model pools information across disciplines to improve forecast accuracy, especially for disciplines with limited historical data.
@@
 None of this changes the overall modelling framework we are proposing.
+
+Fortunately, there is no reason to think scientists of different disciplines would have different mortality experiences.
+A century ago, the dangers of radiation did increase mortality rates amongst chemists and physicists compared to other sciences, but modern science is conducted in extremely safe environments, so it seems reasonable to assume that all science disciplines share similar mortality profiles.
+
+There has been a small increase in average retirement age over the last ten years due to an increase in the age at which the old age pension can be accessed [@pension], and a steady increase in the preservation age at which superannuation can be accessed [@kingston2019superannuation].
+However, there is no existing policy proposal to change either of these in the future, so it is reasonable to take the retirement age distribution in recent years as valid for the foreseeable future.
+Further, we know of no evidence that the socio-economic status of scientists varies with discipline, so there is no reason to think retirement intentions would change with discipline either.
+
+We assume the age distribution of graduates is a product of age-dependent and time-dependent variables, $g_x$ and $G_{i,t}$.
+Primarily, this is a pragmatic choice because we do not have more detailed data available.
+We can get age distributions of graduates across all disciplines in Australia, but not for each discipline; and we can get the numbers of graduates by discipline and year in Australia, but with no age breakdown.
+The most likely consequence of this simplifying assumption is that the variability in graduate numbers by age and time could be underestimated.
+It is conceivable that older graduates are drawn to different disciplines than younger graduates, or that fashionable disciplines change over time, resulting in different age distributions of the graduates over time.
+But without specific data related to this issue, we can only speculate.
+
+It is also worth pointing out that the remainder term $E_{i,x,t}$ will absorb any inaccuracies that result from simplifying model assumptions in the other components, and we forecast the remainder allowing for changes over time, age and discipline.
+In fact, we could ignore all the model components and just forecast $P_{i,x,t}$ directly using a functional time series model, but that would fail to separate out the competing dynamics at play, and lead to much wider prediction intervals.
+By trying to model the individual components where we have available data, even if imperfectly, we capture more of the inherent uncertainty and obtain narrower prediction intervals.
 
@@
 
-The remainder, $E_{i,x,t}$, is also modelled using a functional data model [@HU07], with stationary ARMA models fitted to the principal component scores.
-The scores were found to be stationary using the KPSS test [@KPSS].
+The remainder, $E_{i,x,t}$, is also modelled using a functional data model [@HU07], with ARIMA models fitted to the principal component scores.
+In this case, all scores were found to be stationary using the KPSS test [@KPSS], so ARMA models are used.
 The forecasts for one year are shown in @fig-net-migration-disciplines, with the mean forecast represented by the solid line and 90% prediction intervals indicated by the shaded area.

### 2025-11-23 response.qmd
Cleaned up bib

@@
 bibliography: refs.bib
+csl: apa-single-spaced.csl
 format: 
@@
 ::: {.reviewer}
-1. On page 2, it seems restrictive to have only two reasons, retirement and death, for people
-to leave the workforce.
+1. On page 2, it seems restrictive to have only two reasons, retirement and death, for people to leave the workforce.
 :::
@@
 ::: {.reviewer}
-1. The main model setup is stated on pages 6 and 7. It is not clear which parts of the model
-are new in the literature.
+1. The main model setup is stated on pages 6 and 7. It is not clear which parts of the model are new in the literature.
 :::
@@
 ::: {.reviewer}
-5. There is no mention of the statistical inference of the unknown parameters. For example,
-how were the unknown parameters in the model on pages 6 and 7 estimated?
+5. There is no mention of the statistical inference of the unknown parameters. For example, how were the unknown parameters in the model on pages 6 and 7 estimated?
 :::
 
-Functional principal components [@HU07] was used to compute the principal component scores. 
+Functional principal component analysis [@HU07] was used to compute the principal component scores.
 All univariate ARIMA models were estimated using maximum likelihood estimation.
@@
 ::: {.reviewer}
-6. There is no simulation experiment to investigate the performance of the inference proce-
-dure.
+6. There is no simulation experiment to investigate the performance of the inference procedure.
 :::
@@
 ::: {.reviewer}
-7. In Section 4, the forecasting was done using simulation methods. There is no validation
-of the forecasting accuracy. It is important to demonstrate how good the forecasts are
-compared with existing models.
+7.
+In Section 4, the forecasting was done using simulation methods.
+There is no validation of the forecasting accuracy.
+It is important to demonstrate how good the forecasts are compared with existing models.
 :::
@@
 ::: {.reviewer}
-In short, the contributions of the current version of the paper do not seem to be adequate for
-publication in the journal. Much more work is required to illustrate the value of the proposed
-changes in the workforce modeling.
+In short, the contributions of the current version of the paper do not seem to be adequate for publication in the journal.
+Much more work is required to illustrate the value of the proposed changes in the workforce modeling.
 :::

### 2025-11-23 age_structure_forecasts.qmd
Cleaned up bib

@@
 #| label: tbl-disciplines
+#| tbl-pos: "!hb"
 #| tbl-cap: Classification of scientific disciplines, based on the ASCED Narrow Fields of Education within the Broad Field of Natural and Physical Sciences.

### 2025-11-23 asf1.tex
Added diff

% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
doublespace,
  times]{anzsauth}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{5}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{setspace}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage[]{natbib}
\bibliographystyle{anzsj}

\usepackage[section]{placeins}
\usepackage{colortbl,todonotes}
\usepackage{orcidlink}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Forecasting the age structure of the scientific workforce in Australia},
  pdfauthor={Rob J Hyndman; Khuyen Vanh Nguyen},
  pdfkeywords={cohort analysis, demographic modelling, functional data
models, labour market, workforce planning},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\usepackage{moreverb}
\usepackage{url}
\usepackage{grffile}
\usepackage[UKenglish]{isodate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The year in the following may need to be updated!
\def\volumeyear{}

% The following command ("obviously") effects line numbering
% of the document.

\usepackage{lineno}
\linenumbers

\def\firstletters{\bgroup \catcode`-=10 \catcode`(=10 \filA}
\def\filA#1{\filB#1 {\end} }
\def\filB#1#2 {\ifx\end#1\egroup \else#1 \expandafter\filB\fi}

\runningheads{
Forecasting the workforce age structure
}{
\firstletters{ROB J}HYNDMAN, AND  \firstletters{KHUYEN VANH}NGUYEN 
}

\title{Forecasting the age structure of the scientific workforce in
Australia}

\author{
Rob J Hyndman\addressnum{1} and 
Khuyen Vanh Nguyen
\addressnum{1}
}
\affiliation{
Monash University
}

\address{
\addressnum{1} Department of Econometrics \& Business Statistics, Monash
University\\
\hspace*{1ex} Email: \texttt{Rob.Hyndman@monash.edu} 
}

\date{}
\begin{document}

\begin{abstract}
Planning for a future workforce requires forecasts of age structure
changes to inform policy decisions, particularly related to universities
and immigration. We modify the traditional demographic growth-balance
equation to account for workforce-specific dynamics, replacing births
with graduate entry, modelling exits through death and retirement, and
including a remainder term that captures migration and career changes.
Functional data models are used to model age-specific components, while
ARIMA models are used for time series components. Simulation is employed
to generate forecast distributions, capturing uncertainty from all
components. The approach is illustrated using data on Australia's
scientific workforce, allowing us to forecast the age distribution of
various scientific disciplines for the next ten years. This analysis was
central to an Australian Academy of Science initiative examining the
capability of Australia's science system and identifying workforce gaps.
\end{abstract}

\keywords{cohort analysis; demographic modelling; functional data
models; labour market; workforce planning}

\ack{We thank Alexandra Lucchetti from the Australian Academy of Science
for sourcing the data required for this project, and for helpful
feedback on earlier versions of this paper. Rob Hyndman is a member of
the Australian Research Council Industrial Transformation Training
Centre in Optimisation Technologies, Integrated Methodologies, and
Applications (OPTIMA), Project ID IC200100009. He also receives funding
from the Australian Research Council through Discovery Project
DP250100702.}

\maketitle

\setstretch{1.5}
\section{Introduction}\label{sec-intro}

In planning for the future labour market, it is necessary to forecast
the age structure of the workforce in order to enable informed
decision-making on policies, especially concerning universities and
immigration. We propose a statistical modelling approach to this
problem, illustrated using various scientific disciplines in Australia,
forecasting future workforce age structures over the next decade. The
forecasts described have been used by the Australian Academy of Science
as part of \emph{Australian Science, Australia's Future: Science 2035},
an initiative assessing the capability of the national science system
and its role in achieving Australia's ambitions \citep{AAS2035}.

The economic implications of workforce age structure shifts are
well-documented \citep[e.g.,][]{Bloom2007}, affecting productivity,
pensions and superannuation, and skill shortages
\citep{PC2013, OECD2019a, OECD2019b, pension}. The social implications
are also significant, with an aging workforce leading to changes in
workplace dynamics, potential problems with intergenerational knowledge
transfer, and the need for policies that support older workers. Yet this
problem does not appear to have been previously addressed from a
statistical modelling perspective.

Our approach builds on functional data models, introduced to demographic
modelling by \citet{HU07}. They combined nonparametric smoothing and
functional principal components for age-specific demographic rates.
These models were then used by \citet{HB08} for mortality, fertility,
and migration rates, providing stochastic data generating processes for
the components of demographic balance equations. These separate
component models were then simulated to form future sample paths,
leading to age- and sex-specific stochastic population forecasts. The
modelling framework was later extended by \citet{HBY13} to ensure
coherence of forecasts between sexes or other demographic groups.

We propose to adapt this framework to workforce dynamics by redefining
the demographic components in two ways. First, we replace fertility with
workforce entry, which functions more like a migration process than a
birth process because graduates can enter the workforce at any age.
Second, we allow workers to leave the workforce through two processes:
retirement and death. Of course, people may also leave the workforce for
other reasons, such as a career change or family commitments, but since
we do not have data on these processes, we model them implicitly via a
remainder term.

We describe the methodology in Section~\ref{sec-methodology}. By way of
illustration, we apply the methodology to major scientific disciplines
in Australia, focusing on the Natural and Physical Sciences. We describe
the data sources in Section~\ref{sec-data}, with the results provided in
Section~\ref{sec-results}. The aim of this analysis is to inform future
workforce planning and policy decisions to support the growth of
Australia's scientific community. Finally, we provide some discussion
and conclusions in Section~\ref{sec-conclusion}.

\section{Methodology}\label{sec-methodology}

Suppose our workforce is divided into \(I\) groups, indexed by
\(i=1,\dots,I\). In our application, these are scientific disciplines,
but in principle they could refer to any subdivision of workers. Let
\(P_{i,x,t}\) denote the number of equivalent full-time workers in group
\(i\) who are aged \(x\) at the start of year \(t\), where
\(x=15,16,\dots\). The starting age of 15 is chosen because it is the
minimum age at which individuals are counted as part of the labour force
in the Australian Census \citep{ABSLFSP}. We assume that data are
available for years \(t=1,\dots,T\), and that forecasts are required for
\(P_{i,x,T+h}\) across all ages and groups, for some forecast horizon
\(h>0\).

People can leave the workforce of a group through death, retirement,
emigration, or career change; they can enter the workforce through
graduation, immigration, or career change. Unfortunately, we typically
do not have data on many of these processes, so we will combine career
change, emigration and immigration into a remainder term, which we
denote as \(E_{i,x,t}\). Let \(D_{i,x,t}\) denote the number of deaths
of workers in group \(i\) of age \(x\) in year \(t\), \(R_{i,x,t}\)
denote the number of retirements from the same group of workers, and
\(G_{i,x,t}\) denote the number of new graduates of age \(x\) in year
\(t\) who take up work in group \(i\). The numbers in each case are for
people aged \(x\) at the \emph{start} of year \(t\). Then population
changes can be described using a model similar to the stochastic
population model of \citet{HB08}, excluding the birth process:
\begin{equation}\phantomsection\label{eq-dgb}{
P_{i,x+1,t+1} = P_{i,x,t} - D_{i,x,t} - R_{i,x,t} + G_{i,x,t} + E_{i,x,t},
}\end{equation} where

\begin{itemize}
\tightlist
\item
  \(D_{i,x,t} \sim \text{Binomial}(P_{i,x,t}, q_{i,x,t})\), with
  \(q_{i,x,t}\) being the probability of death for group \(i\) at age
  \(x\) in year \(t\); and
\item
  \(R_{i,x,t} \sim \text{Binomial}((P_{i,x,t}-D_{i,x,t}), r_{i,x,t})\),
  with \(r_{i,x,t}\) being the probability of retirement from group
  \(i\) at age \(x\) in year \(t\).
\end{itemize}

That is, the population each year is equal to the population from the
previous year having aged 1 year, minus the deaths or retirements that
occurred during the previous year, plus the new graduates, plus any
other changes due to migration or career change (which may be negative).
We assume that \(E_{i,x,t} = G_{i,x,t} = 0\) above some age threshold
(say \(x=100\)). Once \(P_{i,x,t} = 0\) when \(x\) is above that
threshold, all future populations \(P_{i,x+k,t+k} = 0\), for
\(k=1,2,\dots\). That is, when the cohort aged \(x\) in year \(t\) has
all retired or died, and \(x\) is above the threshold, they will not be
replaced by new workers of the same age.

As a first approximation, the components \(q\), \(r\), \(E\) and \(G\)
can be assumed to behave independently for each combination of \(i\),
\(x\) and \(t\). In reality, there may be some negative correlation
between \(G\) and \(E\) as insufficient graduates would probably lead to
employers finding people from overseas, while too many graduates would
lead to scientists seeking work elsewhere.

The choice of a Binomial rather than a Poisson distribution (in contrast
to \citet{Brillinger1986}) for deaths and retirements is because the
Binomial distribution ensures that the number of deaths and retirements
cannot exceed the population at risk. In a simulation context, with very
small populations, this is important to avoid nonsensical results.

It is unlikely that we have available separate death and retirement
counts for each group, and retirement data is not available in all
years. So we will let \(q_{i,x,t} = q_{x,t}\) and \(r_{i,x,t} = r_{x}\),
assuming that death rates and retirement rates are the same across all
groups, and that retirement rates do not change over time. Similarly,
graduation numbers are rarely available by discipline and age, so we
will approximate \(G_{i,x,t} = g_xG_{i,t}\) where \(G_{i,t}\) is the
total number of graduates in year \(t\) and \(g_x\) is the proportion of
graduates by age across all disciplines.

This leads to the simpler model
\begin{equation}\phantomsection\label{eq-dgb2}{
P_{i,x+1,t+1} = P_{i,x,t} - D_{i,x,t} - R_{i,x,t} + g_xG_{i,t} + E_{i,x,t},
}\end{equation} where

\begin{itemize}
\tightlist
\item
  \(D_{i,x,t} \sim \text{Binomial}(P_{i,x,t}, q_{x,t})\); and
\item
  \(R_{i,x,t} \sim \text{Binomial}((P_{i,x,t}-D_{i,x,t}), r_{x})\).
\end{itemize}

For the age-specific time-varying components \(q_{x,t}\) and
\(E_{i,x,t}\), we will use functional data models \citep{HU07}. For
\(q_{x,t}\), this is of the form
\begin{equation}\phantomsection\label{eq-fdm}{
\log(q_{x,t}) = \mu(x) + \sum_{k=1}^K \beta_{k,t} \phi_k(x) + \varepsilon_{x,t},
}\end{equation} where \(\mu(x)\) is the mean function, \(\phi_k(x)\) are
functional principal components, \(\beta_{k,t}\) are the principal
component scores, and \(\varepsilon_{x,t}\) is an error term. Each
\(\beta_{k,t}\) is then modelled using a univariate time series model,
such as an ARIMA model. A log-link function is used to ensure that the
probabilities remain positive. An inverse logit link function could also
be used, if the probabilities are close to 1 for some ages. A similar
model is used for \(E_{i,x,t}\), with separate mean functions and
principal components for each group \(i\). The number of components
\(K=6\), for the reasons outlined in \citet{HB08}.

Functional data models have been widely used in demography and other
fields, and have been shown to work particularly well for age-specific
demographic processes \citep{HB08, LCcomparison}. They enable the
inherent smoothness over age to be captured, while modelling the
autocorrelation over time using relatively simple univariate time series
models applied to the principal component scores. In our application, we
use univariate ARIMA models for the \(q_{x,t}\) scores, and ARMA models
for the \(E_{i,x,t}\) scores. The assumption of stationarity for the
\(E_{i,x,t}\) scores is validated for the disciplines we consider.

For the time-varying component, \(G_{i,t}\), we use a global ARIMA model
\citep{HM21} to capture the dynamics over time and across disciplines.
The global model pools information across disciplines to improve
forecast accuracy, especially for disciplines with limited historical
data.

To forecast future working population numbers, \(P_{i,x,t}\), \(t>T\),
we simulate future sample paths of each of the components \(G_{i,t}\),
\(q_{x,t}\), and \(E_{i,x,t}\), simulate \(D_{i,x,t}\) and \(R_{i,x,t}\)
from their respective Binomial distributions, and then use the
demographic growth-balance equation Equation~\ref{eq-dgb2} iteratively
to obtain \(P_{i,x,t}\) for \(t=T+1,T+2,\dots\). This simulation-based
approach allows us to capture the uncertainty in each of the components,
leading to a distribution of possible future outcomes for \(P_{i,x,t}\).

This model is somewhat pragmatic given the data available in our
specific application. If better data were available, other variations on
Equation~\ref{eq-dgb} could be used. For example, if death rates were
available by discipline, then we would replace \(q_{x,t}\) by
\(q_{i,x,t}\) in the Binomial deaths distribution. If retirement rates
were available by year, or by discipline, we could similarly replace
\(r_x\) by a more specific retirement rate in the Binomial retirements
distribution. If we had data on graduations by age and discipline, we
could replace \(g_xG_{i,t}\) by \(G_{i,x,t}\). If we had data on
migration, we could split the remainder \(E_{i,x,t}\) into several
components, and model them separately. None of this changes the overall
modelling framework we are proposing.

\section{Data}\label{sec-data}

To illustrate the methodology, we consider the Natural and Physical
Sciences as defined in the Australian Standard Classification of
Education (ASCED) by the \citet{ABSASCED}. We refer to ASCED's Narrow
Fields as ``disciplines''; these comprise Physics and Astronomy,
Mathematical Sciences, Chemical Sciences, Earth Sciences, Biological
Sciences, Other Natural and Physical Sciences, and Natural and Physical
Sciences not further defined (n.f.d.). Table~\ref{tbl-disciplines} lists
the detailed fields within each scientific discipline.

\begin{table}

\caption{\label{tbl-disciplines}Classification of scientific
disciplines, based on the ASCED Narrow Fields of Education within the
Broad Field of Natural and Physical Sciences. The table lists their
corresponding Detailed Fields. ``n.e.c.'' stands for ``Not Elsewhere
Classified.''}

\centering{

\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{9cm}}
\toprule
\textbf{Narrow Fields} & \textbf{Detailed Fields}\\
\midrule
Physics and Astronomy & Physics, Astronomy.\\
Mathematical Sciences & Mathematics, Statistics, Mathematical Sciences, n.e.c.\\
Chemical Sciences & Organic Chemistry, Inorganic Chemistry, Chemical Sciences, n.e.c.\\
Earth Sciences & Atmospheric Sciences, Geology, Geophysics, Geochemistry, Soil Science, Hydrology, Oceanography, Earth Sciences, n.e.c.\\
Biological Sciences & Biochemistry and Cell Biology, Botany, Ecology and Evolution, Marine Science, Genetics, Microbiology, Human Biology, Zoology, Biological Sciences, n.e.c.\\
Other Natural and Physical Sciences & Medical Science, Forensic Science, Food Science and Biotechnology, Pharmacology, Laboratory Technology, Natural and Physical Sciences, n.e.c.\\
\bottomrule
\end{tabular}}

}

\end{table}%

We define the population of workers in a discipline as those who are
active in the labour market and hold a bachelor's degree or higher in
that discipline. For the purposes of this analysis, we will omit ``Other
Natural and Physical Sciences'' and ``Natural and Physical Sciences
n.f.d.''.

\subsection{Working population}\label{working-population}

Data on the working population were sourced from the \emph{Census of
Population and Housing} \citep{ABSCensus} for census years 2006, 2011,
2016, and 2021. This dataset encompasses one-year age groups, the
highest level of completed non-school qualification level (QALLP), the
corresponding field of study \citep[QALFP,][]{ABSQALFP}, and the
industries in which individuals work. However, labour force
participation status \citep{ABSLFFP} is available only for 2016 and
2021. To estimate worker numbers for 2006 and 2011, the average
participation rates from 2016 and 2021 were applied, assuming overall
age distributions remain consistent.

The resulting estimates of the number of scientists who are active in
the Australian labour market is shown in
Figure~\ref{fig-cohort-interpolation} as the thick lines. Cohort
interpolation \citep{STUPP88}, applying linear interpolation within each
age cohort between census years, is used to estimate values for the
intercensal years (shown as thin lines), giving \(P_{i,x,t}\) for each
discipline \(i\), age \(x\), and year \(t\).

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-cohort-interpolation-1.pdf}}

}

\caption{\label{fig-cohort-interpolation}\(P_{i,x,t}\): Estimated number
of working scientists in Australia by discipline and age, 2006--2021.
Thicker lines are used to denote census years.}

\end{figure}%

\subsection{Retirements}\label{retirements}

Retirement data was sourced from the \emph{Retirement and Retirement
Intentions} dataset (Catalogue 6238) for the 2022--2023 financial year
\citep{ABS6238}. The data are categorised by the industry of an
individual's main job, and are provided in four broad age groups
(45--59, 60--64, 65--69 and 70+). There are 19 industry categories, with
the largest numbers of scientists working in Education and Training
(15.8\%), Professional, Scientific and Technical Services (15.5\%), and
Health Care and Social Assistance (14.6\%). The proportions in other
industries are much smaller. We take a weighted average of retirement
intentions using these top three industries, with proportions rescaled
to sum to 1. The resulting values are shown in
Figure~\ref{fig-retirements} as the gray line. To obtain a
single-year-of-age retirement distribution, we disaggregate the data
using a monotonic cubic spline applied to the cumulative values of these
age groups \citep{SHW04}. The resulting smoothed distribution (\(r_x\))
is shown as the black line in Figure~\ref{fig-retirements}.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-retirements-1.pdf}}

}

\caption{\label{fig-retirements}\(r_x\): Age distribution of retirement
intentions, based on data from the 2022--2023 Australian financial year.
The grey line shows the age-group probabilities; the black line shows
the smoothed probabilities.}

\end{figure}%

\subsection{Deaths}\label{deaths}

Age-specific mortality rates from 1971 to 2021 were obtained from the
\citet{HMD}. Using standard life table methods, these rates are
converted into age-specific probabilities of death, as shown in
Figure~\ref{fig-death-probs}. Over time, mortality probabilities have
generally declined across all age groups, reflecting improvements in
Australian life expectancy.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-death-probs-1.pdf}}

}

\caption{\label{fig-death-probs}\(q_{x,t}\): Age-specific probabilities
of death (on a logarithmic scale) for each year from 1971 to 2021.}

\end{figure}%

No data are available for specific industry groups, so we assume that
all scientists have the same mortality probabilities as the general
population. These probabilities serve as estimates of \(q_{x,t}\).

\subsection{Graduate completions}\label{graduate-completions}

Graduate completion statistics were obtained from the \emph{Award Course
Completions} dataset \citep{DeptEdu}. Figure~\ref{fig-completions} shows
the distribution of graduate completions with a bachelor's degree or
higher, by age for each year from 2006 to 2023. Some missing values
result in gaps in certain lines, but the overall pattern remains highly
consistent across years. Given this consistency, the data is averaged
across all available years, and then smoothed by applying monotonic
cubic splines to the cumulative values \citep{SHW04}. The resulting
averaged distribution, shown as the black line in
Figure~\ref{fig-completions}, smooths out year-to-year fluctuations and
provides an estimate of \(g_x\).

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-completions-1.pdf}}

}

\caption{\label{fig-completions}\(g_x\): Estimated distribution of
graduate completions by age (black). This is estimated by averaging and
smoothing the data for the years 2006 to 2023 (coloured).}

\end{figure}%

The Department of Education provides data on the number of graduates
with a bachelor's degree or higher, categorised by discipline and year
\citep{DeptEdu_Private}. This dataset includes both domestic and
international students. The total number of graduates, \(G_{i,t}\), in
each discipline \(i\) and year \(t\), are shown in
Figure~\ref{fig-graduates}.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-graduates-1.pdf}}

}

\caption{\label{fig-graduates}\(G_{i,t}\): Total number of graduates
with a bachelor's degree or higher by discipline from 2006 to 2023.}

\end{figure}%

The large increase in the working population observed in the 2021 Census
for Mathematical Sciences (Figure~\ref{fig-cohort-interpolation}) can be
partly attributed to the sharp rise in graduate numbers between 2016 and
2021. This is probably due to the impact of data science, and the
growing importance of statistics and machine learning in many areas of
employment.

\subsection{Remainder}\label{remainder}

The demographic growth-balance equation (Equation~\ref{eq-dgb2}), when
rearranged, provides an expression for the remainder including net
migration and career changes:
\begin{equation}\phantomsection\label{eq-remainder}{
E_{i,x,t} = P_{i,x+1,t+1} - P_{i,x,t} - D_{i,x,t} - R_{i,x,t} - g_xG_{i,t},
}\end{equation} However, we do not have data on \(D_{i,x,t}\) and
\(R_{i,x,t}\), so we replace these by their expected values,
\(P_{i,x,t} q_{x,t}\) and \(P_{i,x,t}(1-q_{x,t}) r_x\), respectively. We
can only estimate remainders up to 2020 because we need data for both
year \(t\) and year \(t+1\) in Equation~\ref{eq-remainder}, and our
working population data only extends to 2021. The estimated remainders
are shown in Figure~\ref{fig-remainder}.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-remainder-1.pdf}}

}

\caption{\label{fig-remainder}Estimated remainder \(E_{i,x,t}\) by
discipline, age and year (2006--2020).}

\end{figure}%

The inclusion of international students in the graduate data leads to
large positive values of the remainder for the teenage years, followed
by large negative values when these students return to their home
countries after graduation.

\section{Results}\label{sec-results}

\subsection{Graduate completions}\label{graduate-completions-1}

To forecast future graduate numbers, \(G_{i,t}\), a global ARIMA model
was employed, following the principles outlined by \citet{HM21}. The
global model captures overall trends across disciplines by scaling
graduate data within each discipline, ensuring proportional
contributions from all disciplines before fitting the global ARIMA
model. This improves the numerical stability of the model by
incorporating information across disciplines. The forecast distributions
are shown in Figure~\ref{fig-grad-forecasts}, with the mean forecast
represented by the solid line and 90\% prediction intervals indicated by
the shaded area.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-grad-forecasts-1.pdf}}

}

\caption{\label{fig-grad-forecasts}Forecast of \(G_{i,t}\): the number
of graduates by discipline, 2024--2035, based on historical data from
2006--2023. The shaded regions represent the 90\% prediction intervals,
and the solid lines indicate the mean estimates.}

\end{figure}%

\subsection{Death probabilities}\label{death-probabilities}

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-death-probs-forecasts-1.pdf}}

}

\caption{\label{fig-death-probs-forecasts}Forecasts of \(q_{x,t}\):
age-specific probabilities of death (on a logarithmic scale) for 2035,
based on historical data from 1971--2021. The shaded regions represent
the 90\% prediction intervals, and the solid lines indicate the mean
estimate.}

\end{figure}%

The death probabilities shown in Figure~\ref{fig-death-probs} were first
smoothed using the partially monotonic penalised spline approach of
\citet{HU07}. Then the functional data model Equation~\ref{eq-fdm} was
estimated, with ARIMA models fitted to the coefficients. The forecasts
for one year are shown in Figure~\ref{fig-death-probs-forecasts}, with
the mean forecast represented by the solid line and 90\% prediction
intervals indicated by the shaded area. Note that the historical data
(shown in gray) represent unsmoothed values, while the forecasts are
based on the smoothed functional data model. The additional variation
seen in the historical data is captured in the model through the
Binomial death process.

\subsection{Remainder}\label{remainder-1}

The remainder, \(E_{i,x,t}\), is also modelled using a functional data
model \citep{HU07}, with stationary ARMA models fitted to the principal
component scores. The scores were found to be stationary using the KPSS
test \citep{KPSS}. The forecasts for one year are shown in
Figure~\ref{fig-net-migration-disciplines}, with the mean forecast
represented by the solid line and 90\% prediction intervals indicated by
the shaded area.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-net-migration-disciplines-1.pdf}}

}

\caption{\label{fig-net-migration-disciplines}Forecasts of
\(E_{i,x,t}\): the remainder by discipline for 2035, based on historical
data from 2006--2020. The shaded regions represent the 90\% prediction
intervals, and the solid lines indicate the mean estimates.}

\end{figure}%

\subsection{Simulating future
populations}\label{simulating-future-populations}

We use the demographic growth-balance model Equation~\ref{eq-dgb2} to
iteratively simulate future populations, using the models described
above for the components. The following steps outline the process.

A total of 1000 simulations are run to obtain a distribution of future
age-specific population scenarios. The average of the 1000 simulations
provides the mean age-specific forecast, while quantiles estimate
forecast uncertainty. Figure~\ref{fig-forecast-working-population}
presents the mean and 90\% prediction intervals for 2035.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-forecast-working-population-1.pdf}}

}

\caption{\label{fig-forecast-working-population}Forecasts of
\(P_{i,x,t}\): the working population by discipline for 2035. The shaded
regions represent the 90\% prediction intervals, and the solid lines
indicate the mean estimates.}

\end{figure}%

In 2035, forecast variability is highest in the age period 20--35 years,
before gradually narrowing as the workforce ages. This is due to the
relatively high uncertainty in the new graduates component compared to
the other components. Mid-to-late career estimates primarily reflect the
aging of existing cohorts. The prediction intervals become especially
narrow during the retirement phase, where the workforce dynamics become
more predictable. Since retirements increase after the late 50s,
workforce participation beyond 60 serves as a benchmark for identifying
trends in delayed retirement and extended career duration. Over the next
ten years, we expect an aging workforce in all but the Mathematical
Sciences, where a large increase in the population is forecast.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-forecast-total-working-scientists-1.pdf}}

}

\caption{\label{fig-forecast-total-working-scientists}Forecasted total
number of working scientists across scientific disciplines from 2022 to
2041. The shaded region represents the 90\% prediction interval, the
coloured line indicates the mean estimate, and the black line represents
historical data.}

\end{figure}%

Cohort effects are also visible in
Figure~\ref{fig-forecast-working-population}, where fluctuations in
earlier ages and years propagate through to later ages and years. This
is particularly evident in the mid-career years because there are few
deaths and retirements, few graduates older than 30, and the variation
due to the remainder term is relatively small after age 30.

Summing over ages allows for estimating the forecast distribution of the
total number of working scientists in each future year, as shown in
Figure~\ref{fig-forecast-total-working-scientists}. The forecasts
indicate continued growth, but at a gradually slower pace for all
disciplines other than the Mathematical Sciences. Where the lower bound
is nearly flat, workforce stagnation is possible in a conservative
scenario. Even in the optimistic scenario (corresponding to the upper
bound), growth only slightly exceeds the current pace, except for the
Mathematical Sciences. As noted earlier, the divergent behaviour of the
Mathematical Sciences is likely driven by the growing importance of data
science and related fields.

The wide prediction intervals reflect the uncertainty in the forecasts,
and show that caution is needed when interpreting the results. The only
discipline where there is clear evidence of growth or decline is the
Mathematical Sciences. For all other disciplines, the prediction
intervals include the current level, indicating that stagnation,
increase, or decline is possible.

\section{Discussion}\label{sec-conclusion}

While these forecasts provide a foundation for workforce planning, it is
important to note that they are entirely driven by historical trends and
do not account for possible new developments, such as the impact of AI
and other emerging technologies on the labour market in different
scientific disciplines. Other factors, such as policy changes or global
economic shifts, may also influence workforce trends. These exogenous
factors could be accounted for by adding covariates into the time series
models used, provided relevant data are available.

Evaluating and validating these forecasts is challenging due to the
relatively long forecast horizon compared to the available historical
data. While time series cross-validation \citep{fpp3} could be used to
assess forecast accuracy for shorter horizons, the benefit of the
forecasts is primarily for longer horizons, where such validation is not
possible. The uncertainty in the forecasts, as reflected in the wide
prediction intervals, highlights the need for caution when interpreting
the results.

If more detailed data were available, the model could be refined further
by including, for example, discipline-specific death rates, retirement
data by year and/or discipline, graduate data by age and discipline, and
data on migration and career changes. It is not clear how much these
refinements would improve forecast accuracy, but they would likely
reduce uncertainty in the forecasts.

Forecasts are often designed not just to predict the future, but also to
inform policy decisions, and so modify the future. In this context,
these forecasts could be used to identify potential skill shortages or
surpluses in specific disciplines, guiding decisions on university and
immigration policy, and thus changing the future outcomes
\citep{causality2022}. Consequently, forecast accuracy may be less
important than understanding the range of possible outcomes and their
implications for policy.

While this analysis has focused on the scientific workforce in
Australia, the methodology could be applied to other countries or
workforce sectors, provided similar data are available. The specific
components of the demographic growth-balance equation may need to be
adapted to reflect the available data in other applications.

\section{Software and
reproducibility}\label{software-and-reproducibility}

All results presented here can be reproduced using the code available at
\url{https://github.com/robjhyndman/age_structure_forecasts}. The
analysis was conducted using R version 4.5.1 \citep{R}, with the
following R packages: vital \citep{Rvital}, tsibble \citep{Rtsibble},
fable \citep{Rfable}, targets \citep{targets, targetspaper}, ggplot2
\citep{ggplot2, ggplotbook}, and other tidyverse \citep{tidyverse}
packages.

\bibliography{refs.bib}

\end{document}

### 2025-11-23 asf2.tex
Added diff

--- 2025-11-23 asf1.tex
@@
 changes to inform policy decisions, particularly related to universities
-and immigration. We modify the traditional demographic growth-balance
-equation to account for workforce-specific dynamics, replacing births
+and immigration. We propose a new dynamic statistical model for
+forecasting the age structure of a workforce. Our approach is inspired
+by a stochastic model used in population forecasting, replacing births
 with graduate entry, modelling exits through death and retirement, and
@@
 \maketitle
+
+\urlstyle{tt}
 
@@
 
-We propose to adapt this framework to workforce dynamics by redefining
-the demographic components in two ways. First, we replace fertility with
-workforce entry, which functions more like a migration process than a
-birth process because graduates can enter the workforce at any age.
-Second, we allow workers to leave the workforce through two processes:
-retirement and death. Of course, people may also leave the workforce for
-other reasons, such as a career change or family commitments, but since
-we do not have data on these processes, we model them implicitly via a
-remainder term.
+We propose a related approach for modelling workforce dynamics by
+redefining the demographic components in two ways. First, we replace
+fertility with workforce entry, which functions more like a migration
+process than a birth process because graduates can enter the workforce
+at any age. Second, we \emph{explicitly} model workers leaving the
+workforce through two processes: retirement and death. Of course, people
+may also leave the workforce for other reasons, such as a career change
+or family commitments, but since we do not have data on these processes,
+we model them \emph{implicitly} via a remainder term.
 
@@
 People can leave the workforce of a group through death, retirement,
-emigration, or career change; they can enter the workforce through
-graduation, immigration, or career change. Unfortunately, we typically
-do not have data on many of these processes, so we will combine career
-change, emigration and immigration into a remainder term, which we
-denote as \(E_{i,x,t}\). Let \(D_{i,x,t}\) denote the number of deaths
-of workers in group \(i\) of age \(x\) in year \(t\), \(R_{i,x,t}\)
-denote the number of retirements from the same group of workers, and
-\(G_{i,x,t}\) denote the number of new graduates of age \(x\) in year
-\(t\) who take up work in group \(i\). The numbers in each case are for
-people aged \(x\) at the \emph{start} of year \(t\). Then population
-changes can be described using a model similar to the stochastic
-population model of \citet{HB08}, excluding the birth process:
-\begin{equation}\phantomsection\label{eq-dgb}{
+emigration, family responsibilities, or career change; they can enter
+the workforce through graduation, immigration, changes in family
+responsibilities, or career change. Unfortunately, we typically do not
+have data on many of these processes, so we will combine changes due to
+family responsibilities, career changes, emigration and immigration into
+a remainder term, which we denote as \(E_{i,x,t}\). Let \(D_{i,x,t}\)
+denote the number of deaths of workers in group \(i\) of age \(x\) in
+year \(t\), \(R_{i,x,t}\) denote the number of retirements from the same
+group of workers, and \(G_{i,x,t}\) denote the number of new graduates
+of age \(x\) in year \(t\) who take up work in group \(i\). The numbers
+in each case are for people aged \(x\) at the \emph{start} of year
+\(t\). Then population changes can be described using the following
+model: \begin{equation}\phantomsection\label{eq-dgb}{
 P_{i,x+1,t+1} = P_{i,x,t} - D_{i,x,t} - R_{i,x,t} + G_{i,x,t} + E_{i,x,t},
@@
 replaced by new workers of the same age.
+
+While our model was inspired by the stochastic population model of
+\citet{HB08}, that model has different inputs (births and immigration)
+and fewer outputs (deaths and emigration). Labour market forecasting is
+more complicated with no birth process, several more inputs (graduates,
+immigration, career changes, career renewal), and several more outputs
+(deaths, retirements, emigration, career disruption and career changes).
 
@@
 
+Because the \(\beta_{k,t}\) values are principal component scores, they
+are uncorrelated by construction. While it is possible for there to be
+some cross-correlations between the series at lags other than zero,
+these are usually not large enough for a multivariate model to give more
+accurate forecasts \citep[see,][]{HU07} except in contrived simulated
+examples. On the other hand, \citet{Aue2015} did use multivariate models
+to capture these cross-correlations, although they did not compare them
+on real data.
+
 Functional data models have been widely used in demography and other
@@
 use univariate ARIMA models for the \(q_{x,t}\) scores, and ARMA models
-for the \(E_{i,x,t}\) scores. The assumption of stationarity for the
-\(E_{i,x,t}\) scores is validated for the disciplines we consider.
+for the \(E_{i,x,t}\) scores, each estimated using maximum likelihood
+estimation. The assumption of stationarity for the \(E_{i,x,t}\) scores
+is validated for the disciplines we consider, but is not a requirement
+in general.
 
@@
 \citep{HM21} to capture the dynamics over time and across disciplines.
-The global model pools information across disciplines to improve
-forecast accuracy, especially for disciplines with limited historical
-data.
+This is estimated using least squares estimation. The global model pools
+information across disciplines to improve forecast accuracy, especially
+for disciplines with limited historical data.
 
@@
 
+Fortunately, there is no reason to think scientists of different
+disciplines would have different mortality experiences. A century ago,
+the dangers of radiation did increase mortality rates amongst chemists
+and physicists compared to other sciences, but modern science is
+conducted in extremely safe environments, so it seems reasonable to
+assume that all science disciplines share similar mortality profiles.
+
+There has been a small increase in average retirement age over the last
+ten years due to an increase in the age at which the old age pension can
+be accessed \citep{pension}, and a steady increase in the preservation
+age at which superannuation can be accessed
+\citep{kingston2019superannuation}. However, there is no existing policy
+proposal to change either of these in the future, so it is reasonable to
+take the retirement age distribution in recent years as valid for the
+foreseeable future. Further, we know of no evidence that the
+socio-economic status of scientists varies with discipline, so there is
+no reason to think retirement intentions would change with discipline
+either.
+
+We assume the age distribution of graduates is a product of
+age-dependent and time-dependent variables, \(g_x\) and \(G_{i,t}\).
+Primarily, this is a pragmatic choice because we do not have more
+detailed data available. We can get age distributions of graduates
+across all disciplines in Australia, but not for each discipline; and we
+can get the numbers of graduates by discipline and year in Australia,
+but with no age breakdown. The most likely consequence of this
+simplifying assumption is that the variability in graduate numbers by
+age and time could be underestimated. It is conceivable that older
+graduates are drawn to different disciplines than younger graduates, or
+that fashionable disciplines change over time, resulting in different
+age distributions of the graduates over time. But without specific data
+related to this issue, we can only speculate.
+
+It is also worth pointing out that the remainder term \(E_{i,x,t}\) will
+absorb any inaccuracies that result from simplifying model assumptions
+in the other components, and we forecast the remainder allowing for
+changes over time, age and discipline. In fact, we could ignore all the
+model components and just forecast \(P_{i,x,t}\) directly using a
+functional time series model, but that would fail to separate out the
+competing dynamics at play, and lead to much wider prediction intervals.
+By trying to model the individual components where we have available
+data, even if imperfectly, we capture more of the inherent uncertainty
+and obtain narrower prediction intervals.
+
 \section{Data}\label{sec-data}
@@
 
-\begin{table}
+\begin{table}[!hb]
 
@@
 The remainder, \(E_{i,x,t}\), is also modelled using a functional data
-model \citep{HU07}, with stationary ARMA models fitted to the principal
-component scores. The scores were found to be stationary using the KPSS
-test \citep{KPSS}. The forecasts for one year are shown in
-Figure~\ref{fig-net-migration-disciplines}, with the mean forecast
-represented by the solid line and 90\% prediction intervals indicated by
-the shaded area.
+model \citep{HU07}, with ARIMA models fitted to the principal component
+scores. In this case, all scores were found to be stationary using the
+KPSS test \citep{KPSS}, so ARMA models are used. The forecasts for one
+year are shown in Figure~\ref{fig-net-migration-disciplines}, with the
+mean forecast represented by the solid line and 90\% prediction
+intervals indicated by the shaded area.
 

### 2025-12-01 response.qmd
Explained extra_code in response doc

@@
 We do not assume that the remainder term is stationary.
-We used stationary ARMA processes for the corresponding principal component scores because they all were found to be stationary using a KPSS test.
-But there is no reason why they could not be modelled using non-stationary processes if the data supported it.
+We used stationary ARMA processes for the corresponding principal component scores because they all were found to be stationary using KPSS tests, with a Bonferonni adjustment due to the use of multiple tests.
+The code for these tests can be found in the file `extra_code/stationary.R` in the GitHub repository.
+But there is no reason why the principal component scores could not be modelled using non-stationary processes if the data supported it.
 In particular, if major policy or global economic structural changes took place, this is likely to lead to non-stationarity in the remainder term, leading to greater forecast uncertainty.

### 2025-12-02 R/graduates.R
Finished ASC slides

@@ -116,7 +116,7 @@ make_completions_step <- function(completions) {
     make_single_age(pc, smooth = FALSE)
 }
 
-make_completions_ave <- function(completions, calc_sd = TRUE) {
+make_completions_ave <- function(completions, calc_sd = FALSE) {
   if (calc_sd) {
     FUN <- sd
   } else {
@@ -140,11 +140,13 @@ make_completions_ave <- function(completions, calc_sd = TRUE) {
 make_fig_completions <- function(
   completions,
   ave_completions = NULL,
+  sd_completions = NULL,
   by_year = TRUE,
-  average = FALSE
+  average = FALSE,
+  pi = FALSE
 ) {
-  if (average & is.null(ave_completions)) {
-    stop("Please provide ave_completions if average = TRUE")
+  if (average & (is.null(ave_completions) | is.null(sd_completions))) {
+    stop("Please provide ave_completions and sd_completions if average = TRUE")
   }
   if (average & !by_year) {
     title <- "Average graduate completions"
@@ -160,7 +162,7 @@ make_fig_completions <- function(
       y = "Percentage of graduates",
       title = title
     )
-  if (by_year) {
+  if (by_year & !pi) {
     p <- p +
       geom_step(
         aes(colour = year, group = year),
@@ -169,8 +171,24 @@ make_fig_completions <- function(
       scale_color_gradientn(colours = rainbow(10), name = "Year")
   }
   if (average) {
-    p <- p +
-      geom_line(data = ave_completions)
+    if (pi) {
+      df <- ave_completions |>
+        rename(mean = pc) |>
+        left_join(sd_completions, by = "age") |>
+        rename(sd = pc) |>
+        mutate(
+          lower = pmax(0, mean - 2 * sd),
+          upper = mean + 2 * sd
+        )
+      p <- p +
+        geom_ribbon(
+          data = df,
+          aes(x = age, y = mean, ymin = lower, ymax = upper),
+          fill = "gray",
+          alpha = 0.9
+        )
+    }
+    p <- p + geom_line(data = ave_completions)
   }
   p +
     scale_x_continuous(breaks = seq(20, 100, by = 10)) +

### 2025-12-02 _targets.R

@@ -107,8 +107,20 @@ list(
     make_fig_completions(
       completions_step,
       ave_completions,
+      sd_completions,
       average = TRUE,
       by_year = TRUE
+    )
+  ),
+tar_target(
+    fig_ave_completions2,
+    make_fig_completions(
+      completions_step,
+      ave_completions,
+      sd_completions,
+      average = TRUE,
+      by_year = TRUE,
+      pi = TRUE
     )
   ),
   tar_target(tab2, make_table2(ave_completions)),
